### 2023-07-18 animbook-journal.Rmd
Creating journal template

---
title: "animbook: An R Package for Visualize ..."
date: Sys.Date()
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Faculty of Business and Economics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

### 2023-07-20 animbook-journal.Rmd
Introduction ideas

@@
 ```
+
+# Introduction
+
+- The animated plot has not been used often in the business data presentation
+- We want to see the movement of our variable of interest
+- Business data: Accounting data (sales), Marketing data (customer interest)
+- Help with storytelling
+- Inspiration: The New York Times (Extensive data shows punishing reach of racism for black boys).
+The animation plot shows what demographic group between white and black boys where would end up in society.
+It could be adapted to show, based on the demographic of the company, sees the movement of where they would end up.
+In the marketing data, the demographic of the customers could tell us the story of what product they preferred.

### 2023-07-27 animbook-journal.Rmd
Change the statement on the type of variable the function returned. Write introduction and data source description

@@
 - We want to see the movement of our variable of interest
-- Business data: Accounting data (sales), Marketing data (customer interest)
+- Business data: Accounting data (sales), Marketing data (customer interest), data analysis languages data
 - Help with storytelling
@@
 In the marketing data, the demographic of the customers could tell us the story of what product they preferred.
+
+# Data and Process
+
+Some ideas:
+
+- The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(uniqu identifier), rank(y-axis, factor variable), group(optional).
+
+- The user can input any numerical, categorical and factor variable into the prep_anim function which will return the data in the format that the anim_plot function accepted.
+The x-axis and time index does not need to be the same as this allows for the user to reproduce the nytimes plot which is not time dependent.
+For the rank variable, no matter what the type of variable is in, it will return numerical variable.
+
+-------------------------------------------------------------------------------
+
+When working with the raw data, the data pre-processing is one of the important steps we need to take before further analysis is taken.
+The function in this package will offer some flexibility in the types of the variable it accepted.
+However, there are still some restrictions the user needs to follow.
+In this section, it will provide what are the accepted format and examples for the user the followed to reproduce the final animate plot.
+
+The data set that will be used in this section and in all of the examples of this journal is collected from Bureau van Dijk.
+The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world.
+From the raw data, we are only interested in the ranking of the companies.
+The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.

### 2023-08-01 animbook-journal.Rmd
adding list of what to write

@@
 
+Some ideas:
+
 - The animated plot has not been used often in the business data presentation
@@
 
+-------------------------------------------------------------------------------
+
 # Data and Process
@@
 
-- The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(uniqu identifier), rank(y-axis, factor variable), group(optional).
+- The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(unique identifier), rank(y-axis, factor variable), group(optional).
 
@@
 The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
+
+- The data structure
+- The steps for the user
+- How does the function processes the data

### 2023-09-04 animbook-journal.Rmd
add a couple of paragraphs for the introduction

@@
 
+With the increasing computational powers, the animation with the big data are now become more accessible than ever.
+With the inspiration from a New York Times article, "Extensive Data Shows Punishing Reach of Racism for Black Boys".
+The animation portrays the trajectory of how boys with different demographic could land up in the society.
+Having this plot in mind, the paper proposed a new visualization in help capturing the movement of the observation for each different group over the time period.
+
+  This paper will focus on the designing and validating the new visualization using a nested model (@nested_model).
+With the goal of offering an animation tool for conveying the trend of the observation in the given period.
+The cognitive theory of multimedia learning (@mayer_2005) need to be considered during the designing period.
+This theory employs the theory which helps structure the strategies that will help the learner learn more effectively.
+
+  The challenges of the New York Times article animation was the size of code needed to recreate it, additionally, the business data may or may not have the same information as the one in that article.
+This establish a need in creating the tools for generalizing the animation to the wider range of data while keeping the main objective.
+
 -------------------------------------------------------------------------------

### 2023-09-04 animbook-journal.Rmd
introduction

--- 2023-08-01 animbook-journal.Rmd
@@
 title: "animbook: An R Package for Visualize ..."
-date: Sys.Date()
+date: 04/09/2023
 abstract: >
@@
 
+With the increasing computational powers, animation with large amounts of data is now become more accessible than ever.
+With the inspiration from a New York Times article, "Extensive Data Shows Punishing Reach of Racism for Black Boys".
+The animation portrays the trajectory of how boys with different demographics could land up in society.
+With this plot in mind, the paper proposed a new visualization to help capture the movement of the observation for each different group over the specific period.
+
+  This paper will focus on designing and validating the new visualization using a nested model (@nested_model) to offer an animation tool for conveying the observation trend in the given period.
+The cognitive theory of multimedia learning (@mayer_2005) will be considered during the designing period.
+This theory employs the structure and the strategies that will help the learner learn more effectively.
+
+  The challenge of the New York Times article animation was the amount of code needed to reproduce.
+Additionally, the business data may or may not have the same information as the one in that article.
+It establishes a need to create tools for generalizing the animation to a wider range of data while still maintaining the main objective.
+
+  The structure of this paper will consist of four main section.
+The first section is domain problem and data characterization, identifying the problems the visualization tools try to solve.
+Secondly, the operation and data type abstraction, the description of operations, and the types of data required for the next stage.
+The third section is visualization and interaction design, designing the visuals and refining the tools.
+In the last section, package design, develop the structure of the packages and how to implement the final visualize design into the R package.
+The checking of the threat and validating of that threat will be carried out throughout the entire process of designing the animbook package.
+
+# Domain problem and data characterization
+
+# Operation and data type abstraction
+
+When working with the raw data, the data pre-processing is one of the important steps we need to take before further analysis is taken.
+The function in this package will offer some flexibility in the types of the variable it accepted.
+However, there are still some restrictions the user needs to follow.
+In this section, it will provide what are the accepted format and examples for the user the followed to reproduce the final animate plot.
+
+The data set that will be used in this section and in all of the examples of this journal is collected from Bureau van Dijk.
+The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world.
+From the raw data, we are only interested in the ranking of the companies.
+The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
+
+# Visualization and interaction design
+
+# Package design
+
+Introduction
+
 Some ideas:
@@
 
--------------------------------------------------------------------------------
-
-# Data and Process
+Data and Process
 
@@
 For the rank variable, no matter what the type of variable is in, it will return numerical variable.
-
--------------------------------------------------------------------------------
 

### 2023-09-04 animbook-journal.tex
introduction

--- 2023-09-04 animbook-journal.Rmd
@@
----
-title: "animbook: An R Package for Visualize ..."
-date: 04/09/2023
-abstract: >
+% !TeX root = RJwrapper.tex
+\title{animbook: An R Package for Visualize \ldots{}}
+\author{by Krisanat Anukarnsakulchularp}
+
+\maketitle
+
+\abstract{%
 An abstract of less than 150 words.
-draft: true
-author:  
-  - name: Krisanat Anukarnsakulchularp
-    affiliation: Monash University
-    address:
-    - Faculty of Business and Economics
-    - Melbourne, Australia
-    orcid: 0009-0008-5638-7124
-    email:  kanu0003@student.monash.edu
-type: package
-output: 
-  rjtools::rjournal_web_article:
-    self_contained: yes
-    toc: no
-bibliography: RJreferences.bib
+}
 
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
-```
-
-# Introduction
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
 With the increasing computational powers, animation with large amounts of data is now become more accessible than ever.
-With the inspiration from a New York Times article, "Extensive Data Shows Punishing Reach of Racism for Black Boys".
+With the inspiration from a New York Times article, ``Extensive Data Shows Punishing Reach of Racism for Black Boys''.
 The animation portrays the trajectory of how boys with different demographics could land up in society.
@@
 
-  This paper will focus on designing and validating the new visualization using a nested model (@nested_model) to offer an animation tool for conveying the observation trend in the given period.
-The cognitive theory of multimedia learning (@mayer_2005) will be considered during the designing period.
+This paper will focus on designing and validating the new visualization using a nested model (Munzner (2009)) to offer an animation tool for conveying the observation trend in the given period.
+The cognitive theory of multimedia learning (Mayer (2005)) will be considered during the designing period.
 This theory employs the structure and the strategies that will help the learner learn more effectively.
@@
 
-# Domain problem and data characterization
+\hypertarget{domain-problem-and-data-characterization}{%
+\section{Domain problem and data characterization}\label{domain-problem-and-data-characterization}}
 
-# Operation and data type abstraction
+\hypertarget{operation-and-data-type-abstraction}{%
+\section{Operation and data type abstraction}\label{operation-and-data-type-abstraction}}
 
@@
 
-# Visualization and interaction design
+\hypertarget{visualization-and-interaction-design}{%
+\section{Visualization and interaction design}\label{visualization-and-interaction-design}}
 
-# Package design
+\hypertarget{package-design}{%
+\section{Package design}\label{package-design}}
 
@@
 
-- The animated plot has not been used often in the business data presentation
-- We want to see the movement of our variable of interest
-- Business data: Accounting data (sales), Marketing data (customer interest), data analysis languages data
-- Help with storytelling
-- Inspiration: The New York Times (Extensive data shows punishing reach of racism for black boys).
+\begin{itemize}
+\tightlist
+\item
+  The animated plot has not been used often in the business data presentation
+\item
+  We want to see the movement of our variable of interest
+\item
+  Business data: Accounting data (sales), Marketing data (customer interest), data analysis languages data
+\item
+  Help with storytelling
+\item
+  Inspiration: The New York Times (Extensive data shows punishing reach of racism for black boys).
 The animation plot shows what demographic group between white and black boys where would end up in society.
@@
 In the marketing data, the demographic of the customers could tell us the story of what product they preferred.
+\end{itemize}
 
@@
 
-- The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(unique identifier), rank(y-axis, factor variable), group(optional).
-
-- The user can input any numerical, categorical and factor variable into the prep_anim function which will return the data in the format that the anim_plot function accepted.
+\begin{itemize}
+\item
+  The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(unique identifier), rank(y-axis, factor variable), group(optional).
+\item
+  The user can input any numerical, categorical and factor variable into the prep\_anim function which will return the data in the format that the anim\_plot function accepted.
 The x-axis and time index does not need to be the same as this allows for the user to reproduce the nytimes plot which is not time dependent.
 For the rank variable, no matter what the type of variable is in, it will return numerical variable.
+\end{itemize}
 
@@
 
-- The data structure
-- The steps for the user
-- How does the function processes the data
+\begin{itemize}
+\tightlist
+\item
+  The data structure
+\item
+  The steps for the user
+\item
+  How does the function processes the data
+\end{itemize}
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-mayer_2005}{}}%
+Mayer, Richard E.
+2005.
+{``Cognitive Theory of Multimedia Learning.''} In \emph{The Cambridge Handbook of Multimedia Learning}, edited by RichardEditor Mayer, 31--48.
+Cambridge Handbooks in Psychology.
+Cambridge University Press.
+\url{https://doi.org/10.1017/CBO9780511816819.004}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-nested_model}{}}%
+Munzner, Tamara.
+2009.
+{``A Nested Model for Visualization Design and Validation.''} \emph{IEEE Transactions on Visualization and Computer Graphics} 15 (6): 921--28.
+\url{https://doi.org/10.1109/TVCG.2009.111}.
+
+\end{CSLReferences}
+
+\bibliography{RJreferences.bib}
+
+\address{%
+Krisanat Anukarnsakulchularp\\
+Monash University\\%
+Faculty of Business and Economics\\ Melbourne, Australia\\
+%
+%
+\textit{ORCiD: \href{https://orcid.org/0009-0008-5638-7124}{0009-0008-5638-7124}}\\%
+\href{mailto:kanu0003@student.monash.edu}{\nolinkurl{kanu0003@student.monash.edu}}%
+}

### 2023-09-04 animbook-journal.R

@@ -1,0 +1,6 @@
+# Generated by `rjournal_pdf_article()` using `knitr::purl()`: do not edit by hand
+# Please edit animbook-journal.Rmd to modify this file
+
+## ----setup, include=FALSE-----------------------------------------------------
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+

### 2023-09-05 animbook-journal.tex
add new section

@@
 The third section is visualization and interaction design, designing the visuals and refining the tools.
-In the last section, package design, develop the structure of the packages and how to implement the final visualize design into the R package.
+In the forth section, package design, develop the structure of the packages and how to implement the final visualize design into the R package.
+Lastly, the package usage.
 The checking of the threat and validating of that threat will be carried out throughout the entire process of designing the animbook package.
 
-\hypertarget{domain-problem-and-data-characterization}{%
-\section{Domain problem and data characterization}\label{domain-problem-and-data-characterization}}
+\hypertarget{problem-and-data-characterization}{%
+\section{Problem and data characterization}\label{problem-and-data-characterization}}
 
@@
 \section{Package design}\label{package-design}}
+
+\hypertarget{package-usage}{%
+\section{Package Usage}\label{package-usage}}
 

### 2023-09-11 animbook-journal.Rmd
add new section
add content to the first section

@@
     toc: no
-bibliography: RJreferences.bib
+bibliography: animbook-journal.bib
 
@@
 The third section is visualization and interaction design, designing the visuals and refining the tools.
-In the last section, package design, develop the structure of the packages and how to implement the final visualize design into the R package.
+In the forth section, package design, develop the structure of the packages and how to implement the final visualize design into the R package.
+Lastly, the package usage.
 The checking of the threat and validating of that threat will be carried out throughout the entire process of designing the animbook package.
 
-# Domain problem and data characterization
+# Problem and data characterization
+
+To look for the flow between group, one of the most common tools we look at is sankey chart.
+It represent the movement of the values from one set to another.
+However, with the static sankey, the only information presented are what is the proportion of the movement, and which states the quantities move to, this often enough in explaining the flow and helps making the decision necessary.
+To present more information, color could be used to represent the demographic of the group.
+What if the information that are interesting lies in the times domain, how could the plot captured that information?
+
+!!general sankey plot and sankey with color
+
+The technique that is created by Hans, Ola, and Anna Rosling in 2003 is called Gapminder Trendalyzer.
+Its add an additional dimensions which are the bubble size, animated over changes in a fourth dimension, time.
+The animation in this tools has created a new way for people to analyse and visualize the trend.
+
+!!read effectiveness of animation in trend visualization, then add more information to above paragraph
+
+The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world.
+This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.
 
@@
 # Package design
+
+# Package Usage
 

### 2023-09-11 animbook-journal.tex
add content to the first section

@@
 \section{Problem and data characterization}\label{problem-and-data-characterization}}
+
+To look for the flow between group, one of the most common tools we look at is sankey chart.
+It represent the movement of the values from one set to another.
+However, with the static sankey, the only information presented are what is the proportion of the movement, and which states the quantities move to, this often enough in explaining the flow and helps making the decision necessary.
+To present more information, color could be used to represent the demographic of the group.
+What if the information that are interesting lies in the times domain, how could the plot captured that information?
+
+!!general sankey plot and sankey with color
+
+The technique that is created by Hans, Ola, and Anna Rosling in 2003 is called Gapminder Trendalyzer.
+Its add an additional dimensions which are the bubble size, animated over changes in a fourth dimension, time.
+The animation in this tools has created a new way for people to analyse and visualize the trend.
+
+!!read effectiveness of animation in trend visualization, then add more information to above paragraph
+
+The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world.
+This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.
 
@@
 
-\bibliography{RJreferences.bib}
+\bibliography{animbook-journal.bib}
 

### 2023-10-02 animbook-journal.Rmd
updates journal

@@
 The animation portrays the trajectory of how boys with different demographics could land up in society.
-With this plot in mind, the paper proposed a new visualization to help capture the movement of the observation for each different group over the specific period.
+With this plot in mind, the paper proposed a new communication tool to help capture the movement of the observation for each different group over the specific period.
 
@@
 
+In designing the package for reproduces the NYtimes animated plot, the package end up with a three steps process in recreates the animation.
+The first step which is prepared the data into the right format for the plot function.
+The next stages is to create a ggplot object which then can be inputted into animation function.
+The last step is to added the animation settings to the ggplot object so that the gganimate::animate() function.
+The reason for this three steps process is that it allows the user who does not have a lot of experience to reproduces the animation.
+
+  As per motivations, the main focus for this package was to look at movement between the percentile group.
+Thus the anim_prep() function first purposes was to be able to take any numerical values and output the percentile group of the observations.
+The algorithms behind the group splitting are quantile and cut function.
+The quantile function from the stats R packages takes in the numeric vector and output the corresponding quantiles to the given probabilities.
+The output from the quantile function can then be used as the breaks argument for the cut function that is from the base R packages.
+The concerns of this method is that the users might not always interests in ranking the observations.
+
+  The next logical design is to allows for different scaling.
+As mentioned in the paragraph above the first scaling is "rank".
+The function then expanded the function to allows for the "absolute" scaling.
+This scaling is to assign the quantile groups based on the absolute values scales.
+The default for the function is to breaks the group equally using seq function.
+The input to the seq function are taken by the min and max of the values and increment by the equal steps depend on number of group of interests.
+
+  The algorithms mentions so far only breaks the quantile equally, but that is not always the cases as the users may interested in the group that are not equally breaks.
+
 # Package Usage
+
+## Data preprocesing step
+
+This first step can be done using the anim_prep() function.
+This function required that the users data contained id which is used to uniquely identified each individual observations, values which is numerical values to be used to group the observation together, and time, the variable that distinguish the values between the time and id.
+The users will need to understands what data structure can be input into the function.
+This package included the osiris data as an examples to the users.
+
+# ```{r}
+# animbook <- anim_prep(osiris, ID, sales, year)
+# ```
+
+There are an additional options that allow for more customizations to the data structure or the plot.
+
+- label: group labeling.
+- ngroup: number of groups we want to split the values into.
+- breaks: the group bins size (prototype)
+- group_scaling: the grouping variable for the bins calculations.
+- color: the variable used to color the observations.
+- time_dependent: logical. Whether we want the observations to start at the same time or not.
+- scaling: the scaling method, either `rank` or `absolute`.
+- runif_min: minimum value for random addition to frame numbers
+- runif_max: maximum value for random addition to frame numbers
+
+The function can calculate four different scales using these options.
+
+# ```{r}
+# # rank scaling
+# rank_scaling <- anim_prep(data = osiris, id = ID, values = sales, time = year)
+# 
+# # absolute scaling
+# absolute_scaling <- anim_prep(data = osiris, id = ID, values = sales, time = year,
+#                               scaling = "absolute")
+# 
+# # rank scaling by group
+# rank_group_scaling <- anim_prep(data = osiris, id = ID, values = sales, time = year, 
+#                                 group = country)
+# 
+# # absolute scaling by group
+# absolute_group_scaling <- anim_prep(data = osiris, id = ID, values = sales, time = year,
+#                                     group = country, scaling = "absolute")
+# 
+# rank_scaling
+# ```
+
+This function will return `animbook` object containing a list of the formatted data and settings.
+
+## Plotting the data
+
+After preparing the data, we can not plot it. There are three plots available in this package:
+
+- `kangaroo`, which plots the observation's movement over time.
+- `wallaby`, which subset the plot to either `top` or `bottom` and see which group they are in after the observational period.
+- `funnel_web_spider`, which is a faceted plot by time variable.
+
+# ```{r}
+# label <- c("Top 20%", "20-40", "40-60", "60-80", "80-100", "not listed")
+# 
+# animbook <- anim_prep(data = osiris, id = ID, values = sales, time = year, color = japan, label = label)
+# 
+# # kangaroo plot
+# kangaroo_plot(animbook)
+# 
+# # wallaby plot
+# wallaby_plot(animbook)
+#             
+# # funnel web spider plot
+# funnel_web_plot(animbook)
+# ```
+
+The `kangaroo` and `wallaby` plots can be animated using the function of the next stage.
+`funnel_web_spider` only supported static plot.
+We can also choose whether we want to animate the plot using gganimate or plotly.
+
+## Animating the plot
+
+To animate the plot, we need to save the plot into an object, which then can be passed on to the function.
+
+# ```{r}
+# animbook <- anim_prep_cat(data = aeles, id = id, values = party, time = year, color = gender, time_dependent = FALSE)
+# 
+# p <- wallaby_plot(animbook)
+# 
+# p2 <- anim_animate(p)
+# 
+# gganimate::animate(p2)
+# ```
 

### 2023-10-02 animbook-journal.tex
updates journal

@@
 
+In designing the package for reproduces the NYtimes animated plot, the package end up with a three steps process in recreates the animation.
+The first step which is prepared the data into the right format for the plot function.
+The next stages is to create a ggplot object which then can be inputted into animation function.
+The last step is to added the animation settings to the ggplot object so that the gganimate::animate() function.
+The reason for this three steps process is that it allows the user who does not have a lot of experience to reproduces the animation.
+
+As per motivations, the main focus for this package was to look at movement between the percentile group.
+Thus the anim\_prep() function first purposes was to be able to take any numerical values and output the percentile group of the observations.
+The algorithms behind the group splitting are quantile and cut function.
+The quantile function from the stats R packages takes in the numeric vector and output the corresponding quantiles to the given probabilities.
+The output from the quantile function can then be used as the breaks argument for the cut function that is from the base R packages.
+The concerns of this method is that the users might not always interests in ranking the observations.
+
+The next logical design is to allows for different scaling.
+As mentioned in the paragraph above the first scaling is ``rank''.
+The function then expanded the function to allows for the ``absolute'' scaling.
+This scaling is to assign the quantile groups based on the absolute values scales.
+The default for the function is to breaks the group equally using seq function.
+The input to the seq function are taken by the min and max of the values and increment by the equal steps depend on number of group of interests.
+
+The algorithms mentions so far only breaks the quantile equally, but that is not always the cases as the users may interested in the group that are not equally breaks.
+
 \hypertarget{package-usage}{%
 \section{Package Usage}\label{package-usage}}
+
+\hypertarget{data-preprocesing-step}{%
+\subsection{Data preprocesing step}\label{data-preprocesing-step}}
+
+This first step can be done using the anim\_prep() function.
+This function required that the users data contained id which is used to uniquely identified each individual observations, values which is numerical values to be used to group the observation together, and time, the variable that distinguish the values between the time and id.
+The users will need to understands what data structure can be input into the function.
+This package included the osiris data as an examples to the users.
+
+\hypertarget{r-animbook---anim_preposiris-id-sales-year}{%
+\section{\texorpdfstring{\texttt{\{r\}\ \#\ animbook\ \textless{}-\ anim\_prep(osiris,\ ID,\ sales,\ year)\ \#}}{\{r\} \# animbook \textless- anim\_prep(osiris, ID, sales, year) \#}}\label{r-animbook---anim_preposiris-id-sales-year}}
+
+There are an additional options that allow for more customizations to the data structure or the plot.
+
+\begin{itemize}
+\tightlist
+\item
+  label: group labeling.
+\item
+  ngroup: number of groups we want to split the values into.
+\item
+  breaks: the group bins size (prototype)
+\item
+  group\_scaling: the grouping variable for the bins calculations.
+\item
+  color: the variable used to color the observations.
+\item
+  time\_dependent: logical. Whether we want the observations to start at the same time or not.
+\item
+  scaling: the scaling method, either \texttt{rank} or \texttt{absolute}.
+\item
+  runif\_min: minimum value for random addition to frame numbers
+\item
+  runif\_max: maximum value for random addition to frame numbers
+\end{itemize}
+
+The function can calculate four different scales using these options.
+
+\hypertarget{r-rank-scaling-rank_scaling---anim_prepdata-osiris-id-id-values-sales-time-year-absolute-scaling-absolute_scaling---anim_prepdata-osiris-id-id-values-sales-time-year-scaling-absolute-rank-scaling-by-group-rank_group_scaling---anim_prepdata-osiris-id-id-values-sales-time-year-group-country-absolute-scaling-by-group-absolute_group_scaling---anim_prepdata-osiris-id-id-values-sales-time-year-group-country-scaling-absolute-rank_scaling}{%
+\section{\texorpdfstring{\texttt{\{r\}\ \#\ \#\ rank\ scaling\ \#\ rank\_scaling\ \textless{}-\ anim\_prep(data\ =\ osiris,\ id\ =\ ID,\ values\ =\ sales,\ time\ =\ year)\ \#\ \ \#\ \#\ absolute\ scaling\ \#\ absolute\_scaling\ \textless{}-\ anim\_prep(data\ =\ osiris,\ id\ =\ ID,\ values\ =\ sales,\ time\ =\ year,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ scaling\ =\ "absolute")\ \#\ \ \#\ \#\ rank\ scaling\ by\ group\ \#\ rank\_group\_scaling\ \textless{}-\ anim\_prep(data\ =\ osiris,\ id\ =\ ID,\ values\ =\ sales,\ time\ =\ year,\ \ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ group\ =\ country)\ \#\ \ \#\ \#\ absolute\ scaling\ by\ group\ \#\ absolute\_group\_scaling\ \textless{}-\ anim\_prep(data\ =\ osiris,\ id\ =\ ID,\ values\ =\ sales,\ time\ =\ year,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ group\ =\ country,\ scaling\ =\ "absolute")\ \#\ \ \#\ rank\_scaling\ \#}}{\{r\} \# \# rank scaling \# rank\_scaling \textless- anim\_prep(data = osiris, id = ID, values = sales, time = year) \#  \# \# absolute scaling \# absolute\_scaling \textless- anim\_prep(data = osiris, id = ID, values = sales, time = year, \#                               scaling = "absolute") \#  \# \# rank scaling by group \# rank\_group\_scaling \textless- anim\_prep(data = osiris, id = ID, values = sales, time = year,  \#                                 group = country) \#  \# \# absolute scaling by group \# absolute\_group\_scaling \textless- anim\_prep(data = osiris, id = ID, values = sales, time = year, \#                                     group = country, scaling = "absolute") \#  \# rank\_scaling \#}}\label{r-rank-scaling-rank_scaling---anim_prepdata-osiris-id-id-values-sales-time-year-absolute-scaling-absolute_scaling---anim_prepdata-osiris-id-id-values-sales-time-year-scaling-absolute-rank-scaling-by-group-rank_group_scaling---anim_prepdata-osiris-id-id-values-sales-time-year-group-country-absolute-scaling-by-group-absolute_group_scaling---anim_prepdata-osiris-id-id-values-sales-time-year-group-country-scaling-absolute-rank_scaling}}
+
+This function will return \texttt{animbook} object containing a list of the formatted data and settings.
+
+\hypertarget{plotting-the-data}{%
+\subsection{Plotting the data}\label{plotting-the-data}}
+
+After preparing the data, we can not plot it. There are three plots available in this package:
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{kangaroo}, which plots the observation's movement over time.
+\item
+  \texttt{wallaby}, which subset the plot to either \texttt{top} or \texttt{bottom} and see which group they are in after the observational period.
+\item
+  \texttt{funnel\_web\_spider}, which is a faceted plot by time variable.
+\end{itemize}
+
+\hypertarget{r-label---ctop-20-20-40-40-60-60-80-80-100-not-listed-animbook---anim_prepdata-osiris-id-id-values-sales-time-year-color-japan-label-label-kangaroo-plot-kangaroo_plotanimbook-wallaby-plot-wallaby_plotanimbook-funnel-web-spider-plot-funnel_web_plotanimbook}{%
+\section{\texorpdfstring{\texttt{\{r\}\ \#\ label\ \textless{}-\ c("Top\ 20\%",\ "20-40",\ "40-60",\ "60-80",\ "80-100",\ "not\ listed")\ \#\ \ \#\ animbook\ \textless{}-\ anim\_prep(data\ =\ osiris,\ id\ =\ ID,\ values\ =\ sales,\ time\ =\ year,\ color\ =\ japan,\ label\ =\ label)\ \#\ \ \#\ \#\ kangaroo\ plot\ \#\ kangaroo\_plot(animbook)\ \#\ \ \#\ \#\ wallaby\ plot\ \#\ wallaby\_plot(animbook)\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \#\ \#\ funnel\ web\ spider\ plot\ \#\ funnel\_web\_plot(animbook)\ \#}}{\{r\} \# label \textless- c("Top 20\%", "20-40", "40-60", "60-80", "80-100", "not listed") \#  \# animbook \textless- anim\_prep(data = osiris, id = ID, values = sales, time = year, color = japan, label = label) \#  \# \# kangaroo plot \# kangaroo\_plot(animbook) \#  \# \# wallaby plot \# wallaby\_plot(animbook) \#              \# \# funnel web spider plot \# funnel\_web\_plot(animbook) \#}}\label{r-label---ctop-20-20-40-40-60-60-80-80-100-not-listed-animbook---anim_prepdata-osiris-id-id-values-sales-time-year-color-japan-label-label-kangaroo-plot-kangaroo_plotanimbook-wallaby-plot-wallaby_plotanimbook-funnel-web-spider-plot-funnel_web_plotanimbook}}
+
+The \texttt{kangaroo} and \texttt{wallaby} plots can be animated using the function of the next stage.
+\texttt{funnel\_web\_spider} only supported static plot.
+We can also choose whether we want to animate the plot using gganimate or plotly.
+
+\hypertarget{animating-the-plot}{%
+\subsection{Animating the plot}\label{animating-the-plot}}
+
+To animate the plot, we need to save the plot into an object, which then can be passed on to the function.
+
+\hypertarget{r-animbook---anim_prep_catdata-aeles-id-id-values-party-time-year-color-gender-time_dependent-false-p---wallaby_plotanimbook-p2---anim_animatep-gganimateanimatep2}{%
+\section{\texorpdfstring{\texttt{\{r\}\ \#\ animbook\ \textless{}-\ anim\_prep\_cat(data\ =\ aeles,\ id\ =\ id,\ values\ =\ party,\ time\ =\ year,\ color\ =\ gender,\ time\_dependent\ =\ FALSE)\ \#\ \ \#\ p\ \textless{}-\ wallaby\_plot(animbook)\ \#\ \ \#\ p2\ \textless{}-\ anim\_animate(p)\ \#\ \ \#\ gganimate::animate(p2)\ \#}}{\{r\} \# animbook \textless- anim\_prep\_cat(data = aeles, id = id, values = party, time = year, color = gender, time\_dependent = FALSE) \#  \# p \textless- wallaby\_plot(animbook) \#  \# p2 \textless- anim\_animate(p) \#  \# gganimate::animate(p2) \#}}\label{r-animbook---anim_prep_catdata-aeles-id-id-values-party-time-year-color-gender-time_dependent-false-p---wallaby_plotanimbook-p2---anim_animatep-gganimateanimatep2}}
 

### 2023-10-02 animbook-journal.Rmd
structure of paper

@@
 ---
-title: "animbook: An R Package for Visualize ..."
+title: "animbook: Visualizing changes in performance measures and demographic affiliations using animation"
 date: 04/09/2023
@@
 
-# Problem and data characterization
+# Explanation of the NY Times visualization
 
-To look for the flow between group, one of the most common tools we look at is sankey chart.
+# Data
+
+Diagram illustrating what data is expected, and how it is processed.
+
+# Animation tools
+
+Literature review of animation tools
+
+<!-- To look for the flow between group, one of the most common tools we look at is sankey chart.
 It represent the movement of the values from one set to another.
@@
 The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world.
-This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.
+This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.-->
 
-# Operation and data type abstraction
+<!-- # Operation and data type abstraction
 
@@
 The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
+-->
 
-# Visualization and interaction design
+# Visualization design
 
-# Package design
+This explains how to get from data to the animations, including different sorts of plots.
+
+# Software
+
+## Installation
+
+## Overview of functions
+
+## Example usage
 
@@
 
-# Package Usage
+<!-- # Package Usage
 
-## Data preprocesing step
+## Data preprocesing step-->
 
@@
 
+# Application
+
+## Accounting database: osiris
+
+## Voter behavior
+
 Introduction

### 2023-10-02 animbook-journal.tex
structure of paper

@@
 % !TeX root = RJwrapper.tex
-\title{animbook: An R Package for Visualize \ldots{}}
+\title{animbook: Visualizing changes in performance measures and demographic affiliations using animation}
+
 \author{by Krisanat Anukarnsakulchularp}
@@
 
-\hypertarget{problem-and-data-characterization}{%
-\section{Problem and data characterization}\label{problem-and-data-characterization}}
+\hypertarget{explanation-of-the-ny-times-visualization}{%
+\section{Explanation of the NY Times visualization}\label{explanation-of-the-ny-times-visualization}}
 
-To look for the flow between group, one of the most common tools we look at is sankey chart.
-It represent the movement of the values from one set to another.
-However, with the static sankey, the only information presented are what is the proportion of the movement, and which states the quantities move to, this often enough in explaining the flow and helps making the decision necessary.
-To present more information, color could be used to represent the demographic of the group.
-What if the information that are interesting lies in the times domain, how could the plot captured that information?
+\hypertarget{data}{%
+\section{Data}\label{data}}
 
-!!general sankey plot and sankey with color
+Diagram illustrating what data is expected, and how it is processed.
 
-The technique that is created by Hans, Ola, and Anna Rosling in 2003 is called Gapminder Trendalyzer.
-Its add an additional dimensions which are the bubble size, animated over changes in a fourth dimension, time.
-The animation in this tools has created a new way for people to analyse and visualize the trend.
+\hypertarget{animation-tools}{%
+\section{Animation tools}\label{animation-tools}}
 
-!!read effectiveness of animation in trend visualization, then add more information to above paragraph
+Literature review of animation tools
 
-The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world.
-This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.
+\hypertarget{visualization-design}{%
+\section{Visualization design}\label{visualization-design}}
 
-\hypertarget{operation-and-data-type-abstraction}{%
-\section{Operation and data type abstraction}\label{operation-and-data-type-abstraction}}
+This explains how to get from data to the animations, including different sorts of plots.
 
-When working with the raw data, the data pre-processing is one of the important steps we need to take before further analysis is taken.
-The function in this package will offer some flexibility in the types of the variable it accepted.
-However, there are still some restrictions the user needs to follow.
-In this section, it will provide what are the accepted format and examples for the user the followed to reproduce the final animate plot.
+\hypertarget{software}{%
+\section{Software}\label{software}}
 
-The data set that will be used in this section and in all of the examples of this journal is collected from Bureau van Dijk.
-The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world.
-From the raw data, we are only interested in the ranking of the companies.
-The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
+\hypertarget{installation}{%
+\subsection{Installation}\label{installation}}
 
-\hypertarget{visualization-and-interaction-design}{%
-\section{Visualization and interaction design}\label{visualization-and-interaction-design}}
+\hypertarget{overview-of-functions}{%
+\subsection{Overview of functions}\label{overview-of-functions}}
 
-\hypertarget{package-design}{%
-\section{Package design}\label{package-design}}
+\hypertarget{example-usage}{%
+\subsection{Example usage}\label{example-usage}}
 
@@
 The algorithms mentions so far only breaks the quantile equally, but that is not always the cases as the users may interested in the group that are not equally breaks.
-
-\hypertarget{package-usage}{%
-\section{Package Usage}\label{package-usage}}
-
-\hypertarget{data-preprocesing-step}{%
-\subsection{Data preprocesing step}\label{data-preprocesing-step}}
 
@@
 \section{\texorpdfstring{\texttt{\{r\}\ \#\ animbook\ \textless{}-\ anim\_prep\_cat(data\ =\ aeles,\ id\ =\ id,\ values\ =\ party,\ time\ =\ year,\ color\ =\ gender,\ time\_dependent\ =\ FALSE)\ \#\ \ \#\ p\ \textless{}-\ wallaby\_plot(animbook)\ \#\ \ \#\ p2\ \textless{}-\ anim\_animate(p)\ \#\ \ \#\ gganimate::animate(p2)\ \#}}{\{r\} \# animbook \textless- anim\_prep\_cat(data = aeles, id = id, values = party, time = year, color = gender, time\_dependent = FALSE) \#  \# p \textless- wallaby\_plot(animbook) \#  \# p2 \textless- anim\_animate(p) \#  \# gganimate::animate(p2) \#}}\label{r-animbook---anim_prep_catdata-aeles-id-id-values-party-time-year-color-gender-time_dependent-false-p---wallaby_plotanimbook-p2---anim_animatep-gganimateanimatep2}}
+
+\hypertarget{application}{%
+\section{Application}\label{application}}
+
+\hypertarget{accounting-database-osiris}{%
+\subsection{Accounting database: osiris}\label{accounting-database-osiris}}
+
+\hypertarget{voter-behavior}{%
+\subsection{Voter behavior}\label{voter-behavior}}
 

### 2023-10-09 animbook-journal.Rmd
new introduction and some paragraph

--- 2023-09-11 animbook-journal.Rmd
@@
 
+```{r}
+library(animbook)
+library(tidyverse)
+```
+
 # Introduction
 
-With the increasing computational powers, animation with large amounts of data is now become more accessible than ever.
-With the inspiration from a New York Times article, "Extensive Data Shows Punishing Reach of Racism for Black Boys".
+The concept of "zombie companies" began to attract attention when an article on the proliferation of zombie companies  (@zombie_companies_2008).
+The "zombie companies" are generally defined as companies with an interest coverage ratio of less than one for a period of more than three years.
+However, there is a simpler and more easily understandable way to show these concepts by visualizing the new listings (enters) and the de-listing (exits) of publicly traded companies on a country-by-country basis.
+This visualization method makes it clear that the concepts of zombie companies are not unique to Japan, as indicated in the OECD report (@oecd_report) that the United States has a faster metabolize (more new listings and exits) relative to Japan.
+
+  The visualization above can also be thought of as a movement between groups, which is how many companies have entered the market and how many have exited the market.
+One example of this visualization is from The New York Times article "Extensive data shows punishing reach of racism for black boys" (@the_new_york_time).
 The animation portrays the trajectory of how boys with different demographics could land up in society.
-With this plot in mind, the paper proposed a new visualization to help capture the movement of the observation for each different group over the specific period.
+It can be adapted to our problems by capturing the movement between the groups over a specific period.
 
-  This paper will focus on designing and validating the new visualization using a nested model (@nested_model) to offer an animation tool for conveying the observation trend in the given period.
+  With an advancement in technology, this results in an increase in both the size and complexity of the data.
+It requires an experienced hand to convey the right messages from the data.
+However, as shown in The New York Times article (@the_new_york_time), the animation is not only created just for eye-catching graphics.
+Animation can be used as a tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the audience.
+Based on @Mayer_Moreno_2002, animation can improve learning, especially when the goal is to promote deep understanding.
+It also requires the designer to understand how people learn.
 The cognitive theory of multimedia learning (@mayer_2005) will be considered during the designing period.
-This theory employs the structure and the strategies that will help the learner learn more effectively.
 
   The challenge of the New York Times article animation was the amount of code needed to reproduce.
-Additionally, the business data may or may not have the same information as the one in that article.
-It establishes a need to create tools for generalizing the animation to a wider range of data while still maintaining the main objective.
+Additionally, the business data may or may not have the same information as the one in the article.
+These two purposes establish the objective for creating the R package that could generalize the animation to a wider range of data.
 
-  The structure of this paper will consist of four main section.
-The first section is domain problem and data characterization, identifying the problems the visualization tools try to solve.
-Secondly, the operation and data type abstraction, the description of operations, and the types of data required for the next stage.
-The third section is visualization and interaction design, designing the visuals and refining the tools.
-In the forth section, package design, develop the structure of the packages and how to implement the final visualize design into the R package.
-Lastly, the package usage.
-The checking of the threat and validating of that threat will be carried out throughout the entire process of designing the animbook package.
+  The structure of this paper will consist of both the visualization design and software design.
+The first section will explain about the animation in The New York Times article.
+Secondly, what are the expected data to be input into the plot, and how it is processed.
+The third section is about the animation tools, for example, **gganimate** (@gganimate) and **plotly** (@plotly).
+The next section will be about the design of the package and visualization.
+The last two sections explore the usage of the R package and the application.
 
-# Problem and data characterization
+# Explanation of the NY Times visualization
 
-To look for the flow between group, one of the most common tools we look at is sankey chart.
+# Data
+
+<!-- Diagram illustrating what data is expected, and how it is processed. -->
+
+When working with the raw data, the data pre-processing is one of the important steps we need to take before further analysis is taken.
+The function in this package will offer some flexibility in the types of the variable it accepted.
+However, there are still some restrictions the user needs to follow.
+In this section, it will provide what are the accepted format and examples for the user the followed to reproduce the final animate plot.
+
+The data set that will be used in this section and in all of the examples of this journal is collected from Bureau van Dijk.
+The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world.
+From the raw data, we are only interested in the ranking of the companies.
+The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
+
+# Animation tools
+
+Literature review of animation tools
+
+# Visualization design
+
+This explains how to get from data to the animations, including different sorts of plots.
+
+In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
+The first step is to turn the data into the right format for the plot function.
+The next stage is to create a ggplot object, which can then be inputted into the animation function.
+The last step is adding the animation settings to the ggplot object so the user can animate the plot using the `gganimate::animate()` function.
+The reason for this three-step process is that it allows the user who does not have a lot of experience to reproduce the animation while keeping the customization for an experienced user.
+
+  As per motivations, the main focus for this package was to look at movement between the percentile group.
+Thus, the `anim_prep()` function's first purpose was to be able to take any numerical values and output the percentile group of the observations.
+The algorithms behind the group splitting are the `quantile()` and `cut()` functions.
+The quantile function from the stats R packages (@stats) takes in the numeric vector and outputs the corresponding quantiles to the given probabilities.
+The output from the quantile function can then be used as the breaks argument for the cut function that is from the base R packages.
+The concern of this method is that the users might not always be interested in ranking the observations.
+
+  The next logical design is to allow for different scaling.
+As mentioned in the paragraph above, the first scaling for the function is "rank".
+The function then expanded to allow for the "absolute" scaling.
+This scaling calculates the quantile groups based on the absolute values scales.
+The default is to break the group equally using the `seq()` function.
+The input to the seq function is taken by the min and max of the values and increments by equal steps depending on the number of groups of interests.
+In the real-world scenario, it is not always the case to break the group equally.
+The users may interested in the groups that are not equally broken.
+The function then allows the user to provide the vector of the breakpoint.
+
+# Software
+
+## Installation
+
+## Overview of functions
+
+There are three main stages for this packages, one is to prepare the data, two is plotting the data, and three, animating the plot.
+
+### Prepare the data
+
+The first step can be done using the `anim_prep()` function.
+This function required taht the users data contained id, which is used to uniquely identified each individual observaitons, values, which is numerical values to be used to grouping the observation together, and time, the variable that associated the changes of the observation.
+In the cases when the users already have the values as a group variable, the `anim_prep_cat()` function can then be use instead.
+
+```{r}
+animbook <- anim_prep(osiris, ID, sales, year)
+
+animbook_cat <- anim_prep_cat(aeles, id, party, year)
+```
+
+The additional options for the `anim_prep()` that allow for more customization to the data structure or the plot are as follows:
+
+- label: group labeling.
+- ngroup: number of groups we want to split the values into.
+- breaks: the group bins size
+- group_scaling: the grouping variable for the bins calculations.
+- color: the variable used to color the observations.
+- time_dependent: logical. Whether we want the observations to start at the same time or not.
+- scaling: the scaling method, either `rank` or `absolute`.
+- runif_min: minimum value for random addition to frame numbers
+- runif_max: maximum value for random addition to frame numbers
+
+Using the different combination of the additioanl options, the users could end up with four different scaling.
+
+1. Rank scaling
+
+```{r}
+# rank scaling
+rank_scaling <- anim_prep(data = osiris, id = ID, values = sales, time = year)
+```
+
+2. Absolute scaling
+
+```{r}
+# absolute scaling
+absolute_scaling <- anim_prep(data = osiris, id = ID, values = sales, time = year, 
+                              scaling = "absolute")
+```
+
+3. Rank scaling by group
+
+```{r}
+# rank scaling by group
+rank_scaling_group <- anim_prep(data = osiris, id = ID, values = sales, time = year,
+                                group_scaling = country)
+```
+
+4. Absolute scaling by group
+
+```{r}
+# absoluate scaling by group
+absolute_scaling_group <- anim_prep(data = osiris, id = ID, values = sales, time = year,
+                                    group_scaling = country, scaling = "absolute")
+```
+
+For the `anim_prep_cat()` function, the additional options are:
+
+- label: group labeling.
+- order: the ordering of the group.
+- color: the variable used to color the observations.
+- time_dependent: logical. Whether we want the observations to start at the same time or not.
+- runif_min: minimum value for random addition to frame numbers
+- runif_max: maximum value for random addition to frame numbers
+
+Both the `anim_prep()` and `anim_prep_cat()` function will return "animbook" object containing a list of the standard format data and settings.
+
+### Plotting the data
+
+Once the data is prepared, the next steps is to created the ggplot object as a basis for the animation.
+There are three plots available in this package, two plot could be uses for the animation and other plot is used as a static visualization.
+
+- `kangaroo_plot()`, plots the observation's movement over time.
+- `wallaby_plot()`, the subset plot of the `kangaroo_plot` with the time limit to only start and end.
+- `funnel_web_plot()`, the faceted static plot by time variable.
+
+All of the plot, have an internal function that converted the standard data format into the required structure for each plotting function.
+
+```{r}
+label <- c("Top 20%", "20-40", "40-60", "60-80", "80-100", "not listed")
+
+animbook <- anim_prep(data = osiris, id = ID, values = sales, time = year, color = japan, label = label)
+```
+
+1. Kangaroo's plot
+
+```{r}
+# kangaroo plot
+kangaroo_plot(object = animbook,
+              palette = RColorBrewer::brewer.pal(9, "Set1"), 
+              rendering = "ggplot")
+```
+
+2. Wallaby's plot
+
+```{r}
+# wallaby plot
+wallaby_plot(object = animbook,
+             group_palette = RColorBrewer::brewer.pal(9, "Set1"),
+             shade_palette = RColorBrewer::brewer.pal(9, "Set1"),
+             rendering = "ggplot",
+             subset = "top",
+             relation = "one_many",
+             total_point = NULL)
+```
+
+3. Funnel web spider's plot
+
+```{r}
+# funnel web plot
+funnel_web_plot(object = animbook,
+                palette = RColorBrewer::brewer.pal(9, "Set1"),
+                rendering = "ggplot")
+```
+
+### Animating the plot
+
+To animate the plot, the plot need to be save as an object before passed on to the final function `anim_animate()`.
+
+```{r}
+# animbook <- anim_prep_cat(data = aeles, id = id, values = party, time = year, color = gender, time_dependent = FALSE)
+# 
+# p <- wallaby_plot(animbook)
+# 
+# p2 <- anim_animate(p)
+# 
+# gganimate::animate(p2)
+```
+
+## Example usage
+
+# Application
+
+## Accounting database: osiris
+
+```{r}
+# raw_data <- read_csv("data-raw/osiris2021-sample1000.csv")
+
+# filter the data with sales record in selected period (2009 - 2018)
+
+# data <- raw_data |>
+#   filter(year >= 2000 & year < 2020,
+#         country %in% c("US", "JP", "CN")) |>
+#   select(year, country, ID, sales) |>
+#   filter(!is.na(sales) & sales != 0)
+# 
+# country <- data |>
+#   select(ID, country) |>
+#   distinct()
+# 
+# # complete the data using complete function for the missing year
+# complete_data <- data |>
+#   select(-country) |>
+#   tidyr::complete(year, ID) |>
+#   left_join(country) |>
+#   mutate(ID = as.factor(ID),
+#         year = as.integer(year))
+# 
+# label <- c("Top 25%", "25-50", "50-75", "75-100", "Not listed")
+# 
+# animbook <- anim_prep(osiris, ID, sales, year, label = label, ngroup = 4, color = country, time_dependent = FALSE)
+# 
+# ptop <- wallaby_plot(animbook, subset = "bottom", relation = "many_one", total_point = 500)
+# 
+# ptop2 <- anim_animate(ptop)
+# 
+# gganimate::animate(ptop2)
+# 
+# pbottom <- wallaby_plot(osiris, subset = "bottom", relation = "one_many", total_point = 500)
+# 
+# pbottom2 <- anim_animate(pbottom)
+# 
+# gganimate::animate(pbottom2)
+# 
+# gganimate::anim_save("inst/new_visualisation/exit.gif", ptop2, height = 8,
+#                      width = 9, units = "in", res = 150)
+# 
+# gganimate::anim_save("inst/new_visualisation/enter.gif", pbottom2, height = 8,
+#                      width = 9, units = "in", res = 150)
+```
+
+## Voter behavior
+
+Based on the 2016 Australian election results, how does the top party perform in keeping the old voters for different genders.
+
+```{r}
+# object <- anim_prep_cat(data = aeles,
+#                         id = id,
+#                         values = party,
+#                         time = year,
+#                         color = gender,
+#                         order = NULL,
+#                         time_dependent = FALSE)
+# 
+# # subset can be either "top", "bottom" or values in the data
+# # many_one not working yet
+# 
+# p <- wallaby_plot(object = object,
+#                   group_palette = RColorBrewer::brewer.pal(9, "Set1"),
+#                   shade_palette = RColorBrewer::brewer.pal(9, "Set1"),
+#                   rendering = "ggplot",
+#                   subset = "top",
+#                   relation = "one_many",
+#                   height = 1,
+#                   size = 3,
+#                   width = 100,
+#                   total_point = 1000)
+# 
+# p2 <- anim_animate(p)
+# 
+# gganimate::animate(p2)
+```
+
+<!-- To look for the flow between group, one of the most common tools we look at is sankey chart.
 It represent the movement of the values from one set to another.
@@
 The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
+-->
 
-# Visualization and interaction design
-
-# Package design
-
-# Package Usage
-
-Introduction
+<!-- Introduction
 
@@
 - How does the function processes the data
+-->

### 2023-10-09 animbook-journal.tex
new introduction and some paragraph

--- 2023-09-11 animbook-journal.tex
@@
 % !TeX root = RJwrapper.tex
-\title{animbook: An R Package for Visualize \ldots{}}
+\title{animbook: Visualizing changes in performance measures and demographic affiliations using animation}
 \author{by Krisanat Anukarnsakulchularp}
@@
 
-With the increasing computational powers, animation with large amounts of data is now become more accessible than ever.
-With the inspiration from a New York Times article, ``Extensive Data Shows Punishing Reach of Racism for Black Boys''.
+The concept of ``zombie companies'' began to attract attention when an article on the proliferation of zombie companies (Caballero, Hoshi, and Kashyap (2008)).
+The ``zombie companies'' are generally defined as companies with an interest coverage ratio of less than one for a period of more than three years.
+However, there is a simpler and more easily understandable way to show these concepts by visualizing the new listings (enters) and the de-listing (exits) of publicly traded companies on a country-by-country basis.
+This visualization method makes it clear that the concepts of zombie companies are not unique to Japan, as indicated in the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a faster metabolize (more new listings and exits) relative to Japan.
+
+The visualization above can also be thought of as a movement between groups, which is how many companies have entered the market and how many have exited the market.
+One example of this visualization is from The New York Times article ``Extensive data shows punishing reach of racism for black boys'' (Badger et al.
+(2018)).
 The animation portrays the trajectory of how boys with different demographics could land up in society.
-With this plot in mind, the paper proposed a new visualization to help capture the movement of the observation for each different group over the specific period.
+It can be adapted to our problems by capturing the movement between the groups over a specific period.
 
-This paper will focus on designing and validating the new visualization using a nested model (Munzner (2009)) to offer an animation tool for conveying the observation trend in the given period.
+With an advancement in technology, this results in an increase in both the size and complexity of the data.
+It requires an experienced hand to convey the right messages from the data.
+However, as shown in The New York Times article (Badger et al.
+(2018)), the animation is not only created just for eye-catching graphics.
+Animation can be used as a tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the audience.
+Based on Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.
+It also requires the designer to understand how people learn.
 The cognitive theory of multimedia learning (Mayer (2005)) will be considered during the designing period.
-This theory employs the structure and the strategies that will help the learner learn more effectively.
 
 The challenge of the New York Times article animation was the amount of code needed to reproduce.
-Additionally, the business data may or may not have the same information as the one in that article.
-It establishes a need to create tools for generalizing the animation to a wider range of data while still maintaining the main objective.
+Additionally, the business data may or may not have the same information as the one in the article.
+These two purposes establish the objective for creating the R package that could generalize the animation to a wider range of data.
 
-The structure of this paper will consist of four main section.
-The first section is domain problem and data characterization, identifying the problems the visualization tools try to solve.
-Secondly, the operation and data type abstraction, the description of operations, and the types of data required for the next stage.
-The third section is visualization and interaction design, designing the visuals and refining the tools.
-In the forth section, package design, develop the structure of the packages and how to implement the final visualize design into the R package.
-Lastly, the package usage.
-The checking of the threat and validating of that threat will be carried out throughout the entire process of designing the animbook package.
+The structure of this paper will consist of both the visualization design and software design.
+The first section will explain about the animation in The New York Times article.
+Secondly, what are the expected data to be input into the plot, and how it is processed.
+The third section is about the animation tools, for example, \textbf{gganimate} (Pedersen and Robinson (2020)) and \textbf{plotly} (Sievert (2020)).
+The next section will be about the design of the package and visualization.
+The last two sections explore the usage of the R package and the application.
 
-\hypertarget{problem-and-data-characterization}{%
-\section{Problem and data characterization}\label{problem-and-data-characterization}}
+\hypertarget{explanation-of-the-ny-times-visualization}{%
+\section{Explanation of the NY Times visualization}\label{explanation-of-the-ny-times-visualization}}
 
-To look for the flow between group, one of the most common tools we look at is sankey chart.
-It represent the movement of the values from one set to another.
-However, with the static sankey, the only information presented are what is the proportion of the movement, and which states the quantities move to, this often enough in explaining the flow and helps making the decision necessary.
-To present more information, color could be used to represent the demographic of the group.
-What if the information that are interesting lies in the times domain, how could the plot captured that information?
-
-!!general sankey plot and sankey with color
-
-The technique that is created by Hans, Ola, and Anna Rosling in 2003 is called Gapminder Trendalyzer.
-Its add an additional dimensions which are the bubble size, animated over changes in a fourth dimension, time.
-The animation in this tools has created a new way for people to analyse and visualize the trend.
-
-!!read effectiveness of animation in trend visualization, then add more information to above paragraph
-
-The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world.
-This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.
-
-\hypertarget{operation-and-data-type-abstraction}{%
-\section{Operation and data type abstraction}\label{operation-and-data-type-abstraction}}
+\hypertarget{data}{%
+\section{Data}\label{data}}
 
@@
 
-\hypertarget{visualization-and-interaction-design}{%
-\section{Visualization and interaction design}\label{visualization-and-interaction-design}}
+\hypertarget{animation-tools}{%
+\section{Animation tools}\label{animation-tools}}
 
-\hypertarget{package-design}{%
-\section{Package design}\label{package-design}}
+Literature review of animation tools
 
-\hypertarget{package-usage}{%
-\section{Package Usage}\label{package-usage}}
+\hypertarget{visualization-design}{%
+\section{Visualization design}\label{visualization-design}}
 
-Introduction
+This explains how to get from data to the animations, including different sorts of plots.
 
-Some ideas:
+In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
+The first step is to turn the data into the right format for the plot function.
+The next stage is to create a ggplot object, which can then be inputted into the animation function.
+The last step is adding the animation settings to the ggplot object so the user can animate the plot using the \texttt{gganimate::animate()} function.
+The reason for this three-step process is that it allows the user who does not have a lot of experience to reproduce the animation while keeping the customization for an experienced user.
+
+As per motivations, the main focus for this package was to look at movement between the percentile group.
+Thus, the \texttt{anim\_prep()} function's first purpose was to be able to take any numerical values and output the percentile group of the observations.
+The algorithms behind the group splitting are the \texttt{quantile()} and \texttt{cut()} functions.
+The quantile function from the stats R packages (R Core Team (2013)) takes in the numeric vector and outputs the corresponding quantiles to the given probabilities.
+The output from the quantile function can then be used as the breaks argument for the cut function that is from the base R packages.
+The concern of this method is that the users might not always be interested in ranking the observations.
+
+The next logical design is to allow for different scaling.
+As mentioned in the paragraph above, the first scaling for the function is ``rank''.
+The function then expanded to allow for the ``absolute'' scaling.
+This scaling calculates the quantile groups based on the absolute values scales.
+The default is to break the group equally using the \texttt{seq()} function.
+The input to the seq function is taken by the min and max of the values and increments by equal steps depending on the number of groups of interests.
+In the real-world scenario, it is not always the case to break the group equally.
+The users may interested in the groups that are not equally broken.
+The function then allows the user to provide the vector of the breakpoint.
+
+\hypertarget{software}{%
+\section{Software}\label{software}}
+
+\hypertarget{installation}{%
+\subsection{Installation}\label{installation}}
+
+\hypertarget{overview-of-functions}{%
+\subsection{Overview of functions}\label{overview-of-functions}}
+
+There are three main stages for this packages, one is to prepare the data, two is plotting the data, and three, animating the plot.
+
+\hypertarget{prepare-the-data}{%
+\subsubsection{Prepare the data}\label{prepare-the-data}}
+
+The first step can be done using the \texttt{anim\_prep()} function.
+This function required taht the users data contained id, which is used to uniquely identified each individual observaitons, values, which is numerical values to be used to grouping the observation together, and time, the variable that associated the changes of the observation.
+In the cases when the users already have the values as a group variable, the \texttt{anim\_prep\_cat()} function can then be use instead.
+
+The additional options for the \texttt{anim\_prep()} that allow for more customization to the data structure or the plot are as follows:
 
@@
 \item
-  The animated plot has not been used often in the business data presentation
+  label: group labeling.
 \item
-  We want to see the movement of our variable of interest
+  ngroup: number of groups we want to split the values into.
 \item
-  Business data: Accounting data (sales), Marketing data (customer interest), data analysis languages data
+  breaks: the group bins size
 \item
-  Help with storytelling
+  group\_scaling: the grouping variable for the bins calculations.
 \item
-  Inspiration: The New York Times (Extensive data shows punishing reach of racism for black boys).
-The animation plot shows what demographic group between white and black boys where would end up in society.
-It could be adapted to show, based on the demographic of the company, sees the movement of where they would end up.
-In the marketing data, the demographic of the customers could tell us the story of what product they preferred.
+  color: the variable used to color the observations.
+\item
+  time\_dependent: logical. Whether we want the observations to start at the same time or not.
+\item
+  scaling: the scaling method, either \texttt{rank} or \texttt{absolute}.
+\item
+  runif\_min: minimum value for random addition to frame numbers
+\item
+  runif\_max: maximum value for random addition to frame numbers
 \end{itemize}
 
-Data and Process
+Using the different combination of the additioanl options, the users could end up with four different scaling.
 
-Some ideas:
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Rank scaling
+\item
+  Absolute scaling
+\item
+  Rank scaling by group
+\item
+  Absolute scaling by group
+\end{enumerate}
 
-\begin{itemize}
-\item
-  The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(unique identifier), rank(y-axis, factor variable), group(optional).
-\item
-  The user can input any numerical, categorical and factor variable into the prep\_anim function which will return the data in the format that the anim\_plot function accepted.
-The x-axis and time index does not need to be the same as this allows for the user to reproduce the nytimes plot which is not time dependent.
-For the rank variable, no matter what the type of variable is in, it will return numerical variable.
-\end{itemize}
-
-When working with the raw data, the data pre-processing is one of the important steps we need to take before further analysis is taken.
-The function in this package will offer some flexibility in the types of the variable it accepted.
-However, there are still some restrictions the user needs to follow.
-In this section, it will provide what are the accepted format and examples for the user the followed to reproduce the final animate plot.
-
-The data set that will be used in this section and in all of the examples of this journal is collected from Bureau van Dijk.
-The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world.
-From the raw data, we are only interested in the ranking of the companies.
-The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
+For the \texttt{anim\_prep\_cat()} function, the additional options are:
 
@@
 \item
-  The data structure
+  label: group labeling.
 \item
-  The steps for the user
+  order: the ordering of the group.
 \item
-  How does the function processes the data
+  color: the variable used to color the observations.
+\item
+  time\_dependent: logical. Whether we want the observations to start at the same time or not.
+\item
+  runif\_min: minimum value for random addition to frame numbers
+\item
+  runif\_max: maximum value for random addition to frame numbers
 \end{itemize}
+
+Both the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} function will return ``animbook'' object containing a list of the standard format data and settings.
+
+\hypertarget{plotting-the-data}{%
+\subsubsection{Plotting the data}\label{plotting-the-data}}
+
+Once the data is prepared, the next steps is to created the ggplot object as a basis for the animation.
+There are three plots available in this package, two plot could be uses for the animation and other plot is used as a static visualization.
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{kangaroo\_plot()}, plots the observation's movement over time.
+\item
+  \texttt{wallaby\_plot()}, the subset plot of the \texttt{kangaroo\_plot} with the time limit to only start and end.
+\item
+  \texttt{funnel\_web\_plot()}, the faceted static plot by time variable.
+\end{itemize}
+
+All of the plot, have an internal function that converted the standard data format into the required structure for each plotting function.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Kangaroo's plot
+\end{enumerate}
+
+\includegraphics{animbook-journal_files/figure-latex/unnamed-chunk-8-1.pdf}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Wallaby's plot
+\end{enumerate}
+
+\includegraphics{animbook-journal_files/figure-latex/unnamed-chunk-9-1.pdf}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Funnel web spider's plot
+\end{enumerate}
+
+\includegraphics{animbook-journal_files/figure-latex/unnamed-chunk-10-1.pdf}
+
+\hypertarget{animating-the-plot}{%
+\subsubsection{Animating the plot}\label{animating-the-plot}}
+
+To animate the plot, the plot need to be save as an object before passed on to the final function \texttt{anim\_animate()}.
+
+\hypertarget{example-usage}{%
+\subsection{Example usage}\label{example-usage}}
+
+\hypertarget{application}{%
+\section{Application}\label{application}}
+
+\hypertarget{accounting-database-osiris}{%
+\subsection{Accounting database: osiris}\label{accounting-database-osiris}}
+
+\hypertarget{voter-behavior}{%
+\subsection{Voter behavior}\label{voter-behavior}}
+
+Based on the 2016 Australian election results, how does the top party perform in keeping the old voters for different genders.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-the_new_york_time}{}}%
+Badger, Emily, Claire Cain Miller, Adam Pearce, and Kevin Quealy.
+2018.
+{``Extensive Data Shows Punishing Reach of Racism for Black Boys.''} \emph{The New York Times}.
+The New York Times.
+\url{https://www.nytimes.com/interactive/2018/03/19/upshot/race-class-white-and-black-men.html}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zombie_companies_2008}{}}%
+Caballero, Ricardo J., Takeo Hoshi, and Anil K.
+Kashyap.
+2008.
+{``Zombie Lending and Depressed Restructuring in Japan.''} \emph{The American Economic Review} 98 (5): 1943--77.
+\url{http://www.jstor.org/stable/29730158}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-mayer_2005}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-nested_model}{}}%
-Munzner, Tamara.
-2009.
-{``A Nested Model for Visualization Design and Validation.''} \emph{IEEE Transactions on Visualization and Computer Graphics} 15 (6): 921--28.
-\url{https://doi.org/10.1109/TVCG.2009.111}.
+\leavevmode\vadjust pre{\hypertarget{ref-Mayer_Moreno_2002}{}}%
+Mayer, Richard E., and Roxana Moreno. 2002. \emph{Educational Psychology Review} 14 (1): 87--99. \url{https://doi.org/10.1023/a:1013184611077}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-oecd_report}{}}%
+McGowan, Müge Adalet, Dan Andrews, and Valentine Millot. 2017. {``The Walking Dead?''} no. 1372. https://doi.org/\url{https://doi.org/https://doi.org/10.1787/180d80ad-en}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gganimate}{}}%
+Pedersen, Thomas Lin, and David Robinson. 2020. {``Gganimate: A Grammar of Animated Graphics.''} \emph{R Package Version} 1 (7): 403--8.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stats}{}}%
+R Core Team. 2013. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{http://www.R-project.org/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-plotly}{}}%
+Sievert, Carson. 2020. {``Interactive {Web-Based} Data Visualization with r, Plotly, and Shiny.''} Chapman; Hall/CRC. \url{https://plotly-r.com}.
 

### 2023-10-09 animbook-journal.R

@@ -4,3 +4,152 @@
 ## ----setup, include=FALSE-----------------------------------------------------
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 
+
+## -----------------------------------------------------------------------------
+library(animbook)
+library(tidyverse)
+
+
+## -----------------------------------------------------------------------------
+animbook <- anim_prep(osiris, ID, sales, year)
+
+animbook_cat <- anim_prep_cat(aeles, id, party, year)
+
+
+## -----------------------------------------------------------------------------
+# rank scaling
+rank_scaling <- anim_prep(data = osiris, id = ID, values = sales, time = year)
+
+
+## -----------------------------------------------------------------------------
+# absolute scaling
+absolute_scaling <- anim_prep(data = osiris, id = ID, values = sales, time = year, 
+                              scaling = "absolute")
+
+
+## -----------------------------------------------------------------------------
+# rank scaling by group
+rank_scaling_group <- anim_prep(data = osiris, id = ID, values = sales, time = year,
+                                group_scaling = country)
+
+
+## -----------------------------------------------------------------------------
+# absoluate scaling by group
+absolute_scaling_group <- anim_prep(data = osiris, id = ID, values = sales, time = year,
+                                    group_scaling = country, scaling = "absolute")
+
+
+## -----------------------------------------------------------------------------
+label <- c("Top 20%", "20-40", "40-60", "60-80", "80-100", "not listed")
+
+animbook <- anim_prep(data = osiris, id = ID, values = sales, time = year, color = japan, label = label)
+
+
+## -----------------------------------------------------------------------------
+# kangaroo plot
+kangaroo_plot(object = animbook,
+              palette = RColorBrewer::brewer.pal(9, "Set1"), 
+              rendering = "ggplot")
+
+
+## -----------------------------------------------------------------------------
+# wallaby plot
+wallaby_plot(object = animbook,
+             group_palette = RColorBrewer::brewer.pal(9, "Set1"),
+             shade_palette = RColorBrewer::brewer.pal(9, "Set1"),
+             rendering = "ggplot",
+             subset = "top",
+             relation = "one_many",
+             total_point = NULL)
+
+
[…]

### 2023-10-23 animbook-journal.Rmd
add the section 2, 3 and software

@@
 
+<!-- potential new title: animbook: Visualizing benchmark dynamics using animation, or animbook: Visualizing changes in benchmark using animation-->
+
 # Introduction
@@
 
-# Explanation of the NY Times visualization
+# Explanation of the New York Times visualization
+
+The flow chart featured in one of the New York Time articles unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the @race.
+This visualization reveals that, compared to white children, black children are more likely to drop down to the lower-income group, given that they both grew up in wealthy families.
+
+  In the visualization, each observation is initially classified into one group at the start and potentially transitions into either the same group or a different group.
+This dynamics visualization constructs questions on the broader use of this visualization to other types of data.
+As mentioned in the introduction, one of the data that will make use of this is accounting data.
+Additionally, the marketing data that exhibits the movement of customers shifting the product interest to another competitor can be valuable insight into the data.
+It could be extended to incorporate demographic information of the customers.
+It would allow the marketing analyst to gain a significant understanding of both the company's products and the overall market.
+This also applies to the election data for the analyst to consolidate the campaign for their political party.
+
+  This animation was developed using two software based on JavaScript, D3.js (@d3js), and WebGL (reference).
+The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization.
+It enables the designers to bind both the data and graphical elements to the DOM (Document Object Model).
+On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins.
+For the animation in this paper, the programming languages that will be used for recreating and revising the visualization done by The New York Times articles is R (@r).
 
@@
 
-<!-- Diagram illustrating what data is expected, and how it is processed. -->
+Before any visualizations can be performed, the users must first understand the data concept known as `tidy data` (@tidy-data).
+There are three fundamental key principles: each variable forms a column, each observation forms a row, and each type of observational unit forms a table.
+These three keys are Codd's third normal form (@relational), but phrase in the language of statistics.
+The tidy data format focuses on a single dataset instead of many connected datasets typically found in a relational database.
 
-When working with the raw data, the data pre-processing is one of the important steps we need to take before further analysis is taken.
-The function in this package will offer some flexibility in the types of the variable it accepted.
-However, there are still some restrictions the user needs to follow.
-In this section, it will provide what are the accepted format and examples for the user the followed to reproduce the final animate plot.
+  The accounting data that will be used in this section and in most of the examples for this paper was collected from Bureau van Dijk (reference).
+This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide.
+The only variables of interest from this data set are ID, year, country, and sales.
+A subset version of this data set, which only contained variables of interest from 2006 to 2018, is included in this package.
 
-The data set that will be used in this section and in all of the examples of this journal is collected from Bureau van Dijk.
-The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world.
-From the raw data, we are only interested in the ranking of the companies.
-The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
+  Now that the tidy data concept is established and the example data is introduced, let's explore how the data got transformed.
+As seen in the visualization, each observation is classified into a group.
+In the accounting data, however, it is represented in a numerical form instead of categories.
+The numerical value needs to be somehow mapped to a category.
+One way to handle this is by ranking the sales and grouping the rankings into quantiles.
+In some cases, this may not be the best option.
+As the observation is moved up by quantiles, one is bound to move down.
+It can be resolved by using an alternative method, which is grouping values based on their absolute values.
+Users may also be interested in grouping the data based on different demographics, for example, ranking within a specific country.
+This generalization leads to a total of four scaling methods for the numerical data.
+
+  Original data:
+
+```{r}
+example <- osiris |> 
+  filter(country %in% c("AU", "US"),
+                between(year, 2006, 2007)) |> 
+  arrange(desc(sales))
+
+example |> 
+  filter(ID %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
+  reframe(ID, year, sales, country) |> 
+  arrange(ID)
+```
+
+1. Ranking by year.
+
+```{r}
+rank <- anim_prep(example, ID, sales, year, color = country)
+
+rank$data |> 
+  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
+  rename(country = color) |> 
+  select(-frame)
+```
+
+2. Fix bins relative to absolute values by year.
+
+```{r}
+absolute <- anim_prep(example, ID, sales, year, color = country, scaling = "absolute")
+
+absolute$data |> 
+  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
+  rename(country = color) |> 
+  select(-frame)
+```
+
+3. Ranking by year within a group.
+
+```{r}
+rank_group <- anim_prep(example, ID, sales, year, color = country, group_scaling = country)
+
+rank_group$data |> 
+  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
+  rename(country = group) |> 
+  select(-c(frame, color))
+```
+
+4. Fix bins relative to absolute values by year within a group (bug in code).
+
+```{r}
+absolute_group <- anim_prep(example, ID, sales, year, color = country, group_scaling = country, scaling = "absolute")
+
+absolute_group$data |> 
+  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
+  rename(country = group) |> 
+  select(-c(frame, color))
+```
+
+  For the first and third scaling methods, group splitting is executed using the `quantiles()` and `cut()` functions.
+The `quantile` function from the `stats` R package (@stats) takes a numeric vector and outputs the corresponding quantiles to the given probabilities.
+The output from the `quantile` function is then used as the `breaks` argument for the cut function that is part of the base R packages.
+
+  In contrast, the second and fourth scaling methods calculate the quantile based on the absolute values scales.
+The default approach is to break the group equally using the `seq()` function.
+The `seq()` function takes input values from the minimum and maximum values and increments by equal steps depending on the number of groups of interest.
+
+```{r data-diagram, fig.cap="The data transformation diagram."}
+knitr::include_graphics("figures/data-diagram.png")
+```
+
+  Based on Figure \@ref(fig:data-diagram), these are only the initial steps in formatting the data into a category.
+Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animbook data structure.
+It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values.
+Its lets the **gganimate** or **plotly** to perceive where the observation would be on the plot at a given frame.
+
+  The frame variable is assigned by sorting the data based on the id and time using the `arrange()` function, followed by applying the `group_by()` function on the id, allowing the `row_number()` function to be performed within each group.
+The functions mentioned in this paragraph are from the `dplyr` packages (@dplyr).
 
@@
 
+# Software
+
+## Installation
+
+## Overview of functions
+
 In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
@@
 
-  As per motivations, the main focus for this package was to look at movement between the percentile group.
-Thus, the `anim_prep()` function's first purpose was to be able to take any numerical values and output the percentile group of the observations.
-The algorithms behind the group splitting are the `quantile()` and `cut()` functions.
-The quantile function from the stats R packages (@stats) takes in the numeric vector and outputs the corresponding quantiles to the given probabilities.
-The output from the quantile function can then be used as the breaks argument for the cut function that is from the base R packages.
-The concern of this method is that the users might not always be interested in ranking the observations.
-
-  The next logical design is to allow for different scaling.
-As mentioned in the paragraph above, the first scaling for the function is "rank".
-The function then expanded to allow for the "absolute" scaling.
-This scaling calculates the quantile groups based on the absolute values scales.
-The default is to break the group equally using the `seq()` function.
-The input to the seq function is taken by the min and max of the values and increments by equal steps depending on the number of groups of interests.
-In the real-world scenario, it is not always the case to break the group equally.
-The users may interested in the groups that are not equally broken.
-The function then allows the user to provide the vector of the breakpoint.
-
-# Software
-
-## Installation
-
-## Overview of functions
-
-There are three main stages for this packages, one is to prepare the data, two is plotting the data, and three, animating the plot.
-
 ### Prepare the data
@@
 The first step can be done using the `anim_prep()` function.
-This function required taht the users data contained id, which is used to uniquely identified each individual observaitons, values, which is numerical values to be used to grouping the observation together, and time, the variable that associated the changes of the observation.
-In the cases when the users already have the values as a group variable, the `anim_prep_cat()` function can then be use instead.
+This function required that the user data contained ID, which is used to identify each individual observation, values, which are numerical values to be used to group the observation together, and time, the variable associated with the changes of the observation.
+In the cases when the users already have the values as a group variable, the `anim_prep_cat()` function can then be used instead.
 
@@
 
-animbook_cat <- anim_prep_cat(aeles, id, party, year)
+animbook_cat <- anim_prep_cat(d_w_change, id, qnt, time)
 ```
@@
 - ngroup: number of groups we want to split the values into.
-- breaks: the group bins size
+- breaks: the group bins' size
 - group_scaling: the grouping variable for the bins calculations.
@@
 
-Using the different combination of the additioanl options, the users could end up with four different scaling.
+Using the different combinations of the additional options, the users could end up with four different scales, as mentioned in the \@ref(data) section.
 
@@
 
-Both the `anim_prep()` and `anim_prep_cat()` function will return "animbook" object containing a list of the standard format data and settings.
+Both the `anim_prep()` and `anim_prep_cat()` functions will return the "animbook" object containing a list of the standard format data and settings.
 
@@
 
-Once the data is prepared, the next steps is to created the ggplot object as a basis for the animation.
-There are three plots available in this package, two plot could be uses for the animation and other plot is used as a static visualization.
+Once the data is prepared.
+The next step is to create the ggplot object as a basis for the animation.
+There are three plots available in this package.
+Two of the plots could be used for the animation, and another plot is used as a static visualization.
 
-- `kangaroo_plot()`, plots the observation's movement over time.
-- `wallaby_plot()`, the subset plot of the `kangaroo_plot` with the time limit to only start and end.
-- `funnel_web_plot()`, the faceted static plot by time variable.
+- `kangaroo_plot()`: plots the observation's movement over time.
+- `wallaby_plot()`: the subset plot of the `kangaroo_plot` with the time limit to only start and end.
+- `funnel_web_plot()`: the faceted static plot by time variable.
 
-All of the plot, have an internal function that converted the standard data format into the required structure for each plotting function.
+All of the plots have an internal function that converts the standard data format into the required structure for each plotting function.
 
 ```{r}
-label <- c("Top 20%", "20-40", "40-60", "60-80", "80-100", "not listed")
-
-animbook <- anim_prep(data = osiris, id = ID, values = sales, time = year, color = japan, label = label)
+animbook <- anim_prep_cat(data = d_w_change, id = id, values = qnt, time = time, color = gp)
 ```
@@
 
-```{r}
+```{r, out.width="70%"}
 # kangaroo plot
@@
 
-```{r}
+```{r, out.width="70%"}
 # wallaby plot
@@
 
-```{r}
+```{r, out.width="70%"}
 # funnel web plot
@@
 ```{r}
-# animbook <- anim_prep_cat(data = aeles, id = id, values = party, time = year, color = gender, time_dependent = FALSE)
+# animate <- anim_prep_cat(d_w_change, id = id, values = qnt, time = time, color = gp, time_dependent = FALSE)
 # 
-# p <- wallaby_plot(animbook)
+# p <- wallaby_plot(animate)
 # 
@@
 # 
-# gganimate::animate(p2)
+# gganimate::anim_save("figures/dwchange.gif", p2)
+```
+
+```{r}
+# knitr::include_graphics("figures/dwchange.gif")
 ```
@@
 
-The data set that will be used in this section and in all of the examples of this journal is collected from Bureau van Dijk.
+The data set that will be used in this section and in all of the examples of this paper is collected from Bureau van Dijk.
 The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world.

### 2023-10-23 animbook-journal.R

@@ -11,9 +11,61 @@ library(tidyverse)
 
 
 ## -----------------------------------------------------------------------------
+example <- osiris |> 
+  filter(country %in% c("AU", "US"),
+                between(year, 2006, 2007)) |> 
+  arrange(desc(sales)) 
+
+example |> 
+  filter(ID %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
+  reframe(ID, year, sales, country) |> 
+  arrange(ID)
+
+
+## -----------------------------------------------------------------------------
+rank <- anim_prep(example, ID, sales, year, color = country)
+
+rank$data |> 
+  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
+  rename(country = color) |> 
+  select(-frame)
+
+
+## -----------------------------------------------------------------------------
+absolute <- anim_prep(example, ID, sales, year, color = country, scaling = "absolute")
+
+absolute$data |> 
+  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
+  rename(country = color) |> 
+  select(-frame)
+
+
+## -----------------------------------------------------------------------------
+rank_group <- anim_prep(example, ID, sales, year, color = country, group_scaling = country)
+
+rank_group$data |> 
+  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
+  rename(country = group) |> 
+  select(-c(frame, color))
+
+
+## -----------------------------------------------------------------------------
+absolute_group <- anim_prep(example, ID, sales, year, color = country, group_scaling = country, scaling = "absolute")
+
+absolute_group$data |> 
+  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
+  rename(country = group) |> 
+  select(-c(frame, color))
+
+
+## ----data-diagram, fig.cap="The data transformation diagram."-----------------
+knitr::include_graphics("figures/data-diagram.png")
+
+
+## -----------------------------------------------------------------------------
 animbook <- anim_prep(osiris, ID, sales, year)
 
-animbook_cat <- anim_prep_cat(aeles, id, party, year)
+animbook_cat <- anim_prep_cat(d_w_change, id, qnt, time)
 
 
 ## -----------------------------------------------------------------------------
[…]

### 2023-10-23 animbook-journal.tex
updates log

@@
 
-\hypertarget{explanation-of-the-ny-times-visualization}{%
-\section{Explanation of the NY Times visualization}\label{explanation-of-the-ny-times-visualization}}
+\hypertarget{explanation-of-the-new-york-times-visualization}{%
+\section{Explanation of the New York Times visualization}\label{explanation-of-the-new-york-times-visualization}}
+
+The flow chart featured in one of the New York Time articles unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the Chetty et al.
+(2020).
+This visualization reveals that, compared to white children, black children are more likely to drop down to the lower-income group, given that they both grew up in wealthy families.
+
+In the visualization, each observation is initially classified into one group at the start and potentially transitions into either the same group or a different group.
+This dynamics visualization constructs questions on the broader use of this visualization to other types of data.
+As mentioned in the introduction, one of the data that will make use of this is accounting data.
+Additionally, the marketing data that exhibits the movement of customers shifting the product interest to another competitor can be valuable insight into the data.
+It could be extended to incorporate demographic information of the customers.
+It would allow the marketing analyst to gain a significant understanding of both the company's products and the overall market.
+This also applies to the election data for the analyst to consolidate the campaign for their political party.
+
+This animation was developed using two software based on JavaScript, D3.js (Bostock (2012)), and WebGL (reference).
+The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization.
+It enables the designers to bind both the data and graphical elements to the DOM (Document Object Model).
+On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins.
+For the animation in this paper, the programming languages that will be used for recreating and revising the visualization done by The New York Times articles is R (R Core Team (2021)).
 
@@
 
-When working with the raw data, the data pre-processing is one of the important steps we need to take before further analysis is taken.
-The function in this package will offer some flexibility in the types of the variable it accepted.
-However, there are still some restrictions the user needs to follow.
-In this section, it will provide what are the accepted format and examples for the user the followed to reproduce the final animate plot.
+Before any visualizations can be performed, the users must first understand the data concept known as \texttt{tidy\ data} (Wickham (2014)).
+There are three fundamental key principles: each variable forms a column, each observation forms a row, and each type of observational unit forms a table.
+These three keys are Codd's third normal form (Codd (1990)), but phrase in the language of statistics.
+The tidy data format focuses on a single dataset instead of many connected datasets typically found in a relational database.
 
-The data set that will be used in this section and in all of the examples of this journal is collected from Bureau van Dijk.
-The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world.
-From the raw data, we are only interested in the ranking of the companies.
-The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
+The accounting data that will be used in this section and in most of the examples for this paper was collected from Bureau van Dijk (reference).
+This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide.
+The only variables of interest from this data set are ID, year, country, and sales.
+A subset version of this data set, which only contained variables of interest from 2006 to 2018, is included in this package.
+
+Now that the tidy data concept is established and the example data is introduced, let's explore how the data got transformed.
+As seen in the visualization, each observation is classified into a group.
+In the accounting data, however, it is represented in a numerical form instead of categories.
+The numerical value needs to be somehow mapped to a category.
+One way to handle this is by ranking the sales and grouping the rankings into quantiles.
+In some cases, this may not be the best option.
+As the observation is moved up by quantiles, one is bound to move down.
+It can be resolved by using an alternative method, which is grouping values based on their absolute values.
+Users may also be interested in grouping the data based on different demographics, for example, ranking within a specific country.
+This generalization leads to a total of four scaling methods for the numerical data.
+
+Original data:
+
+\begin{verbatim}
+#> # A tibble: 12 x 4
+#>    ID           year    sales country
+#>    <fct>       <int>    <dbl> <fct>  
+#>  1 AU004085330  2007  1043282 AU     
+#>  2 AU004085330  2006   846245 AU     
+#>  3 AU009134114  2006    67842 AU     
+#>  4 AU009134114  2007    47868 AU     
+#>  5 AU009219809  2007   326335 AU     
+#>  6 AU009219809  2006   218384 AU     
+#>  7 US161229730  2007     5991 US     
+#>  8 US161229730  2006     4308 US     
+#>  9 US470731996  2007  8126500 US     
+#> 10 US470731996  2006  7205000 US     
+#> 11 US751825172  2007 22935000 US     
+#> 12 US751825172  2006 22563000 US
+\end{verbatim}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Ranking by year.
+\end{enumerate}
+
+\begin{verbatim}
+#> # A tibble: 12 x 4
+#>    id           time qtile country
+#>    <fct>       <int> <dbl> <fct>  
+#>  1 AU004085330  2006     2 AU     
+#>  2 AU004085330  2007     2 AU     
+#>  3 AU009134114  2006     3 AU     
+#>  4 AU009134114  2007     3 AU     
+#>  5 AU009219809  2006     3 AU     
+#>  6 AU009219809  2007     2 AU     
+#>  7 US161229730  2006     4 US     
+#>  8 US161229730  2007     4 US     
+#>  9 US470731996  2006     1 US     
+#> 10 US470731996  2007     1 US     
+#> 11 US751825172  2006     1 US     
+#> 12 US751825172  2007     1 US
+\end{verbatim}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Fix bins relative to absolute values by year.
+\end{enumerate}
+
+\begin{verbatim}
+#> # A tibble: 12 x 4
+#>    id           time qtile country
+#>    <fct>       <int> <dbl> <fct>  
+#>  1 AU004085330  2006     5 AU     
+#>  2 AU004085330  2007     5 AU     
+#>  3 AU009134114  2006     5 AU     
+#>  4 AU009134114  2007     5 AU     
+#>  5 AU009219809  2006     5 AU     
+#>  6 AU009219809  2007     5 AU     
+#>  7 US161229730  2006     5 US     
+#>  8 US161229730  2007     5 US     
+#>  9 US470731996  2006     4 US     
+#> 10 US470731996  2007     4 US     
+#> 11 US751825172  2006     1 US     
+#> 12 US751825172  2007     1 US
+\end{verbatim}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Ranking by year within a group.
+\end{enumerate}
+
+\begin{verbatim}
+#> # A tibble: 12 x 4
+#>    id           time qtile country
+#>    <fct>       <int> <dbl> <fct>  
+#>  1 AU004085330  2006     4 AU     
+#>  2 AU004085330  2007     4 AU     
+#>  3 AU009134114  2006     4 AU     
+#>  4 AU009134114  2007     4 AU     
+#>  5 AU009219809  2006     4 AU     
+#>  6 AU009219809  2007     4 AU     
+#>  7 US161229730  2006     4 US     
+#>  8 US161229730  2007     3 US     
+#>  9 US470731996  2006     1 US     
+#> 10 US470731996  2007     1 US     
+#> 11 US751825172  2006     1 US     
+#> 12 US751825172  2007     1 US
+\end{verbatim}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{3}
+\tightlist
+\item
+  Fix bins relative to absolute values by year within a group (bug in code).
+\end{enumerate}
+
+\begin{verbatim}
+#> # A tibble: 12 x 4
+#>    id           time qtile country
+#>    <fct>       <int> <dbl> <fct>  
+#>  1 AU004085330  2006     5 AU     
+#>  2 AU004085330  2007     5 AU     
+#>  3 AU009134114  2006     5 AU     
+#>  4 AU009134114  2007     5 AU     
+#>  5 AU009219809  2006     5 AU     
+#>  6 AU009219809  2007     5 AU     
+#>  7 US161229730  2006     5 US     
+#>  8 US161229730  2007     5 US     
+#>  9 US470731996  2006     4 US     
+#> 10 US470731996  2007     4 US     
+#> 11 US751825172  2006     1 US     
+#> 12 US751825172  2007     1 US
+\end{verbatim}
+
+For the first and third scaling methods, group splitting is executed using the \texttt{quantiles()} and \texttt{cut()} functions.
+The \texttt{quantile} function from the \texttt{stats} R package (R Core Team (2013)) takes a numeric vector and outputs the corresponding quantiles to the given probabilities.
+The output from the \texttt{quantile} function is then used as the \texttt{breaks} argument for the cut function that is part of the base R packages.
+
+In contrast, the second and fourth scaling methods calculate the quantile based on the absolute values scales.
+The default approach is to break the group equally using the \texttt{seq()} function.
+The \texttt{seq()} function takes input values from the minimum and maximum values and increments by equal steps depending on the number of groups of interest.
+
+\begin{figure}
+\includegraphics[width=40.33in]{figures/data-diagram} \caption{The data transformation diagram.}\label{fig:data-diagram}
+\end{figure}
+
+Based on Figure \ref{fig:data-diagram}, these are only the initial steps in formatting the data into a category.
+Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animbook data structure.
+It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values.
+Its lets the \textbf{gganimate} or \textbf{plotly} to perceive where the observation would be on the plot at a given frame.
+
+The frame variable is assigned by sorting the data based on the id and time using the \texttt{arrange()} function, followed by applying the \texttt{group\_by()} function on the id, allowing the \texttt{row\_number()} function to be performed within each group.
+The functions mentioned in this paragraph are from the \texttt{dplyr} packages (Wickham et al.
+(2023)).
 
@@
 
-In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
-The first step is to turn the data into the right format for the plot function.
-The next stage is to create a ggplot object, which can then be inputted into the animation function.
-The last step is adding the animation settings to the ggplot object so the user can animate the plot using the \texttt{gganimate::animate()} function.
-The reason for this three-step process is that it allows the user who does not have a lot of experience to reproduce the animation while keeping the customization for an experienced user.
-
-As per motivations, the main focus for this package was to look at movement between the percentile group.
-Thus, the \texttt{anim\_prep()} function's first purpose was to be able to take any numerical values and output the percentile group of the observations.
-The algorithms behind the group splitting are the \texttt{quantile()} and \texttt{cut()} functions.
-The quantile function from the stats R packages (R Core Team (2013)) takes in the numeric vector and outputs the corresponding quantiles to the given probabilities.
-The output from the quantile function can then be used as the breaks argument for the cut function that is from the base R packages.
-The concern of this method is that the users might not always be interested in ranking the observations.
-
-The next logical design is to allow for different scaling.
-As mentioned in the paragraph above, the first scaling for the function is ``rank''.
-The function then expanded to allow for the ``absolute'' scaling.
-This scaling calculates the quantile groups based on the absolute values scales.
-The default is to break the group equally using the \texttt{seq()} function.
-The input to the seq function is taken by the min and max of the values and increments by equal steps depending on the number of groups of interests.
-In the real-world scenario, it is not always the case to break the group equally.
-The users may interested in the groups that are not equally broken.
-The function then allows the user to provide the vector of the breakpoint.
-
 \hypertarget{software}{%
@@
 
-There are three main stages for this packages, one is to prepare the data, two is plotting the data, and three, animating the plot.
+In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
+The first step is to turn the data into the right format for the plot function.
+The next stage is to create a ggplot object, which can then be inputted into the animation function.
+The last step is adding the animation settings to the ggplot object so the user can animate the plot using the \texttt{gganimate::animate()} function.
+The reason for this three-step process is that it allows the user who does not have a lot of experience to reproduce the animation while keeping the customization for an experienced user.
 
@@
 The first step can be done using the \texttt{anim\_prep()} function.
-This function required taht the users data contained id, which is used to uniquely identified each individual observaitons, values, which is numerical values to be used to grouping the observation together, and time, the variable that associated the changes of the observation.
-In the cases when the users already have the values as a group variable, the \texttt{anim\_prep\_cat()} function can then be use instead.
+This function required that the user data contained ID, which is used to identify each individual observation, values, which are numerical values to be used to group the observation together, and time, the variable associated with the changes of the observation.
+In the cases when the users already have the values as a group variable, the \texttt{anim\_prep\_cat()} function can then be used instead.
 
@@
 \item
-  breaks: the group bins size
+  breaks: the group bins' size
 \item
@@
 
-Using the different combination of the additioanl options, the users could end up with four different scaling.
+Using the different combinations of the additional options, the users could end up with four different scales, as mentioned in the \ref{data} section.
 
@@
 
-Both the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} function will return ``animbook'' object containing a list of the standard format data and settings.
+Both the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} functions will return the ``animbook'' object containing a list of the standard format data and settings.
 
@@
 
-Once the data is prepared, the next steps is to created the ggplot object as a basis for the animation.
-There are three plots available in this package, two plot could be uses for the animation and other plot is used as a static visualization.
+Once the data is prepared.
+The next step is to create the ggplot object as a basis for the animation.
+There are three plots available in this package.
+Two of the plots could be used for the animation, and another plot is used as a static visualization.
 
@@
 \item
-  \texttt{kangaroo\_plot()}, plots the observation's movement over time.
+  \texttt{kangaroo\_plot()}: plots the observation's movement over time.
 \item
-  \texttt{wallaby\_plot()}, the subset plot of the \texttt{kangaroo\_plot} with the time limit to only start and end.
+  \texttt{wallaby\_plot()}: the subset plot of the \texttt{kangaroo\_plot} with the time limit to only start and end.
 \item
-  \texttt{funnel\_web\_plot()}, the faceted static plot by time variable.
+  \texttt{funnel\_web\_plot()}: the faceted static plot by time variable.
 \end{itemize}
 
-All of the plot, have an internal function that converted the standard data format into the required structure for each plotting function.
+All of the plots have an internal function that converts the standard data format into the required structure for each plotting function.
 
@@
 
-\includegraphics{animbook-journal_files/figure-latex/unnamed-chunk-8-1.pdf}
+\includegraphics[width=0.7\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-13-1}
 
@@
 
-\includegraphics{animbook-journal_files/figure-latex/unnamed-chunk-9-1.pdf}
+\includegraphics[width=0.7\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-14-1}
 
@@
 
-\includegraphics{animbook-journal_files/figure-latex/unnamed-chunk-10-1.pdf}
+\includegraphics[width=0.7\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-15-1}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-d3js}{}}%
+Bostock, Mike. 2012. {``D3.js - Data-Driven Documents.''} 2012. \url{http://d3js.org/}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-zombie_companies_2008}{}}%
@@
 \url{http://www.jstor.org/stable/29730158}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-race}{}}%
+Chetty, Raj, Nathaniel Hendren, Maggie Jones, and Sonya Porter.
+2020.
+{``Race and Economic Opportunity in the United States: An Intergenerational Perspective*.''} \emph{The Quarterly Journal of Economics} 135 (May): 711--83.
+\url{https://doi.org/10.1093/qje/qjz042}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-relational}{}}%
+Codd, E. F. 1990. \emph{The Relational Model for Database Management: Version 2}. USA: Addison-Wesley Longman Publishing Co., Inc.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-r}{}}%
+---------. 2021. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-plotly}{}}%
 Sievert, Carson. 2020. {``Interactive {Web-Based} Data Visualization with r, Plotly, and Shiny.''} Chapman; Hall/CRC. \url{https://plotly-r.com}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tidy-data}{}}%
+Wickham, Hadley. 2014. {``Tidy Data.''} \emph{Journal of Statistical Software} 59 (10): 1--23. \url{https://doi.org/10.18637/jss.v059.i10}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dplyr}{}}%
+Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis Vaughan. 2023. \emph{Dplyr: A Grammar of Data Manipulation}.
 

### 2023-10-24 animbook-journal.Rmd
animation added
pdf version of figure now sized

@@
 output: 
-  rjtools::rjournal_web_article:
+  rjtools::rjournal_article:
     self_contained: yes
@@
 
-```{r data-diagram, fig.cap="The data transformation diagram."}
+```{r data-diagram, fig.cap="The data transformation diagram.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
 knitr::include_graphics("figures/data-diagram.png")
@@
 
+```{r dwchange-gif, out.extra="class = 'gif'", fig.cap = "Something", eval=knitr::is_html_output()}
+knitr::include_graphics("figures/dwchange.gif")
+```
+
 ## Example usage

### 2023-10-24 animbook-journal.R

@@ -58,7 +58,7 @@ absolute_group$data |>
   select(-c(frame, color))
 
 
-## ----data-diagram, fig.cap="The data transformation diagram."-----------------
+## ----data-diagram, fig.cap="The data transformation diagram.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"----
 knitr::include_graphics("figures/data-diagram.png")
 
 
@@ -95,14 +95,14 @@ absolute_scaling_group <- anim_prep(data = osiris, id = ID, values = sales, time
 animbook <- anim_prep_cat(data = d_w_change, id = id, values = qnt, time = time, color = gp)
 
 
-## ----out.width="70%"----------------------------------------------------------
+## ---- out.width="70%"---------------------------------------------------------
 # kangaroo plot
 kangaroo_plot(object = animbook,
               palette = RColorBrewer::brewer.pal(9, "Set1"), 
               rendering = "ggplot")
 
 
-## ----out.width="70%"----------------------------------------------------------
+## ---- out.width="70%"---------------------------------------------------------
 # wallaby plot
 wallaby_plot(object = animbook,
              group_palette = RColorBrewer::brewer.pal(9, "Set1"),
@@ -113,7 +113,7 @@ wallaby_plot(object = animbook,
              total_point = NULL)
 
 
-## ----out.width="70%"----------------------------------------------------------
+## ---- out.width="70%"---------------------------------------------------------
 # funnel web plot
 funnel_web_plot(object = animbook,
                 palette = RColorBrewer::brewer.pal(9, "Set1"),
@@ -132,6 +132,10 @@ funnel_web_plot(object = animbook,
 
 ## -----------------------------------------------------------------------------
 # knitr::include_graphics("figures/dwchange.gif")
+
+
+## ----dwchange-gif, out.extra="class = 'gif'", fig.cap = "Something", eval=knitr::is_html_output()----
+#> knitr::include_graphics("figures/dwchange.gif")
 
 
 ## -----------------------------------------------------------------------------

### 2023-10-26 animbook-journal.Rmd
paper 1st version

--- 2023-10-23 animbook-journal.Rmd
@@
 title: "animbook: Visualizing changes in performance measures and demographic affiliations using animation"
-date: 04/09/2023
 abstract: >
@@
     address:
-    - Faculty of Business and Economics
+    - Department of Econometrics and Business Statistics
     - Melbourne, Australia
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
 ```
@@
 
-<!-- potential new title: animbook: Visualizing benchmark dynamics using animation, or animbook: Visualizing changes in benchmark using animation-->
-
 # Introduction
@@
 The "zombie companies" are generally defined as companies with an interest coverage ratio of less than one for a period of more than three years.
-However, there is a simpler and more easily understandable way to show these concepts by visualizing the new listings (enters) and the de-listing (exits) of publicly traded companies on a country-by-country basis.
-This visualization method makes it clear that the concepts of zombie companies are not unique to Japan, as indicated in the OECD report (@oecd_report) that the United States has a faster metabolize (more new listings and exits) relative to Japan.
+These companies are taking space in the market but adding no life to the economy.
+There could be other movement patterns, beyond zombies, that are interesting, such as companies that suddenly become very successful, or in politics voters who switch party affiliation between elections.
+Viewing changes between categories over time is an interesting challenge for visualization.
 
-  The visualization above can also be thought of as a movement between groups, which is how many companies have entered the market and how many have exited the market.
-One example of this visualization is from The New York Times article "Extensive data shows punishing reach of racism for black boys" (@the_new_york_time).
-The animation portrays the trajectory of how boys with different demographics could land up in society.
-It can be adapted to our problems by capturing the movement between the groups over a specific period.
+  The New York Times provided a possible solution in the article "Extensive data show punishing reach of racism for black boys" (@the_new_york_time) to tell the story of how racism appears to inhibit socioeconomic change.
+This approach can be adapted to address the zombie problem by capturing the movement between groups over a specific period.
 
@@
 Animation can be used as a tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the audience.
-Based on @Mayer_Moreno_2002, animation can improve learning, especially when the goal is to promote deep understanding.
-It also requires the designer to understand how people learn.
-The cognitive theory of multimedia learning (@mayer_2005) will be considered during the designing period.
 
-  The challenge of the New York Times article animation was the amount of code needed to reproduce.
+  The challenge in reproducing the New York Times article animation was the amount of code required.
 Additionally, the business data may or may not have the same information as the one in the article.
-These two purposes establish the objective for creating the R package that could generalize the animation to a wider range of data.
+These considerations establish the objective for creating the R package that could generalize the animation to a wider range of data.
 
   The structure of this paper will consist of both the visualization design and software design.
-The first section will explain about the animation in The New York Times article.
-Secondly, what are the expected data to be input into the plot, and how it is processed.
-The third section is about the animation tools, for example, **gganimate** (@gganimate) and **plotly** (@plotly).
-The next section will be about the design of the package and visualization.
-The last two sections explore the usage of the R package and the application.
+The first section will explain the animation in The New York Times article and why it might be relevant to the problems.
+Secondly, what is the expected data to be input into the plot, and how it is processed.
+The third section is about the animation tools, followed by the section on package and visualization design.
+The last two sections explore the usage of the R package and the application to other types of data.
 
@@
 
-The flow chart featured in one of the New York Time articles unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the @race.
+The flow chart featured in one of the New York Times articles unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the @race.
 This visualization reveals that, compared to white children, black children are more likely to drop down to the lower-income group, given that they both grew up in wealthy families.
@@
 This dynamics visualization constructs questions on the broader use of this visualization to other types of data.
-As mentioned in the introduction, one of the data that will make use of this is accounting data.
-Additionally, the marketing data that exhibits the movement of customers shifting the product interest to another competitor can be valuable insight into the data.
-It could be extended to incorporate demographic information of the customers.
-It would allow the marketing analyst to gain a significant understanding of both the company's products and the overall market.
-This also applies to the election data for the analyst to consolidate the campaign for their political party.
+The potential use of this visualization on accounting data is to convey a message, as reported by the @oecd_report, that the concept of zombie companies is not unique to Japan alone.
+It is also present in the United States, which has a faster metabolize rate (more new listings and exits) relative to Japan.
+
+  The political data that exhibits the movement of voters switching party affiliations between elections can be a valuable insight into the behavior of the voters.
+This data could be extended to incorporate demographic information about the voters, providing analysts with a significant insight into voter behavior.
+This allows them to consolidate effective campaigns for their political party.
+This also applies to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.
 
@@
 On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins.
-For the animation in this paper, the programming languages that will be used for recreating and revising the visualization done by The New York Times articles is R (@r).
+For the animation in this paper, the programming language that will be used for recreating and revising the visualization done by The New York Times articles is R (@r).
 
@@
 
-  The accounting data that will be used in this section and in most of the examples for this paper was collected from Bureau van Dijk (reference).
-This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide.
-The only variables of interest from this data set are ID, year, country, and sales.
-A subset version of this data set, which only contained variables of interest from 2006 to 2018, is included in this package.
+```{r data-diagram, fig.cap="The diagram shows what are the expected data forms.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+knitr::include_graphics("figures/data-diagram.png")
+```
 
-  Now that the tidy data concept is established and the example data is introduced, let's explore how the data got transformed.
-As seen in the visualization, each observation is classified into a group.
-In the accounting data, however, it is represented in a numerical form instead of categories.
-The numerical value needs to be somehow mapped to a category.
+  In the data structure, there are requirements that must be followed for reproducing the animation.
+The data must have ID and time variables.
+These form what we call a unique ID.
+Also, the values variable can be either a numerical or categorical variable.
+The type of this variable will determine the stage the data set is in.
+This format ensures that during the data pre-processing, the R function understands what needs to be done with the data.
+
+  Figure \@ref(fig:data-diagram) shows which stages the data is in, given the type of values variable.
+Start with the raw data structure.
+The values are presented in the numerical format.
+It is referred to as 'raw' because, in the New York Times animation, it is expressed in the categorical format.
+However, in most cases, the data is in numerical values and requires transformation.
+The second form is categorized data, as mentioned earlier, which involves transforming numerical into categories.
+This transformation may not be necessary if it already exists in the categorized format, as in the case of political data (party affiliation).
+The last form is animated data, where the frame is assigned to each unique ID.
+
+# Animation tools
+
+```{r animation-diagram, fig.cap="The diagram shows how the animation is done using the successive pictures.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+knitr::include_graphics("figures/animation-diagram.png")
+```
+
+The principle underlying the animation is called persistence of vision (@animation-mechanic).
+When an image disappears, the brain will retain the previous images for a brief period of time.
+It is this slight period of retention that allows humans to separate sequential images.
+If this is seen in quick succession, it will appear as if the objects are in motion.
+This is illustrated in Figure \@ref(fig:animation-diagram).
+There are multiple ways to create an animation in the R environment (@r), including packages like `gganimate` and `plot`.
+
+  The `gganimate` package (@gganimate) is an extension from the `ggplot2` package (@ggplot2) to include the description of an animation.
+It added new grammar classes to the plot object, allowing it to understand how the plot should change over time.
+The use of `transition_*()` functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time.
+The output from the `gganimate` can be rendered or saved in multiple formats.
+This includes `gifski_renderer()` from the `gifski` package (@gifski) to save the animation in GIF format or `av_renderer()` from the `av` package (@av) to save it into a video file format.
+
+  Plotly is a graphing library that provides tools for creating an interactive plot in multiple programming languages, such as R, JavaScript, Python, and Julia.
+In R, plotly can be accessed through the `plotly` package (@plotly), which integrates plotly.js from the JavaScript graphing library.
+The usage of this library can be from a converting function, `ggplotly()`, or a standalone function, `plot_ly()`.
+The conversion is accomplished by taking the elements from the `ggplot` object and then redrawing them using the plotly.js.
+
+```{r animated-diagram, fig.cap="The diagram shows how the frames were used in the animated plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+knitr::include_graphics("figures/animated-diagram.png")
+```
+
+  In the context of data, as shown in Figure \@ref(fig:animated-diagram), observations are positioned at specific points in time.
+The further the distance between these points, the less smooth the animation becomes.
+This issue can be eliminated by interpolating additional points in between the observations.
+In the `gganimate` package, the interpolation is achieved using the `tweenr` package (@tweenr), while in `plotly`, it utilizes d3.interpolate (@d3js).
+
+  Figure \@ref(fig:animated-diagram) demonstrates how the frame variables are applied in an animated plot.
+The frame variable within the animated data structure allows the animation function to determine the position of observations on the plot at any given frame.
+
+# Visualization design
+
+The animated visualization can be an effective communication tool (@Mayer_Moreno_2002; @effective-trend).
+It helps with communicating complex data, enhancing the narrative, and keeping it engaged for the audience.
+According to @Mayer_Moreno_2002, animation can improve learning, especially when the goal is to promote deep understanding.
+
+  According to @mayer_2005, designing multimedia requires the designer to understand how people learn.
+One of the principles in @mayer_2005, Redundancy, suggests that a piece of excess information could overload the learners.
+By this principle, the animation must be carefully designed to avoid this pitfall.
+
+  From the New York Times animation, multiple information are shown in the visualization.
+It includes points in motion, distribution at the end, and proportional counters.
+However, this could lead to information overload (@mayer_2005).
+Therefore, the distribution at the end and proportional counters are excluded.
+Instead, the new element has been integrated, proportional shaded areas.
+It displays the proportion of observation within each group.
+
+```{r proportional-shade, fig.show="hold", out.width="50%", fig.cap="The plot shows the difference between the sigmoid and sine curves."}
+knitr::include_graphics("figures/sigmoid-shade.png")
+knitr::include_graphics("figures/sine-shade.png")
+```
+
+  As mentioned in the Animation tools section, the paths of observations are getting interpolated.
+These functions only generate a linear path between points.
+However, linear paths may not be suitable for creating proportional shading, as they do not accurately represent the proportions.
+Non-linear curves like the sigmoid curves should be considered instead, as they provide a better display of proportions.
+These curves are commonly used in multiple Sankey diagrams, but there is a limitation on this shape.
+The issue is shown in Figure \@ref(fig:proportional-shade).
+While it does accurately represent the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation (@Shaffer_2019).
+
+# Software
+
+## Installation
+
+You can install the development version of animbook from [GitHub](https://github.com/KrisanatA/animbook) with:
+
+``` r
+# install.packages("devtools")
+devtools::install_github("KrisanatA/animbook")
+```
+
+## Overviw of functions
+
+In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
+The first step is to turn the data into the right format for the plot function.
+The next stage is to create a ggplot object, which can then be inputted into the animation function.
+The last step is adding the animation settings to the ggplot object so the user can animate the plot using the `gganimate::animate()` function.
+The reason for this three-step process is that it allows the user who does not have a lot of experience to reproduce the animation while keeping the customization for an experienced user.
+
+### Data preprocessing
+
+From Figure \@ref(fig:data-diagram), there is a need to map numerical value to a category.
 One way to handle this is by ranking the sales and grouping the rankings into quantiles.
 In some cases, this may not be the best option.
-As the observation is moved up by quantiles, one is bound to move down.
-It can be resolved by using an alternative method, which is grouping values based on their absolute values.
+When the observation is moved up by quantile, one is bound to move down.
+This issue can be resolved by using an alternative method, which is grouping values based on their absolute values.
 Users may also be interested in grouping the data based on different demographics, for example, ranking within a specific country.
-This generalization leads to a total of four scaling methods for the numerical data.
+This generalization leads to four different scaling methods for the numerical data.
 
@@
 ```{r}
-example <- osiris |> 
-  filter(country %in% c("AU", "US"),
-                between(year, 2006, 2007)) |> 
-  arrange(desc(sales))
-
-example |> 
-  filter(ID %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
-  reframe(ID, year, sales, country) |> 
-  arrange(ID)
+dbl_change |> 
+  filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
+  reframe(id, time, values, gp) |> 
+  arrange(gp, id)
 ```
@@
 ```{r}
-rank <- anim_prep(example, ID, sales, year, color = country)
+rank <- anim_prep(dbl_change, id, values, time, color = gp)
 
 rank$data |> 
-  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
-  rename(country = color) |> 
-  select(-frame)
+  filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
+  rename(gp = color) |> 
+  select(-frame) |> 
+  arrange(gp, id)
 ```
@@
 ```{r}
-absolute <- anim_prep(example, ID, sales, year, color = country, scaling = "absolute")
+absolute <- anim_prep(dbl_change, id, values, time, color = gp, scaling = "absolute")
 
 absolute$data |> 
-  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
-  rename(country = color) |> 
-  select(-frame)
+  filter(id %in% c(1, 14, 21, 100, 106, 148)) |>  
+  rename(gp = color) |> 
+  select(-frame) |> 
+  arrange(gp, id)
 ```
@@
 ```{r}
-rank_group <- anim_prep(example, ID, sales, year, color = country, group_scaling = country)
+rank_group <- anim_prep(dbl_change, id, values, time, color = gp, group_scaling = gp)
 
 rank_group$data |> 
-  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
-  rename(country = group) |> 
-  select(-c(frame, color))
+  filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
+  rename(gp = group) |> 
+  select(-c(frame, color)) |> 
+  arrange(gp, id)
 ```
 
-4. Fix bins relative to absolute values by year within a group (bug in code).
+  4. Fix bins relative to absolute values by year within a group.
 
 ```{r}
-absolute_group <- anim_prep(example, ID, sales, year, color = country, group_scaling = country, scaling = "absolute")
+absolute_group <- anim_prep(dbl_change, id, values, time, color = gp, group_scaling = gp, scaling = "absolute")
 
 absolute_group$data |> 
-  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
-  rename(country = group) |> 
-  select(-c(frame, color))
+  filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
+  rename(gp = group) |> 
+  select(-c(frame, color)) |> 
+  arrange(gp, id)
 ```
@@
 The `seq()` function takes input values from the minimum and maximum values and increments by equal steps depending on the number of groups of interest.
+Additionally, the users have the option to specify the breaks themselves if they choose to do so.
 
-```{r data-diagram, fig.cap="The data transformation diagram."}
-knitr::include_graphics("figures/data-diagram.png")
-```
+  These are only the initial steps in formatting the data into a category.
+Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animated data structure.
+It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values.
+It lets the `gganimate` or `plotly` to perceive where the observation would be on the plot at a given frame as seen in the \@ref(fig:animated-diagram).
 
-  Based on Figure \@ref(fig:data-diagram), these are only the initial steps in formatting the data into a category.
-Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animbook data structure.
-It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values.
-Its lets the **gganimate** or **plotly** to perceive where the observation would be on the plot at a given frame.
-
-  The frame variable is assigned by sorting the data based on the id and time using the `arrange()` function, followed by applying the `group_by()` function on the id, allowing the `row_number()` function to be performed within each group.
+  The frame variable is assigned by sorting the data based on the ID and time using the `arrange()` function, followed by applying the `group_by()` function on the ID, allowing the `row_number()` function to be performed within each group.
 The functions mentioned in this paragraph are from the `dplyr` packages (@dplyr).
 
-# Animation tools
+  All of the pre-processing steps mentioned above are completed using the `anim_prep()` or `anim_prep_cat()` function, depending on the stages of the data structure.
+The `anim_prep()` function is used for raw data format, while the `anim_prep_cat()` function is for categorized data format.
+There are additional arguments that facilitate the users for more customization.
 
-Literature review of animation tools
+  For the `anim_prep()` function, the arguments are as follows:
 
-# Visualization design
+- data: A data frame containing the data to be prepared for visualization.
+- id: The column name that represents the unique identifier variable.
+- values: The column name that contains the numeric values to be visualized.
+- time: The column name represents the time variable.
+- label: A vector of labels to be used for the y-axis in the visualization.
+- ngroup:	The number of groups or categories to create for scaling values.
+- breaks: A vector of breaks for creating bins.
+- group_scaling: The column name that represents the grouping variable.
+- color: The column name to be used in ggplot2::aes() for the plot function.
+- time_dependent: Logical. Should the visualization be time-dependent? Default is TRUE.
+- scaling: The scaling method to be used; "rank" or "absolute."
+- runif_min: The minimum value for random addition to frame numbers.
+- runif_max: The maximum value for random addition to frame numbers.
 
-This explains how to get from data to the animations, including different sorts of plots.
+  For the `anim_prep_cat()` function, the arguments are as follows:
 
-# Software
+- data: A data frame containing the data to be prepared for visualization.
+- id: The column name that represents the unique identifier variable.
+- values: The column name that contains the numeric values to be visualized.
+- time: The column name represents the time variable.
+- label: A vector of labels to be used for the y-axis in the visualization.
+- order: A vector of order for sorting the category values.
+- color: The column name to be used in ggplot2::aes() for the plot function.
+- time_dependent: Logical. Should the visualization be time-dependent? Default is TRUE.
+- runif_min: The minimum value for random addition to frame numbers.
+- runif_max: The maximum value for random addition to frame numbers.
 
-## Installation
-
-## Overview of functions
-
-In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
-The first step is to turn the data into the right format for the plot function.
-The next stage is to create a ggplot object, which can then be inputted into the animation function.
-The last step is adding the animation settings to the ggplot object so the user can animate the plot using the `gganimate::animate()` function.
-The reason for this three-step process is that it allows the user who does not have a lot of experience to reproduce the animation while keeping the customization for an experienced user.
-
-### Prepare the data
-
-The first step can be done using the `anim_prep()` function.
-This function required that the user data contained ID, which is used to identify each individual observation, values, which are numerical values to be used to group the observation together, and time, the variable associated with the changes of the observation.
-In the cases when the users already have the values as a group variable, the `anim_prep_cat()` function can then be used instead.
-
-```{r}
-animbook <- anim_prep(osiris, ID, sales, year)
-
-animbook_cat <- anim_prep_cat(d_w_change, id, qnt, time)
-```
-
-The additional options for the `anim_prep()` that allow for more customization to the data structure or the plot are as follows:
-
-- label: group labeling.
-- ngroup: number of groups we want to split the values into.
-- breaks: the group bins' size
-- group_scaling: the grouping variable for the bins calculations.
-- color: the variable used to color the observations.
-- time_dependent: logical. Whether we want the observations to start at the same time or not.
-- scaling: the scaling method, either `rank` or `absolute`.
-- runif_min: minimum value for random addition to frame numbers
-- runif_max: maximum value for random addition to frame numbers
-
-Using the different combinations of the additional options, the users could end up with four different scales, as mentioned in the \@ref(data) section.
-
-1. Rank scaling
-
-```{r}
-# rank scaling
-rank_scaling <- anim_prep(data = osiris, id = ID, values = sales, time = year)
-```
-
-2. Absolute scaling
-
-```{r}
-# absolute scaling
-absolute_scaling <- anim_prep(data = osiris, id = ID, values = sales, time = year, 
-                              scaling = "absolute")
-```
-
-3. Rank scaling by group
-
-```{r}
-# rank scaling by group
-rank_scaling_group <- anim_prep(data = osiris, id = ID, values = sales, time = year,
-                                group_scaling = country)
-```
-
-4. Absolute scaling by group
-
-```{r}
-# absoluate scaling by group
-absolute_scaling_group <- anim_prep(data = osiris, id = ID, values = sales, time = year,
-                                    group_scaling = country, scaling = "absolute")
-```
-
-For the `anim_prep_cat()` function, the additional options are:
-
-- label: group labeling.
-- order: the ordering of the group.
-- color: the variable used to color the observations.
-- time_dependent: logical. Whether we want the observations to start at the same time or not.
-- runif_min: minimum value for random addition to frame numbers
-- runif_max: maximum value for random addition to frame numbers
-
-Both the `anim_prep()` and `anim_prep_cat()` functions will return the "animbook" object containing a list of the standard format data and settings.
-
-### Plotting the data
+### Plotting function
 
 Once the data is prepared.
-The next step is to create the ggplot object as a basis for the animation.
+The next step is to create the `ggplot` object as a basis for the animation.
 There are three plots available in this package.
 Two of the plots could be used for the animation, and another plot is used as a static visualization.
+All of the plots have an internal function that converts the standard data format into the required structure for each plotting function.
 
@@
 
-All of the plots have an internal function that converts the standard data format into the required structure for each plotting function.
+  The main focus of this paper will be on the `wallaby_plot()`, which draws inspiration from the New York Times animation and combines the knowledge gained from the previous sections in creating the visualization.
 
-```{r}
-animbook <- anim_prep_cat(data = d_w_change, id = id, values = qnt, time = time, color = gp)
+  The `wallaby_data()` function is responsible for performing data manipulation and formatting tasks on the original object.
+It includes creating additional data components for labeling and shading.
+This function also responds by interpolating the non-linear path.
+It performs this task by mapping the `sine()` function provided in this package to each observation using the `map()` function from the `purrr` package (@purrr).
+The frame is recalculated using the same method mentioned in the data preprocessing section.
+The `sankey_shade()` function is called to generate the proportional shaded data.
+
+```{r shade-algorithm, fig.show="hold", out.width="50%", fig.cap="The plot shows how does the algorithm work."}
+knitr::include_graphics("figures/sankey-shade-1.png")
+knitr::include_graphics("figures/sankey-shade-2.png")
 ```
 
-1. Kangaroo's plot
+  The algorithm behind the `sankey_shade()` function is illustrated in Figure \@ref(fig:shade-algorithm).
+It started by calculating the corner points for all of the shaded areas.
+Then, use the `sine()` function to interpolate the point between the left and right.
 
-```{r, out.width="70%"}
-# kangaroo plot
-kangaroo_plot(object = animbook,
-              palette = RColorBrewer::brewer.pal(9, "Set1"), 
-              rendering = "ggplot")
+  Now that the data are in the right format for the wallaby's plot, the `geom_point()` function is used for plotting the observations, `geom_polygon()` is used for creating the proportional shaded areas, and `geom_text()` is used for creating labels.
+These three functions are from the `ggplot2` package (@ggplot2).
+During this process, the aesthetics mapping will be different depending on the rendering tool to be used, which can be either `gganimate` or `plotly`.
+The difference between the two rendering tools is that for `plotly`, the `ids` and `frame` arguments need to be specified during the creation of the `ggplot` object.
+
+  The arguments for Wallaby's plot are as follows.
+- object: The animbook object returned from the prep function.
+- group_palette: The vector of the palette used by the function to supply the color to each group.
+- shade_palette: The vector of the palette used by the function to supply the color to the shaded area.
+- rendering: The choice of method used to create and display the plot, either gganimate or plotly.
+- subset: A character string specifying the variable used for subsetting the data. The "top" and "bottom" strings can also be used in this argument.
+- relation: The choice of relationship for the values to display on the plot, either "one_many." or "many_one."
+- total_point: The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.
+- height: The proportion of the area occupied by the observations in the shaded areas.
+- width: The distance between the first and last observation in the animation.
+- size: The point size.
+- alpha: The opacity of the proportional shaded areas.
+
+### Animating function
+
+It is necessary to save the plot as a `ggplot` object before passing it to the final function, `anim_animate()`, to animate.
+This function will automatically detect which rendering method was specified in the previous steps and add the minimum requirement functions accordingly.
+By default, if the user specifies the rendering as `gganimate`, then it will add the `transition_time()` function from the `gganimate` package (@gganimate).
+Otherwise, the `animation_opts()` function will be added from the `plotly` package (@plotly).
+
+## Example usage
+
+Step 1: Prepare the data
+
+```{r, echo=TRUE}
+animbook <- anim_prep_cat(cat_change, 
+                          id = id, 
+                          values = qnt, 
+                          time = time, 
+                          color = gp, 
+                          time_dependent = FALSE)
+
+head(animbook$data, 10)
+str(animbook)
 ```
 
-2. Wallaby's plot
+Step 2: Plotting the data
 
-```{r, out.width="70%"}
-# wallaby plot
-wallaby_plot(object = animbook,
+```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+p <- wallaby_plot(object = animbook,
              group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-             shade_palette = RColorBrewer::brewer.pal(9, "Set1"),
+             shade_palette = c("#737373", "#969696", "#BDBDBD","#D9D9D9","#D9D9D9","#D9D9D9"),
              rendering = "ggplot",
@@
              total_point = NULL)
+
+p
 ```
 
-3. Funnel web spider's plot
+Step 3: Animating the plot
 
-```{r, out.width="70%"}
-# funnel web plot
-funnel_web_plot(object = animbook,
-                palette = RColorBrewer::brewer.pal(9, "Set1"),
-                rendering = "ggplot")
+```{r, eval=FALSE}
+p2 <- anim_animate(p)
+
+gganimate::anim_save("figures/catchange.gif", p2)
 ```
 
-### Animating the plot
+``` r
+p2 <- anim_animate(p)
 
-To animate the plot, the plot need to be save as an object before passed on to the final function `anim_animate()`.
-
-```{r}
-# animate <- anim_prep_cat(d_w_change, id = id, values = qnt, time = time, color = gp, time_dependent = FALSE)
-# 
-# p <- wallaby_plot(animate)
-# 
-# p2 <- anim_animate(p)
-# 
-# gganimate::anim_save("figures/dwchange.gif", p2)
+gganimate::animate(p2)
 ```
 
-```{r}
-# knitr::include_graphics("figures/dwchange.gif")
+```{r catchange-figure, fig.cap = "Animate visualization using example data.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+knitr::include_graphics("figures/animation-example.png")
 ```
 
-## Example usage
+```{r catchange-gif, out.extra="class = 'gif'", fig.cap = "Animate visualization using example data.", eval=knitr::is_html_output()}
+knitr::include_graphics("figures/catchange.gif")
+```
 
@@
 
-```{r}
-# raw_data <- read_csv("data-raw/osiris2021-sample1000.csv")
+The accounting Osiris data that will be used in this section was collected from Bureau van Dijk (@bvd).
+This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide.
+The only variables of interest from this data set are ID, year, country, and sales.
+A subset version of this data set, which only contained variables of interest from 2006 to 2018, is included in this package.
 
-# filter the data with sales record in selected period (2009 - 2018)
+  As mentioned in the OECD report (@oecd_report), the United States has a faster metabolize rate relative to Japan company.
+An animation will be created using the `animbook` package to enhance communication with data.
 
-# data <- raw_data |>
-#   filter(year >= 2000 & year < 2020,
-#         country %in% c("US", "JP", "CN")) |>
-#   select(year, country, ID, sales) |>
-#   filter(!is.na(sales) & sales != 0)
-# 
-# country <- data |>
-#   select(ID, country) |>
-#   distinct()
-# 
-# # complete the data using complete function for the missing year
-# complete_data <- data |>
-#   select(-country) |>
-#   tidyr::complete(year, ID) |>
-#   left_join(country) |>
-#   mutate(ID = as.factor(ID),
-#         year = as.integer(year))
-# 
-# label <- c("Top 25%", "25-50", "50-75", "75-100", "Not listed")
-# 
-# animbook <- anim_prep(osiris, ID, sales, year, label = label, ngroup = 4, color = country, time_dependent = FALSE)
-# 
-# ptop <- wallaby_plot(animbook, subset = "bottom", relation = "many_one", total_point = 500)
-# 
-# ptop2 <- anim_animate(ptop)
-# 
-# gganimate::animate(ptop2)
-# 
-# pbottom <- wallaby_plot(osiris, subset = "bottom", relation = "one_many", total_point = 500)
-# 
-# pbottom2 <- anim_animate(pbottom)
-# 
-# gganimate::animate(pbottom2)
-# 
-# gganimate::anim_save("inst/new_visualisation/exit.gif", ptop2, height = 8,
-#                      width = 9, units = "in", res = 150)
-# 
-# gganimate::anim_save("inst/new_visualisation/enter.gif", pbottom2, height = 8,
-#                      width = 9, units = "in", res = 150)
+  First, filter the countries to include only the United States and Japan.
+Then, prepare the Osiris data using the `anim_prep` function with the first scaling, which is a ranking method.
+Next, use the `wallaby_plot` function to create a `ggplot` object and add default settings for `gganimate` rendering.
+
+```{r, echo=TRUE}
+data <- osiris |> 
+  filter(country %in% c("US", "JP"))
+
+label <- c("Top 25%", "25-50", "50-75", "75-100", "Not listed")
+
+accounting <- anim_prep(data, 
+                      id = ID, 
+                      values = sales, 
+                      time = year, 
+                      label = label, 
+                      ngroup = 4, 
+                      color = country, 
+                      time_dependent = FALSE)
+
+p <- wallaby_plot(accounting,
+                  group_palette = RColorBrewer::brewer.pal(9, "Set1"),
+                  shade_palette = c("#737373", "#969696", "#BDBDBD","#D9D9D9","#D9D9D9","#D9D9D9"),
+                  subset = "bottom",
+                  relation = "many_one",
+                  height = 1,
+                  size = 2,
+                  width = 100,
+                  total_point = 1000)
+
+p2 <- anim_animate(p)
 ```
 
-## Voter behavior
-
-Based on the 2016 Australian election results, how does the top party perform in keeping the old voters for different genders.
-
-```{r}
-# object <- anim_prep_cat(data = aeles,
-#                         id = id,
-#                         values = party,
-#                         time = year,
-#                         color = gender,
-#                         order = NULL,
-#                         time_dependent = FALSE)
-# 
-# # subset can be either "top", "bottom" or values in the data
-# # many_one not working yet
-# 
-# p <- wallaby_plot(object = object,
-#                   group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-#                   shade_palette = RColorBrewer::brewer.pal(9, "Set1"),
-#                   rendering = "ggplot",
-#                   subset = "top",
-#                   relation = "one_many",
-#                   height = 1,
-#                   size = 3,
-#                   width = 100,
-#                   total_point = 1000)
-# 
-# p2 <- anim_animate(p)
-# 
-# gganimate::animate(p2)
+```{r, eval=FALSE}
+gganimate::anim_save("figures/exit.gif", p2, height = 8, fps = 30,
+                     nframes = 400, width = 9, units = "in", res = 150)
 ```
 
-<!-- To look for the flow between group, one of the most common tools we look at is sankey chart.
-It represent the movement of the values from one set to another.
-However, with the static sankey, the only information presented are what is the proportion of the movement, and which states the quantities move to, this often enough in explaining the flow and helps making the decision necessary.
-To present more information, color could be used to represent the demographic of the group.
-What if the information that are interesting lies in the times domain, how could the plot captured that information?
+``` r
+gganimate::animate(p2)
+```
 
-!!general sankey plot and sankey with color
+```{r osiris-figure, fig.cap = "The animate visualization shows the companies that exited the market.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+knitr::include_graphics("figures/animation-exit.png")
+```
 
-The technique that is created by Hans, Ola, and Anna Rosling in 2003 is called Gapminder Trendalyzer.
-Its add an additional dimensions which are the bubble size, animated over changes in a fourth dimension, time.
-The animation in this tools has created a new way for people to analyse and visualize the trend.
+```{r osiris-gif, out.extra="class = 'gif'", fig.cap = "The animate visualization shows the companies that exited the market.", eval=knitr::is_html_output()}
+knitr::include_graphics("figures/exit.gif")
+```
 
-!!read effectiveness of animation in trend visualization, then add more information to above paragraph
+From the plot, a higher proportion of US companies have exited the market, confirming the OECD report (@oecd_report) that the United States has a higher turnover rate than Japan.
+An interesting finding is that all of the top 25% of companies that exited the market are only from the United States.
+It may be due to the absence of Japanese companies in the top 25% in 2006, or it could be that Japanese companies in the top 25% did not delist.
 
-The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world.
-This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.-->
+## Voter behaviour
 
-<!-- # Operation and data type abstraction
+The Australian Election Study data was collected from ADA Dataverse (@aeles).
+The dataset included in the `animbook` package contains 1,468 rows and 4 variables of information: ID, year, party, and gender.
+This dataset comprises survey responses from the 2019 election.
+The year column was transformed from the two different questions to answer the question, based on the 2016 Australian election results, how the top party performs in keeping the old voters for different genders.
 
-When working with the raw data, the data pre-processing is one of the important steps we need to take before further analysis is taken.
-The function in this package will offer some flexibility in the types of the variable it accepted.
-However, there are still some restrictions the user needs to follow.
-In this section, it will provide what are the accepted format and examples for the user the followed to reproduce the final animate plot.
+```{r, echo=TRUE}
+voter <- anim_prep_cat(data = aeles,
+                       id = id,
+                       values = party,
+                       time = year,
+                       color = gender,
+                       order = NULL,
+                       time_dependent = FALSE)
 
-The data set that will be used in this section and in all of the examples of this paper is collected from Bureau van Dijk.
-The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world.
-From the raw data, we are only interested in the ranking of the companies.
-The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
--->
+p_voter <- wallaby_plot(object = voter,
+                  group_palette = RColorBrewer::brewer.pal(9, "Set1"),
+                  shade_palette = c("#737373", "#969696", "#BDBDBD","#D9D9D9","#D9D9D9","#D9D9D9"),
+                  rendering = "ggplot",
+                  subset = "top",
+                  relation = "one_many",
+                  height = 1,
+                  size = 2,
+                  width = 100,
+                  total_point = 1000)
 
-<!-- Introduction
+p2_voter <- anim_animate(p_voter)
+```
 
-Some ideas:
+```{r, eval=FALSE}
+gganimate::anim_save("figures/voter.gif", p2_voter, height = 8, fps = 30,
+                     nframes = 400, width = 9, units = "in", res = 150)
+```
 
-- The animated plot has not been used often in the business data presentation
-- We want to see the movement of our variable of interest
-- Business data: Accounting data (sales), Marketing data (customer interest), data analysis languages data
-- Help with storytelling
-- Inspiration: The New York Times (Extensive data shows punishing reach of racism for black boys).
-The animation plot shows what demographic group between white and black boys where would end up in society.
-It could be adapted to show, based on the demographic of the company, sees the movement of where they would end up.
-In the marketing data, the demographic of the customers could tell us the story of what product they preferred.
+``` r
+gganimate::animate(p2_voter)
+```
 
-Data and Process
+```{r voter-figure, fig.cap = "The animate visualization shows how does the top party perform in keeping the old  voters for different genders.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+knitr::include_graphics("figures/animation-voter.png")
+```
 
-Some ideas:
+```{r voter-gif, out.extra="class = 'gif'", fig.cap = "The animate visualization shows how does the top party perform in keeping the old  voters for different genders.", eval=knitr::is_html_output()}
+knitr::include_graphics("figures/voter.gif")
+```
 
-- The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(unique identifier), rank(y-axis, factor variable), group(optional).
+From the animation, it is clear that individuals who identified their gender as 'others' shifted their votes from the Liberal, the leading party in 2016, to the Greens party.
+These changes could be due to the Green Party's "A FAIRER, MORE EQUAL COMMUNITY" campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.
+If the Liberal Party wishes to retain this demographic of voters, they may need to consider implementing a campaign focused on LGBTIQ+ issues.
 
-- The user can input any numerical, categorical and factor variable into the prep_anim function which will return the data in the format that the anim_plot function accepted.
-The x-axis and time index does not need to be the same as this allows for the user to reproduce the nytimes plot which is not time dependent.
-For the rank variable, no matter what the type of variable is in, it will return numerical variable.
+# Summary
 
-When working with the raw data, the data pre-processing is one of the important steps we need to take before further analysis is taken.
-The function in this package will offer some flexibility in the types of the variable it accepted.
-However, there are still some restrictions the user needs to follow.
-In this section, it will provide what are the accepted format and examples for the user the followed to reproduce the final animate plot.
+Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences.
+In the current version of `animbook`, the feature to have different speed for each observation have not yet been implemented.
+This feature will introduce a new dimension that allows the users to explore the data further.
 
-The data set that will be used in this section and in all of the examples of this paper is collected from Bureau van Dijk.
-The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world.
-From the raw data, we are only interested in the ranking of the companies.
-The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
-
-- The data structure
-- The steps for the user
-- How does the function processes the data
--->
+This paper is based on the 0.0.0.9 version of the `animbook` package. This version is available on [GitHub](https://github.com/KrisanatA/animbook).

### 2023-10-26 animbook-journal.tex
pdf version of figure now sized
paper 1st version

@@
 The ``zombie companies'' are generally defined as companies with an interest coverage ratio of less than one for a period of more than three years.
-However, there is a simpler and more easily understandable way to show these concepts by visualizing the new listings (enters) and the de-listing (exits) of publicly traded companies on a country-by-country basis.
-This visualization method makes it clear that the concepts of zombie companies are not unique to Japan, as indicated in the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a faster metabolize (more new listings and exits) relative to Japan.
+These companies are taking space in the market but adding no life to the economy.
+There could be other movement patterns, beyond zombies, that are interesting, such as companies that suddenly become very successful, or in politics voters who switch party affiliation between elections.
+Viewing changes between categories over time is an interesting challenge for visualization.
 
-The visualization above can also be thought of as a movement between groups, which is how many companies have entered the market and how many have exited the market.
-One example of this visualization is from The New York Times article ``Extensive data shows punishing reach of racism for black boys'' (Badger et al.
-(2018)).
-The animation portrays the trajectory of how boys with different demographics could land up in society.
-It can be adapted to our problems by capturing the movement between the groups over a specific period.
+The New York Times provided a possible solution in the article ``Extensive data show punishing reach of racism for black boys'' (Badger et al.
+(2018)) to tell the story of how racism appears to inhibit socioeconomic change.
+This approach can be adapted to address the zombie problem by capturing the movement between groups over a specific period.
 
@@
 Animation can be used as a tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the audience.
-Based on Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.
-It also requires the designer to understand how people learn.
-The cognitive theory of multimedia learning (Mayer (2005)) will be considered during the designing period.
 
-The challenge of the New York Times article animation was the amount of code needed to reproduce.
+The challenge in reproducing the New York Times article animation was the amount of code required.
 Additionally, the business data may or may not have the same information as the one in the article.
-These two purposes establish the objective for creating the R package that could generalize the animation to a wider range of data.
+These considerations establish the objective for creating the R package that could generalize the animation to a wider range of data.
 
 The structure of this paper will consist of both the visualization design and software design.
-The first section will explain about the animation in The New York Times article.
-Secondly, what are the expected data to be input into the plot, and how it is processed.
-The third section is about the animation tools, for example, \textbf{gganimate} (Pedersen and Robinson (2020)) and \textbf{plotly} (Sievert (2020)).
-The next section will be about the design of the package and visualization.
-The last two sections explore the usage of the R package and the application.
+The first section will explain the animation in The New York Times article and why it might be relevant to the problems.
+Secondly, what is the expected data to be input into the plot, and how it is processed.
+The third section is about the animation tools, followed by the section on package and visualization design.
+The last two sections explore the usage of the R package and the application to other types of data.
 
@@
 
-The flow chart featured in one of the New York Time articles unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the Chetty et al.
+The flow chart featured in one of the New York Times articles unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the Chetty et al.
 (2020).
@@
 This dynamics visualization constructs questions on the broader use of this visualization to other types of data.
-As mentioned in the introduction, one of the data that will make use of this is accounting data.
-Additionally, the marketing data that exhibits the movement of customers shifting the product interest to another competitor can be valuable insight into the data.
-It could be extended to incorporate demographic information of the customers.
-It would allow the marketing analyst to gain a significant understanding of both the company's products and the overall market.
-This also applies to the election data for the analyst to consolidate the campaign for their political party.
+The potential use of this visualization on accounting data is to convey a message, as reported by the McGowan, Andrews, and Millot (2017), that the concept of zombie companies is not unique to Japan alone.
+It is also present in the United States, which has a faster metabolize rate (more new listings and exits) relative to Japan.
+
+The political data that exhibits the movement of voters switching party affiliations between elections can be a valuable insight into the behavior of the voters.
+This data could be extended to incorporate demographic information about the voters, providing analysts with a significant insight into voter behavior.
+This allows them to consolidate effective campaigns for their political party.
+This also applies to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.
 
@@
 On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins.
-For the animation in this paper, the programming languages that will be used for recreating and revising the visualization done by The New York Times articles is R (R Core Team (2021)).
+For the animation in this paper, the programming language that will be used for recreating and revising the visualization done by The New York Times articles is R (R Core Team (2021)).
 
@@
 
-The accounting data that will be used in this section and in most of the examples for this paper was collected from Bureau van Dijk (reference).
-This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide.
-The only variables of interest from this data set are ID, year, country, and sales.
-A subset version of this data set, which only contained variables of interest from 2006 to 2018, is included in this package.
+\begin{figure}
 
-Now that the tidy data concept is established and the example data is introduced, let's explore how the data got transformed.
-As seen in the visualization, each observation is classified into a group.
-In the accounting data, however, it is represented in a numerical form instead of categories.
-The numerical value needs to be somehow mapped to a category.
+{\centering \includegraphics[width=1\linewidth]{figures/data-diagram}
+
+}
+
+\caption{The diagram shows what are the expected data forms.}\label{fig:data-diagram}
+\end{figure}
+
+In the data structure, there are requirements that must be followed for reproducing the animation.
+The data must have ID and time variables.
+These form what we call a unique ID.
+Also, the values variable can be either a numerical or categorical variable.
+The type of this variable will determine the stage the data set is in.
+This format ensures that during the data pre-processing, the R function understands what needs to be done with the data.
+
+Figure \ref{fig:data-diagram} shows which stages the data is in, given the type of values variable.
+Start with the raw data structure.
+The values are presented in the numerical format.
+It is referred to as `raw' because, in the New York Times animation, it is expressed in the categorical format.
+However, in most cases, the data is in numerical values and requires transformation.
+The second form is categorized data, as mentioned earlier, which involves transforming numerical into categories.
+This transformation may not be necessary if it already exists in the categorized format, as in the case of political data (party affiliation).
+The last form is animated data, where the frame is assigned to each unique ID.
+
+\hypertarget{animation-tools}{%
+\section{Animation tools}\label{animation-tools}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figures/animation-diagram}
+
+}
+
+\caption{The diagram shows how the animation is done using the successive pictures.}\label{fig:animation-diagram}
+\end{figure}
+
+The principle underlying the animation is called persistence of vision (Webster (2005)).
+When an image disappears, the brain will retain the previous images for a brief period of time.
+It is this slight period of retention that allows humans to separate sequential images.
+If this is seen in quick succession, it will appear as if the objects are in motion.
+This is illustrated in Figure \ref{fig:animation-diagram}.
+There are multiple ways to create an animation in the R environment (R Core Team (2021)), including packages like \texttt{gganimate} and \texttt{plot}.
+
+The \texttt{gganimate} package (Pedersen and Robinson (2020)) is an extension from the \texttt{ggplot2} package (Wickham (2016)) to include the description of an animation.
+It added new grammar classes to the plot object, allowing it to understand how the plot should change over time.
+The use of \texttt{transition\_*()} functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time.
+The output from the \texttt{gganimate} can be rendered or saved in multiple formats.
+This includes \texttt{gifski\_renderer()} from the \texttt{gifski} package (Ooms (2023b)) to save the animation in GIF format or \texttt{av\_renderer()} from the \texttt{av} package (Ooms (2023a)) to save it into a video file format.
+
+Plotly is a graphing library that provides tools for creating an interactive plot in multiple programming languages, such as R, JavaScript, Python, and Julia.
+In R, plotly can be accessed through the \texttt{plotly} package (Sievert (2020)), which integrates plotly.js from the JavaScript graphing library.
+The usage of this library can be from a converting function, \texttt{ggplotly()}, or a standalone function, \texttt{plot\_ly()}.
+The conversion is accomplished by taking the elements from the \texttt{ggplot} object and then redrawing them using the plotly.js.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figures/animated-diagram}
+
+}
+
+\caption{The diagram shows how the frames were used in the animated plot.}\label{fig:animated-diagram}
+\end{figure}
+
+In the context of data, as shown in Figure \ref{fig:animated-diagram}, observations are positioned at specific points in time.
+The further the distance between these points, the less smooth the animation becomes.
+This issue can be eliminated by interpolating additional points in between the observations.
+In the \texttt{gganimate} package, the interpolation is achieved using the \texttt{tweenr} package (Pedersen (2022)), while in \texttt{plotly}, it utilizes d3.interpolate (Bostock (2012)).
+
+Figure \ref{fig:animated-diagram} demonstrates how the frame variables are applied in an animated plot.
+The frame variable within the animated data structure allows the animation function to determine the position of observations on the plot at any given frame.
+
+\hypertarget{visualization-design}{%
+\section{Visualization design}\label{visualization-design}}
+
+The animated visualization can be an effective communication tool (Mayer and Moreno (2002); Robertson et al.
+(2008)).
+It helps with communicating complex data, enhancing the narrative, and keeping it engaged for the audience.
+According to Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.
+
+According to Mayer (2005), designing multimedia requires the designer to understand how people learn.
+One of the principles in Mayer (2005), Redundancy, suggests that a piece of excess information could overload the learners.
+By this principle, the animation must be carefully designed to avoid this pitfall.
+
+From the New York Times animation, multiple information are shown in the visualization.
+It includes points in motion, distribution at the end, and proportional counters.
+However, this could lead to information overload (Mayer (2005)).
+Therefore, the distribution at the end and proportional counters are excluded.
+Instead, the new element has been integrated, proportional shaded areas.
+It displays the proportion of observation within each group.
+
+\begin{figure}
+\includegraphics[width=0.5\linewidth]{figures/sigmoid-shade} \includegraphics[width=0.5\linewidth]{figures/sine-shade} \caption{The plot shows the difference between the sigmoid and sine curves.}\label{fig:proportional-shade}
+\end{figure}
+
+As mentioned in the Animation tools section, the paths of observations are getting interpolated.
+These functions only generate a linear path between points.
+However, linear paths may not be suitable for creating proportional shading, as they do not accurately represent the proportions.
+Non-linear curves like the sigmoid curves should be considered instead, as they provide a better display of proportions.
+These curves are commonly used in multiple Sankey diagrams, but there is a limitation on this shape.
+The issue is shown in Figure \ref{fig:proportional-shade}.
+While it does accurately represent the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation (Shaffer (2019)).
+
+\hypertarget{software}{%
+\section{Software}\label{software}}
+
+\hypertarget{installation}{%
+\subsection{Installation}\label{installation}}
+
+You can install the development version of animbook from \href{https://github.com/KrisanatA/animbook}{GitHub} with:
+
+\begin{verbatim}
+# install.packages("devtools")
+devtools::install_github("KrisanatA/animbook")
+\end{verbatim}
+
+\hypertarget{overviw-of-functions}{%
+\subsection{Overviw of functions}\label{overviw-of-functions}}
+
+In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
+The first step is to turn the data into the right format for the plot function.
+The next stage is to create a ggplot object, which can then be inputted into the animation function.
+The last step is adding the animation settings to the ggplot object so the user can animate the plot using the \texttt{gganimate::animate()} function.
+The reason for this three-step process is that it allows the user who does not have a lot of experience to reproduce the animation while keeping the customization for an experienced user.
+
+\hypertarget{data-preprocessing}{%
+\subsubsection{Data preprocessing}\label{data-preprocessing}}
+
+From Figure \ref{fig:data-diagram}, there is a need to map numerical value to a category.
 One way to handle this is by ranking the sales and grouping the rankings into quantiles.
 In some cases, this may not be the best option.
-As the observation is moved up by quantiles, one is bound to move down.
-It can be resolved by using an alternative method, which is grouping values based on their absolute values.
+When the observation is moved up by quantile, one is bound to move down.
+This issue can be resolved by using an alternative method, which is grouping values based on their absolute values.
 Users may also be interested in grouping the data based on different demographics, for example, ranking within a specific country.
-This generalization leads to a total of four scaling methods for the numerical data.
+This generalization leads to four different scaling methods for the numerical data.
 
@@
 #> # A tibble: 12 x 4
-#>    ID           year    sales country
+#>    id     time values gp   
 #>    <fct> <int>  <dbl> <fct>
-#>  1 AU004085330  2007  1043282 AU     
-#>  2 AU004085330  2006   846245 AU     
-#>  3 AU009134114  2006    67842 AU     
-#>  4 AU009134114  2007    47868 AU     
-#>  5 AU009219809  2007   326335 AU     
-#>  6 AU009219809  2006   218384 AU     
-#>  7 US161229730  2007     5991 US     
-#>  8 US161229730  2006     4308 US     
-#>  9 US470731996  2007  8126500 US     
-#> 10 US470731996  2006  7205000 US     
-#> 11 US751825172  2007 22935000 US     
-#> 12 US751825172  2006 22563000 US
+#>  1 1      2020  4255. X    
+#>  2 1      2023  3357. X    
+#>  3 14     2020  6763. X    
+#>  4 14     2023  1197. X    
+#>  5 100    2020  6864. X    
+#>  6 100    2023  2321. X    
+#>  7 21     2020   698. Y    
+#>  8 21     2023  3970. Y    
+#>  9 106    2020  4110. Y    
+#> 10 106    2023  2866. Y    
+#> 11 148    2020  7174. Y    
+#> 12 148    2023  4217. Y
 \end{verbatim}
@@
 #> # A tibble: 12 x 4
-#>    id           time qtile country
-#>    <fct>       <int> <dbl> <fct>  
-#>  1 AU004085330  2006     2 AU     
-#>  2 AU004085330  2007     2 AU     
-#>  3 AU009134114  2006     3 AU     
-#>  4 AU009134114  2007     3 AU     
-#>  5 AU009219809  2006     3 AU     
-#>  6 AU009219809  2007     2 AU     
-#>  7 US161229730  2006     4 US     
-#>  8 US161229730  2007     4 US     
-#>  9 US470731996  2006     1 US     
-#> 10 US470731996  2007     1 US     
-#> 11 US751825172  2006     1 US     
-#> 12 US751825172  2007     1 US
+#>    id     time qtile gp   
+#>    <fct> <int> <int> <fct>
+#>  1 1      2020     3 X    
+#>  2 1      2023     2 X    
+#>  3 14     2020     2 X    
+#>  4 14     2023     4 X    
+#>  5 100    2020     2 X    
+#>  6 100    2023     3 X    
+#>  7 21     2020     5 Y    
+#>  8 21     2023     2 Y    
+#>  9 106    2020     3 Y    
+#> 10 106    2023     3 Y    
+#> 11 148    2020     2 Y    
+#> 12 148    2023     1 Y
 \end{verbatim}
@@
 #> # A tibble: 12 x 4
-#>    id           time qtile country
-#>    <fct>       <int> <dbl> <fct>  
-#>  1 AU004085330  2006     5 AU     
-#>  2 AU004085330  2007     5 AU     
-#>  3 AU009134114  2006     5 AU     
-#>  4 AU009134114  2007     5 AU     
-#>  5 AU009219809  2006     5 AU     
-#>  6 AU009219809  2007     5 AU     
-#>  7 US161229730  2006     5 US     
-#>  8 US161229730  2007     5 US     
-#>  9 US470731996  2006     4 US     
-#> 10 US470731996  2007     4 US     
-#> 11 US751825172  2006     1 US     
-#> 12 US751825172  2007     1 US
+#>    id     time qtile gp   
+#>    <fct> <int> <int> <fct>
+#>  1 1      2020     3 X    
+#>  2 1      2023     4 X    
+#>  3 14     2020     2 X    
+#>  4 14     2023     5 X    
+#>  5 100    2020     2 X    
+#>  6 100    2023     4 X    
+#>  7 21     2020     5 Y    
+#>  8 21     2023     4 Y    
+#>  9 106    2020     3 Y    
+#> 10 106    2023     4 Y    
+#> 11 148    2020     2 Y    
+#> 12 148    2023     3 Y
 \end{verbatim}
@@
 #> # A tibble: 12 x 4
-#>    id           time qtile country
-#>    <fct>       <int> <dbl> <fct>  
-#>  1 AU004085330  2006     4 AU     
-#>  2 AU004085330  2007     4 AU     
-#>  3 AU009134114  2006     4 AU     
-#>  4 AU009134114  2007     4 AU     
-#>  5 AU009219809  2006     4 AU     
-#>  6 AU009219809  2007     4 AU     
-#>  7 US161229730  2006     4 US     
-#>  8 US161229730  2007     3 US     
-#>  9 US470731996  2006     1 US     
-#> 10 US470731996  2007     1 US     
-#> 11 US751825172  2006     1 US     
-#> 12 US751825172  2007     1 US
+#>    id     time qtile gp   
+#>    <fct> <int> <int> <fct>
+#>  1 1      2020     3 X    
+#>  2 1      2023     2 X    
+#>  3 14     2020     2 X    
+#>  4 14     2023     5 X    
+#>  5 100    2020     2 X    
+#>  6 100    2023     3 X    
+#>  7 21     2020     5 Y    
+#>  8 21     2023     2 Y    
+#>  9 106    2020     3 Y    
+#> 10 106    2023     3 Y    
+#> 11 148    2020     2 Y    
+#> 12 148    2023     1 Y
 \end{verbatim}
@@
 \item
-  Fix bins relative to absolute values by year within a group (bug in code).
+  Fix bins relative to absolute values by year within a group.
 \end{enumerate}
@@
 #> # A tibble: 12 x 4
-#>    id           time qtile country
-#>    <fct>       <int> <dbl> <fct>  
-#>  1 AU004085330  2006     5 AU     
-#>  2 AU004085330  2007     5 AU     
-#>  3 AU009134114  2006     5 AU     
-#>  4 AU009134114  2007     5 AU     
-#>  5 AU009219809  2006     5 AU     
-#>  6 AU009219809  2007     5 AU     
-#>  7 US161229730  2006     5 US     
-#>  8 US161229730  2007     5 US     
-#>  9 US470731996  2006     4 US     
-#> 10 US470731996  2007     4 US     
-#> 11 US751825172  2006     1 US     
-#> 12 US751825172  2007     1 US
+#>    id     time qtile gp   
+#>    <fct> <int> <int> <fct>
+#>  1 1      2020     3 X    
+#>  2 1      2023     4 X    
+#>  3 14     2020     2 X    
+#>  4 14     2023     5 X    
+#>  5 100    2020     2 X    
+#>  6 100    2023     4 X    
+#>  7 21     2020     5 Y    
+#>  8 21     2023     3 Y    
+#>  9 106    2020     3 Y    
+#> 10 106    2023     4 Y    
+#> 11 148    2020     2 Y    
+#> 12 148    2023     3 Y
 \end{verbatim}
@@
 The \texttt{seq()} function takes input values from the minimum and maximum values and increments by equal steps depending on the number of groups of interest.
+Additionally, the users have the option to specify the breaks themselves if they choose to do so.
 
-\begin{figure}
-\includegraphics[width=40.33in]{figures/data-diagram} \caption{The data transformation diagram.}\label{fig:data-diagram}
-\end{figure}
+These are only the initial steps in formatting the data into a category.
+Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animated data structure.
+It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values.
+It lets the \texttt{gganimate} or \texttt{plotly} to perceive where the observation would be on the plot at a given frame as seen in the \ref{fig:animated-diagram}.
 
-Based on Figure \ref{fig:data-diagram}, these are only the initial steps in formatting the data into a category.
-Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animbook data structure.
-It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values.
-Its lets the \textbf{gganimate} or \textbf{plotly} to perceive where the observation would be on the plot at a given frame.
-
-The frame variable is assigned by sorting the data based on the id and time using the \texttt{arrange()} function, followed by applying the \texttt{group\_by()} function on the id, allowing the \texttt{row\_number()} function to be performed within each group.
+The frame variable is assigned by sorting the data based on the ID and time using the \texttt{arrange()} function, followed by applying the \texttt{group\_by()} function on the ID, allowing the \texttt{row\_number()} function to be performed within each group.
 The functions mentioned in this paragraph are from the \texttt{dplyr} packages (Wickham et al.
@@
 
-\hypertarget{animation-tools}{%
-\section{Animation tools}\label{animation-tools}}
+All of the pre-processing steps mentioned above are completed using the \texttt{anim\_prep()} or \texttt{anim\_prep\_cat()} function, depending on the stages of the data structure.
+The \texttt{anim\_prep()} function is used for raw data format, while the \texttt{anim\_prep\_cat()} function is for categorized data format.
+There are additional arguments that facilitate the users for more customization.
 
-Literature review of animation tools
-
-\hypertarget{visualization-design}{%
-\section{Visualization design}\label{visualization-design}}
-
-This explains how to get from data to the animations, including different sorts of plots.
-
-\hypertarget{software}{%
-\section{Software}\label{software}}
-
-\hypertarget{installation}{%
-\subsection{Installation}\label{installation}}
-
-\hypertarget{overview-of-functions}{%
-\subsection{Overview of functions}\label{overview-of-functions}}
-
-In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
-The first step is to turn the data into the right format for the plot function.
-The next stage is to create a ggplot object, which can then be inputted into the animation function.
-The last step is adding the animation settings to the ggplot object so the user can animate the plot using the \texttt{gganimate::animate()} function.
-The reason for this three-step process is that it allows the user who does not have a lot of experience to reproduce the animation while keeping the customization for an experienced user.
-
-\hypertarget{prepare-the-data}{%
-\subsubsection{Prepare the data}\label{prepare-the-data}}
-
-The first step can be done using the \texttt{anim\_prep()} function.
-This function required that the user data contained ID, which is used to identify each individual observation, values, which are numerical values to be used to group the observation together, and time, the variable associated with the changes of the observation.
-In the cases when the users already have the values as a group variable, the \texttt{anim\_prep\_cat()} function can then be used instead.
-
-The additional options for the \texttt{anim\_prep()} that allow for more customization to the data structure or the plot are as follows:
+For the \texttt{anim\_prep()} function, the arguments are as follows:
 
 \begin{itemize}
-\tightlist
 \item
-  label: group labeling.
+  data: A data frame containing the data to be prepared for visualization.
 \item
-  ngroup: number of groups we want to split the values into.
+  id: The column name that represents the unique identifier variable.
 \item
-  breaks: the group bins' size
+  values: The column name that contains the numeric values to be visualized.
 \item
-  group\_scaling: the grouping variable for the bins calculations.
+  time: The column name represents the time variable.
 \item
-  color: the variable used to color the observations.
+  label: A vector of labels to be used for the y-axis in the visualization.
 \item
-  time\_dependent: logical. Whether we want the observations to start at the same time or not.
+  ngroup: The number of groups or categories to create for scaling values.
 \item
-  scaling: the scaling method, either \texttt{rank} or \texttt{absolute}.
+  breaks: A vector of breaks for creating bins.
 \item
-  runif\_min: minimum value for random addition to frame numbers
+  group\_scaling: The column name that represents the grouping variable.
 \item
-  runif\_max: maximum value for random addition to frame numbers
+  color: The column name to be used in ggplot2::aes() for the plot function.
+\item
+  time\_dependent: Logical. Should the visualization be time-dependent? Default is TRUE.
+\item
+  scaling: The scaling method to be used; ``rank'' or ``absolute.''
+\item
+  runif\_min: The minimum value for random addition to frame numbers.
+\item
+  runif\_max: The maximum value for random addition to frame numbers.
+
+  For the \texttt{anim\_prep\_cat()} function, the arguments are as follows:
+\item
+  data: A data frame containing the data to be prepared for visualization.
+\item
+  id: The column name that represents the unique identifier variable.
+\item
+  values: The column name that contains the numeric values to be visualized.
+\item
+  time: The column name represents the time variable.
+\item
+  label: A vector of labels to be used for the y-axis in the visualization.
+\item
+  order: A vector of order for sorting the category values.
+\item
+  color: The column name to be used in ggplot2::aes() for the plot function.
+\item
+  time\_dependent: Logical. Should the visualization be time-dependent? Default is TRUE.
+\item
+  runif\_min: The minimum value for random addition to frame numbers.
+\item
+  runif\_max: The maximum value for random addition to frame numbers.
 \end{itemize}
 
-Using the different combinations of the additional options, the users could end up with four different scales, as mentioned in the \ref{data} section.
+\hypertarget{plotting-function}{%
+\subsubsection{Plotting function}\label{plotting-function}}
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  Rank scaling
-\item
-  Absolute scaling
-\item
-  Rank scaling by group
-\item
-  Absolute scaling by group
-\end{enumerate}
-
-For the \texttt{anim\_prep\_cat()} function, the additional options are:
+Once the data is prepared.
+The next step is to create the \texttt{ggplot} object as a basis for the animation.
+There are three plots available in this package.
+Two of the plots could be used for the animation, and another plot is used as a static visualization.
+All of the plots have an internal function that converts the standard data format into the required structure for each plotting function.
 
 \begin{itemize}
-\tightlist
-\item
-  label: group labeling.
-\item
-  order: the ordering of the group.
-\item
-  color: the variable used to color the observations.
-\item
-  time\_dependent: logical. Whether we want the observations to start at the same time or not.
-\item
-  runif\_min: minimum value for random addition to frame numbers
-\item
-  runif\_max: maximum value for random addition to frame numbers
-\end{itemize}
-
-Both the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} functions will return the ``animbook'' object containing a list of the standard format data and settings.
-
-\hypertarget{plotting-the-data}{%
-\subsubsection{Plotting the data}\label{plotting-the-data}}
-
-Once the data is prepared.
-The next step is to create the ggplot object as a basis for the animation.
-There are three plots available in this package.
-Two of the plots could be used for the animation, and another plot is used as a static visualization.
-
-\begin{itemize}
-\tightlist
 \item
@@
   \texttt{funnel\_web\_plot()}: the faceted static plot by time variable.
+
+  The main focus of this paper will be on the \texttt{wallaby\_plot()}, which draws inspiration from the New York Times animation and combines the knowledge gained from the previous sections in creating the visualization.
+
+  The \texttt{wallaby\_data()} function is responsible for performing data manipulation and formatting tasks on the original object.
+It includes creating additional data components for labeling and shading.
+This function also responds by interpolating the non-linear path.
+It performs this task by mapping the \texttt{sine()} function provided in this package to each observation using the \texttt{map()} function from the \texttt{purrr} package (Wickham and Henry (2023)).
+The frame is recalculated using the same method mentioned in the data preprocessing section.
+The \texttt{sankey\_shade()} function is called to generate the proportional shaded data.
 \end{itemize}
 
-All of the plots have an internal function that converts the standard data format into the required structure for each plotting function.
+\begin{figure}
+\includegraphics[width=0.5\linewidth]{figures/sankey-shade-1} \includegraphics[width=0.5\linewidth]{figures/sankey-shade-2} \caption{The plot shows how does the algorithm work.}\label{fig:shade-algorithm}
+\end{figure}
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Kangaroo's plot
-\end{enumerate}
+The algorithm behind the \texttt{sankey\_shade()} function is illustrated in Figure \ref{fig:shade-algorithm}.
+It started by calculating the corner points for all of the shaded areas.
+Then, use the \texttt{sine()} function to interpolate the point between the left and right.
 
-\includegraphics[width=0.7\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-13-1}
+Now that the data are in the right format for the wallaby's plot, the \texttt{geom\_point()} function is used for plotting the observations, \texttt{geom\_polygon()} is used for creating the proportional shaded areas, and \texttt{geom\_text()} is used for creating labels.
+These three functions are from the \texttt{ggplot2} package (Wickham (2016)).
+During this process, the aesthetics mapping will be different depending on the rendering tool to be used, which can be either \texttt{gganimate} or \texttt{plotly}.
+The difference between the two rendering tools is that for \texttt{plotly}, the \texttt{ids} and \texttt{frame} arguments need to be specified during the creation of the \texttt{ggplot} object.
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  Wallaby's plot
-\end{enumerate}
+The arguments for Wallaby's plot are as follows.
+- object: The animbook object returned from the prep function.
+- group\_palette: The vector of the palette used by the function to supply the color to each group.
+- shade\_palette: The vector of the palette used by the function to supply the color to the shaded area.
+- rendering: The choice of method used to create and display the plot, either gganimate or plotly.
+- subset: A character string specifying the variable used for subsetting the data. The ``top'' and ``bottom'' strings can also be used in this argument.
+- relation: The choice of relationship for the values to display on the plot, either ``one\_many.'' or ``many\_one.''
+- total\_point: The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.
+- height: The proportion of the area occupied by the observations in the shaded areas.
+- width: The distance between the first and last observation in the animation.
+- size: The point size.
+- alpha: The opacity of the proportional shaded areas.
 
-\includegraphics[width=0.7\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-14-1}
+\hypertarget{animating-function}{%
+\subsubsection{Animating function}\label{animating-function}}
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Funnel web spider's plot
-\end{enumerate}
-
-\includegraphics[width=0.7\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-15-1}
-
-\hypertarget{animating-the-plot}{%
-\subsubsection{Animating the plot}\label{animating-the-plot}}
-
-To animate the plot, the plot need to be save as an object before passed on to the final function \texttt{anim\_animate()}.
+It is necessary to save the plot as a \texttt{ggplot} object before passing it to the final function, \texttt{anim\_animate()}, to animate.
+This function will automatically detect which rendering method was specified in the previous steps and add the minimum requirement functions accordingly.
+By default, if the user specifies the rendering as \texttt{gganimate}, then it will add the \texttt{transition\_time()} function from the \texttt{gganimate} package (Pedersen and Robinson (2020)).
+Otherwise, the \texttt{animation\_opts()} function will be added from the \texttt{plotly} package (Sievert (2020)).
 
@@
 \subsection{Example usage}\label{example-usage}}
+
+Step 1: Prepare the data
+
+\begin{verbatim}
+animbook <- anim_prep_cat(cat_change, 
+                          id = id, 
+                          values = qnt, 
+                          time = time, 
+                          color = gp, 
+                          time_dependent = FALSE)
+
+head(animbook$data, 10)
+\end{verbatim}
+
+\begin{verbatim}
+#> # A tibble: 10 x 5
+#>    id     time qtile frame color
+#>    <fct> <int> <dbl> <dbl> <fct>
+#>  1 1      2020     5    37 X    
+#>  2 1      2023     5    38 X    
+#>  3 2      2020     5    42 X    
+#>  4 2      2023     5    43 X    
+#>  5 3      2020     5     9 X    
+#>  6 3      2023     5    10 X    
+#>  7 4      2020     5    27 X    
+#>  8 4      2023     5    28 X    
+#>  9 5      2020     5    20 X    
+#> 10 5      2023     5    21 X
+\end{verbatim}
+
+\begin{verbatim}
+str(animbook)
+\end{verbatim}
+
+\begin{verbatim}
+#> List of 2
+#>  $ data    : tibble [400 x 5] (S3: tbl_df/tbl/data.frame)
+#>   ..$ id   : Factor w/ 200 levels "1","2","3","4",..: 1 1 2 2 3 3 4 4 5 5 ...
+#>   ..$ time : int [1:400] 2020 2023 2020 2023 2020 2023 2020 2023 2020 2023 ...
+#>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
+#>   ..$ frame: num [1:400] 37 38 42 43 9 10 27 28 20 21 ...
+#>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
+#>  $ settings:List of 7
+#>   ..$ gap           : num 0.1
+#>   ..$ xbreaks       : int [1:2] 2020 2023
+#>   ..$ label         : chr [1:5] "A" "B" "C" "D" ...
+#>   ..$ order         : chr [1:5] "A" "B" "C" "D" ...
+#>   ..$ time_dependent: logi FALSE
+#>   ..$ runif_min     : num 1
+#>   ..$ runif_max     : num 50
+#>  - attr(*, "class")= chr "animbook"
+\end{verbatim}
+
+Step 2: Plotting the data
+
+\begin{verbatim}
+p <- wallaby_plot(object = animbook,
+             group_palette = RColorBrewer::brewer.pal(9, "Set1"),
+             shade_palette = c("#737373", "#969696", "#BDBDBD","#D9D9D9","#D9D9D9","#D9D9D9"),
+             rendering = "ggplot",
+             subset = "top",
+             relation = "one_many",
+             total_point = NULL)
+
+p
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-8-1} \end{center}
+
+Step 3: Animating the plot
+
+\begin{verbatim}
+p2 <- anim_animate(p)
+
+gganimate::animate(p2)
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figures/animation-example}
+
+}
+
+\caption{Animate visualization using example data.}\label{fig:catchange-figure}
+\end{figure}
 
@@
 
-\hypertarget{voter-behavior}{%
-\subsection{Voter behavior}\label{voter-behavior}}
+The accounting Osiris data that will be used in this section was collected from Bureau van Dijk ({``Osiris''} (n.d.)).
+This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide.
+The only variables of interest from this data set are ID, year, country, and sales.
+A subset version of this data set, which only contained variables of interest from 2006 to 2018, is included in this package.
 
-Based on the 2016 Australian election results, how does the top party perform in keeping the old voters for different genders.
+As mentioned in the OECD report (McGowan, Andrews, and Millot (2017)), the United States has a faster metabolize rate relative to Japan company.
+An animation will be created using the \texttt{animbook} package to enhance communication with data.
+
+First, filter the countries to include only the United States and Japan.
+Then, prepare the Osiris data using the \texttt{anim\_prep} function with the first scaling, which is a ranking method.
+Next, use the \texttt{wallaby\_plot} function to create a \texttt{ggplot} object and add default settings for \texttt{gganimate} rendering.
+
+\begin{verbatim}
+data <- osiris |> 
+  filter(country %in% c("US", "JP"))
+
+label <- c("Top 25%", "25-50", "50-75", "75-100", "Not listed")
+
+accounting <- anim_prep(data, 
+                      id = ID, 
+                      values = sales, 
+                      time = year, 
+                      label = label, 
+                      ngroup = 4, 
+                      color = country, 
+                      time_dependent = FALSE)
+
+p <- wallaby_plot(accounting,
+                  group_palette = RColorBrewer::brewer.pal(9, "Set1"),
+                  shade_palette = c("#737373", "#969696", "#BDBDBD","#D9D9D9","#D9D9D9","#D9D9D9"),
+                  subset = "bottom",
+                  relation = "many_one",
+                  height = 1,
+                  size = 2,
+                  width = 100,
+                  total_point = 1000)
+
+p2 <- anim_animate(p)
+\end{verbatim}
+
+\begin{verbatim}
+gganimate::animate(p2)
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figures/animation-exit}
+
+}
+
+\caption{The animate visualization shows the companies that exited the market.}\label{fig:osiris-figure}
+\end{figure}
+
+From the plot, a higher proportion of US companies have exited the market, confirming the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a higher turnover rate than Japan.
+An interesting finding is that all of the top 25\% of companies that exited the market are only from the United States.
+It may be due to the absence of Japanese companies in the top 25\% in 2006, or it could be that Japanese companies in the top 25\% did not delist.
+
+\hypertarget{voter-behaviour}{%
+\subsection{Voter behaviour}\label{voter-behaviour}}
+
+The Australian Election Study data was collected from ADA Dataverse (McAllister et al.
+(2023)).
+The dataset included in the \texttt{animbook} package contains 1,468 rows and 4 variables of information: ID, year, party, and gender.
+This dataset comprises survey responses from the 2019 election.
+The year column was transformed from the two different questions to answer the question, based on the 2016 Australian election results, how the top party performs in keeping the old voters for different genders.
+
+\begin{verbatim}
+voter <- anim_prep_cat(data = aeles,
+                       id = id,
+                       values = party,
+                       time = year,
+                       color = gender,
+                       order = NULL,
+                       time_dependent = FALSE)
+
+p_voter <- wallaby_plot(object = voter,
+                  group_palette = RColorBrewer::brewer.pal(9, "Set1"),
+                  shade_palette = c("#737373", "#969696", "#BDBDBD","#D9D9D9","#D9D9D9","#D9D9D9"),
+                  rendering = "ggplot",
+                  subset = "top",
+                  relation = "one_many",
+                  height = 1,
+                  size = 2,
+                  width = 100,
+                  total_point = 1000)
+
+p2_voter <- anim_animate(p_voter)
+\end{verbatim}
+
+\begin{verbatim}
+gganimate::animate(p2_voter)
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figures/animation-voter}
+
+}
+
+\caption{The animate visualization shows how does the top party perform in keeping the old  voters for different genders.}\label{fig:voter-figure}
+\end{figure}
+
+From the animation, it is clear that individuals who identified their gender as `others' shifted their votes from the Liberal, the leading party in 2016, to the Greens party.
+These changes could be due to the Green Party's ``A FAIRER, MORE EQUAL COMMUNITY'' campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.
+If the Liberal Party wishes to retain this demographic of voters, they may need to consider implementing a campaign focused on LGBTIQ+ issues.
+
+\hypertarget{summary}{%
+\section{Summary}\label{summary}}
+
+Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences.
+In the current version of \texttt{animbook}, the feature to have different speed for each observation have not yet been implemented.
+This feature will introduce a new dimension that allows the users to explore the data further.
+
+This paper is based on the 0.0.0.9 version of the \texttt{animbook} package. This version is available on \href{https://github.com/KrisanatA/animbook}{GitHub}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-aeles}{}}%
+McAllister, Ian, Jill Sheppard, Sarah Cameron, and Jackman Simon. 2023. {``Australian Election Study, 2022.''} ADA Dataverse. \url{https://doi.org/10.26193/W3U2S3}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-oecd_report}{}}%
 McGowan, Müge Adalet, Dan Andrews, and Valentine Millot. 2017. {``The Walking Dead?''} no. 1372. https://doi.org/\url{https://doi.org/https://doi.org/10.1787/180d80ad-en}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-av}{}}%
+Ooms, Jeroen. 2023a. \emph{Av: Working with Audio and Video in r}. \url{https://CRAN.R-project.org/package=av}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gifski}{}}%
+---------. 2023b. \emph{Gifski: Highest Quality GIF Encoder}. \url{https://CRAN.R-project.org/package=gifski}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bvd}{}}%
+{``Osiris.''} n.d. \emph{Bvd}. Bureau van Dijk. \url{https://www.bvdinfo.com/en-gb/our-products/data/international/osiris}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tweenr}{}}%
+Pedersen, Thomas Lin. 2022. \emph{Tweenr: Interpolate Data for Smooth Animations}. \url{https://CRAN.R-project.org/package=tweenr}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-effective-trend}{}}%
+Robertson, George, Roland Fernandez, Danyel Fisher, Bongshin Lee, and John Stasko.
+2008.
+{``Effectiveness of Animation in Trend Visualization.''} \emph{IEEE Transactions on Visualization and Computer Graphics} 14 (6): 1325--32.
+\url{https://doi.org/10.1109/TVCG.2008.125}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Shaffer_2019}{}}%
+Shaffer, Jeffrey. 2019. {``Sankey Diagrams: Why i Used the Sigmoid Function and Why You Probably Shouldn't.''} \emph{Data + Science}. \url{https://www.dataplusscience.com/Sigmoid.html}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-plotly}{}}%
 Sievert, Carson. 2020. {``Interactive {Web-Based} Data Visualization with r, Plotly, and Shiny.''} Chapman; Hall/CRC. \url{https://plotly-r.com}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-animation-mechanic}{}}%
+Webster, Chris. 2005. \emph{Animation : The Mechanics of Motion}. Focal Press Visual Effects and Animation Series. Oxford ; Burlington, MA: Elsevier Focal Press.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
+---------. 2016. \emph{Ggplot2: Elegant Graphics for Data Analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-dplyr}{}}%
 Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis Vaughan. 2023. \emph{Dplyr: A Grammar of Data Manipulation}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-purrr}{}}%
+Wickham, Hadley, and Lionel Henry. 2023. \emph{Purrr: Functional Programming Tools}. \url{https://CRAN.R-project.org/package=purrr}.
 
@@
 Monash University\\%
-Faculty of Business and Economics\\ Melbourne, Australia\\
+Department of Econometrics and Business Statistics\\ Melbourne, Australia\\
 %

### 2023-10-26 animbook-journal.R

@@ -2,7 +2,7 @@
 # Please edit animbook-journal.Rmd to modify this file
 
 ## ----setup, include=FALSE-----------------------------------------------------
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
 
 
 ## -----------------------------------------------------------------------------
@@ -10,204 +10,186 @@ library(animbook)
 library(tidyverse)
 
 
-## -----------------------------------------------------------------------------
-example <- osiris |> 
-  filter(country %in% c("AU", "US"),
-                between(year, 2006, 2007)) |> 
-  arrange(desc(sales)) 
-
-example |> 
-  filter(ID %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
-  reframe(ID, year, sales, country) |> 
-  arrange(ID)
-
-
-## -----------------------------------------------------------------------------
-rank <- anim_prep(example, ID, sales, year, color = country)
-
-rank$data |> 
-  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
-  rename(country = color) |> 
-  select(-frame)
-
-
-## -----------------------------------------------------------------------------
-absolute <- anim_prep(example, ID, sales, year, color = country, scaling = "absolute")
-
-absolute$data |> 
-  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
-  rename(country = color) |> 
-  select(-frame)
-
-
-## -----------------------------------------------------------------------------
-rank_group <- anim_prep(example, ID, sales, year, color = country, group_scaling = country)
-
-rank_group$data |> 
-  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
-  rename(country = group) |> 
-  select(-c(frame, color))
-
-
-## -----------------------------------------------------------------------------
-absolute_group <- anim_prep(example, ID, sales, year, color = country, group_scaling = country, scaling = "absolute")
-
-absolute_group$data |> 
-  filter(id %in% c("US751825172", "US470731996", "AU004085330", "AU009134114", "AU009219809", "US161229730")) |> 
-  rename(country = group) |> 
-  select(-c(frame, color))
-
-
[…]

### 2023-10-27 animbook-journal.Rmd
small changes to intro paragraph

@@
 
-The concept of "zombie companies" began to attract attention when an article on the proliferation of zombie companies (@zombie_companies_2008).
-The "zombie companies" are generally defined as companies with an interest coverage ratio of less than one for a period of more than three years.
-These companies are taking space in the market but adding no life to the economy.
-There could be other movement patterns, beyond zombies, that are interesting, such as companies that suddenly become very successful, or in politics voters who switch party affiliation between elections.
+The concept of "zombie companies" began to attract attention when @zombie_companies_2008 reported on their proliferation in Japan.
+Zombie companies are defined as those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy.
+We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time.
+Generally, studying movement patterns is interesting for many problems, including rocket ship startups that rapidly perform well, or in politics, to study voters who switch party affiliation between elections.
 Viewing changes between categories over time is an interesting challenge for visualization.
 
-  The New York Times provided a possible solution in the article "Extensive data show punishing reach of racism for black boys" (@the_new_york_time) to tell the story of how racism appears to inhibit socioeconomic change.
-This approach can be adapted to address the zombie problem by capturing the movement between groups over a specific period.
+The New York Times provided a possible solution in the article titled "Extensive data show punishing reach of racism for black boys" (@the_new_york_time) to tell the story of how racism appears to inhibit socioeconomic change.
+This animation is the motivation for the new visualization presented here, to be applied generally.
 

### 2023-10-27 animbook-journal.Rmd
added a screenshot of the NYT figure and tried referecing sections

@@
 bibliography: animbook-journal.bib
-
 ---
@@
 The concept of "zombie companies" began to attract attention when @zombie_companies_2008 reported on their proliferation in Japan.
-Zombie companies are defined as those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy.
+Zombie companies are those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy.
 We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time.
@@
 
-With an advancement in technology, this results in an increase in both the size and complexity of the data.
-It requires an experienced hand to convey the right messages from the data.
-However, as shown in The New York Times article (@the_new_york_time), the animation is not only created just for eye-catching graphics.
-Animation can be used as a tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the audience.
+The challenge in producing an animation like that in New York Times article animation is the transformation of the data, and connection with elements of the plot that will be animated.
+The complexities include standardizing starting times of the temporal variable, allowing for the user to choose the number of categories, standardizing distributions and allowing the user to input pre-computed categorical data.
+These considerations provide the objective for creating an R package that can generalize the animation to suitably apply to a wide range of data.
 
-  The challenge in reproducing the New York Times article animation was the amount of code required.
-Additionally, the business data may or may not have the same information as the one in the article.
-These considerations establish the objective for creating the R package that could generalize the animation to a wider range of data.
+The structure of this paper is as follows.
+Section @NYT explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
+The next section describes the expected data format, and how it is processed.
+Following this, is an explanation of available the animation tools, and how they are employed for this problem.
+A  section on the functions of the package and how the visualization is designed, demonstrate how the data is mapped to the animation.
+The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.
 
-  The structure of this paper will consist of both the visualization design and software design.
-The first section will explain the animation in The New York Times article and why it might be relevant to the problems.
-Secondly, what is the expected data to be input into the plot, and how it is processed.
-The third section is about the animation tools, followed by the section on package and visualization design.
-The last two sections explore the usage of the R package and the application to other types of data.
+# Explanation of the New York Times visualization {#NYT}
 
-# Explanation of the New York Times visualization
+```{r nyt, fig.cap="Screenshot of the New York Times animation, that is the motivation for this visualization package.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+knitr::include_graphics("figures/NYT.jpg")
+```
 
-The flow chart featured in one of the New York Times articles unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the @race.
+The interactive chart featured in the New York Times article (Figure \@ref(fig:nyt)) unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the @race.
 This visualization reveals that, compared to white children, black children are more likely to drop down to the lower-income group, given that they both grew up in wealthy families.
@@
 
+# Acknowledgements {-}
+
 This paper is based on the 0.0.0.9 version of the `animbook` package. This version is available on [GitHub](https://github.com/KrisanatA/animbook).

### 2023-10-28 animbook-journal.Rmd
second version of the paper

@@
 The structure of this paper is as follows.
-Section @NYT explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
-The next section describes the expected data format, and how it is processed.
-Following this, is an explanation of available the animation tools, and how they are employed for this problem.
-A  section on the functions of the package and how the visualization is designed, demonstrate how the data is mapped to the animation.
+The section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
+The next section describes the expected data format.
+Following this is an explanation of available animation tools, and how they are employed for this problem.
+A section on the functions of the package and how the visualization is designed, demonstrates how the data is mapped to the animation.
 The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.
@@
 ```{r nyt, fig.cap="Screenshot of the New York Times animation, that is the motivation for this visualization package.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
-knitr::include_graphics("figures/NYT.jpg")
+knitr::include_graphics("figures/NYT.png")
 ```
@@
 This is illustrated in Figure \@ref(fig:animation-diagram).
-There are multiple ways to create an animation in the R environment (@r), including packages like `gganimate` and `plot`.
+There are multiple ways to create an animation in the R environment (@r), including packages like `gganimate` and `Plotly`.
 
@@
 This issue can be eliminated by interpolating additional points in between the observations.
-In the `gganimate` package, the interpolation is achieved using the `tweenr` package (@tweenr), while in `plotly`, it utilizes d3.interpolate (@d3js).
+In the `gganimate` package (@gganimate), the interpolation is achieved using the `tweenr` package (@tweenr), while in `plotly`, it utilizes d3.interpolate (@d3js).
 
@@
 
-  Original data:
-
 ```{r}
-dbl_change |> 
+original <- dbl_change |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
@@
   arrange(gp, id)
-```
 
-  1. Ranking by year.
-
-```{r}
 rank <- anim_prep(dbl_change, id, values, time, color = gp)
 
-rank$data |> 
+rank_data <- rank$data |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
-  rename(gp = color) |> 
+  rename(gp = color,
+         rank = qtile) |> 
   select(-frame) |> 
   arrange(gp, id)
-```
 
-  2. Fix bins relative to absolute values by year.
-
-```{r}
 absolute <- anim_prep(dbl_change, id, values, time, color = gp, scaling = "absolute")
 
-absolute$data |> 
+absolute_data <- absolute$data |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |>  
-  rename(gp = color) |> 
+  rename(gp = color,
+         absolute = qtile) |> 
   select(-frame) |> 
   arrange(gp, id)
-```
 
-  3. Ranking by year within a group.
-
-```{r}
 rank_group <- anim_prep(dbl_change, id, values, time, color = gp, group_scaling = gp)
 
-rank_group$data |> 
+rank_group_data <- rank_group$data |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
-  rename(gp = group) |> 
+  rename(gp = group,
+         rank_group = qtile) |> 
   select(-c(frame, color)) |> 
@@
 
-  4. Fix bins relative to absolute values by year within a group.
-
 ```{r}
@@
 
-absolute_group$data |> 
+absolute_group_data <- absolute_group$data |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
-  rename(gp = group) |> 
+  rename(gp = group,
+         absolute_group = qtile) |> 
   select(-c(frame, color)) |> 
@@
 
-  For the first and third scaling methods, group splitting is executed using the `quantiles()` and `cut()` functions.
+```{r}
+original |> 
+  left_join(rank_data, by = c("id", "time", "gp")) |> 
+  left_join(rank_group_data, by = c("id", "time", "gp")) |> 
+  left_join(absolute_data, by = c("id", "time", "gp")) |> 
+  left_join(absolute_group_data, by = c("id", "time", "gp")) |> 
+  reframe(id, time, gp, values, rank, rank_group, absolute, absolute_group)
+```
+
+  1. Ranking by year. (rank)
+  2. Ranking by year within a group. (rank_group)
+  3. Fix bins relative to absolute values by year. (absolute)
+  4. Fix bins relative to absolute values by year within a group. (absolute_group)
+
+  For the first and second scaling methods, group splitting is executed using the `quantiles()` and `cut()` functions.
 The `quantile` function from the `stats` R package (@stats) takes a numeric vector and outputs the corresponding quantiles to the given probabilities.
@@
 
-  In contrast, the second and fourth scaling methods calculate the quantile based on the absolute values scales.
+  In contrast, the third and fourth scaling methods calculate the quantile based on the absolute values scales.
 The default approach is to break the group equally using the `seq()` function.
@@
 
-  For the `anim_prep()` function, the arguments are as follows:
+  In the `anim_prep()` and `anim_prep_cat()`, there are required arguments that need to be specified. The lists are as follows:
 
@@
   - time: The column name represents the time variable.
-- label: A vector of labels to be used for the y-axis in the visualization.
+
+  As shown previously, there are a total of four different scaling for the `anim_prep()` function. Both the use can customization of these scaling can be set using the following arguments:
+
   - ngroup:	The number of groups or categories to create for scaling values.
@@
   - group_scaling: The column name that represents the grouping variable.
-- color: The column name to be used in ggplot2::aes() for the plot function.
-- time_dependent: Logical. Should the visualization be time-dependent? Default is TRUE.
   - scaling: The scaling method to be used; "rank" or "absolute."
-- runif_min: The minimum value for random addition to frame numbers.
-- runif_max: The maximum value for random addition to frame numbers.
 
-  For the `anim_prep_cat()` function, the arguments are as follows:
+  For the `anim_prep_cat()` function, the arguments that allowed the user to order the category are by using this argument:
 
-- data: A data frame containing the data to be prepared for visualization.
-- id: The column name that represents the unique identifier variable.
-- values: The column name that contains the numeric values to be visualized.
-- time: The column name represents the time variable.
+  - order: A vector of order for sorting the category values.
+
+  Then, for further customization regarding how the final visualization looks. The following arguments can be adjusted:
+
   - label: A vector of labels to be used for the y-axis in the visualization.
-- order: A vector of order for sorting the category values.
   - color: The column name to be used in ggplot2::aes() for the plot function.
@@
 
-Step 1: Prepare the data
+In this section, the package usage will be demonstrated using the `cat_change` dataset included in this package.
+This dataset is simulated data that has changed from category A to E between two time points.
+Since this data is already in the categorized data structure, the `anim_prep_cat()` function is utilized.
+
+  The output produced from this package is referred to as the `animbook` object.
+This contained a list of data and settings that hold prepared data for visualization, along with a list of settings used in the plot function.
 
@@
 
-Step 2: Plotting the data
+  To obtain a `ggplot` object for the animation function, the `wallaby_plot` is used.
+For further customization, the `shade_palette`, `subset`, and `relation` arguments are applied to define the final appearance of the animation.
 
@@
              group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-             shade_palette = c("#737373", "#969696", "#BDBDBD","#D9D9D9","#D9D9D9","#D9D9D9"),
+             shade_palette = c("#737373", "#969696", "#BDBDBD",
+                               "#D9D9D9","#D9D9D9","#D9D9D9"),
              rendering = "ggplot",
@@
 
-Step 3: Animating the plot
+  Once the `ggplot` object is obtained, the `anim_animate()` function can be used to transform it into a `gganimate` object.
+This then can be passed onto the `gganimate::animate()` function for rendering.
 
@@
 
-gganimate::anim_save("figures/catchange.gif", p2)
+gganimate::anim_save("figures/catchange.gif", p2, height = 8, fps = 30,
+                     nframes = 400, width = 9, units = "in", res = 150)
 ```
@@
 ```
+
+  This is an example of how the users can apply the three-step process in creating an animation plot using the `animbook` package.
 
@@
                   group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-                  shade_palette = c("#737373", "#969696", "#BDBDBD","#D9D9D9","#D9D9D9","#D9D9D9"),
+                  shade_palette = c("#737373", "#969696", "#BDBDBD",
+                                    "#D9D9D9","#D9D9D9","#D9D9D9"),
                   subset = "bottom",
@@
 
-```{r osiris-figure, fig.cap = "The animate visualization shows the companies that exited the market.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+```{r osiris-figure, fig.cap = "The animate visualization shows the companies that exited the market.
+There are more United States companies that fall down into a not listed group compared to Japanese companies.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
 knitr::include_graphics("figures/animation-exit.png")
@@
 
-```{r osiris-gif, out.extra="class = 'gif'", fig.cap = "The animate visualization shows the companies that exited the market.", eval=knitr::is_html_output()}
+```{r osiris-gif, out.extra="class = 'gif'", fig.cap = "The animate visualization shows the companies that exited the market.
+There are more United States companies that fall down into a not listed group compared to Japanese companies.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/exit.gif")
@@
 
-## Voter behaviour
+## Voter behavior
 
@@
                   group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-                  shade_palette = c("#737373", "#969696", "#BDBDBD","#D9D9D9","#D9D9D9","#D9D9D9"),
+                  shade_palette = c("#737373", "#969696", "#BDBDBD",
+                                    "#D9D9D9","#D9D9D9","#D9D9D9"),
                   rendering = "ggplot",
@@
 
-```{r voter-figure, fig.cap = "The animate visualization shows how does the top party perform in keeping the old  voters for different genders.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+```{r voter-figure, fig.cap = "The animate visualization shows how does the top party perform in keeping the old voters for different genders.
+Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
 knitr::include_graphics("figures/animation-voter.png")
@@
 
-```{r voter-gif, out.extra="class = 'gif'", fig.cap = "The animate visualization shows how does the top party perform in keeping the old  voters for different genders.", eval=knitr::is_html_output()}
+```{r voter-gif, out.extra="class = 'gif'", fig.cap = "The animate visualization shows how does the top party perform in keeping the old  voters for different genders.
+Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/voter.gif")
@@
 This feature will introduce a new dimension that allows the users to explore the data further.
+Additionally, both new animated and static plots could also be added, as seen in the New York Times article (@the_new_york_time), to compare the demographics at a specific point in time.
+On top of that, the `cli` package (@cli) could be used for a more aesthetically pleasing command-line interface.
 
@@
 
-This paper is based on the 0.0.0.9 version of the `animbook` package. This version is available on [GitHub](https://github.com/KrisanatA/animbook).
+This paper is created using the `rjtools` packages (@rjtools) and is based on the 0.0.0.9 version of the `animbook` package.
+This version is available on [GitHub](https://github.com/KrisanatA/animbook).
+
+I also acknowledge the use of ChatGPT (https://chat.openai.com/) to paraphrase the sentence.

### 2023-10-28 animbook-journal.tex
second version of the paper

@@
 
-The concept of ``zombie companies'' began to attract attention when an article on the proliferation of zombie companies (Caballero, Hoshi, and Kashyap (2008)).
-The ``zombie companies'' are generally defined as companies with an interest coverage ratio of less than one for a period of more than three years.
-These companies are taking space in the market but adding no life to the economy.
-There could be other movement patterns, beyond zombies, that are interesting, such as companies that suddenly become very successful, or in politics voters who switch party affiliation between elections.
+The concept of ``zombie companies'' began to attract attention when Caballero, Hoshi, and Kashyap (2008) reported on their proliferation in Japan.
+Zombie companies are those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy.
+We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time.
+Generally, studying movement patterns is interesting for many problems, including rocket ship startups that rapidly perform well, or in politics, to study voters who switch party affiliation between elections.
 Viewing changes between categories over time is an interesting challenge for visualization.
 
-The New York Times provided a possible solution in the article ``Extensive data show punishing reach of racism for black boys'' (Badger et al.
+The New York Times provided a possible solution in the article titled ``Extensive data show punishing reach of racism for black boys'' (Badger et al.
 (2018)) to tell the story of how racism appears to inhibit socioeconomic change.
-This approach can be adapted to address the zombie problem by capturing the movement between groups over a specific period.
+This animation is the motivation for the new visualization presented here, to be applied generally.
 
-With an advancement in technology, this results in an increase in both the size and complexity of the data.
-It requires an experienced hand to convey the right messages from the data.
-However, as shown in The New York Times article (Badger et al.
-(2018)), the animation is not only created just for eye-catching graphics.
-Animation can be used as a tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the audience.
+The challenge in producing an animation like that in New York Times article animation is the transformation of the data, and connection with elements of the plot that will be animated.
+The complexities include standardizing starting times of the temporal variable, allowing for the user to choose the number of categories, standardizing distributions and allowing the user to input pre-computed categorical data.
+These considerations provide the objective for creating an R package that can generalize the animation to suitably apply to a wide range of data.
 
-The challenge in reproducing the New York Times article animation was the amount of code required.
-Additionally, the business data may or may not have the same information as the one in the article.
-These considerations establish the objective for creating the R package that could generalize the animation to a wider range of data.
+The structure of this paper is as follows.
+The section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
+The next section describes the expected data format.
+Following this is an explanation of available animation tools, and how they are employed for this problem.
+A section on the functions of the package and how the visualization is designed, demonstrates how the data is mapped to the animation.
+The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.
 
-The structure of this paper will consist of both the visualization design and software design.
-The first section will explain the animation in The New York Times article and why it might be relevant to the problems.
-Secondly, what is the expected data to be input into the plot, and how it is processed.
-The third section is about the animation tools, followed by the section on package and visualization design.
-The last two sections explore the usage of the R package and the application to other types of data.
+\hypertarget{NYT}{%
+\section{Explanation of the New York Times visualization}\label{NYT}}
 
-\hypertarget{explanation-of-the-new-york-times-visualization}{%
-\section{Explanation of the New York Times visualization}\label{explanation-of-the-new-york-times-visualization}}
+\begin{figure}
 
-The flow chart featured in one of the New York Times articles unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the Chetty et al.
+{\centering \includegraphics[width=1\linewidth]{figures/NYT}
+
+}
+
+\caption{Screenshot of the New York Times animation, that is the motivation for this visualization package.}\label{fig:nyt}
+\end{figure}
+
+The interactive chart featured in the New York Times article (Figure \ref{fig:nyt}) unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the Chetty et al.
 (2020).
@@
 This is illustrated in Figure \ref{fig:animation-diagram}.
-There are multiple ways to create an animation in the R environment (R Core Team (2021)), including packages like \texttt{gganimate} and \texttt{plot}.
+There are multiple ways to create an animation in the R environment (R Core Team (2021)), including packages like \texttt{gganimate} and \texttt{Plotly}.
 
@@
 This issue can be eliminated by interpolating additional points in between the observations.
-In the \texttt{gganimate} package, the interpolation is achieved using the \texttt{tweenr} package (Pedersen (2022)), while in \texttt{plotly}, it utilizes d3.interpolate (Bostock (2012)).
+In the \texttt{gganimate} package (Pedersen and Robinson (2020)), the interpolation is achieved using the \texttt{tweenr} package (Pedersen (2022)), while in \texttt{plotly}, it utilizes d3.interpolate (Bostock (2012)).
 
@@
 
-Original data:
-
 \begin{verbatim}
-#> # A tibble: 12 x 4
-#>    id     time values gp   
-#>    <fct> <int>  <dbl> <fct>
-#>  1 1      2020  4255. X    
-#>  2 1      2023  3357. X    
-#>  3 14     2020  6763. X    
-#>  4 14     2023  1197. X    
-#>  5 100    2020  6864. X    
-#>  6 100    2023  2321. X    
-#>  7 21     2020   698. Y    
-#>  8 21     2023  3970. Y    
-#>  9 106    2020  4110. Y    
-#> 10 106    2023  2866. Y    
-#> 11 148    2020  7174. Y    
-#> 12 148    2023  4217. Y
+#> # A tibble: 12 x 8
+#>    id     time gp    values  rank rank_group absolute absolute_group
+#>    <fct> <int> <fct>  <dbl> <int>      <int>    <int>          <int>
+#>  1 1      2020 X      4255.     3          3        3              3
+#>  2 1      2023 X      3357.     2          2        4              4
+#>  3 14     2020 X      6763.     2          2        2              2
+#>  4 14     2023 X      1197.     4          5        5              5
+#>  5 100    2020 X      6864.     2          2        2              2
+#>  6 100    2023 X      2321.     3          3        4              4
+#>  7 21     2020 Y       698.     5          5        5              5
+#>  8 21     2023 Y      3970.     2          2        4              3
+#>  9 106    2020 Y      4110.     3          3        3              3
+#> 10 106    2023 Y      2866.     3          3        4              4
+#> 11 148    2020 Y      7174.     2          2        2              2
+#> 12 148    2023 Y      4217.     1          1        3              3
 \end{verbatim}
@@
 \item
-  Ranking by year.
+  Ranking by year. (rank)
+\item
+  Ranking by year within a group. (rank\_group)
+\item
+  Fix bins relative to absolute values by year. (absolute)
+\item
+  Fix bins relative to absolute values by year within a group. (absolute\_group)
 \end{enumerate}
 
-\begin{verbatim}
-#> # A tibble: 12 x 4
-#>    id     time qtile gp   
-#>    <fct> <int> <int> <fct>
-#>  1 1      2020     3 X    
-#>  2 1      2023     2 X    
-#>  3 14     2020     2 X    
-#>  4 14     2023     4 X    
-#>  5 100    2020     2 X    
-#>  6 100    2023     3 X    
-#>  7 21     2020     5 Y    
-#>  8 21     2023     2 Y    
-#>  9 106    2020     3 Y    
-#> 10 106    2023     3 Y    
-#> 11 148    2020     2 Y    
-#> 12 148    2023     1 Y
-\end{verbatim}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  Fix bins relative to absolute values by year.
-\end{enumerate}
-
-\begin{verbatim}
-#> # A tibble: 12 x 4
-#>    id     time qtile gp   
-#>    <fct> <int> <int> <fct>
-#>  1 1      2020     3 X    
-#>  2 1      2023     4 X    
-#>  3 14     2020     2 X    
-#>  4 14     2023     5 X    
-#>  5 100    2020     2 X    
-#>  6 100    2023     4 X    
-#>  7 21     2020     5 Y    
-#>  8 21     2023     4 Y    
-#>  9 106    2020     3 Y    
-#> 10 106    2023     4 Y    
-#> 11 148    2020     2 Y    
-#> 12 148    2023     3 Y
-\end{verbatim}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Ranking by year within a group.
-\end{enumerate}
-
-\begin{verbatim}
-#> # A tibble: 12 x 4
-#>    id     time qtile gp   
-#>    <fct> <int> <int> <fct>
-#>  1 1      2020     3 X    
-#>  2 1      2023     2 X    
-#>  3 14     2020     2 X    
-#>  4 14     2023     5 X    
-#>  5 100    2020     2 X    
-#>  6 100    2023     3 X    
-#>  7 21     2020     5 Y    
-#>  8 21     2023     2 Y    
-#>  9 106    2020     3 Y    
-#> 10 106    2023     3 Y    
-#> 11 148    2020     2 Y    
-#> 12 148    2023     1 Y
-\end{verbatim}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{3}
-\tightlist
-\item
-  Fix bins relative to absolute values by year within a group.
-\end{enumerate}
-
-\begin{verbatim}
-#> # A tibble: 12 x 4
-#>    id     time qtile gp   
-#>    <fct> <int> <int> <fct>
-#>  1 1      2020     3 X    
-#>  2 1      2023     4 X    
-#>  3 14     2020     2 X    
-#>  4 14     2023     5 X    
-#>  5 100    2020     2 X    
-#>  6 100    2023     4 X    
-#>  7 21     2020     5 Y    
-#>  8 21     2023     3 Y    
-#>  9 106    2020     3 Y    
-#> 10 106    2023     4 Y    
-#> 11 148    2020     2 Y    
-#> 12 148    2023     3 Y
-\end{verbatim}
-
-For the first and third scaling methods, group splitting is executed using the \texttt{quantiles()} and \texttt{cut()} functions.
+For the first and second scaling methods, group splitting is executed using the \texttt{quantiles()} and \texttt{cut()} functions.
 The \texttt{quantile} function from the \texttt{stats} R package (R Core Team (2013)) takes a numeric vector and outputs the corresponding quantiles to the given probabilities.
@@
 
-In contrast, the second and fourth scaling methods calculate the quantile based on the absolute values scales.
+In contrast, the third and fourth scaling methods calculate the quantile based on the absolute values scales.
 The default approach is to break the group equally using the \texttt{seq()} function.
@@
 
-For the \texttt{anim\_prep()} function, the arguments are as follows:
+In the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()}, there are required arguments that need to be specified. The lists are as follows:
 
 \begin{itemize}
+\tightlist
 \item
@@
   time: The column name represents the time variable.
-\item
-  label: A vector of labels to be used for the y-axis in the visualization.
+\end{itemize}
+
+As shown previously, there are a total of four different scaling for the \texttt{anim\_prep()} function. Both the use can customization of these scaling can be set using the following arguments:
+
+\begin{itemize}
+\tightlist
 \item
@@
 \item
-  color: The column name to be used in ggplot2::aes() for the plot function.
+  scaling: The scaling method to be used; ``rank'' or ``absolute.''
+\end{itemize}
+
+For the \texttt{anim\_prep\_cat()} function, the arguments that allowed the user to order the category are by using this argument:
+
+\begin{itemize}
+\tightlist
 \item
-  time\_dependent: Logical. Should the visualization be time-dependent? Default is TRUE.
-\item
-  scaling: The scaling method to be used; ``rank'' or ``absolute.''
-\item
-  runif\_min: The minimum value for random addition to frame numbers.
-\item
-  runif\_max: The maximum value for random addition to frame numbers.
+  order: A vector of order for sorting the category values.
+\end{itemize}
 
-  For the \texttt{anim\_prep\_cat()} function, the arguments are as follows:
-\item
-  data: A data frame containing the data to be prepared for visualization.
-\item
-  id: The column name that represents the unique identifier variable.
-\item
-  values: The column name that contains the numeric values to be visualized.
-\item
-  time: The column name represents the time variable.
+Then, for further customization regarding how the final visualization looks. The following arguments can be adjusted:
+
+\begin{itemize}
+\tightlist
 \item
   label: A vector of labels to be used for the y-axis in the visualization.
-\item
-  order: A vector of order for sorting the category values.
 \item
@@
 
-Step 1: Prepare the data
+In this section, the package usage will be demonstrated using the \texttt{cat\_change} dataset included in this package.
+This dataset is simulated data that has changed from category A to E between two time points.
+Since this data is already in the categorized data structure, the \texttt{anim\_prep\_cat()} function is utilized.
+
+The output produced from this package is referred to as the \texttt{animbook} object.
+This contained a list of data and settings that hold prepared data for visualization, along with a list of settings used in the plot function.
 
@@
 #>    <fct> <int> <dbl> <dbl> <fct>
-#>  1 1      2020     5    37 X    
-#>  2 1      2023     5    38 X    
-#>  3 2      2020     5    42 X    
-#>  4 2      2023     5    43 X    
-#>  5 3      2020     5     9 X    
-#>  6 3      2023     5    10 X    
-#>  7 4      2020     5    27 X    
-#>  8 4      2023     5    28 X    
-#>  9 5      2020     5    20 X    
-#> 10 5      2023     5    21 X
+#>  1 1      2020     5    10 X    
+#>  2 1      2023     5    11 X    
+#>  3 2      2020     5    44 X    
+#>  4 2      2023     5    45 X    
+#>  5 3      2020     5    11 X    
+#>  6 3      2023     5    12 X    
+#>  7 4      2020     5    21 X    
+#>  8 4      2023     5    22 X    
+#>  9 5      2020     5     6 X    
+#> 10 5      2023     5     7 X
 \end{verbatim}
@@
 #>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
-#>   ..$ frame: num [1:400] 37 38 42 43 9 10 27 28 20 21 ...
+#>   ..$ frame: num [1:400] 10 11 44 45 11 12 21 22 6 7 ...
 #>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
@@
 
-Step 2: Plotting the data
+To obtain a \texttt{ggplot} object for the animation function, the \texttt{wallaby\_plot} is used.
+For further customization, the \texttt{shade\_palette}, \texttt{subset}, and \texttt{relation} arguments are applied to define the final appearance of the animation.
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-8-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-6-1} \end{center}
 
-Step 3: Animating the plot
+Once the \texttt{ggplot} object is obtained, the \texttt{anim\_animate()} function can be used to transform it into a \texttt{gganimate} object.
+This then can be passed onto the \texttt{gganimate::animate()} function for rendering.
 
@@
 \end{figure}
+
+This is an example of how the users can apply the three-step process in creating an animation plot using the \texttt{animbook} package.
 
@@
 
-\caption{The animate visualization shows the companies that exited the market.}\label{fig:osiris-figure}
+\caption{The animate visualization shows the companies that exited the market.
+There are more United States companies that fall down into a not listed group compared to Japanese companies.}\label{fig:osiris-figure}
 \end{figure}
@@
 
-\hypertarget{voter-behaviour}{%
-\subsection{Voter behaviour}\label{voter-behaviour}}
+\hypertarget{voter-behavior}{%
+\subsection{Voter behavior}\label{voter-behavior}}
 
@@
 
-\caption{The animate visualization shows how does the top party perform in keeping the old  voters for different genders.}\label{fig:voter-figure}
+\caption{The animate visualization shows how does the top party perform in keeping the old voters for different genders.
+Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.}\label{fig:voter-figure}
 \end{figure}
@@
 This feature will introduce a new dimension that allows the users to explore the data further.
+Additionally, both new animated and static plots could also be added, as seen in the New York Times article (Badger et al.
+(2018)), to compare the demographics at a specific point in time.
+On top of that, the \texttt{cli} package (Csárdi (2023)) could be used for a more aesthetically pleasing command-line interface.
 
-This paper is based on the 0.0.0.9 version of the \texttt{animbook} package. This version is available on \href{https://github.com/KrisanatA/animbook}{GitHub}.
+\hypertarget{acknowledgements}{%
+\section*{Acknowledgements}\label{acknowledgements}}
+\addcontentsline{toc}{section}{Acknowledgements}
+
+This paper is created using the \texttt{rjtools} packages (O'Hara-Wild et al.
+(2023)) and is based on the 0.0.0.9 version of the \texttt{animbook} package.
+This version is available on \href{https://github.com/KrisanatA/animbook}{GitHub}.
+
+I also acknowledge the use of ChatGPT (\url{https://chat.openai.com/}) to paraphrase the sentence.
 
@@
 2008.
-{``Zombie Lending and Depressed Restructuring in Japan.''} \emph{The American Economic Review} 98 (5): 1943--77.
+{``Zombie Lending and Depressed Restructuring in {J}apan.''} \emph{The American Economic Review} 98 (5): 1943--77.
 \url{http://www.jstor.org/stable/29730158}.
@@
 Codd, E. F. 1990. \emph{The Relational Model for Database Management: Version 2}. USA: Addison-Wesley Longman Publishing Co., Inc.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cli}{}}%
+Csárdi, Gábor. 2023. \emph{Cli: Helpers for Developing Command Line Interfaces}. \url{https://CRAN.R-project.org/package=cli}.
 
@@
 McGowan, Müge Adalet, Dan Andrews, and Valentine Millot. 2017. {``The Walking Dead?''} no. 1372. https://doi.org/\url{https://doi.org/https://doi.org/10.1787/180d80ad-en}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rjtools}{}}%
+O'Hara-Wild, Mitchell, Stephanie Kobakian, H.
+Sherry Zhang, Di Cook, Simon Urbanek, and Christophe Dervieux.
+2023.
+\emph{Rjtools: Preparing, Checking, and Submitting Articles to the 'r Journal'}.
+\url{https://CRAN.R-project.org/package=rjtools}.
 

### 2023-10-28 animbook-journal.R

@@ -10,6 +10,10 @@ library(animbook)
 library(tidyverse)
 
 
+## ----nyt, fig.cap="Screenshot of the New York Times animation, that is the motivation for this visualization package.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"----
+knitr::include_graphics("figures/NYT.png")
+
+
 ## ----data-diagram, fig.cap="The diagram shows what are the expected data forms.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"----
 knitr::include_graphics("figures/data-diagram.png")
 
@@ -28,38 +32,35 @@ knitr::include_graphics("figures/sine-shade.png")
 
 
 ## -----------------------------------------------------------------------------
-dbl_change |> 
+original <- dbl_change |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
   reframe(id, time, values, gp) |> 
   arrange(gp, id)
 
-
-## -----------------------------------------------------------------------------
 rank <- anim_prep(dbl_change, id, values, time, color = gp) 
 
-rank$data |> 
+rank_data <- rank$data |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
-  rename(gp = color) |> 
+  rename(gp = color,
+         rank = qtile) |> 
   select(-frame) |> 
   arrange(gp, id)
 
-
-## -----------------------------------------------------------------------------
 absolute <- anim_prep(dbl_change, id, values, time, color = gp, scaling = "absolute") 
 
-absolute$data |> 
+absolute_data <- absolute$data |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |>  
-  rename(gp = color) |> 
+  rename(gp = color,
+         absolute = qtile) |> 
   select(-frame) |> 
   arrange(gp, id)
 
-
-## -----------------------------------------------------------------------------
 rank_group <- anim_prep(dbl_change, id, values, time, color = gp, group_scaling = gp) 
 
-rank_group$data |> 
+rank_group_data <- rank_group$data |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
-  rename(gp = group) |> 
+  rename(gp = group,
+         rank_group = qtile) |> 
   select(-c(frame, color)) |> 
   arrange(gp, id)
 
@@ -67,11 +68,21 @@ rank_group$data |>
 ## -----------------------------------------------------------------------------
[…]

### 2023-10-28 animbook-journal.Rmd
add more control theory in the animation tools section

@@
 The frame variable within the animated data structure allows the animation function to determine the position of observations on the plot at any given frame.
+
+  From @learner-control, it suggests that having control options for the animation can improve the efficiency of the learning process.
+Additionally, the length and speed of the animation should also be taken into consideration.
+According to @mayer-2010, the working memory, responsible for selecting and processing information from sensory memory, only holds a processed version of what was presented for generally less than thirty seconds.
+
+  In `gganimate`, the issue of integrating controls can be addressed by setting the `renderer` argument to be `av_renderer()`, which allows the animation output to be in MP4 format.
+This format provides users with controls for the animation when opened on media applications provided in their systems.
+As for adjusting the length and speed of the animation, the `nframes` and `fps` arguments can be utilized.
+The `nframes` dictates the number of frames to be rendered, while `fps` controls how many frames are displayed in one second.
+Using these two parameters, the duration of the animation in seconds can be calculated as follows: length = nframes/fps.
+
+  In the case of `plotly`, control integration is already implemented by default.
+The `frame` and `transition` arguments within the `animation_opts()` function can be specified to set the length and speed of the animation.
 
@@
 This feature will introduce a new dimension that allows the users to explore the data further.
+The plotly rendering is also not yet been optimized for use.
 Additionally, both new animated and static plots could also be added, as seen in the New York Times article (@the_new_york_time), to compare the demographics at a specific point in time.

### 2023-10-28 animbook-journal.tex
add more control theory in the animation tools section

@@
 
+From Hasler, Kersten, and Sweller (2007), it suggests that having control options for the animation can improve the efficiency of the learning process.
+Additionally, the length and speed of the animation should also be taken into consideration.
+According to R.
+Mayer (2010), the working memory, responsible for selecting and processing information from sensory memory, only holds a processed version of what was presented for generally less than thirty seconds.
+
+In \texttt{gganimate}, the issue of integrating controls can be addressed by setting the \texttt{renderer} argument to be \texttt{av\_renderer()}, which allows the animation output to be in MP4 format.
+This format provides users with controls for the animation when opened on media applications provided in their systems.
+As for adjusting the length and speed of the animation, the \texttt{nframes} and \texttt{fps} arguments can be utilized.
+The \texttt{nframes} dictates the number of frames to be rendered, while \texttt{fps} controls how many frames are displayed in one second.
+Using these two parameters, the duration of the animation in seconds can be calculated as follows: length = nframes/fps.
+
+In the case of \texttt{plotly}, control integration is already implemented by default.
+The \texttt{frame} and \texttt{transition} arguments within the \texttt{animation\_opts()} function can be specified to set the length and speed of the animation.
+
 \hypertarget{visualization-design}{%
@@
 
-The animated visualization can be an effective communication tool (Mayer and Moreno (2002); Robertson et al.
+The animated visualization can be an effective communication tool (R.
+E.
+Mayer and Moreno (2002); Robertson et al.
 (2008)).
 It helps with communicating complex data, enhancing the narrative, and keeping it engaged for the audience.
-According to Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.
+According to R.
+E.
+Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.
 
-According to Mayer (2005), designing multimedia requires the designer to understand how people learn.
-One of the principles in Mayer (2005), Redundancy, suggests that a piece of excess information could overload the learners.
+According to R.
+E.
+Mayer (2005), designing multimedia requires the designer to understand how people learn.
+One of the principles in R.
+E.
+Mayer (2005), Redundancy, suggests that a piece of excess information could overload the learners.
 By this principle, the animation must be carefully designed to avoid this pitfall.
@@
 It includes points in motion, distribution at the end, and proportional counters.
-However, this could lead to information overload (Mayer (2005)).
+However, this could lead to information overload (R.
+E.
+Mayer (2005)).
 Therefore, the distribution at the end and proportional counters are excluded.
@@
 #>  2 1      2023     5    11 X    
-#>  3 2      2020     5    44 X    
-#>  4 2      2023     5    45 X    
+#>  3 2      2020     5     5 X    
+#>  4 2      2023     5     6 X    
 #>  5 3      2020     5    11 X    
 #>  6 3      2023     5    12 X    
-#>  7 4      2020     5    21 X    
-#>  8 4      2023     5    22 X    
-#>  9 5      2020     5     6 X    
-#> 10 5      2023     5     7 X
+#>  7 4      2020     5    39 X    
+#>  8 4      2023     5    40 X    
+#>  9 5      2020     5    10 X    
+#> 10 5      2023     5    11 X
 \end{verbatim}
@@
 #>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
-#>   ..$ frame: num [1:400] 10 11 44 45 11 12 21 22 6 7 ...
+#>   ..$ frame: num [1:400] 10 11 5 6 11 12 39 40 10 11 ...
 #>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
@@
 This feature will introduce a new dimension that allows the users to explore the data further.
+The plotly rendering is also not yet been optimized for use.
 Additionally, both new animated and static plots could also be added, as seen in the New York Times article (Badger et al.
@@
 Csárdi, Gábor. 2023. \emph{Cli: Helpers for Developing Command Line Interfaces}. \url{https://CRAN.R-project.org/package=cli}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-learner-control}{}}%
+Hasler, Béatrice, Bernd Kersten, and John Sweller.
+2007.
+{``Learner Control, Cognitive Load and Instructional Animation.
+Applied Cognitive Psychology, 21, 713-729.''} \emph{Applied Cognitive Psychology} 21 (September): 713--29.
+\url{https://doi.org/10.1002/acp.1345}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mayer-2010}{}}%
+Mayer, Richard. 2010. {``Applying the Science of Learning to Medical Education.''} \emph{Medical Education} 44 (June): 543--49. \url{https://doi.org/10.1111/j.1365-2923.2010.03624.x}.
 

### 2023-10-28 animbook-journal.Rmd
add abstract

@@
 abstract: >
-  An abstract of less than 150 words.
+  Categorical data has often been presented statically despite its potential to unveil an intriguing movement pattern relevant to the various domains of data, including company ranking quantile in the accounting data and shifts in voter party affiliations.
+Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," this paper aims to develop an R package, animbook, that can generalize the animation to suitably apply to a wider range of data.
+The package included a function that allowed for the transformation of the data and connection with elements of the plot that would be animated.
+This results in an animation tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the general audience.
 draft: true

### 2023-10-28 animbook-journal.tex
add abstract

@@
 \abstract{%
-An abstract of less than 150 words.
+Categorical data has often been presented statically despite its potential to unveil an intriguing movement pattern relevant to the various domains of data, including company ranking quantile in the accounting data and shifts in voter party affiliations.
+Inspired by the animation in the New York Times article ``Extensive data show punishing reach of racism for black boys,'' this paper aims to develop an R package, animbook, that can generalize the animation to suitably apply to a wider range of data.
+The package included a function that allowed for the transformation of the data and connection with elements of the plot that would be animated.
+This results in an animation tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the general audience.
 }
@@
 #>    <fct> <int> <dbl> <dbl> <fct>
-#>  1 1      2020     5    10 X    
-#>  2 1      2023     5    11 X    
-#>  3 2      2020     5     5 X    
-#>  4 2      2023     5     6 X    
-#>  5 3      2020     5    11 X    
-#>  6 3      2023     5    12 X    
-#>  7 4      2020     5    39 X    
-#>  8 4      2023     5    40 X    
-#>  9 5      2020     5    10 X    
-#> 10 5      2023     5    11 X
+#>  1 1      2020     5    21 X    
+#>  2 1      2023     5    22 X    
+#>  3 2      2020     5    31 X    
+#>  4 2      2023     5    32 X    
+#>  5 3      2020     5     6 X    
+#>  6 3      2023     5     7 X    
+#>  7 4      2020     5    27 X    
+#>  8 4      2023     5    28 X    
+#>  9 5      2020     5    20 X    
+#> 10 5      2023     5    21 X
 \end{verbatim}
@@
 #>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
-#>   ..$ frame: num [1:400] 10 11 5 6 11 12 39 40 10 11 ...
+#>   ..$ frame: num [1:400] 21 22 31 32 6 7 27 28 20 21 ...
 #>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...

### 2023-10-28 animbook-journal.Rmd
small fixes

@@
 
-# Introduction
+# Introduction {#intro}
 
@@
 The structure of this paper is as follows.
-The section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
+The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
 The next section describes the expected data format.
@@
 
-# Explanation of the New York Times visualization {#NYT}
+# Explanation of the New York Times visualization {#NYTvis}
 
@@
 
-# Data
+# Data {#data}
 
@@
 
-```{r data-diagram, fig.cap="The diagram shows what are the expected data forms.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+```{r data-diagram, fig.cap="The data can be provided in the raw or categorized form, and will be processed into the format needed for the animation.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
 knitr::include_graphics("figures/data-diagram.png")
@@
 
-# Animation tools
+# Animation tools {#animation}
 
@@
 
-# Visualization design
+# Visualization design {#design}
 
@@
 
-# Software
+# Software {#software}
 
@@
 
-## Overviw of functions
+## Overview of functions
 

### 2023-10-28 animbook-journal.Rmd
updated the data section

@@
 
-```{r data-diagram, fig.cap="The data can be provided in the raw or categorized form, and will be processed into the format needed for the animation.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+```{r data-diagram, fig.cap="The animation expects data with an ID and a time variable, along with a numerical variable (raw form), which is possibly converted to categorical (categorized).
+The data can be provided in the raw or categorized form, and will be processed into the format needed for the animation where the categorical variable is treated as a quantile and an animation frame variable is created.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/data-diagram.png")
@@
   In the data structure, there are requirements that must be followed for reproducing the animation.
-The data must have ID and time variables.
-These form what we call a unique ID.
+The data must have at least ID and time variables, in addition to the measured variable which would usually be numeric, but may be categorical.
+The ID variable indicates the individual which is followed over time, such as the company name.
+There may also be a grouping variable, such as country where the company is registered.
+<!--These form what we call a unique ID.
 Also, the values variable can be either a numerical or categorical variable.
 The type of this variable will determine the stage the data set is in.
-This format ensures that during the data pre-processing, the R function understands what needs to be done with the data.
+This format ensures that during the data pre-processing, the R function understands what needs to be done with the data.-->
 
-  Figure \@ref(fig:data-diagram) shows which stages the data is in, given the type of values variable.
-Start with the raw data structure.
-The values are presented in the numerical format.
-It is referred to as 'raw' because, in the New York Times animation, it is expressed in the categorical format.
-However, in most cases, the data is in numerical values and requires transformation.
-The second form is categorized data, as mentioned earlier, which involves transforming numerical into categories.
-This transformation may not be necessary if it already exists in the categorized format, as in the case of political data (party affiliation).
-The last form is animated data, where the frame is assigned to each unique ID.
+  Figure \@ref(fig:data-diagram) illustrates the expected format of the data and variables created to prepare it for the animation.
+We start with the raw data structure.
+The values are presented in the numerical format, which we call the 'raw' form.
+<!--because, in the New York Times animation, it is expressed in the categorical format.--> In most cases, the measured variable will be numerical and require transformation.
+The second form is categorized data, which involves transforming numerical variable into categories, typically quantiles.
+This transformation may not be necessary if it is already provided in the categorized format. The last form is animated data, where the frame is assigned to each unique ID.
 

### 2023-10-28 animbook-journal.Rmd
up to section 6

@@
 
-```{r animation-diagram, fig.cap="The diagram shows how the animation is done using the successive pictures.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+```{r animation-diagram, fig.cap="The diagram shows how the animation is done using the successive pictures.
+When small changes are seen in quick succession, it will appear as if the objects are in motion.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/animation-diagram.png")
@@
 
-The principle underlying the animation is called persistence of vision (@animation-mechanic).
+ A principle important for designing a useful animation is called persistence of vision (@animation-mechanic).
 When an image disappears, the brain will retain the previous images for a brief period of time.
@@
 This is illustrated in Figure \@ref(fig:animation-diagram).
-There are multiple ways to create an animation in the R environment (@r), including packages like `gganimate` and `Plotly`.
 
-  The `gganimate` package (@gganimate) is an extension from the `ggplot2` package (@ggplot2) to include the description of an animation.
+ There are multiple ways to create an animation in the R environment (@r), including the packages \CRANpkg{gganimate} (@gganimate) and \CRANpkg{plotly} (@plotly).
+
+ The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (@ggplot2) to include the description of an animation.
 It added new grammar classes to the plot object, allowing it to understand how the plot should change over time.
@@
 The output from the `gganimate` can be rendered or saved in multiple formats.
-This includes `gifski_renderer()` from the `gifski` package (@gifski) to save the animation in GIF format or `av_renderer()` from the `av` package (@av) to save it into a video file format.
+This includes `gifski_renderer()` from the \CRANpkg{gifski} package (@gifski) to save the animation in GIF format or `av_renderer()` from the `av` package (@av) to save it into a video file format.
 
-  Plotly is a graphing library that provides tools for creating an interactive plot in multiple programming languages, such as R, JavaScript, Python, and Julia.
-In R, plotly can be accessed through the `plotly` package (@plotly), which integrates plotly.js from the JavaScript graphing library.
+ The `plotly` software is a graphing library that provides tools for creating an interactive plot in multiple programming languages, such as R, JavaScript, Python, and Julia.
+In R, plotly can be accessed through the \CRANpkg{plotly} package, which integrates plotly.js from the JavaScript graphing library.
 The usage of this library can be from a converting function, `ggplotly()`, or a standalone function, `plot_ly()`.
@@
 
-```{r animated-diagram, fig.cap="The diagram shows how the frames were used in the animated plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+```{r animated-diagram, fig.cap="The diagram shows how the frames were used in the animated plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/animated-diagram.png")
@@
 This issue can be eliminated by interpolating additional points in between the observations.
-In the `gganimate` package (@gganimate), the interpolation is achieved using the `tweenr` package (@tweenr), while in `plotly`, it utilizes d3.interpolate (@d3js).
+In the \CRANpkg{gganimate} package, the interpolation is achieved using the \CRANpkg{tweenr} package (@tweenr), while in \CRANpkg{plotly}, it utilizes d3.interpolate (@d3js).
 

### 2023-10-29 animbook-journal.Rmd
3rd version of the paper

@@
 
-```{r nyt, fig.cap="Screenshot of the New York Times animation, that is the motivation for this visualization package.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package..", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
 knitr::include_graphics("figures/NYT.png")
@@
 
-Before any visualizations can be performed, the users must first understand the data concept known as `tidy data` (@tidy-data).
-There are three fundamental key principles: each variable forms a column, each observation forms a row, and each type of observational unit forms a table.
-These three keys are Codd's third normal form (@relational), but phrase in the language of statistics.
-The tidy data format focuses on a single dataset instead of many connected datasets typically found in a relational database.
-
 ```{r data-diagram, fig.cap="The animation expects data with an ID and a time variable, along with a numerical variable (raw form), which is possibly converted to categorical (categorized).
-The data can be provided in the raw or categorized form, and will be processed into the format needed for the animation where the categorical variable is treated as a quantile and an animation frame variable is created.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
+The data can be provided in the raw or categorized form and will be processed into the format needed for the animation, where the categorical variable is treated as a quantile and an animation frame variable is created.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/data-diagram.png")
@@
 In the data structure, there are requirements that must be followed for reproducing the animation.
-The data must have at least ID and time variables, in addition to the measured variable which would usually be numeric, but may be categorical.
-The ID variable indicates the individual which is followed over time, such as the company name.
-There may also be a grouping variable, such as country where the company is registered.
-<!--These form what we call a unique ID.
-Also, the values variable can be either a numerical or categorical variable.
-The type of this variable will determine the stage the data set is in.
-This format ensures that during the data pre-processing, the R function understands what needs to be done with the data.-->
+First, the data set needs to be in the `tidy data` format (@tidy-data).
+The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well.
+The ID variable indicates the individual, which is followed over time, such as the company name.
+There may also be a grouping variable, such as the country where the company is registered.
 
@@
 The values are presented in the numerical format, which we call the 'raw' form.
-<!--because, in the New York Times animation, it is expressed in the categorical format.--> In most cases, the measured variable will be numerical and require transformation.
-The second form is categorized data, which involves transforming numerical variable into categories, typically quantiles.
-This transformation may not be necessary if it is already provided in the categorized format. The last form is animated data, where the frame is assigned to each unique ID.
+In most cases, the measured variable will be numerical and require transformation.
+The second form is categorized data, which involves transforming numerical variables into categories, typically quantiles.
+This transformation may not be necessary if it is already provided in the categorized format.
+The last form is animated data, where the frame is assigned to each unique ID.
 
@@
 The use of `transition_*()` functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time.
-The output from the `gganimate` can be rendered or saved in multiple formats.
-This includes `gifski_renderer()` from the \CRANpkg{gifski} package (@gifski) to save the animation in GIF format or `av_renderer()` from the `av` package (@av) to save it into a video file format.
+This includes `gifski_renderer()` from the \CRANpkg{gifski} package {@gifski} to save animation in GIF format or `av_renderer()` from the \CRANpkg{av} package {@av} to save it into a video file format.
 
- The `plotly` software is a graphing library that provides tools for creating an interactive plot in multiple programming languages, such as R, JavaScript, Python, and Julia.
+  The `plotly` software is a graphic library that provides tools for creating an interactive plot in multiple programming languages, such as R, JavaScript, Python, and Julia.
 In R, plotly can be accessed through the \CRANpkg{plotly} package, which integrates plotly.js from the JavaScript graphing library.
@@
 
-```{r animated-diagram, fig.cap="The diagram shows how the frames were used in the animated plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
+```{r animated-diagram, fig.cap="The diagram shows how the frames were used in the animated plot.
+Frame one is depicted in blue, and frame two is represented in red.
+Each blue component is mapped exclusively to the Frame 1 plot, while all the second-frame elements are excluded, and vice versa.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/animated-diagram.png")
@@
 
-  In `gganimate`, the issue of integrating controls can be addressed by setting the `renderer` argument to be `av_renderer()`, which allows the animation output to be in MP4 format.
-This format provides users with controls for the animation when opened on media applications provided in their systems.
+  In \CRANpkg{gganimate}, the issue of integrating controls can be addressed by setting the `renderer` argument to be `av_renderer()`, which allows the animation output to be in media applications provided in their systems.
 As for adjusting the length and speed of the animation, the `nframes` and `fps` arguments can be utilized.
@@
 
-  In the case of `plotly`, control integration is already implemented by default.
+  In the case of \CRANpkg{plotly}, control integration is already implemented by default.
 The `frame` and `transition` arguments within the `animation_opts()` function can be specified to set the length and speed of the animation.
@@
 
-  According to @mayer_2005, designing multimedia requires the designer to understand how people learn.
+  @mayer_2005 states that designing multimedia requires the designer to understand how people learn.
 One of the principles in @mayer_2005, Redundancy, suggests that a piece of excess information could overload the learners.
@@
 
-  From the New York Times animation, multiple information are shown in the visualization.
-It includes points in motion, distribution at the end, and proportional counters.
-However, this could lead to information overload (@mayer_2005).
-Therefore, the distribution at the end and proportional counters are excluded.
-Instead, the new element has been integrated, proportional shaded areas.
-It displays the proportion of observation within each group.
-
-```{r proportional-shade, fig.show="hold", out.width="50%", fig.cap="The plot shows the difference between the sigmoid and sine curves."}
+```{r proportional-shade, fig.show="hold", out.width="50%", fig.cap="The plot shows the difference between the sigmoid (shown in the left figure) and the sine curve (shown in the right figure).
+In the sigmoid, as the curve progresses, it becomes narrower, resulting in a less accurate representation of proportions compared to the sine curve."}
 knitr::include_graphics("figures/sigmoid-shade.png")
@@
 ```
+
+  In the animation, the proportional shaded area has been incorporated to facilitate a quick grasp of the proportion information.
+It displays the proportion of observation within each group.
+The design also needs to account for situations where the visualization lacks an adequate number of data points.
+In such cases, it can be challenging to visually discern the movement pattern of the subgroup, requiring the implementation of observation interpolation.
 
@@
 The issue is shown in Figure \@ref(fig:proportional-shade).
-While it does accurately represent the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation (@Shaffer_2019).
+While it does accurately represent the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation (@Shaffer_2019)
 
@@
 
-You can install the development version of animbook from [GitHub](https://github.com/KrisanatA/animbook) with:
+The development version of \pkg{animbook} can be installed from [GitHub](https://github.com/KrisanatA/animbook) with:
 
@@
 
-In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
-The first step is to turn the data into the right format for the plot function.
-The next stage is to create a ggplot object, which can then be inputted into the animation function.
-The last step is adding the animation settings to the ggplot object so the user can animate the plot using the `gganimate::animate()` function.
-The reason for this three-step process is that it allows the user who does not have a lot of experience to reproduce the animation while keeping the customization for an experienced user.
+In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation.
+The initial step is to reformat the data to the animated data structure as seen in \@ref(fig:data-diagram).
+The second stage is creating a `ggplot` object, which can be subsequently passed into the animation function.
+The final step involves transforming the `ggplot` to a `gganimate` object by integrating the animation settings.
+This three-step structure was implemented to ensure that users, regardless of their level of experience, can produce the animations with simplicity while retaining customization for more experienced users.
 
@@
 This issue can be resolved by using an alternative method, which is grouping values based on their absolute values.
-Users may also be interested in grouping the data based on different demographics, for example, ranking within a specific country.
+Users may also be interested in grouping the data based on different groups, for example, ranking within a specific country.
 This generalization leads to four different scaling methods for the numerical data.
@@
   arrange(gp, id)
-```
 
-```{r}
 absolute_group <- anim_prep(dbl_change, id, values, time, color = gp, group_scaling = gp, scaling = "absolute")
@@
   For the first and second scaling methods, group splitting is executed using the `quantiles()` and `cut()` functions.
-The `quantile` function from the `stats` R package (@stats) takes a numeric vector and outputs the corresponding quantiles to the given probabilities.
-The output from the `quantile` function is then used as the `breaks` argument for the cut function that is part of the base R packages.
+The `quantile()` function from the \CRANpkg{stats} package (@stats) takes a numeric vector and outputs the corresponding quantiles to the given probabilities.
+The output from the `quantile()` function is then used as the `breaks` argument for the `cut()` function that is part of the base R packages (@r).
 
   In contrast, the third and fourth scaling methods calculate the quantile based on the absolute values scales.
-The default approach is to break the group equally using the `seq()` function.
-The `seq()` function takes input values from the minimum and maximum values and increments by equal steps depending on the number of groups of interest.
+To avoid varying values scales among groups, the variables are first normalized to a range between 0 and 1.
+The default approach then breaks the group equally using the `seq()` function.
+The `seq()` function takes input values from 0 to 1 and increments by equal steps depending on the number of groups of interest.
 Additionally, the users have the option to specify the breaks themselves if they choose to do so.
@@
 It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values.
-It lets the `gganimate` or `plotly` to perceive where the observation would be on the plot at a given frame as seen in the \@ref(fig:animated-diagram).
+It lets the \CRANpkg{gganimate} or \CRANpkg{plotly} perceive where the observation would be on the plot at a given frame, as seen in Figure \@ref(fig:animated-diagram).
 
   The frame variable is assigned by sorting the data based on the ID and time using the `arrange()` function, followed by applying the `group_by()` function on the ID, allowing the `row_number()` function to be performed within each group.
-The functions mentioned in this paragraph are from the `dplyr` packages (@dplyr).
+The functions mentioned in this paragraph are from the \CRANpkg{dplyr} package (@dplyr).
 
@@
 The `anim_prep()` function is used for raw data format, while the `anim_prep_cat()` function is for categorized data format.
-There are additional arguments that facilitate the users for more customization.
+There are additional arguments that allow users for more customization.
 
-  In the `anim_prep()` and `anim_prep_cat()`, there are required arguments that need to be specified. The lists are as follows:
+```{r}
+argument <- c("data", "id", "values", "time", "ngroup", "breaks", "group_scaling",
+               "scaling", "order", "label", "color", "time_dependent", "runif_min",
+               "runif_max")
 
-  - data: A data frame containing the data to be prepared for visualization.
-  - id: The column name that represents the unique identifier variable.
-  - values: The column name that contains the numeric values to be visualized.
-  - time: The column name represents the time variable.
+description <- c("A data frame containing the data to be prepared for visualization.",
+                 "The column name that represents the unique identifier variable.",
+                 "The column name that contains the numeric values to be visualized.",
+                 "The column name represents the time variable.",
+                 "The number of groups or categories to create for scaling values.",
+                 "A vector of breaks for creating bins.",
+                 "The column name that represents the grouping variable.",
+                 "The scaling method to be used; \"rank\" or \"absolute.\"",
+                 "A vector of order for sorting the category values.",
+                 "A vector of labels to be used for the y-axis in the visualization.",
+                 "The column name to be used in ggplot2::aes() for the plot function.",
+                 "Logical. Should the visualization be time-dependent? Default is TRUE.",
+                 "The minimum value for random addition to frame numbers.",
+                 "The maximum value for random addition to frame numbers.")
 
-  As shown previously, there are a total of four different scaling for the `anim_prep()` function. Both the use can customization of these scaling can be set using the following arguments:
+argument_table <- tibble::tibble(Argument = argument,
+                         Description = description)
+```
 
-  - ngroup:	The number of groups or categories to create for scaling values.
-  - breaks: A vector of breaks for creating bins.
-  - group_scaling: The column name that represents the grouping variable.
-  - scaling: The scaling method to be used; "rank" or "absolute."
+```{r tbl-required}
+argument_table |> 
+  filter(argument %in% c("data", "id", "values", "time")) |> 
+  knitr::kable(caption = "The required argument for the prep function.")
+```
 
-  For the `anim_prep_cat()` function, the arguments that allowed the user to order the category are by using this argument:
+```{r tbl-animprep}
+argument_table |> 
+  filter(argument %in% c("ngroup", "breaks", "group_scaling", "scaline")) |> 
+  knitr::kable(caption = "The argument in the anim\\_prep for customized the data scaling.")
+```
 
-  - order: A vector of order for sorting the category values.
+```{r tbl-animprepcat}
+argument_table |> 
+  filter(argument %in% c("order")) |> 
+  knitr::kable(caption = "The argument in the anim\\_prep\\_cat for customized the order of the category.")
+```
 
-  Then, for further customization regarding how the final visualization looks. The following arguments can be adjusted:
+```{r tbl-visual}
+argument_table |> 
+  filter(argument %in% c("label", "color", "time_dependent", 
+                         "runif_min", "runif_max")) |> 
+  knitr::kable(caption = "The additional argument for customizing the aesthetics of the visualization.")
+```
 
-  - label: A vector of labels to be used for the y-axis in the visualization.
-  - color: The column name to be used in ggplot2::aes() for the plot function.
-  - time_dependent: Logical. Should the visualization be time-dependent? Default is TRUE.
-  - runif_min: The minimum value for random addition to frame numbers.
-  - runif_max: The maximum value for random addition to frame numbers.
+  In the `anim_prep()` and `anim_prep_cat()`, there are required arguments that need to be specified. The lists are in the Table \@ref(tab:tbl-required).
+
+  As shown previously, there are a total of four different scaling for the `anim_prep()` function.
+Both the use can customization of these scaling can be set using the following arguments in Table \@ref(tab:tbl-animprep).
+
+  For the `anim_prep_cat()` function, the arguments that allowed the user to order the category are by using this argument in Table \@ref(tab:tbl-animprepcat).
+
+  Then, for further customization regarding how the final visualization looks. The following arguments in Table \@ref(tab:tbl-visual) can be adjusted.
 
@@
 This function also responds by interpolating the non-linear path.
-It performs this task by mapping the `sine()` function provided in this package to each observation using the `map()` function from the `purrr` package (@purrr).
+It performs this task by mapping the `sine()` function provided in this package to each observation using the `map()` function from the \CRANpkg{purrr} package (@purrr).
 The frame is recalculated using the same method mentioned in the data preprocessing section.
@@
 
-```{r shade-algorithm, fig.show="hold", out.width="50%", fig.cap="The plot shows how does the algorithm work."}
+```{r shade-algorithm, fig.show="hold", out.width="50%", fig.cap="The plot shows how the algorithm for the sankey\\_shade() function works.
+The left figure represents the initial step of the algorithm, which calculates all the corner points.
+The right figure demonstrates the subsequent step, where points in-between the left and right are interpolated using the sine() function."}
 knitr::include_graphics("figures/sankey-shade-1.png")
@@
 
-  The algorithm behind the `sankey_shade()` function is illustrated in Figure \@ref(fig:shade-algorithm).
+  The algorithm behind the `sankey_shade()` function for generating the proportional shaded data is illustrated in Figure \@ref(fig:shade-algorithm).
 It started by calculating the corner points for all of the shaded areas.
@@
   Now that the data are in the right format for the wallaby's plot, the `geom_point()` function is used for plotting the observations, `geom_polygon()` is used for creating the proportional shaded areas, and `geom_text()` is used for creating labels.
-These three functions are from the `ggplot2` package (@ggplot2).
+These three functions are from the \CRANpkg{ggplot2} package.
 During this process, the aesthetics mapping will be different depending on the rendering tool to be used, which can be either `gganimate` or `plotly`.
@@
 
-  The arguments for Wallaby's plot are as follows.
-  - object: The animbook object returned from the prep function.
-  - group_palette: The vector of the palette used by the function to supply the color to each group.
-  - shade_palette: The vector of the palette used by the function to supply the color to the shaded area.
-  - rendering: The choice of method used to create and display the plot, either gganimate or plotly.
-  - subset: A character string specifying the variable used for subsetting the data. The "top" and "bottom" strings can also be used in this argument.
-  - relation: The choice of relationship for the values to display on the plot, either "one_many." or "many_one."
-  - total_point: The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.
-  - height: The proportion of the area occupied by the observations in the shaded areas.
-  - width: The distance between the first and last observation in the animation.
-  - size: The point size.
-  - alpha: The opacity of the proportional shaded areas.
+```{r, eval=knitr::is_html_output()}
+argument2 <- c("object", "group_palette", "shade_palette", "rendering",
+               "subset", "relation", "total_point", "height", "width", "size",
+               "alpha")
+
+description2 <- c("The animbook object returned from the prep function.",
+                  "The vector of the palette used by the function to supply the color to each group.",
+                  "The vector of the palette used by the function to supply the color to the shaded area.",
+                  "The choice of method used to create and display the plot, either gganimate or plotly.",
+                  "A character string specifying the variable used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument.",
+                  "The choice of relationship for the values to display on the plot, either \"one_many.\" or \"many_one.\"",
+                  "The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.",
+                  "The proportion of the area occupied by the observations in the shaded areas.",
+                  "The distance between the first and last observation in the animation.",
+                  "The point size.",
+                  "The opacity of the proportional shaded areas.")
+
+argument_table2 <- tibble::tibble(Argument = argument2,
+                                  Description = description2)
+```
+
+```{r, eval=knitr::is_html_output()}
+argument_table2 |> 
+  knitr::kable(caption = "The arguments for the wallaby\\_plot function.")
+```
+
+```{r, eval=knitr::is_latex_output()}
+argument2 <- c("object", "group_palette", "shade_palette", "rendering",
+               "subset", "relation", "total_point", "height", "width", "size",
+               "alpha")
+
+description2 <- c("The animbook object returned from the prep function.",
+                  "The vector of the palette used by the function to supply the color to each group.",
+                  "The vector of the palette used by the function to supply the color to the shaded area.",
+                  "The choice of method used to create and display the plot, either gganimate or plotly.",
+                  "A character string specifying the variable used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument.",
+                  "The choice of relationship for the values to display on the plot, either \"one_many.\" or \"many_one.\"",
+                  "The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.",
+                  "The proportion of the area occupied by the observations in the shaded areas.",
+                  "The distance between the first and last observation in the animation.",
+                  "The point size.",
+                  "The opacity of the proportional shaded areas.")
+
+argument_table2 <- tibble::tibble(Argument = argument2,
+                                  Description = description2)
+```
+
+```{r, eval=knitr::is_latex_output()}
+argument_table2 |> 
+  kableExtra::kable(caption = "The arguments for the wallaby\\_plot function.", format = "latex") |> 
+  kableExtra::column_spec(2, width = "30em")
+```
 
@@
 This function will automatically detect which rendering method was specified in the previous steps and add the minimum requirement functions accordingly.
-By default, if the user specifies the rendering as `gganimate`, then it will add the `transition_time()` function from the `gganimate` package (@gganimate).
-Otherwise, the `animation_opts()` function will be added from the `plotly` package (@plotly).
+By default, if the user specifies the rendering as `gganimate`, then it will add the `transition_time()` function from the \CRANpkg{gganimate} package.
+Otherwise, the `animation_opts()` function will be added from the \CRANpkg{plotly} package.
 
@@
   Once the `ggplot` object is obtained, the `anim_animate()` function can be used to transform it into a `gganimate` object.
-This then can be passed onto the `gganimate::animate()` function for rendering.
+This then can be passed onto the `animate()` function from the \CRANpkg{gganimate} for rendering.
 
@@
 ```
-
-```{r catchange-figure, fig.cap = "Animate visualization using example data.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+```{r catchange-figure, fig.cap = "Animate visualization using example data.
+All of the X observations stay within the same group, while Y observations change from group A to group E.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
 knitr::include_graphics("figures/animation-example.png")
@@
 
-```{r catchange-gif, out.extra="class = 'gif'", fig.cap = "Animate visualization using example data.", eval=knitr::is_html_output()}
+```{r catchange-gif, out.extra="class = 'gif'", fig.cap = "Animate visualization using example data.
+All of the X observations stay within the same group, while Y observations change from group A to group E.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/catchange.gif")
@@
 An animation will be created using the `animbook` package to enhance communication with data.
-
 First, filter the countries to include only the United States and Japan.
@@
 ```{r, echo=TRUE}
+# library(animbook)
+# library(dplyr)
+
 data <- osiris |> 
@@
 
+kan_p <- kangaroo_plot(accounting)
+
 p2 <- anim_animate(p)
+kan_p2 <- anim_animate(kan_p)
 ```
@@
                      nframes = 400, width = 9, units = "in", res = 150)
+
+gganimate::anim_save("figures/kan-osiris.gif", kan_p2, height = 8, fps = 10,
+                     nframes = 400, width = 9, units = "in", res = 150)
 ```
@@
 gganimate::animate(p2)
+
+gganimate::animate(kan_p2)
 ```
@@
 
+```{r kan-osiris-figure, fig.cap = "The animate visualization shows the movement of the companies between the groups from 2006 to 2018.
+In 2006, there were no Japanese companies in the Top 25\\% group.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+knitr::include_graphics("figures/osiris.png")
+```
+
+```{r kan-osiris-gif, out.extra="class = 'gif'", fig.cap = "The animate visualization shows the movement of the companies between the groups from 2006 to 2018.
+In 2006, there were no Japanese companies in the Top 25% group.", eval=knitr::is_html_output()}
+knitr::include_graphics("figures/kan-osiris.gif")
+```
+
   From the plot, a higher proportion of US companies have exited the market, confirming the OECD report (@oecd_report) that the United States has a higher turnover rate than Japan.
 An interesting finding is that all of the top 25% of companies that exited the market are only from the United States.
-It may be due to the absence of Japanese companies in the top 25% in 2006, or it could be that Japanese companies in the top 25% did not delist.
+It may be due to the absence of Japanese companies in the Top 25% in 2006, or it could be that Japanese companies who started in the Top 25% in 2006 did not delist.
+Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`, confirmed that there are non-Japanese companies that start at the Top 25% in 2006.
 
@@
 The Australian Election Study data was collected from ADA Dataverse (@aeles).
-The dataset included in the `animbook` package contains 1,468 rows and 4 variables of information: ID, year, party, and gender.
+The dataset included in the \pkg{animbook} package contains 1,468 rows and 4 variables of information: ID, year, party, and gender.
 This dataset comprises survey responses from the 2019 election.
@@
 
-From the animation, it is clear that individuals who identified their gender as 'others' shifted their votes from the Liberal, the leading party in 2016, to the Greens party.
+From Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:voter-figure}','\\@ref(fig:voter-gif)'))`, it is clear that individuals who identified their gender as 'others' shifted their votes from the Liberal, the leading party in 2016, to the Greens party.
 These changes could be due to the Green Party's "A FAIRER, MORE EQUAL COMMUNITY" campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.
@@
 Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences.
-In the current version of `animbook`, the feature to have different speed for each observation have not yet been implemented.
+In the current version of \pkg{animbook}, the feature to have different speeds for each observation has not yet been implemented.
 This feature will introduce a new dimension that allows the users to explore the data further.
@@
 Additionally, both new animated and static plots could also be added, as seen in the New York Times article (@the_new_york_time), to compare the demographics at a specific point in time.
-On top of that, the `cli` package (@cli) could be used for a more aesthetically pleasing command-line interface.
+On top of that, the \CRANpkg{cli} package (@cli) could be used for a more aesthetically pleasing command-line interface.
 
@@
 
-This paper is created using the `rjtools` packages (@rjtools) and is based on the 0.0.0.9 version of the `animbook` package.
+This paper is created using the \CRANpkg{rjtools} packages (@rjtools) and is based on the 0.0.0.9 version of the \pkg{animbook} package.
 This version is available on [GitHub](https://github.com/KrisanatA/animbook).

### 2023-10-29 animbook-journal.tex
3rd version of the paper

@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\hypertarget{intro}{%
+\section{Introduction}\label{intro}}
 
@@
 
-\hypertarget{NYT}{%
-\section{Explanation of the New York Times visualization}\label{NYT}}
+\hypertarget{NYTvis}{%
+\section{Explanation of the New York Times visualization}\label{NYTvis}}
 
@@
 
-\caption{Screenshot of the New York Times animation, that is the motivation for this visualization package.}\label{fig:nyt}
+\caption{Screenshot of the New York Times animation, which is the motivation for this visualization package..}\label{fig:nyt}
 \end{figure}
@@
 
-Before any visualizations can be performed, the users must first understand the data concept known as \texttt{tidy\ data} (Wickham (2014)).
-There are three fundamental key principles: each variable forms a column, each observation forms a row, and each type of observational unit forms a table.
-These three keys are Codd's third normal form (Codd (1990)), but phrase in the language of statistics.
-The tidy data format focuses on a single dataset instead of many connected datasets typically found in a relational database.
-
 \begin{figure}
@@
 
-\caption{The diagram shows what are the expected data forms.}\label{fig:data-diagram}
+\caption{The animation expects data with an ID and a time variable, along with a numerical variable (raw form), which is possibly converted to categorical (categorized).
+The data can be provided in the raw or categorized form and will be processed into the format needed for the animation, where the categorical variable is treated as a quantile and an animation frame variable is created.}\label{fig:data-diagram}
 \end{figure}
@@
 In the data structure, there are requirements that must be followed for reproducing the animation.
-The data must have ID and time variables.
-These form what we call a unique ID.
-Also, the values variable can be either a numerical or categorical variable.
-The type of this variable will determine the stage the data set is in.
-This format ensures that during the data pre-processing, the R function understands what needs to be done with the data.
+First, the data set needs to be in the \texttt{tidy\ data} format (Wickham (2014)).
+The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well.
+The ID variable indicates the individual, which is followed over time, such as the company name.
+There may also be a grouping variable, such as the country where the company is registered.
 
-Figure \ref{fig:data-diagram} shows which stages the data is in, given the type of values variable.
-Start with the raw data structure.
-The values are presented in the numerical format.
-It is referred to as `raw' because, in the New York Times animation, it is expressed in the categorical format.
-However, in most cases, the data is in numerical values and requires transformation.
-The second form is categorized data, as mentioned earlier, which involves transforming numerical into categories.
-This transformation may not be necessary if it already exists in the categorized format, as in the case of political data (party affiliation).
+Figure \ref{fig:data-diagram} illustrates the expected format of the data and variables created to prepare it for the animation.
+We start with the raw data structure.
+The values are presented in the numerical format, which we call the `raw' form.
+In most cases, the measured variable will be numerical and require transformation.
+The second form is categorized data, which involves transforming numerical variables into categories, typically quantiles.
+This transformation may not be necessary if it is already provided in the categorized format.
 The last form is animated data, where the frame is assigned to each unique ID.
 
-\hypertarget{animation-tools}{%
-\section{Animation tools}\label{animation-tools}}
+\hypertarget{animation}{%
+\section{Animation tools}\label{animation}}
 
@@
 
-\caption{The diagram shows how the animation is done using the successive pictures.}\label{fig:animation-diagram}
+\caption{The diagram shows how the animation is done using the successive pictures.
+When small changes are seen in quick succession, it will appear as if the objects are in motion.}\label{fig:animation-diagram}
 \end{figure}
 
-The principle underlying the animation is called persistence of vision (Webster (2005)).
+A principle important for designing a useful animation is called persistence of vision (Webster (2005)).
 When an image disappears, the brain will retain the previous images for a brief period of time.
@@
 This is illustrated in Figure \ref{fig:animation-diagram}.
-There are multiple ways to create an animation in the R environment (R Core Team (2021)), including packages like \texttt{gganimate} and \texttt{Plotly}.
 
-The \texttt{gganimate} package (Pedersen and Robinson (2020)) is an extension from the \texttt{ggplot2} package (Wickham (2016)) to include the description of an animation.
+There are multiple ways to create an animation in the R environment (R Core Team (2021)), including the packages \CRANpkg{gganimate} (Pedersen and Robinson (2020)) and \CRANpkg{plotly} (Sievert (2020)).
+
+The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (Wickham (2016)) to include the description of an animation.
 It added new grammar classes to the plot object, allowing it to understand how the plot should change over time.
 The use of \texttt{transition\_*()} functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time.
-The output from the \texttt{gganimate} can be rendered or saved in multiple formats.
-This includes \texttt{gifski\_renderer()} from the \texttt{gifski} package (Ooms (2023b)) to save the animation in GIF format or \texttt{av\_renderer()} from the \texttt{av} package (Ooms (2023a)) to save it into a video file format.
+This includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package \{Ooms (2023b)\} to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package \{Ooms (2023a)\} to save it into a video file format.
 
-Plotly is a graphing library that provides tools for creating an interactive plot in multiple programming languages, such as R, JavaScript, Python, and Julia.
-In R, plotly can be accessed through the \texttt{plotly} package (Sievert (2020)), which integrates plotly.js from the JavaScript graphing library.
+The \texttt{plotly} software is a graphic library that provides tools for creating an interactive plot in multiple programming languages, such as R, JavaScript, Python, and Julia.
+In R, plotly can be accessed through the \CRANpkg{plotly} package, which integrates plotly.js from the JavaScript graphing library.
 The usage of this library can be from a converting function, \texttt{ggplotly()}, or a standalone function, \texttt{plot\_ly()}.
@@
 
-\caption{The diagram shows how the frames were used in the animated plot.}\label{fig:animated-diagram}
+\caption{The diagram shows how the frames were used in the animated plot.
+Frame one is depicted in blue, and frame two is represented in red.
+Each blue component is mapped exclusively to the Frame 1 plot, while all the second-frame elements are excluded, and vice versa.}\label{fig:animated-diagram}
 \end{figure}
@@
 This issue can be eliminated by interpolating additional points in between the observations.
-In the \texttt{gganimate} package (Pedersen and Robinson (2020)), the interpolation is achieved using the \texttt{tweenr} package (Pedersen (2022)), while in \texttt{plotly}, it utilizes d3.interpolate (Bostock (2012)).
+In the \CRANpkg{gganimate} package, the interpolation is achieved using the \CRANpkg{tweenr} package (Pedersen (2022)), while in \CRANpkg{plotly}, it utilizes d3.interpolate (Bostock (2012)).
 
@@
 
-In \texttt{gganimate}, the issue of integrating controls can be addressed by setting the \texttt{renderer} argument to be \texttt{av\_renderer()}, which allows the animation output to be in MP4 format.
-This format provides users with controls for the animation when opened on media applications provided in their systems.
+In \CRANpkg{gganimate}, the issue of integrating controls can be addressed by setting the \texttt{renderer} argument to be \texttt{av\_renderer()}, which allows the animation output to be in media applications provided in their systems.
 As for adjusting the length and speed of the animation, the \texttt{nframes} and \texttt{fps} arguments can be utilized.
@@
 
-In the case of \texttt{plotly}, control integration is already implemented by default.
+In the case of \CRANpkg{plotly}, control integration is already implemented by default.
 The \texttt{frame} and \texttt{transition} arguments within the \texttt{animation\_opts()} function can be specified to set the length and speed of the animation.
 
-\hypertarget{visualization-design}{%
-\section{Visualization design}\label{visualization-design}}
+\hypertarget{design}{%
+\section{Visualization design}\label{design}}
 
@@
 
-According to R.
+R.
 E.
-Mayer (2005), designing multimedia requires the designer to understand how people learn.
+Mayer (2005) states that designing multimedia requires the designer to understand how people learn.
 One of the principles in R.
@@
 
-From the New York Times animation, multiple information are shown in the visualization.
-It includes points in motion, distribution at the end, and proportional counters.
-However, this could lead to information overload (R.
-E.
-Mayer (2005)).
-Therefore, the distribution at the end and proportional counters are excluded.
-Instead, the new element has been integrated, proportional shaded areas.
+\begin{figure}
+\includegraphics[width=0.5\linewidth]{figures/sigmoid-shade} \includegraphics[width=0.5\linewidth]{figures/sine-shade} \caption{The plot shows the difference between the sigmoid (shown in the left figure) and the sine curve (shown in the right figure).
+In the sigmoid, as the curve progresses, it becomes narrower, resulting in a less accurate representation of proportions compared to the sine curve.}\label{fig:proportional-shade}
+\end{figure}
+
+In the animation, the proportional shaded area has been incorporated to facilitate a quick grasp of the proportion information.
 It displays the proportion of observation within each group.
-
-\begin{figure}
-\includegraphics[width=0.5\linewidth]{figures/sigmoid-shade} \includegraphics[width=0.5\linewidth]{figures/sine-shade} \caption{The plot shows the difference between the sigmoid and sine curves.}\label{fig:proportional-shade}
-\end{figure}
+The design also needs to account for situations where the visualization lacks an adequate number of data points.
+In such cases, it can be challenging to visually discern the movement pattern of the subgroup, requiring the implementation of observation interpolation.
 
@@
 The issue is shown in Figure \ref{fig:proportional-shade}.
-While it does accurately represent the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation (Shaffer (2019)).
+While it does accurately represent the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation (Shaffer (2019))
 
@@
 
-You can install the development version of animbook from \href{https://github.com/KrisanatA/animbook}{GitHub} with:
+The development version of \pkg{animbook} can be installed from \href{https://github.com/KrisanatA/animbook}{GitHub} with:
 
@@
 
-\hypertarget{overviw-of-functions}{%
-\subsection{Overviw of functions}\label{overviw-of-functions}}
+\hypertarget{overview-of-functions}{%
+\subsection{Overview of functions}\label{overview-of-functions}}
 
-In designing the package for reproducing the New York Times animated plot, the package ended up with a three-step process in recreating the animation.
-The first step is to turn the data into the right format for the plot function.
-The next stage is to create a ggplot object, which can then be inputted into the animation function.
-The last step is adding the animation settings to the ggplot object so the user can animate the plot using the \texttt{gganimate::animate()} function.
-The reason for this three-step process is that it allows the user who does not have a lot of experience to reproduce the animation while keeping the customization for an experienced user.
+In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation.
+The initial step is to reformat the data to the animated data structure as seen in \ref{fig:data-diagram}.
+The second stage is creating a \texttt{ggplot} object, which can be subsequently passed into the animation function.
+The final step involves transforming the \texttt{ggplot} to a \texttt{gganimate} object by integrating the animation settings.
+This three-step structure was implemented to ensure that users, regardless of their level of experience, can produce the animations with simplicity while retaining customization for more experienced users.
 
@@
 For the first and second scaling methods, group splitting is executed using the \texttt{quantiles()} and \texttt{cut()} functions.
-The \texttt{quantile} function from the \texttt{stats} R package (R Core Team (2013)) takes a numeric vector and outputs the corresponding quantiles to the given probabilities.
-The output from the \texttt{quantile} function is then used as the \texttt{breaks} argument for the cut function that is part of the base R packages.
+The \texttt{quantile()} function from the \CRANpkg{stats} package (R Core Team (2013)) takes a numeric vector and outputs the corresponding quantiles to the given probabilities.
+The output from the \texttt{quantile()} function is then used as the \texttt{breaks} argument for the \texttt{cut()} function that is part of the base R packages (R Core Team (2021)).
 
 In contrast, the third and fourth scaling methods calculate the quantile based on the absolute values scales.
-The default approach is to break the group equally using the \texttt{seq()} function.
-The \texttt{seq()} function takes input values from the minimum and maximum values and increments by equal steps depending on the number of groups of interest.
+To avoid varying values scales among groups, the variables are first normalized to a range between 0 and 1.
+The default approach then breaks the group equally using the \texttt{seq()} function.
+The \texttt{seq()} function takes input values from 0 to 1 and increments by equal steps depending on the number of groups of interest.
 Additionally, the users have the option to specify the breaks themselves if they choose to do so.
@@
 It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values.
-It lets the \texttt{gganimate} or \texttt{plotly} to perceive where the observation would be on the plot at a given frame as seen in the \ref{fig:animated-diagram}.
+It lets the \CRANpkg{gganimate} or \CRANpkg{plotly} perceive where the observation would be on the plot at a given frame, as seen in Figure \ref{fig:animated-diagram}.
 
 The frame variable is assigned by sorting the data based on the ID and time using the \texttt{arrange()} function, followed by applying the \texttt{group\_by()} function on the ID, allowing the \texttt{row\_number()} function to be performed within each group.
-The functions mentioned in this paragraph are from the \texttt{dplyr} packages (Wickham et al.
+The functions mentioned in this paragraph are from the \CRANpkg{dplyr} package (Wickham et al.
 (2023)).
@@
 The \texttt{anim\_prep()} function is used for raw data format, while the \texttt{anim\_prep\_cat()} function is for categorized data format.
-There are additional arguments that facilitate the users for more customization.
+There are additional arguments that allow users for more customization.
 
-In the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()}, there are required arguments that need to be specified. The lists are as follows:
+\begin{table}
 
-\begin{itemize}
-\tightlist
-\item
-  data: A data frame containing the data to be prepared for visualization.
-\item
-  id: The column name that represents the unique identifier variable.
-\item
-  values: The column name that contains the numeric values to be visualized.
-\item
-  time: The column name represents the time variable.
-\end{itemize}
+\caption{\label{tab:tbl-required}The required argument for the prep function.}
+\centering
+\begin{tabular}[t]{l|l}
+\hline
+Argument & Description\\
+\hline
+data & A data frame containing the data to be prepared for visualization.\\
+\hline
+id & The column name that represents the unique identifier variable.\\
+\hline
+values & The column name that contains the numeric values to be visualized.\\
+\hline
+time & The column name represents the time variable.\\
+\hline
+\end{tabular}
+\end{table}
 
-As shown previously, there are a total of four different scaling for the \texttt{anim\_prep()} function. Both the use can customization of these scaling can be set using the following arguments:
+\begin{table}
 
-\begin{itemize}
-\tightlist
-\item
-  ngroup: The number of groups or categories to create for scaling values.
-\item
-  breaks: A vector of breaks for creating bins.
-\item
-  group\_scaling: The column name that represents the grouping variable.
-\item
-  scaling: The scaling method to be used; ``rank'' or ``absolute.''
-\end{itemize}
+\caption{\label{tab:tbl-animprep}The argument in the anim\_prep for customized the data scaling.}
+\centering
+\begin{tabular}[t]{l|l}
+\hline
+Argument & Description\\
+\hline
+ngroup & The number of groups or categories to create for scaling values.\\
+\hline
+breaks & A vector of breaks for creating bins.\\
+\hline
+group\_scaling & The column name that represents the grouping variable.\\
+\hline
+\end{tabular}
+\end{table}
 
-For the \texttt{anim\_prep\_cat()} function, the arguments that allowed the user to order the category are by using this argument:
+\begin{table}
 
-\begin{itemize}
-\tightlist
-\item
-  order: A vector of order for sorting the category values.
-\end{itemize}
+\caption{\label{tab:tbl-animprepcat}The argument in the anim\_prep\_cat for customized the order of the category.}
+\centering
+\begin{tabular}[t]{l|l}
+\hline
+Argument & Description\\
+\hline
+order & A vector of order for sorting the category values.\\
+\hline
+\end{tabular}
+\end{table}
 
-Then, for further customization regarding how the final visualization looks. The following arguments can be adjusted:
+\begin{table}
 
-\begin{itemize}
-\tightlist
-\item
-  label: A vector of labels to be used for the y-axis in the visualization.
-\item
-  color: The column name to be used in ggplot2::aes() for the plot function.
-\item
-  time\_dependent: Logical. Should the visualization be time-dependent? Default is TRUE.
-\item
-  runif\_min: The minimum value for random addition to frame numbers.
-\item
-  runif\_max: The maximum value for random addition to frame numbers.
-\end{itemize}
+\caption{\label{tab:tbl-visual}The additional argument for customizing the aesthetics of the visualization.}
+\centering
+\begin{tabular}[t]{l|l}
+\hline
+Argument & Description\\
+\hline
+label & A vector of labels to be used for the y-axis in the visualization.\\
+\hline
+color & The column name to be used in ggplot2::aes() for the plot function.\\
+\hline
+time\_dependent & Logical. Should the visualization be time-dependent? Default is TRUE.\\
+\hline
+runif\_min & The minimum value for random addition to frame numbers.\\
+\hline
+runif\_max & The maximum value for random addition to frame numbers.\\
+\hline
+\end{tabular}
+\end{table}
+
+In the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()}, there are required arguments that need to be specified. The lists are in the Table \ref{tab:tbl-required}.
+
+As shown previously, there are a total of four different scaling for the \texttt{anim\_prep()} function.
+Both the use can customization of these scaling can be set using the following arguments in Table \ref{tab:tbl-animprep}.
+
+For the \texttt{anim\_prep\_cat()} function, the arguments that allowed the user to order the category are by using this argument in Table \ref{tab:tbl-animprepcat}.
+
+Then, for further customization regarding how the final visualization looks. The following arguments in Table \ref{tab:tbl-visual} can be adjusted.
 
@@
 \begin{itemize}
+\tightlist
 \item
@@
   \texttt{funnel\_web\_plot()}: the faceted static plot by time variable.
+\end{itemize}
 
@@
 This function also responds by interpolating the non-linear path.
-It performs this task by mapping the \texttt{sine()} function provided in this package to each observation using the \texttt{map()} function from the \texttt{purrr} package (Wickham and Henry (2023)).
+It performs this task by mapping the \texttt{sine()} function provided in this package to each observation using the \texttt{map()} function from the \CRANpkg{purrr} package (Wickham and Henry (2023)).
 The frame is recalculated using the same method mentioned in the data preprocessing section.
 The \texttt{sankey\_shade()} function is called to generate the proportional shaded data.
-\end{itemize}
 
 \begin{figure}
-\includegraphics[width=0.5\linewidth]{figures/sankey-shade-1} \includegraphics[width=0.5\linewidth]{figures/sankey-shade-2} \caption{The plot shows how does the algorithm work.}\label{fig:shade-algorithm}
+\includegraphics[width=0.5\linewidth]{figures/sankey-shade-1} \includegraphics[width=0.5\linewidth]{figures/sankey-shade-2} \caption{The plot shows how the algorithm for the sankey\_shade() function works.
+The left figure represents the initial step of the algorithm, which calculates all the corner points.
+The right figure demonstrates the subsequent step, where points in-between the left and right are interpolated using the sine() function.}\label{fig:shade-algorithm}
 \end{figure}
 
-The algorithm behind the \texttt{sankey\_shade()} function is illustrated in Figure \ref{fig:shade-algorithm}.
+The algorithm behind the \texttt{sankey\_shade()} function for generating the proportional shaded data is illustrated in Figure \ref{fig:shade-algorithm}.
 It started by calculating the corner points for all of the shaded areas.
@@
 Now that the data are in the right format for the wallaby's plot, the \texttt{geom\_point()} function is used for plotting the observations, \texttt{geom\_polygon()} is used for creating the proportional shaded areas, and \texttt{geom\_text()} is used for creating labels.
-These three functions are from the \texttt{ggplot2} package (Wickham (2016)).
+These three functions are from the \CRANpkg{ggplot2} package.
 During this process, the aesthetics mapping will be different depending on the rendering tool to be used, which can be either \texttt{gganimate} or \texttt{plotly}.
@@
 
-The arguments for Wallaby's plot are as follows.
-- object: The animbook object returned from the prep function.
-- group\_palette: The vector of the palette used by the function to supply the color to each group.
-- shade\_palette: The vector of the palette used by the function to supply the color to the shaded area.
-- rendering: The choice of method used to create and display the plot, either gganimate or plotly.
-- subset: A character string specifying the variable used for subsetting the data. The ``top'' and ``bottom'' strings can also be used in this argument.
-- relation: The choice of relationship for the values to display on the plot, either ``one\_many.'' or ``many\_one.''
-- total\_point: The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.
-- height: The proportion of the area occupied by the observations in the shaded areas.
-- width: The distance between the first and last observation in the animation.
-- size: The point size.
-- alpha: The opacity of the proportional shaded areas.
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-8}The arguments for the wallaby\_plot function.}
+\centering
+\begin{tabular}[t]{l|>{\raggedright\arraybackslash}p{30em}}
+\hline
+Argument & Description\\
+\hline
+object & The animbook object returned from the prep function.\\
+\hline
+group\_palette & The vector of the palette used by the function to supply the color to each group.\\
+\hline
+shade\_palette & The vector of the palette used by the function to supply the color to the shaded area.\\
+\hline
+rendering & The choice of method used to create and display the plot, either gganimate or plotly.\\
+\hline
+subset & A character string specifying the variable used for subsetting the data. The "top" and "bottom" strings can also be used in this argument.\\
+\hline
+relation & The choice of relationship for the values to display on the plot, either "one\_many." or "many\_one."\\
+\hline
+total\_point & The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.\\
+\hline
+height & The proportion of the area occupied by the observations in the shaded areas.\\
+\hline
+width & The distance between the first and last observation in the animation.\\
+\hline
+size & The point size.\\
+\hline
+alpha & The opacity of the proportional shaded areas.\\
+\hline
+\end{tabular}
+\end{table}
 
@@
 This function will automatically detect which rendering method was specified in the previous steps and add the minimum requirement functions accordingly.
-By default, if the user specifies the rendering as \texttt{gganimate}, then it will add the \texttt{transition\_time()} function from the \texttt{gganimate} package (Pedersen and Robinson (2020)).
-Otherwise, the \texttt{animation\_opts()} function will be added from the \texttt{plotly} package (Sievert (2020)).
+By default, if the user specifies the rendering as \texttt{gganimate}, then it will add the \texttt{transition\_time()} function from the \CRANpkg{gganimate} package.
+Otherwise, the \texttt{animation\_opts()} function will be added from the \CRANpkg{plotly} package.
 
@@
 #>    <fct> <int> <dbl> <dbl> <fct>
-#>  1 1      2020     5    21 X    
-#>  2 1      2023     5    22 X    
-#>  3 2      2020     5    31 X    
-#>  4 2      2023     5    32 X    
-#>  5 3      2020     5     6 X    
-#>  6 3      2023     5     7 X    
-#>  7 4      2020     5    27 X    
-#>  8 4      2023     5    28 X    
-#>  9 5      2020     5    20 X    
-#> 10 5      2023     5    21 X
+#>  1 1      2020     5    33 X    
+#>  2 1      2023     5    34 X    
+#>  3 2      2020     5     5 X    
+#>  4 2      2023     5     6 X    
+#>  5 3      2020     5    48 X    
+#>  6 3      2023     5    49 X    
+#>  7 4      2020     5    33 X    
+#>  8 4      2023     5    34 X    
+#>  9 5      2020     5     3 X    
+#> 10 5      2023     5     4 X
 \end{verbatim}
@@
 #>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
-#>   ..$ frame: num [1:400] 21 22 31 32 6 7 27 28 20 21 ...
+#>   ..$ frame: num [1:400] 33 34 5 6 48 49 33 34 3 4 ...
 #>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-6-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-10-1} \end{center}
 
 Once the \texttt{ggplot} object is obtained, the \texttt{anim\_animate()} function can be used to transform it into a \texttt{gganimate} object.
-This then can be passed onto the \texttt{gganimate::animate()} function for rendering.
+This then can be passed onto the \texttt{animate()} function from the \CRANpkg{gganimate} for rendering.
 
@@
 
-\caption{Animate visualization using example data.}\label{fig:catchange-figure}
+\caption{Animate visualization using example data. All of the X observations stay within the same group, while Y observations change from group A to group E.}\label{fig:catchange-figure}
 \end{figure}
@@
 An animation will be created using the \texttt{animbook} package to enhance communication with data.
-
 First, filter the countries to include only the United States and Japan.
@@
 \begin{verbatim}
+# library(animbook)
+# library(dplyr)
+
 data <- osiris |> 
@@
 
+kan_p <- kangaroo_plot(accounting)
+
 p2 <- anim_animate(p)
+kan_p2 <- anim_animate(kan_p)
 \end{verbatim}
@@
 gganimate::animate(p2)
+
+gganimate::animate(kan_p2)
 \end{verbatim}
@@
 
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figures/osiris}
+
+}
+
+\caption{The animate visualization shows the movement of the companies between the groups from 2006 to 2018.
+In 2006, there were no Japanese companies in the Top 25\% group.}\label{fig:kan-osiris-figure}
+\end{figure}
+
 From the plot, a higher proportion of US companies have exited the market, confirming the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a higher turnover rate than Japan.
 An interesting finding is that all of the top 25\% of companies that exited the market are only from the United States.
-It may be due to the absence of Japanese companies in the top 25\% in 2006, or it could be that Japanese companies in the top 25\% did not delist.
+It may be due to the absence of Japanese companies in the Top 25\% in 2006, or it could be that Japanese companies who started in the Top 25\% in 2006 did not delist.
+Figure \ref{fig:kan-osiris-figure}, confirmed that there are non-Japanese companies that start at the Top 25\% in 2006.
 
@@
 (2023)).
-The dataset included in the \texttt{animbook} package contains 1,468 rows and 4 variables of information: ID, year, party, and gender.
+The dataset included in the \pkg{animbook} package contains 1,468 rows and 4 variables of information: ID, year, party, and gender.
 This dataset comprises survey responses from the 2019 election.
@@
 
-From the animation, it is clear that individuals who identified their gender as `others' shifted their votes from the Liberal, the leading party in 2016, to the Greens party.
+From Figure \ref{fig:voter-figure}, it is clear that individuals who identified their gender as `others' shifted their votes from the Liberal, the leading party in 2016, to the Greens party.
 These changes could be due to the Green Party's ``A FAIRER, MORE EQUAL COMMUNITY'' campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.
@@
 Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences.
-In the current version of \texttt{animbook}, the feature to have different speed for each observation have not yet been implemented.
+In the current version of \pkg{animbook}, the feature to have different speeds for each observation has not yet been implemented.
 This feature will introduce a new dimension that allows the users to explore the data further.
@@
 (2018)), to compare the demographics at a specific point in time.
-On top of that, the \texttt{cli} package (Csárdi (2023)) could be used for a more aesthetically pleasing command-line interface.
+On top of that, the \CRANpkg{cli} package (Csárdi (2023)) could be used for a more aesthetically pleasing command-line interface.
 
@@
 
-This paper is created using the \texttt{rjtools} packages (O'Hara-Wild et al.
-(2023)) and is based on the 0.0.0.9 version of the \texttt{animbook} package.
+This paper is created using the \CRANpkg{rjtools} packages (O'Hara-Wild et al.
+(2023)) and is based on the 0.0.0.9 version of the \pkg{animbook} package.
 This version is available on \href{https://github.com/KrisanatA/animbook}{GitHub}.
@@
 \url{https://doi.org/10.1093/qje/qjz042}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-relational}{}}%
-Codd, E. F. 1990. \emph{The Relational Model for Database Management: Version 2}. USA: Addison-Wesley Longman Publishing Co., Inc.
 

### 2023-10-29 animbook-journal.R

@@ -10,23 +10,23 @@ library(animbook)
 library(tidyverse)
 
 
-## ----nyt, fig.cap="Screenshot of the New York Times animation, that is the motivation for this visualization package.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"----
+## ----nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package..", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"----
 knitr::include_graphics("figures/NYT.png")
 
 
-## ----data-diagram, fig.cap="The diagram shows what are the expected data forms.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"----
+## ----data-diagram, fig.cap="The animation expects data with an ID and a time variable, along with a numerical variable (raw form), which is possibly converted to categorical (categorized). The data can be provided in the raw or categorized form and will be processed into the format needed for the animation, where the categorical variable is treated as a quantile and an animation frame variable is created.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
 knitr::include_graphics("figures/data-diagram.png")
 
 
-## ----animation-diagram, fig.cap="The diagram shows how the animation is done using the successive pictures.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"----
+## ----animation-diagram, fig.cap="The diagram shows how the animation is done using the successive pictures. When small changes are seen in quick succession, it will appear as if the objects are in motion.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
 knitr::include_graphics("figures/animation-diagram.png")
 
 
-## ----animated-diagram, fig.cap="The diagram shows how the frames were used in the animated plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"----
+## ----animated-diagram, fig.cap="The diagram shows how the frames were used in the animated plot. Frame one is depicted in blue, and frame two is represented in red. Each blue component is mapped exclusively to the Frame 1 plot, while all the second-frame elements are excluded, and vice versa.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
 knitr::include_graphics("figures/animated-diagram.png")
 
 
-## ----proportional-shade, fig.show="hold", out.width="50%", fig.cap="The plot shows the difference between the sigmoid and sine curves."----
[…]

### 2023-10-29 animbook-journal.Rmd
revised design section

@@
 The animated visualization can be an effective communication tool (@Mayer_Moreno_2002; @effective-trend).
-It helps with communicating complex data, enhancing the narrative, and keeping it engaged for the audience.
+It helps with communicating changing data values, enhancing the narrative, and keeping it engaging for the audience.
 According to @Mayer_Moreno_2002, animation can improve learning, especially when the goal is to promote deep understanding.
@@
 
-  As mentioned in the Animation tools section, the paths of observations are getting interpolated.
-These functions only generate a linear path between points.
-However, linear paths may not be suitable for creating proportional shading, as they do not accurately represent the proportions.
-Non-linear curves like the sigmoid curves should be considered instead, as they provide a better display of proportions.
-These curves are commonly used in multiple Sankey diagrams, but there is a limitation on this shape.
-The issue is shown in Figure \@ref(fig:proportional-shade).
-While it does accurately represent the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation (@Shaffer_2019)
+  The paths of observations need to be interpolated to create small changes in the position of points to produce the appearance of motion, as mentioned in the Animation tools section.
+These interpolate functions in \CRANpkg{gganimate} and \CRANpkg{plotly} only generate a linear path between points.
+However, linear paths are visually less appealing than non-linear paths.
+<!-- Non-linear curves like the sigmoid curves are considered instead, as they provide a better display of proportions.--> Sigmoid curves are commonly used in Sankey diagrams, however, @Shaffer_2019 argues that a sine curve more accurately represents proportion throughout the path.
+This is illustrated in Figure \@ref(fig:proportional-shade).
+The sigmoid accurately represents the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation than the sine curve.
 

### 2023-10-29 animbook-journal.Rmd
figure widths and ChatGPT acknowledgement

@@
 
-```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package..", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package..", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/NYT.png")
@@
 
-```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
+```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 p <- wallaby_plot(object = animbook,
@@
 
-I also acknowledge the use of ChatGPT (https://chat.openai.com/) to paraphrase the sentence.
+I also acknowledge the use of ChatGPT (https://chat.openai.com/) to improve the text, grammar and spelling.

### 2023-10-29 animbook-journal.Rmd
working on examples

@@
 This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide.
-The only variables of interest from this data set are ID, year, country, and sales.
-A subset version of this data set, which only contained variables of interest from 2006 to 2018, is included in this package.
+The variables of interest from this data set are ID, year, country, and sales.
+A subset of companies from this data set is used recorded from 2006 to 2018.
+This sample is included in the package.
 
-  As mentioned in the OECD report (@oecd_report), the United States has a faster metabolize rate relative to Japan company.
-An animation will be created using the `animbook` package to enhance communication with data.
-First, filter the countries to include only the United States and Japan.
-Then, prepare the Osiris data using the `anim_prep` function with the first scaling, which is a ranking method.
-Next, use the `wallaby_plot` function to create a `ggplot` object and add default settings for `gganimate` rendering.
+  An OECD report (@oecd_report) claims that the United States has a faster metabolic rate relative to Japanese companies.
+We use the wallaby plot and kangaroo plot animation to explore this.
+The steps are:
+
+- Filter the countries to include only the United States and Japan. 
+- Prepare the data using the `anim_prep` function with the first scaling, which is a ranking method. 
+- Use the `wallaby_plot` and `kangaroo_plot` functions to create `ggplot` objects and add default settings for `gganimate` rendering.
 
@@
 
-```{r osiris-figure, fig.cap = "The animate visualization shows the companies that exited the market.
+```{r osiris-figure, fig.cap = "The wallaby plot  visualization shows the companies that exited the market.
 There are more United States companies that fall down into a not listed group compared to Japanese companies.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
@@
 
-```{r osiris-gif, out.extra="class = 'gif'", fig.cap = "The animate visualization shows the companies that exited the market.
+```{r osiris-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows the companies that exited the market.
 There are more United States companies that fall down into a not listed group compared to Japanese companies.", eval=knitr::is_html_output()}
@@
 
-```{r kan-osiris-figure, fig.cap = "The animate visualization shows the movement of the companies between the groups from 2006 to 2018.
-In 2006, there were no Japanese companies in the Top 25\\% group.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+```{r kan-osiris-figure, fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018, for a sample of data extracted from the Osiris database.
+The 'not listed' category indicates companies not yet listed, or removed from the listing.
+Most companies stay in the same quantile group, with a small number moving up and down.
+Most of the movement is made by American companies, which supports the OECD report.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
 knitr::include_graphics("figures/osiris.png")
@@
 
-```{r kan-osiris-gif, out.extra="class = 'gif'", fig.cap = "The animate visualization shows the movement of the companies between the groups from 2006 to 2018.
-In 2006, there were no Japanese companies in the Top 25% group.", eval=knitr::is_html_output()}
+```{r kan-osiris-gif, out.extra="class = 'gif'", fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018, for a sample of data extracted from the Osiris database.
+The 'not listed' category indicates companies not yet listed, or removed from the listing.
+Most companies stay in the same quantile group, with a small number moving up and down.
+Most of the movement is made by American companies, which supports the OECD report.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/kan-osiris.gif")
@@
 An interesting finding is that all of the top 25% of companies that exited the market are only from the United States.
-It may be due to the absence of Japanese companies in the Top 25% in 2006, or it could be that Japanese companies who started in the Top 25% in 2006 did not delist.
+It may be due to the absence of Japanese companies in the Top 25% in 2006, or it could be that Japanese companies who started in the Top 25% in 2006 were not delisted.
 Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`, confirmed that there are non-Japanese companies that start at the Top 25% in 2006.
@@
 This dataset comprises survey responses from the 2019 election.
-The year column was transformed from the two different questions to answer the question, based on the 2016 Australian election results, how the top party performs in keeping the old voters for different genders.
+The year column was transformed from the two different questions to answer how the top party performs in keeping the old voters for different genders, relative to the 2016 Australian election results.
 
@@
 
-```{r voter-figure, fig.cap = "The animate visualization shows how does the top party perform in keeping the old voters for different genders.
+```{r voter-figure, fig.cap = "The wallaby plot visualization shows how does the top party perform in keeping the old voters for different genders.
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
@@
 
-```{r voter-gif, out.extra="class = 'gif'", fig.cap = "The animate visualization shows how does the top party perform in keeping the old  voters for different genders.
+```{r voter-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows how does the top party perform in keeping the old  voters for different genders.
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.", eval=knitr::is_html_output()}

### 2023-10-29 animbook-journal.Rmd
small typo fix

@@
 
-  From the plot, a higher proportion of US companies have exited the market, confirming the OECD report (@oecd_report) that the United States has a higher turnover rate than Japan.
+  From the kangaroo plot, a higher proportion of US companies have exited the market, confirming the OECD report (@oecd_report) that the United States has a higher turnover rate than Japan.
 An interesting finding is that all of the top 25% of companies that exited the market are only from the United States.

### 2023-10-29 animbook-journal.Rmd
4th version of the paper

--- 2023-10-29 animbook-journal.Rmd
@@
     email:  kanu0003@student.monash.edu
+  - name: Dianne Cook
+    affiliation: Monash University 
+    address: 
+      - Department of Econometrics and Business Statistics
+      - Melbourne, Australia
+    email: dicook@monash.edu
+    orcid: 0000-0002-3813-7155
 type: package
@@
 We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time.
-Generally, studying movement patterns is interesting for many problems, including rocket ship startups that rapidly perform well, or in politics, to study voters who switch party affiliation between elections.
+Generally, studying movement patterns is interesting for many problems, including rocket ship start-ups that rapidly perform well or in politics, to study voters who switch party affiliation between elections.
 Viewing changes between categories over time is an interesting challenge for visualization.
@@
   The New York Times provided a possible solution in the article titled "Extensive data show punishing reach of racism for black boys" (@the_new_york_time) to tell the story of how racism appears to inhibit socioeconomic change.
-This animation is the motivation for the new visualization presented here, to be applied generally.
+This animation is the motivation for the new visualization presented here to be applied generally.
 
-The challenge in producing an animation like that in New York Times article animation is the transformation of the data, and connection with elements of the plot that will be animated.
-The complexities include standardizing starting times of the temporal variable, allowing for the user to choose the number of categories, standardizing distributions and allowing the user to input pre-computed categorical data.
+  The challenge in producing an animation like that in the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated.
+The complexities include allowing the user to choose the number of categories, standardizing distributions, and allowing the user to input pre-computed categorical data.
 These considerations provide the objective for creating an R package that can generalize the animation to suitably apply to a wide range of data.
@@
 The next section describes the expected data format.
-Following this is an explanation of available animation tools, and how they are employed for this problem.
-A section on the functions of the package and how the visualization is designed, demonstrates how the data is mapped to the animation.
+Following this is an explanation of available animation tools and how they are employed for this problem.
+A section on the functions of the package and how the visualization is designed demonstrates how the data is mapped to the animation.
 The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.
@@
 
-```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package..", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
+```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/NYT.png")
@@
 However, linear paths are visually less appealing than non-linear paths.
-<!-- Non-linear curves like the sigmoid curves are considered instead, as they provide a better display of proportions.--> Sigmoid curves are commonly used in Sankey diagrams, however, @Shaffer_2019 argues that a sine curve more accurately represents proportion throughout the path.
+Sigmoid curves are commonly used in Sankey diagrams (@Hvitfeldt_2018).
+However, @Shaffer_2019 argues that a sine curve more accurately represents proportion throughout the path.
 This is illustrated in Figure \@ref(fig:proportional-shade).
-The sigmoid accurately represents the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation than the sine curve.
+The sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.
 
@@
 
+kan_p <- kangaroo_plot(accounting)
+
 p <- wallaby_plot(accounting,
@@
 
-kan_p <- kangaroo_plot(accounting)
+kan_p2 <- anim_animate(kan_p)
 
 p2 <- anim_animate(p)
-kan_p2 <- anim_animate(kan_p)
 ```
@@
 ``` r
+gganimate::animate(kan_p2)
+
 gganimate::animate(p2)
-
-gganimate::animate(kan_p2)
 ```
 
-```{r osiris-figure, fig.cap = "The wallaby plot  visualization shows the companies that exited the market.
-There are more United States companies that fall down into a not listed group compared to Japanese companies.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
-knitr::include_graphics("figures/animation-exit.png")
-```
-
-```{r osiris-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows the companies that exited the market.
-There are more United States companies that fall down into a not listed group compared to Japanese companies.", eval=knitr::is_html_output()}
-knitr::include_graphics("figures/exit.gif")
-```
-
-```{r kan-osiris-figure, fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018, for a sample of data extracted from the Osiris database.
-The 'not listed' category indicates companies not yet listed, or removed from the listing.
+```{r kan-osiris-figure, fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database.
+The 'not listed' category indicates companies not yet listed or removed from the listing.
 Most companies stay in the same quantile group, with a small number moving up and down.
@@
 
-```{r kan-osiris-gif, out.extra="class = 'gif'", fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018, for a sample of data extracted from the Osiris database.
-The 'not listed' category indicates companies not yet listed, or removed from the listing.
+```{r kan-osiris-gif, out.extra="class = 'gif'", fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database.
+The 'not listed' category indicates companies not yet listed or removed from the listing.
 Most companies stay in the same quantile group, with a small number moving up and down.
@@
 
-  From the plot, a higher proportion of US companies have exited the market, confirming the OECD report (@oecd_report) that the United States has a higher turnover rate than Japan.
-An interesting finding is that all of the top 25% of companies that exited the market are only from the United States.
-It may be due to the absence of Japanese companies in the Top 25% in 2006, or it could be that Japanese companies who started in the Top 25% in 2006 were not delisted.
-Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`, confirmed that there are non-Japanese companies that start at the Top 25% in 2006.
+```{r osiris-figure, fig.cap = "The wallaby plot visualization shows the companies that exited the market.
+There are more United States companies that fall down into a not listed group (got de-listed) compared to Japanese companies.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+knitr::include_graphics("figures/animation-exit.png")
+```
+
+```{r osiris-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows the companies that exited the market.
+There are more United States companies that fall down into a not listed group (got de-listed) compared to Japanese companies.", eval=knitr::is_html_output()}
+knitr::include_graphics("figures/exit.gif")
+```
+
+  From the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`), most companies are staying in the same quantile group, with only a small number moving upward or downward.
+Most of the movement is made by American companies, supporting the OECD report (@oecd_report) that the United States has a higher turnover rate compared to Japan.
+To emphasize this point, the wallaby plot can be utilized (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`), this reinforces that there are more American companies de-listed compared to Japanese companies.
+There could be various reasons for this trend, such as the absence of Japanese companies in the Top 25% in 2006 or the possibility that Japanese companies who started in the Top 25% in 2006 were not de-listed.
 
@@
 This dataset comprises survey responses from the 2019 election.
-The year column was transformed from the two different questions to answer how the top party performs in keeping the old voters for different genders, relative to the 2016 Australian election results.
+The year column was transformed from the two different questions to answer how the top party performs in keeping the old voters for different genders relative to the 2016 Australian election results.
 
@@
 p_voter <- wallaby_plot(object = voter,
-                  group_palette = RColorBrewer::brewer.pal(9, "Set1"),
+                  group_palette = c("pink", "blue", "red"),
                   shade_palette = c("#737373", "#969696", "#BDBDBD",
@@
                   height = 1,
-                  size = 2,
+                  size = 2.5,
                   width = 100,
@@
 
-```{r voter-figure, fig.cap = "The wallaby plot visualization shows how does the top party perform in keeping the old voters for different genders.
-Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+```{r voter-figure, fig.cap = "The wallaby plot visualization shows how the top party performs in keeping the old voters of different genders.
+Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
+Interestingly, individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
 knitr::include_graphics("figures/animation-voter.png")
@@
 
-```{r voter-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows how does the top party perform in keeping the old  voters for different genders.
-Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.", eval=knitr::is_html_output()}
+```{r voter-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows how the top party performs in keeping the old voters of different genders.
+Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
+Interestingly, individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/voter.gif")
@@
 
-From Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:voter-figure}','\\@ref(fig:voter-gif)'))`, it is clear that individuals who identified their gender as 'others' shifted their votes from the Liberal, the leading party in 2016, to the Greens party.
-These changes could be due to the Green Party's "A FAIRER, MORE EQUAL COMMUNITY" campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.
+  From Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:voter-figure}','\\@ref(fig:voter-gif)'))`, it reveals an intriguing pattern where individuals who identified their gender as 'others' have shifted their voting preference from the Liberal Party, the leading party in 2006, to the Greens Party.
+This change in behavior could be linked to the Green Party's "A FAIRER, MORE EQUAL COMMUNITY" campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.
+
+  Liberal Party analysts may find it worthwhile to delve into this topic further, considering both the benefits and drawbacks.
 If the Liberal Party wishes to retain this demographic of voters, they may need to consider implementing a campaign focused on LGBTIQ+ issues.
+However, this may also lead to a further defection of conservative voters.
 

### 2023-10-29 animbook-journal.tex
4th version of the paper

@@
 \title{animbook: Visualizing changes in performance measures and demographic affiliations using animation}
-\author{by Krisanat Anukarnsakulchularp}
+\author{by Krisanat Anukarnsakulchularp and Dianne Cook}
 
@@
 (2018)) to tell the story of how racism appears to inhibit socioeconomic change.
-This animation is the motivation for the new visualization presented here, to be applied generally.
+This animation is the motivation for the new visualization presented here to be applied generally.
 
-The challenge in producing an animation like that in New York Times article animation is the transformation of the data, and connection with elements of the plot that will be animated.
-The complexities include standardizing starting times of the temporal variable, allowing for the user to choose the number of categories, standardizing distributions and allowing the user to input pre-computed categorical data.
+The challenge in producing an animation like that in the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated.
+The complexities include allowing the user to choose the number of categories, standardizing distributions, and allowing the user to input pre-computed categorical data.
 These considerations provide the objective for creating an R package that can generalize the animation to suitably apply to a wide range of data.
@@
 
-\caption{Screenshot of the New York Times animation, which is the motivation for this visualization package..}\label{fig:nyt}
+\caption{Screenshot of the New York Times animation, which is the motivation for this visualization package.}\label{fig:nyt}
 \end{figure}
@@
 (2008)).
-It helps with communicating complex data, enhancing the narrative, and keeping it engaged for the audience.
+It helps with communicating changing data values, enhancing the narrative, and keeping it engaging for the audience.
 According to R.
@@
 
-As mentioned in the Animation tools section, the paths of observations are getting interpolated.
-These functions only generate a linear path between points.
-However, linear paths may not be suitable for creating proportional shading, as they do not accurately represent the proportions.
-Non-linear curves like the sigmoid curves should be considered instead, as they provide a better display of proportions.
-These curves are commonly used in multiple Sankey diagrams, but there is a limitation on this shape.
-The issue is shown in Figure \ref{fig:proportional-shade}.
-While it does accurately represent the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation (Shaffer (2019))
+The paths of observations need to be interpolated to create small changes in the position of points to produce the appearance of motion, as mentioned in the Animation tools section.
+These interpolate functions in \CRANpkg{gganimate} and \CRANpkg{plotly} only generate a linear path between points.
+However, linear paths are visually less appealing than non-linear paths.
+Sigmoid curves are commonly used in Sankey diagrams (Hvitfeldt (2018)).
+However, Shaffer (2019) argues that a sine curve more accurately represents proportion throughout the path.
+This is illustrated in Figure \ref{fig:proportional-shade}.
+The sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.
 
@@
 #>    <fct> <int> <dbl> <dbl> <fct>
-#>  1 1      2020     5    33 X    
-#>  2 1      2023     5    34 X    
-#>  3 2      2020     5     5 X    
-#>  4 2      2023     5     6 X    
-#>  5 3      2020     5    48 X    
-#>  6 3      2023     5    49 X    
-#>  7 4      2020     5    33 X    
-#>  8 4      2023     5    34 X    
-#>  9 5      2020     5     3 X    
-#> 10 5      2023     5     4 X
+#>  1 1      2020     5    11 X    
+#>  2 1      2023     5    12 X    
+#>  3 2      2020     5    39 X    
+#>  4 2      2023     5    40 X    
+#>  5 3      2020     5     3 X    
+#>  6 3      2023     5     4 X    
+#>  7 4      2020     5    12 X    
+#>  8 4      2023     5    13 X    
+#>  9 5      2020     5    46 X    
+#> 10 5      2023     5    47 X
 \end{verbatim}
@@
 #>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
-#>   ..$ frame: num [1:400] 33 34 5 6 48 49 33 34 3 4 ...
+#>   ..$ frame: num [1:400] 11 12 39 40 3 4 12 13 46 47 ...
 #>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
@@
 
-The accounting Osiris data that will be used in this section was collected from Bureau van Dijk ({``Osiris''} (n.d.)).
+The accounting Osiris data that will be used in this section was collected from Bureau van Dijk ({``Osiris''} (2023)).
 This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide.
-The only variables of interest from this data set are ID, year, country, and sales.
-A subset version of this data set, which only contained variables of interest from 2006 to 2018, is included in this package.
+The variables of interest from this data set are ID, year, country, and sales.
+A subset of companies from this data set is used recorded from 2006 to 2018.
+This sample is included in the package.
 
-As mentioned in the OECD report (McGowan, Andrews, and Millot (2017)), the United States has a faster metabolize rate relative to Japan company.
-An animation will be created using the \texttt{animbook} package to enhance communication with data.
-First, filter the countries to include only the United States and Japan.
-Then, prepare the Osiris data using the \texttt{anim\_prep} function with the first scaling, which is a ranking method.
-Next, use the \texttt{wallaby\_plot} function to create a \texttt{ggplot} object and add default settings for \texttt{gganimate} rendering.
+An OECD report (McGowan, Andrews, and Millot (2017)) claims that the United States has a faster metabolic rate relative to Japanese companies.
+We use the wallaby plot and kangaroo plot animation to explore this.
+The steps are:
+
+\begin{itemize}
+\tightlist
+\item
+  Filter the countries to include only the United States and Japan.
+\item
+  Prepare the data using the \texttt{anim\_prep} function with the first scaling, which is a ranking method.
+\item
+  Use the \texttt{wallaby\_plot} and \texttt{kangaroo\_plot} functions to create \texttt{ggplot} objects and add default settings for \texttt{gganimate} rendering.
+\end{itemize}
 
@@
 
-kan_p <- kangaroo_plot(accounting)
+kan_p2 <- anim_animate(kan_p)
 
 p2 <- anim_animate(p)
-kan_p2 <- anim_animate(kan_p)
 \end{verbatim}
@@
 \begin{verbatim}
+gganimate::animate(kan_p2)
+
 gganimate::animate(p2)
+\end{verbatim}
 
-gganimate::animate(kan_p2)
-\end{verbatim}
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figures/osiris}
+
+}
+
+\caption{The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database.
+The 'not listed' category indicates companies not yet listed or removed from the listing.
+Most companies stay in the same quantile group, with a small number moving up and down.
+Most of the movement is made by American companies, which supports the OECD report.}\label{fig:kan-osiris-figure}
+\end{figure}
 
@@
 
-\caption{The animate visualization shows the companies that exited the market.
-There are more United States companies that fall down into a not listed group compared to Japanese companies.}\label{fig:osiris-figure}
+\caption{The wallaby plot visualization shows the companies that exited the market.
+There are more United States companies that fall down into a not listed group (got de-listed) compared to Japanese companies.}\label{fig:osiris-figure}
 \end{figure}
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{figures/osiris}
-
-}
-
-\caption{The animate visualization shows the movement of the companies between the groups from 2006 to 2018.
-In 2006, there were no Japanese companies in the Top 25\% group.}\label{fig:kan-osiris-figure}
-\end{figure}
-
-From the plot, a higher proportion of US companies have exited the market, confirming the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a higher turnover rate than Japan.
-An interesting finding is that all of the top 25\% of companies that exited the market are only from the United States.
-It may be due to the absence of Japanese companies in the Top 25\% in 2006, or it could be that Japanese companies who started in the Top 25\% in 2006 did not delist.
-Figure \ref{fig:kan-osiris-figure}, confirmed that there are non-Japanese companies that start at the Top 25\% in 2006.
+From the kangaroo plot (Figure \ref{fig:kan-osiris-figure}), most companies are staying in the same quantile group, with only a small number moving upward or downward.
+Most of the movement is made by American companies, supporting the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a higher turnover rate compared to Japan.
+To emphasize this point, the wallaby plot can be utilized (Figure \ref{fig:osiris-figure}), this reinforces that there are more American companies de-listed compared to Japanese companies.
+There could be various reasons for this trend, such as the absence of Japanese companies in the Top 25\% in 2006 or the possibility that Japanese companies who started in the Top 25\% in 2006 were not de-listed.
 
@@
 This dataset comprises survey responses from the 2019 election.
-The year column was transformed from the two different questions to answer the question, based on the 2016 Australian election results, how the top party performs in keeping the old voters for different genders.
+The year column was transformed from the two different questions to answer how the top party performs in keeping the old voters for different genders relative to the 2016 Australian election results.
 
@@
 
-\caption{The animate visualization shows how does the top party perform in keeping the old voters for different genders.
-Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.}\label{fig:voter-figure}
+\caption{The wallaby plot visualization shows how the top party performs in keeping the old voters of different genders.
+Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
+Interestingly, individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.}\label{fig:voter-figure}
 \end{figure}
 
-From Figure \ref{fig:voter-figure}, it is clear that individuals who identified their gender as `others' shifted their votes from the Liberal, the leading party in 2016, to the Greens party.
-These changes could be due to the Green Party's ``A FAIRER, MORE EQUAL COMMUNITY'' campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.
+From Figure \ref{fig:voter-figure}, it reveals an intriguing pattern where individuals who identified their gender as `others' have shifted their voting preference from the Liberal Party, the leading party in 2006, to the Greens Party.
+This change in behavior could be linked to the Green Party's ``A FAIRER, MORE EQUAL COMMUNITY'' campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.
+
+Liberal Party analysts may find it worthwhile to delve into this topic further, considering both the benefits and drawbacks.
 If the Liberal Party wishes to retain this demographic of voters, they may need to consider implementing a campaign focused on LGBTIQ+ issues.
+However, this may also lead to a further defection of conservative voters.
 
@@
 
-I also acknowledge the use of ChatGPT (\url{https://chat.openai.com/}) to paraphrase the sentence.
+I also acknowledge the use of ChatGPT (\url{https://chat.openai.com/}) to improve the text, grammar and spelling.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Hvitfeldt_2018}{}}%
+Hvitfeldt, Emil. 2018. {``Recreate - Sankey Flow Chart.''} \emph{Recreate - Sankey Flow Chart}. \url{https://emilhvitfeldt.com/post/2018-03-20-recreate-sankey-flow-chart/}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-mayer-2010}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bvd}{}}%
-{``Osiris.''} n.d. \emph{Bvd}. Bureau van Dijk. \url{https://www.bvdinfo.com/en-gb/our-products/data/international/osiris}.
+{``Osiris.''} 2023. \emph{Bvd}. Bureau van Dijk. \url{https://www.bvdinfo.com/en-gb/our-products/data/international/osiris}.
 
@@
 }
+
+\address{%
+Dianne Cook\\
+Monash University\\%
+Department of Econometrics and Business Statistics\\ Melbourne, Australia\\
+%
+%
+\textit{ORCiD: \href{https://orcid.org/0000-0002-3813-7155}{0000-0002-3813-7155}}\\%
+\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}%
+}

### 2023-10-29 animbook-journal.R

@@ -10,7 +10,7 @@ library(animbook)
 library(tidyverse)
 
 
-## ----nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package..", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"----
+## ----nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
 knitr::include_graphics("figures/NYT.png")
 
 
@@ -202,7 +202,7 @@ head(animbook$data, 10)
 str(animbook)
 
 
-## ----echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-page"----
+## ----echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
 p <- wallaby_plot(object = animbook,
              group_palette = RColorBrewer::brewer.pal(9, "Set1"),
              shade_palette = c("#737373", "#969696", "#BDBDBD",
@@ -248,6 +248,8 @@ accounting <- anim_prep(data,
                       color = country, 
                       time_dependent = FALSE)
 
+kan_p <- kangaroo_plot(accounting)
+
 p <- wallaby_plot(accounting,
                   group_palette = RColorBrewer::brewer.pal(9, "Set1"),
                   shade_palette = c("#737373", "#969696", "#BDBDBD",
@@ -259,10 +261,9 @@ p <- wallaby_plot(accounting,
                   width = 100,
                   total_point = 1000)
 
-kan_p <- kangaroo_plot(accounting)
+kan_p2 <- anim_animate(kan_p)
 
 p2 <- anim_animate(p)
-kan_p2 <- anim_animate(kan_p)
 
 
 ## ----eval=FALSE---------------------------------------------------------------
@@ -273,20 +274,20 @@ kan_p2 <- anim_animate(kan_p)
 #>                      nframes = 400, width = 9, units = "in", res = 150)
 
 
-## ----osiris-figure, fig.cap = "The animate visualization shows the companies that exited the market. There are more United States companies that fall down into a not listed group compared to Japanese companies.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()----
-knitr::include_graphics("figures/animation-exit.png")
-
-
[…]

### 2023-10-29 animbook-journal.Rmd
revised abstract

@@
 abstract: >
-  Categorical data has often been presented statically despite its potential to unveil an intriguing movement pattern relevant to the various domains of data, including company ranking quantile in the accounting data and shifts in voter party affiliations.
-Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," this paper aims to develop an R package, animbook, that can generalize the animation to suitably apply to a wider range of data.
-The package included a function that allowed for the transformation of the data and connection with elements of the plot that would be animated.
-This results in an animation tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the general audience.
+  Performance is often reported in quantiles or ranks, and often repeatedly provided over time.
+Between elections, voters often switch party preferences, which produces categorical values over time.
+Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys,", we provide new visualization functions to generate animations that display this type of data, in an R package called \CRANpkg{animbook}.
+Functions to pre-process the data and prepare it for the animation,  are provided.
+The methods will be suitable generally for data where categorical variables are measured over time, and provide a way to engagingly view changes.
 draft: true

### 2023-10-29 animbook-journal.Rmd
tidied up the osiris paragraph

@@
 Most of the movement is made by American companies, supporting the OECD report (@oecd_report) that the United States has a higher turnover rate compared to Japan.
-To emphasize this point, the wallaby plot can be utilized (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`), this reinforces that there are more American companies de-listed compared to Japanese companies.
-There could be various reasons for this trend, such as the absence of Japanese companies in the Top 25% in 2006 or the possibility that Japanese companies who started in the Top 25% in 2006 were not de-listed.
+To emphasize this point, the wallaby plot can be utilized (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`).
+There are clearly more American companies de-listed compared to Japanese companies, and we can see that there are no Japanese companies in the Top 25% in 2006 that were de-listed.
 

### 2023-10-30 animbook-journal.Rmd
add normalization part for 1st and 2nd scaling

@@
 abstract: >
-  Performance is often reported in quantiles or ranks, and often repeatedly provided over time.
+  Performance is often reported in quantiles or ranks and often repeatedly provided over time.
 Between elections, voters often switch party preferences, which produces categorical values over time.
-Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys,", we provide new visualization functions to generate animations that display this type of data, in an R package called \CRANpkg{animbook}.
-Functions to pre-process the data and prepare it for the animation,  are provided.
+Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," we provide new visualization functions to generate animations that display this type of data in an R package called \pkg{animbook}.
+Functions to pre-process the data and prepare it for the animation are provided.
 The methods will be suitable generally for data where categorical variables are measured over time, and provide a way to engagingly view changes.
@@
 
-  For the first and second scaling methods, group splitting is executed using the `quantiles()` and `cut()` functions.
-The `quantile()` function from the \CRANpkg{stats} package (@stats) takes a numeric vector and outputs the corresponding quantiles to the given probabilities.
-The output from the `quantile()` function is then used as the `breaks` argument for the `cut()` function that is part of the base R packages (@r).
+  For the first and second scaling methods, it is necessary to rank the values based on time, and in cases where a group is provided, they are ranked based on both time and groups.
+To ensure that the rank scales among different groups are the same, the variables are first normalized to a range between 0 and 1.
+The third and fourth scaling methods also involve a normalization step, but they are based on raw values instead of rank values.
 
-  In contrast, the third and fourth scaling methods calculate the quantile based on the absolute values scales.
-To avoid varying values scales among groups, the variables are first normalized to a range between 0 and 1.
-The default approach then breaks the group equally using the `seq()` function.
-The `seq()` function takes input values from 0 to 1 and increments by equal steps depending on the number of groups of interest.
-Additionally, the users have the option to specify the breaks themselves if they choose to do so.
+  All of these scaling methods utilized the `cut()` function from the base R package (@r) to split the values into quantiles.
+The `cut()` function requires the specification of the `breaks` argument.
+If it is not provided, the prep function in this package defaults to using the `seq()` function, which sets the minimum and maximum values to 0 and 1, respectively, and then increments by equal steps based on the number of groups of interest.
+Additionally, the users have the option to specify the breaks themselves if they choose to do so, noting that the breaks provided need to be between 0 and 1, and the length of the vector needs to be the number of groups plus 1.
 

### 2023-10-30 animbook-journal.tex
add normalization part for 1st and 2nd scaling

@@
 \abstract{%
-Categorical data has often been presented statically despite its potential to unveil an intriguing movement pattern relevant to the various domains of data, including company ranking quantile in the accounting data and shifts in voter party affiliations.
-Inspired by the animation in the New York Times article ``Extensive data show punishing reach of racism for black boys,'' this paper aims to develop an R package, animbook, that can generalize the animation to suitably apply to a wider range of data.
-The package included a function that allowed for the transformation of the data and connection with elements of the plot that would be animated.
-This results in an animation tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the general audience.
+Performance is often reported in quantiles or ranks and often repeatedly provided over time.
+Between elections, voters often switch party preferences, which produces categorical values over time.
+Inspired by the animation in the New York Times article ``Extensive data show punishing reach of racism for black boys,'' we provide new visualization functions to generate animations that display this type of data in an R package called \pkg{animbook}.
+Functions to pre-process the data and prepare it for the animation are provided.
+The methods will be suitable generally for data where categorical variables are measured over time, and provide a way to engagingly view changes.
 }
@@
 
-For the first and second scaling methods, group splitting is executed using the \texttt{quantiles()} and \texttt{cut()} functions.
-The \texttt{quantile()} function from the \CRANpkg{stats} package (R Core Team (2013)) takes a numeric vector and outputs the corresponding quantiles to the given probabilities.
-The output from the \texttt{quantile()} function is then used as the \texttt{breaks} argument for the \texttt{cut()} function that is part of the base R packages (R Core Team (2021)).
+For the first and second scaling methods, it is necessary to rank the values based on time, and in cases where a group is provided, they are ranked based on both time and groups.
+To ensure that the rank scales among different groups are the same, the variables are first normalized to a range between 0 and 1.
+The third and fourth scaling methods also involve a normalization step, but they are based on raw values instead of rank values.
 
-In contrast, the third and fourth scaling methods calculate the quantile based on the absolute values scales.
-To avoid varying values scales among groups, the variables are first normalized to a range between 0 and 1.
-The default approach then breaks the group equally using the \texttt{seq()} function.
-The \texttt{seq()} function takes input values from 0 to 1 and increments by equal steps depending on the number of groups of interest.
-Additionally, the users have the option to specify the breaks themselves if they choose to do so.
+All of these scaling methods utilized the \texttt{cut()} function from the base R package (R Core Team (2021)) to split the values into quantiles.
+The \texttt{cut()} function requires the specification of the \texttt{breaks} argument.
+If it is not provided, the prep function in this package defaults to using the \texttt{seq()} function, which sets the minimum and maximum values to 0 and 1, respectively, and then increments by equal steps based on the number of groups of interest.
+Additionally, the users have the option to specify the breaks themselves if they choose to do so, noting that the breaks provided need to be between 0 and 1, and the length of the vector needs to be the number of groups plus 1.
 
@@
 #>    <fct> <int> <dbl> <dbl> <fct>
-#>  1 1      2020     5    11 X    
-#>  2 1      2023     5    12 X    
-#>  3 2      2020     5    39 X    
-#>  4 2      2023     5    40 X    
-#>  5 3      2020     5     3 X    
-#>  6 3      2023     5     4 X    
-#>  7 4      2020     5    12 X    
-#>  8 4      2023     5    13 X    
-#>  9 5      2020     5    46 X    
-#> 10 5      2023     5    47 X
+#>  1 1      2020     5     2 X    
+#>  2 1      2023     5     3 X    
+#>  3 2      2020     5    20 X    
+#>  4 2      2023     5    21 X    
+#>  5 3      2020     5    34 X    
+#>  6 3      2023     5    35 X    
+#>  7 4      2020     5    20 X    
+#>  8 4      2023     5    21 X    
+#>  9 5      2020     5    45 X    
+#> 10 5      2023     5    46 X
 \end{verbatim}
@@
 #>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
-#>   ..$ frame: num [1:400] 11 12 39 40 3 4 12 13 46 47 ...
+#>   ..$ frame: num [1:400] 2 3 20 21 34 35 20 21 45 46 ...
 #>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
@@
 Most of the movement is made by American companies, supporting the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a higher turnover rate compared to Japan.
-To emphasize this point, the wallaby plot can be utilized (Figure \ref{fig:osiris-figure}), this reinforces that there are more American companies de-listed compared to Japanese companies.
-There could be various reasons for this trend, such as the absence of Japanese companies in the Top 25\% in 2006 or the possibility that Japanese companies who started in the Top 25\% in 2006 were not de-listed.
+To emphasize this point, the wallaby plot can be utilized (Figure \ref{fig:osiris-figure}).
+There are clearly more American companies de-listed compared to Japanese companies, and we can see that there are no Japanese companies in the Top 25\% in 2006 that were de-listed.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-stats}{}}%
-R Core Team. 2013. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{http://www.R-project.org/}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-r}{}}%
----------. 2021. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
+R Core Team. 2021. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
 

### 2023-10-30 animbook-journal.Rmd
last check before ETC5543 submission

@@
 
-  This animation was developed using two software based on JavaScript, D3.js (@d3js), and WebGL (reference).
+  This animation was developed using the software based on JavaScript, D3.js (@d3js), and WebGL (@webgl).
 The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization.
@@
 The use of `transition_*()` functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time.
-This includes `gifski_renderer()` from the \CRANpkg{gifski} package {@gifski} to save animation in GIF format or `av_renderer()` from the \CRANpkg{av} package {@av} to save it into a video file format.
+This includes `gifski_renderer()` from the \CRANpkg{gifski} package (@gifski) to save animation in GIF format or `av_renderer()` from the \CRANpkg{av} package (@av) to save it into a video file format.
 
@@
 In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation.
-The initial step is to reformat the data to the animated data structure as seen in \@ref(fig:data-diagram).
+The initial step is to reformat the data to the animated data structure as seen in Figure \@ref(fig:data-diagram).
 The second stage is creating a `ggplot` object, which can be subsequently passed into the animation function.
@@
 argument_table |> 
-  filter(argument %in% c("ngroup", "breaks", "group_scaling", "scaline")) |> 
+  filter(argument %in% c("ngroup", "breaks", "group_scaling", "scaling")) |> 
   knitr::kable(caption = "The argument in the anim\\_prep for customized the data scaling.")
@@
 
-This paper is created using the \CRANpkg{rjtools} packages (@rjtools) and is based on the 0.0.0.9 version of the \pkg{animbook} package.
+This paper is created using the \CRANpkg{rjtools} packages (@rjtools) and utilized the \CRANpkg{dplyr}, \CRANpkg{knitr}, \CRANpkg{gganimate}, and \CRANpkg{kableExtra} for creating the visual included in this paper.
+This paper is based on the 0.0.0.9 version of the \pkg{animbook} package.
 This version is available on [GitHub](https://github.com/KrisanatA/animbook).
+I also acknowledge the use of ChatGPT (https://chat.openai.com/) to improve the text, grammar, and spelling.
 
-I also acknowledge the use of ChatGPT (https://chat.openai.com/) to improve the text, grammar and spelling.
+- The presentation for the ETC5543 can be found on [GitHub.](https://github.com/KrisanatA/animbook-presentation)
+- This paper is contained in the following [GitHub repository.](https://github.com/KrisanatA/animbook-journal)

### 2023-10-30 animbook-journal.tex
last check before ETC5543 submission

@@
 
-This animation was developed using two software based on JavaScript, D3.js (Bostock (2012)), and WebGL (reference).
+This animation was developed using the software based on JavaScript, D3.js (Bostock (2012)), and WebGL (Mozilla Foundation (2011)).
 The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization.
@@
 The use of \texttt{transition\_*()} functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time.
-This includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package \{Ooms (2023b)\} to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package \{Ooms (2023a)\} to save it into a video file format.
+This includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package (Ooms (2023b)) to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package (Ooms (2023a)) to save it into a video file format.
 
@@
 In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation.
-The initial step is to reformat the data to the animated data structure as seen in \ref{fig:data-diagram}.
+The initial step is to reformat the data to the animated data structure as seen in Figure \ref{fig:data-diagram}.
 The second stage is creating a \texttt{ggplot} object, which can be subsequently passed into the animation function.
@@
 group\_scaling & The column name that represents the grouping variable.\\
+\hline
+scaling & The scaling method to be used; "rank" or "absolute."\\
 \hline
@@
 #>    <fct> <int> <dbl> <dbl> <fct>
-#>  1 1      2020     5     2 X    
-#>  2 1      2023     5     3 X    
-#>  3 2      2020     5    20 X    
-#>  4 2      2023     5    21 X    
-#>  5 3      2020     5    34 X    
-#>  6 3      2023     5    35 X    
-#>  7 4      2020     5    20 X    
-#>  8 4      2023     5    21 X    
-#>  9 5      2020     5    45 X    
-#> 10 5      2023     5    46 X
+#>  1 1      2020     5    36 X    
+#>  2 1      2023     5    37 X    
+#>  3 2      2020     5    49 X    
+#>  4 2      2023     5    50 X    
+#>  5 3      2020     5    48 X    
+#>  6 3      2023     5    49 X    
+#>  7 4      2020     5    50 X    
+#>  8 4      2023     5    51 X    
+#>  9 5      2020     5    43 X    
+#> 10 5      2023     5    44 X
 \end{verbatim}
@@
 #>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
-#>   ..$ frame: num [1:400] 2 3 20 21 34 35 20 21 45 46 ...
+#>   ..$ frame: num [1:400] 36 37 49 50 48 49 50 51 43 44 ...
 #>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
@@
 This paper is created using the \CRANpkg{rjtools} packages (O'Hara-Wild et al.
-(2023)) and is based on the 0.0.0.9 version of the \pkg{animbook} package.
+(2023)) and utilized the \CRANpkg{dplyr}, \CRANpkg{knitr}, \CRANpkg{gganimate}, and \CRANpkg{kableExtra} for creating the visual included in this paper.
+This paper is based on the 0.0.0.9 version of the \pkg{animbook} package.
 This version is available on \href{https://github.com/KrisanatA/animbook}{GitHub}.
+I also acknowledge the use of ChatGPT (\url{https://chat.openai.com/}) to improve the text, grammar, and spelling.
 
-I also acknowledge the use of ChatGPT (\url{https://chat.openai.com/}) to improve the text, grammar and spelling.
+\begin{itemize}
+\tightlist
+\item
+  The presentation for the ETC5543 can be found on \href{https://github.com/KrisanatA/animbook-presentation}{GitHub.}
+\item
+  This paper is contained in the following \href{https://github.com/KrisanatA/animbook-journal}{GitHub repository.}
+\end{itemize}
 
@@
 McGowan, Müge Adalet, Dan Andrews, and Valentine Millot. 2017. {``The Walking Dead?''} no. 1372. https://doi.org/\url{https://doi.org/https://doi.org/10.1787/180d80ad-en}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-webgl}{}}%
+Mozilla Foundation. 2011. {``WebGL.''} Khronos WebGL Working Group. \href{https://www.khronos.org/webgl/}{www.khronos.org/webgl/}.
 

### 2023-10-30 animbook-journal.R

@@ -115,7 +115,7 @@ argument_table |>
 
 ## ----tbl-animprep-------------------------------------------------------------
 argument_table |> 
-  filter(argument %in% c("ngroup", "breaks", "group_scaling", "scaline")) |> 
+  filter(argument %in% c("ngroup", "breaks", "group_scaling", "scaling")) |> 
   knitr::kable(caption = "The argument in the anim\\_prep for customized the data scaling.")
 
 

### 2023-11-27 animbook-journal.Rmd
change the paper to the new package structure

@@
 In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation.
-The initial step is to reformat the data to the animated data structure as seen in Figure \@ref(fig:data-diagram).
+The initial step is to reformat the data into a categorized data structure, as seen in Figure \@ref(fig:data-diagram).
 The second stage is creating a `ggplot` object, which can be subsequently passed into the animation function.
+During the second stage, an internal function will turn the categorized data into an animated data structure.
 The final step involves transforming the `ggplot` to a `gganimate` object by integrating the animation settings.
@@
 
-rank <- anim_prep(dbl_change, id, values, time, color = gp)
+rank <- anim_prep(dbl_change, id, values, time, group = gp)
 
-rank_data <- rank$data |> 
+class(rank) <- c("tbl_df", "tbl", "data.frame")
+
+rank_data <- rank |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
-  rename(gp = color,
+  rename(gp = group,
          rank = qtile) |>  
-  select(-frame) |> 
   arrange(gp, id)
 
-absolute <- anim_prep(dbl_change, id, values, time, color = gp, scaling = "absolute")
+absolute <- anim_prep(dbl_change, id, values, time, group = gp, scaling = "absolute")
 
-absolute_data <- absolute$data |> 
+class(absolute) <- c("tbl_df", "tbl", "data.frame")
+
+absolute_data <- absolute |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |>  
-  rename(gp = color,
+  rename(gp = group,
          absolute = qtile) |> 
-  select(-frame) |> 
   arrange(gp, id)
 
-rank_group <- anim_prep(dbl_change, id, values, time, color = gp, group_scaling = gp)
+rank_group <- anim_prep(dbl_change, id, values, time, group = gp, group_scaling = gp)
 
-rank_group_data <- rank_group$data |> 
+class(rank_group) <- c("tbl_df", "tbl", "data.frame")
+
+rank_group_data <- rank_group |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
@@
          rank_group = qtile) |> 
-  select(-c(frame, color)) |> 
   arrange(gp, id)
 
-absolute_group <- anim_prep(dbl_change, id, values, time, color = gp, group_scaling = gp, scaling = "absolute")
+absolute_group <- anim_prep(dbl_change, id, values, time, group = gp, group_scaling = gp, scaling = "absolute")
 
-absolute_group_data <- absolute_group$data |> 
+class(absolute_group) <- c("tbl_df", "tbl", "data.frame")
+
+absolute_group_data <- absolute_group |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
@@
          absolute_group = qtile) |> 
-  select(-c(frame, color)) |> 
   arrange(gp, id)
@@
 
+  All of the pre-processing steps mentioned above are completed using the `anim_prep()` or `anim_prep_cat()` function, depending on the stages of the data structure.
+The `anim_prep()` function is used for raw data format, while the `anim_prep_cat()` function is for categorized data format.
+There are additional arguments that allow users for more customization.
+
   These are only the initial steps in formatting the data into a category.
@@
 The functions mentioned in this paragraph are from the \CRANpkg{dplyr} package (@dplyr).
-
-  All of the pre-processing steps mentioned above are completed using the `anim_prep()` or `anim_prep_cat()` function, depending on the stages of the data structure.
-The `anim_prep()` function is used for raw data format, while the `anim_prep_cat()` function is for categorized data format.
-There are additional arguments that allow users for more customization.
+These are done by the internal function for each of the plots provided in the packages.
 
 ```{r}
-argument <- c("data", "id", "values", "time", "ngroup", "breaks", "group_scaling",
-               "scaling", "order", "label", "color", "time_dependent", "runif_min",
-               "runif_max")
+argument <- c("data", "id", "values", "time", "group", "ncat", "breaks", "label",
+              "group_scaling", "scaling", "order", "time_dependent")
 
@@
                  "The column name represents the time variable.",
+                 "The column name that distinguishes between the values group.",
                  "The number of groups or categories to create for scaling values.",
                  "A vector of breaks for creating bins.",
+                 "A vector of labels to be used for the y-axis in the visualization.",
                  "The column name that represents the grouping variable.",
@@
                  "A vector of order for sorting the category values.",
-                 "A vector of labels to be used for the y-axis in the visualization.",
-                 "The column name to be used in ggplot2::aes() for the plot function.",
-                 "Logical. Should the visualization be time-dependent? Default is TRUE.",
-                 "The minimum value for random addition to frame numbers.",
-                 "The maximum value for random addition to frame numbers.")
+                 "Logical. Should the visualization be time-dependent? Default is TRUE.")
 
@@
 argument_table |> 
-  filter(argument %in% c("ngroup", "breaks", "group_scaling", "scaling")) |> 
+  filter(argument %in% c("ncat", "breaks", "group_scaling", "scaling")) |> 
   knitr::kable(caption = "The argument in the anim\\_prep for customized the data scaling.")
@@
 argument_table |> 
-  filter(argument %in% c("label", "color", "time_dependent", 
-                         "runif_min", "runif_max")) |> 
+  filter(argument %in% c("label", "group", "time_dependent")) |> 
   knitr::kable(caption = "The additional argument for customizing the aesthetics of the visualization.")
@@
 Two of the plots could be used for the animation, and another plot is used as a static visualization.
-All of the plots have an internal function that converts the standard data format into the required structure for each plotting function.
+All of the plots have an internal function that converts the categorized data format into the animated structure for each plotting function.
 
@@
 The frame is recalculated using the same method mentioned in the data preprocessing section.
-The `sankey_shade()` function is called to generate the proportional shaded data.
+The `proportional_shade()` function is called to generate the proportional shaded data.
 
-```{r shade-algorithm, fig.show="hold", out.width="50%", fig.cap="The plot shows how the algorithm for the sankey\\_shade() function works.
+```{r shade-algorithm, fig.show="hold", out.width="50%", fig.cap="The plot shows how the algorithm for the proportional\\_shade() function works.
 The left figure represents the initial step of the algorithm, which calculates all the corner points.
@@
 
-  The algorithm behind the `sankey_shade()` function for generating the proportional shaded data is illustrated in Figure \@ref(fig:shade-algorithm).
+  The algorithm behind the `proportional_shade()` function for generating the proportional shaded data is illustrated in Figure \@ref(fig:shade-algorithm).
 It started by calculating the corner points for all of the shaded areas.
@@
 ```{r, eval=knitr::is_html_output()}
-argument2 <- c("object", "group_palette", "shade_palette", "rendering",
+argument2 <- c("data", "group_palette", "shade_palette", "rendering",
                "subset", "relation", "total_point", "height", "width", "size",
@@
 
-description2 <- c("The animbook object returned from the prep function.",
+description2 <- c("The categorized data returned from the prep function.",
                   "The vector of the palette used by the function to supply the color to each group.",
@@
 ```{r, eval=knitr::is_latex_output()}
-argument2 <- c("object", "group_palette", "shade_palette", "rendering",
+argument2 <- c("data", "group_palette", "shade_palette", "rendering",
                "subset", "relation", "total_point", "height", "width", "size",
@@
 Since this data is already in the categorized data structure, the `anim_prep_cat()` function is utilized.
-
-  The output produced from this package is referred to as the `animbook` object.
-This contained a list of data and settings that hold prepared data for visualization, along with a list of settings used in the plot function.
+The output produced from this package is referred to as the `categorized` data.
 
@@
                           time = time, 
-                          color = gp, 
-                          time_dependent = FALSE)
+                          group = gp)
 
-head(animbook$data, 10)
+head(animbook, 10)
 str(animbook)
@@
 ```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
-p <- wallaby_plot(object = animbook,
+p <- wallaby_plot(data = animbook,
              group_palette = RColorBrewer::brewer.pal(9, "Set1"),
@@
                                "#D9D9D9","#D9D9D9","#D9D9D9"),
-             rendering = "ggplot",
+             rendering = "gganimate",
              subset = "top",
@@
 ```
+
 ```{r catchange-figure, fig.cap = "Animate visualization using example data.
@@
                       label = label, 
-                      ngroup = 4, 
-                      color = country, 
-                      time_dependent = FALSE)
+                      ncat = 4, 
+                      group = country)
 
@@
                        time = year,
-                       color = gender,
-                       order = NULL,
-                       time_dependent = FALSE)
+                       group = gender,
+                       order = NULL)
 
-p_voter <- wallaby_plot(object = voter,
+p_voter <- wallaby_plot(data = voter,
                   group_palette = c("pink", "blue", "red"),
@@
                                     "#D9D9D9","#D9D9D9","#D9D9D9"),
-                  rendering = "ggplot",
+                  rendering = "gganimate",
                   subset = "top",

### 2023-11-27 animbook-journal.tex
change the paper to the new package structure

@@
 In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation.
-The initial step is to reformat the data to the animated data structure as seen in Figure \ref{fig:data-diagram}.
+The initial step is to reformat the data into a categorized data structure, as seen in Figure \ref{fig:data-diagram}.
 The second stage is creating a \texttt{ggplot} object, which can be subsequently passed into the animation function.
+During the second stage, an internal function will turn the categorized data into an animated data structure.
 The final step involves transforming the \texttt{ggplot} to a \texttt{gganimate} object by integrating the animation settings.
@@
 
+All of the pre-processing steps mentioned above are completed using the \texttt{anim\_prep()} or \texttt{anim\_prep\_cat()} function, depending on the stages of the data structure.
+The \texttt{anim\_prep()} function is used for raw data format, while the \texttt{anim\_prep\_cat()} function is for categorized data format.
+There are additional arguments that allow users for more customization.
+
 These are only the initial steps in formatting the data into a category.
@@
 (2023)).
-
-All of the pre-processing steps mentioned above are completed using the \texttt{anim\_prep()} or \texttt{anim\_prep\_cat()} function, depending on the stages of the data structure.
-The \texttt{anim\_prep()} function is used for raw data format, while the \texttt{anim\_prep\_cat()} function is for categorized data format.
-There are additional arguments that allow users for more customization.
+These are done by the internal function for each of the plots provided in the packages.
 
@@
 \hline
-ngroup & The number of groups or categories to create for scaling values.\\
+ncat & The number of groups or categories to create for scaling values.\\
 \hline
@@
 \hline
+group & The column name that distinguishes between the values group.\\
+\hline
 label & A vector of labels to be used for the y-axis in the visualization.\\
 \hline
-color & The column name to be used in ggplot2::aes() for the plot function.\\
-\hline
 time\_dependent & Logical. Should the visualization be time-dependent? Default is TRUE.\\
-\hline
-runif\_min & The minimum value for random addition to frame numbers.\\
-\hline
-runif\_max & The maximum value for random addition to frame numbers.\\
 \hline
@@
 The frame is recalculated using the same method mentioned in the data preprocessing section.
-The \texttt{sankey\_shade()} function is called to generate the proportional shaded data.
+The \texttt{proportional\_shade()} function is called to generate the proportional shaded data.
 
 \begin{figure}
-\includegraphics[width=0.5\linewidth]{figures/sankey-shade-1} \includegraphics[width=0.5\linewidth]{figures/sankey-shade-2} \caption{The plot shows how the algorithm for the sankey\_shade() function works.
+\includegraphics[width=0.5\linewidth]{figures/sankey-shade-1} \includegraphics[width=0.5\linewidth]{figures/sankey-shade-2} \caption{The plot shows how the algorithm for the proportional\_shade() function works.
 The left figure represents the initial step of the algorithm, which calculates all the corner points.
@@
 
-The algorithm behind the \texttt{sankey\_shade()} function for generating the proportional shaded data is illustrated in Figure \ref{fig:shade-algorithm}.
+The algorithm behind the \texttt{proportional\_shade()} function for generating the proportional shaded data is illustrated in Figure \ref{fig:shade-algorithm}.
 It started by calculating the corner points for all of the shaded areas.
@@
 \hline
-object & The animbook object returned from the prep function.\\
+data & The categorized data returned from the prep function.\\
 \hline
@@
 Since this data is already in the categorized data structure, the \texttt{anim\_prep\_cat()} function is utilized.
-
-The output produced from this package is referred to as the \texttt{animbook} object.
-This contained a list of data and settings that hold prepared data for visualization, along with a list of settings used in the plot function.
+The output produced from this package is referred to as the \texttt{categorized} data.
 
@@
                           time = time, 
-                          color = gp, 
-                          time_dependent = FALSE)
+                          group = gp)
 
-head(animbook$data, 10)
+head(animbook, 10)
 \end{verbatim}
@@
 #> # A tibble: 10 x 5
-#>    id     time qtile frame color
-#>    <fct> <int> <dbl> <dbl> <fct>
-#>  1 1      2020     5    36 X    
-#>  2 1      2023     5    37 X    
-#>  3 2      2020     5    49 X    
-#>  4 2      2023     5    50 X    
-#>  5 3      2020     5    48 X    
-#>  6 3      2023     5    49 X    
-#>  7 4      2020     5    50 X    
-#>  8 4      2023     5    51 X    
-#>  9 5      2020     5    43 X    
-#> 10 5      2023     5    44 X
+#>    id     time qtile label group
+#>    <fct> <int> <dbl> <chr> <fct>
+#>  1 1      2020     5 A     X    
+#>  2 2      2020     5 A     X    
+#>  3 3      2020     5 A     X    
+#>  4 4      2020     5 A     X    
+#>  5 5      2020     5 A     X    
+#>  6 6      2020     5 A     X    
+#>  7 7      2020     5 A     X    
+#>  8 8      2020     5 A     X    
+#>  9 9      2020     5 A     X    
+#> 10 10     2020     5 A     X
 \end{verbatim}
@@
 \begin{verbatim}
-#> List of 2
-#>  $ data    : tibble [400 x 5] (S3: tbl_df/tbl/data.frame)
-#>   ..$ id   : Factor w/ 200 levels "1","2","3","4",..: 1 1 2 2 3 3 4 4 5 5 ...
-#>   ..$ time : int [1:400] 2020 2023 2020 2023 2020 2023 2020 2023 2020 2023 ...
-#>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
-#>   ..$ frame: num [1:400] 36 37 49 50 48 49 50 51 43 44 ...
-#>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
-#>  $ settings:List of 7
-#>   ..$ gap           : num 0.1
-#>   ..$ xbreaks       : int [1:2] 2020 2023
-#>   ..$ label         : chr [1:5] "A" "B" "C" "D" ...
-#>   ..$ order         : chr [1:5] "A" "B" "C" "D" ...
-#>   ..$ time_dependent: logi FALSE
-#>   ..$ runif_min     : num 1
-#>   ..$ runif_max     : num 50
-#>  - attr(*, "class")= chr "animbook"
+#> tibble[,5] (S3: tbl_df/tbl/data.frame/categorized)
+#>  $ id   : Factor w/ 200 levels "1","2","3","4",..: 1 2 3 4 5 6 7 8 9 10 ...
+#>  $ time : int [1:400] 2020 2020 2020 2020 2020 2020 2020 2020 2020 2020 ...
+#>  $ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
+#>  $ label: chr [1:400] "A" "A" "A" "A" ...
+#>  $ group: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
 \end{verbatim}
@@
 \begin{verbatim}
-p <- wallaby_plot(object = animbook,
+p <- wallaby_plot(data = animbook,
              group_palette = RColorBrewer::brewer.pal(9, "Set1"),

### 2023-11-27 animbook-journal.R

@@ -37,40 +37,44 @@ original <- dbl_change |>
   reframe(id, time, values, gp) |> 
   arrange(gp, id)
 
-rank <- anim_prep(dbl_change, id, values, time, color = gp) 
+rank <- anim_prep(dbl_change, id, values, time, group = gp) 
 
-rank_data <- rank$data |> 
+class(rank) <- c("tbl_df", "tbl", "data.frame")
+
+rank_data <- rank |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
-  rename(gp = color,
-         rank = qtile) |> 
-  select(-frame) |> 
+  rename(gp = group,
+         rank = qtile) |>  
   arrange(gp, id)
 
-absolute <- anim_prep(dbl_change, id, values, time, color = gp, scaling = "absolute") 
+absolute <- anim_prep(dbl_change, id, values, time, group = gp, scaling = "absolute") 
 
-absolute_data <- absolute$data |> 
+class(absolute) <- c("tbl_df", "tbl", "data.frame")
+
+absolute_data <- absolute |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |>  
-  rename(gp = color,
+  rename(gp = group,
          absolute = qtile) |> 
-  select(-frame) |> 
   arrange(gp, id)
 
-rank_group <- anim_prep(dbl_change, id, values, time, color = gp, group_scaling = gp) 
+rank_group <- anim_prep(dbl_change, id, values, time, group = gp, group_scaling = gp) 
 
-rank_group_data <- rank_group$data |> 
+class(rank_group) <- c("tbl_df", "tbl", "data.frame")
+
+rank_group_data <- rank_group |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
   rename(gp = group,
          rank_group = qtile) |> 
-  select(-c(frame, color)) |> 
   arrange(gp, id)
 
-absolute_group <- anim_prep(dbl_change, id, values, time, color = gp, group_scaling = gp, scaling = "absolute") 
+absolute_group <- anim_prep(dbl_change, id, values, time, group = gp, group_scaling = gp, scaling = "absolute") 
 
-absolute_group_data <- absolute_group$data |> 
+class(absolute_group) <- c("tbl_df", "tbl", "data.frame")
+
+absolute_group_data <- absolute_group |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
[…]

### 2023-12-04 animbook-journal.Rmd
to do list 28/11/23

@@
 
-The development version of \pkg{animbook} can be installed from [GitHub](https://github.com/KrisanatA/animbook) with:
+The development version of \pkg{animbook} can be installed from [https://github.com/KrisanatA/animbook](https://github.com/KrisanatA/animbook) with:
 
@@
 ```{r}
-argument <- c("data", "id", "values", "time", "group", "ncat", "breaks", "label",
-              "group_scaling", "scaling", "order", "time_dependent")
+argument_num <- c("data", "id", "values", "time", "group", "ncat", "breaks", "label", 
+              "group_scaling", "scaling")
 
-description <- c("A data frame containing the data to be prepared for visualization.",
-                 "The column name that represents the unique identifier variable.",
-                 "The column name that contains the numeric values to be visualized.",
-                 "The column name represents the time variable.",
-                 "The column name that distinguishes between the values group.",
-                 "The number of groups or categories to create for scaling values.",
-                 "A vector of breaks for creating bins.",
-                 "A vector of labels to be used for the y-axis in the visualization.",
-                 "The column name that represents the grouping variable.",
-                 "The scaling method to be used; \"rank\" or \"absolute.\"",
-                 "A vector of order for sorting the category values.",
-                 "Logical. Should the visualization be time-dependent? Default is TRUE.")
+description_num <- c("The numerical data to be prepared for visualization.",
+                     "The column name in the data that will be used to identify an individual over time. For example, company name.",
+                     "The column name in the data that will be used for the y-axis (must be numerical).",
+                     "The column name in the data represents the time variable (x-axis).",
+                     "The column name in the data for distinguishes between the values group (for example, country). In the visualization, this will be used as a color argument.",
+                     "The number of categories to create for scaling values. The default for this function is 5 categories.",
+                     "A vector of breaks for creating bins. If this is not provided, the bins will have equal size.",
+                     "A vector of labels to be used for the y-axis in the visualization. If this is not provided, the labels will be the position on the y-axis.",
+                     "The column name in the data that will be used for grouping. Allow the function to isolate the calculation between the groups.",
+                     "The scaling method to be used; \"rank\" or \"absolute\". The default scaling is \"rank\".")
 
-argument_table <- tibble::tibble(Argument = argument,
-                         Description = description)
+argument_num_tab <- tibble::tibble(Argument = argument_num,
+                                   Description = description_num)
 ```
 
-```{r tbl-required}
-argument_table |> 
-  filter(argument %in% c("data", "id", "values", "time")) |> 
-  knitr::kable(caption = "The required argument for the prep function.")
+```{r}
+argument_cat <- c("data", "id", "values", "time", "group", "order", "label")
+
+description_cat <- c("The data that contains the values in the categorized format.",
+                     "The column name in the data that will be used to identify an individual over time. For example, election parties.",
+                     "The column name in the data that will be used for the y-axis (must be a factor).",
+                     "The column name in the data represents the time variable (x-axis).",
+                     "The column name in the data for distinguishes between the values group (for example, gender). In the visualization, this will be used as a color argument.",
+                     "A vector of order for sorting the category values. If this is not provided, it will be arranged based on the number of observations (largest to smallest).",
+                     "A vector of labels to be used for the y-axis in the visualization. If this is not provided, the labels will be the position on the y-axis.")
+
+argument_cat_tab <- tibble::tibble(Argument = argument_cat,
+                                   Description = description_cat)
 ```
 
-```{r tbl-animprep}
-argument_table |> 
-  filter(argument %in% c("ncat", "breaks", "group_scaling", "scaling")) |> 
-  knitr::kable(caption = "The argument in the anim\\_prep for customized the data scaling.")
+```{r tbl-num, eval=knitr::is_html_output()}
+argument_num_tab |> 
+  knitr::kable(caption = "The arguments for the anim\\_prep function.")
 ```
 
-```{r tbl-animprepcat}
-argument_table |> 
-  filter(argument %in% c("order")) |> 
-  knitr::kable(caption = "The argument in the anim\\_prep\\_cat for customized the order of the category.")
+```{r tbl-num-la, eval=knitr::is_latex_output()}
+argument_num_tab |> 
+  kableExtra::kable(caption = "The arguments for the anim\\_prep function.", format = "latex") |> 
+  kableExtra::column_spec(2, width = "30em")
 ```
 
-```{r tbl-visual}
-argument_table |> 
-  filter(argument %in% c("label", "group", "time_dependent")) |> 
-  knitr::kable(caption = "The additional argument for customizing the aesthetics of the visualization.")
+```{r tbl-cat, eval=knitr::is_html_output()}
+argument_cat_tab |> 
+  knitr::kable(caption = "The arguments for the anim\\_prep\\_cat function.")
 ```
 
-  In the `anim_prep()` and `anim_prep_cat()`, there are required arguments that need to be specified. The lists are in the Table \@ref(tab:tbl-required).
+```{r tbl-cat-la, eval=knitr::is_latex_output()}
+argument_num_tab |> 
+  kableExtra::kable(caption = "The argumenst for the anim\\_prep\\_cat function.", format = "latex") |> 
+  kableExtra::column_spec(2, width = "30em")
+```
 
-  As shown previously, there are a total of four different scaling for the `anim_prep()` function.
-Both the use can customization of these scaling can be set using the following arguments in Table \@ref(tab:tbl-animprep).
+  The argument for the `anim_prep()` and `anim_prep_cat()` function are listed in the Table `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-num-la}','\\@ref(tab:tbl-num)'))` and `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-cat-la}','\\@ref(tab:tbl-cat)'))` respectively.
+The `data`, `id`, `values`, and `time` arguments are required for both functions.
 
-  For the `anim_prep_cat()` function, the arguments that allowed the user to order the category are by using this argument in Table \@ref(tab:tbl-animprepcat).
+  The `ncat`, `breaks`, `group_scaling`, and `scaling` arguments are for the user to customize the data scaling calculation in the `anim_prep()` function.
+In the `anim_prep_cat` function, the users can customize the order of the category to be shown on the y-axis using the `order` argument.
 
-  Then, for further customization regarding how the final visualization looks. The following arguments in Table \@ref(tab:tbl-visual) can be adjusted.
+  Then, for further customization regarding how the final visualization looks. The `group`, `label`, and `time_dependent` arguments can be adjusted.
 
@@
 
-```{r, eval=knitr::is_html_output()}
+```{r}
 argument2 <- c("data", "group_palette", "shade_palette", "rendering",
@@
                   "The vector of the palette used by the function to supply the color to the shaded area.",
-                  "The choice of method used to create and display the plot, either gganimate or plotly.",
-                  "A character string specifying the variable used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument.",
-                  "The choice of relationship for the values to display on the plot, either \"one_many.\" or \"many_one.\"",
+                  "The choice of method used to create and display the plot, either gganimate or plotly. Default is gganimate.",
+                  "A character string specifying the variable used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument. Default is \"top\".",
+                  "The choice of relationship for the values to display on the plot, either \"one_many.\" or \"many_one\". Default is \"one_many\".",
                   "The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.",
-                  "The proportion of the area occupied by the observations in the shaded areas.",
-                  "The distance between the first and last observation in the animation.",
-                  "The point size.",
-                  "The opacity of the proportional shaded areas.")
+                  "The proportion of the area occupied by the observations in the shaded areas. Default is 0.6.",
+                  "The distance between the first and last observation in the animation. Default is 50.",
+                  "The point size. Default is 2.",
+                  "The opacity of the proportional shaded areas. Default is 0.1.")
 
@@
   knitr::kable(caption = "The arguments for the wallaby\\_plot function.")
-```
-
-```{r, eval=knitr::is_latex_output()}
-argument2 <- c("data", "group_palette", "shade_palette", "rendering",
-               "subset", "relation", "total_point", "height", "width", "size",
-               "alpha")
-
-description2 <- c("The categorized data returned from the prep function.",
-                  "The vector of the palette used by the function to supply the color to each group.",
-                  "The vector of the palette used by the function to supply the color to the shaded area.",
-                  "The choice of method used to create and display the plot, either gganimate or plotly.",
-                  "A character string specifying the variable used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument.",
-                  "The choice of relationship for the values to display on the plot, either \"one_many.\" or \"many_one.\"",
-                  "The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.",
-                  "The proportion of the area occupied by the observations in the shaded areas.",
-                  "The distance between the first and last observation in the animation.",
-                  "The point size.",
-                  "The opacity of the proportional shaded areas.")
-
-argument_table2 <- tibble::tibble(Argument = argument2,
-                                  Description = description2)
 ```
@@
 ```{r catchange-gif, out.extra="class = 'gif'", fig.cap = "Animate visualization using example data.
-All of the X observations stay within the same group, while Y observations change from group A to group E.", eval=knitr::is_html_output()}
+All of the X observations stay within the same group, while some of the Y observations change from group A to group E.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/catchange.gif")
@@
 
-The accounting Osiris data that will be used in this section was collected from Bureau van Dijk (@bvd).
-This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide.
-The variables of interest from this data set are ID, year, country, and sales.
-A subset of companies from this data set is used recorded from 2006 to 2018.
-This sample is included in the package.
+The data included in the package contained a record of 790 companies from 2006 to 2018.
+The variables in this data are year, ID, country, sales, and japan.
+It is a subset of the 2021 sample data collected from the Bureau van Dijk (@bvd).
+The original data comprises 1000 companies from 1991 to 2020.
+It has 94 variables of information on listed and major unlisted/delisted companies worldwide.
 
-  An OECD report (@oecd_report) claims that the United States has a faster metabolic rate relative to Japanese companies.
-We use the wallaby plot and kangaroo plot animation to explore this.
-The steps are:
+  An OECD report (@oecd_report) claims that the United States has a faster metabolic rate relative to Japanese companies, indicating that more US companies are listed and exited.
+The wallaby plot allows for the observation of the entry and exit behavior.
+It provides an insight into the number of companies involved in these actions.
+Additionally, the kangaroo plot animation displays a full view of the movement of the companies over time, helping to explain any behavior not depicted in the wallaby plot.
+It particularly looks at the movement between the beginning and end of the observation period.
 
-- Filter the countries to include only the United States and Japan. 
-- Prepare the data using the `anim_prep` function with the first scaling, which is a ranking method. 
-- Use the `wallaby_plot` and `kangaroo_plot` functions to create `ggplot` objects and add default settings for `gganimate` rendering.
+  The steps needed to create a visualization:
+1. Filter the countries to include only the United States and Japan. 
+2. Prepare the data using the `anim_prep` function with the first scaling, which is a ranking method. 
+3. Use the `wallaby_plot` and `kangaroo_plot` functions to create `ggplot` objects and add default settings for `gganimate` rendering.
 
@@
 Most of the movement is made by American companies, supporting the OECD report (@oecd_report) that the United States has a higher turnover rate compared to Japan.
-To emphasize this point, the wallaby plot can be utilized (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`).
-There are clearly more American companies de-listed compared to Japanese companies, and we can see that there are no Japanese companies in the Top 25% in 2006 that were de-listed.
+
+  Using the wallaby plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`), it emphasize the high turnover rate from the kangaroo plot.
+There are clearly more American companies de-listed compared to Japanese companies, and it can be seen that there are no Japanese companies in the Top 25% in 2006 that were de-listed.
 
@@
 
-The Australian Election Study data was collected from ADA Dataverse (@aeles).
-The dataset included in the \pkg{animbook} package contains 1,468 rows and 4 variables of information: ID, year, party, and gender.
-This dataset comprises survey responses from the 2019 election.
-The year column was transformed from the two different questions to answer how the top party performs in keeping the old voters for different genders relative to the 2016 Australian election results.
+The election survey dataset included in the \pkg{animbook} package focuses on the voter behavior of the 734 individuals who participated in the 2019 survey.
+The variables in this data are id, year, party, and gender.
+The ID variable has been de-identified to ensure the privacy of the responders, preventing the identification of the survey participants.
+The year column is derived from the two different questions in the survey, which answered how the top party performs in keeping the old voters of different genders relative to the 2016 Australian election results.
+This dataset was collected from ADA Dataverse (@aeles).
 
@@
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
-Interestingly, individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+Interestingly, an individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.
+However, not many of them are shown in the plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
 knitr::include_graphics("figures/animation-voter.png")
@@
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
-Interestingly, individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.", eval=knitr::is_html_output()}
+Interestingly, an individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.
+However, not many of them are shown in the plot.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/voter.gif")
@@
 
-  Liberal Party analysts may find it worthwhile to delve into this topic further, considering both the benefits and drawbacks.
-If the Liberal Party wishes to retain this demographic of voters, they may need to consider implementing a campaign focused on LGBTIQ+ issues.
-However, this may also lead to a further defection of conservative voters.
+  According to the survey (@lgbtiq), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities.
+However, the Labor Party only give a broad statement of commitment to a range of LGBTIQ+ and human right issues.
+This includes working with LGBTIQ+ Australians and advocates to ensure equality before the law and full access to Medicare.
 
@@
 Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences.
-In the current version of \pkg{animbook}, the feature to have different speeds for each observation has not yet been implemented.
-This feature will introduce a new dimension that allows the users to explore the data further.
-The plotly rendering is also not yet been optimized for use.
-Additionally, both new animated and static plots could also be added, as seen in the New York Times article (@the_new_york_time), to compare the demographics at a specific point in time.
-On top of that, the \CRANpkg{cli} package (@cli) could be used for a more aesthetically pleasing command-line interface.
+The paper outlines the anticipated data format for input into the prep function, covering raw, categorized, and animated formats.
+It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualization design choices.
+The software is explained in detail with examples and real-world applications.
+If more time were available, the features allowing a vary in speeds for each observation could enhance the visualization with an additional dimension.
+Additionally, the new animated and static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
 
@@
 This paper is based on the 0.0.0.9 version of the \pkg{animbook} package.
-This version is available on [GitHub](https://github.com/KrisanatA/animbook).
+This version is available on [https://github.com/KrisanatA/animbook](https://github.com/KrisanatA/animbook).
 I also acknowledge the use of ChatGPT (https://chat.openai.com/) to improve the text, grammar, and spelling.
 
-- The presentation for the ETC5543 can be found on [GitHub.](https://github.com/KrisanatA/animbook-presentation)
-- This paper is contained in the following [GitHub repository.](https://github.com/KrisanatA/animbook-journal)
+I would like to acknowledge Chika Saka for providing the inspiration that led to the development of this R package.
+Additionally, thanks to Masayuki Jimichi for the efforts in collecting the sample Osiris data, which contributed to the practical application of the package.

### 2023-12-04 animbook-journal.tex
to do list 28/11/23

@@
 
-The development version of \pkg{animbook} can be installed from \href{https://github.com/KrisanatA/animbook}{GitHub} with:
+The development version of \pkg{animbook} can be installed from \url{https://github.com/KrisanatA/animbook} with:
 
@@
 
-\caption{\label{tab:tbl-required}The required argument for the prep function.}
+\caption{\label{tab:tbl-num-la}The arguments for the anim\_prep function.}
 \centering
-\begin{tabular}[t]{l|l}
+\begin{tabular}[t]{l|>{\raggedright\arraybackslash}p{30em}}
 \hline
@@
 \hline
-data & A data frame containing the data to be prepared for visualization.\\
+data & The numerical data to be prepared for visualization.\\
 \hline
-id & The column name that represents the unique identifier variable.\\
+id & The column name in the data that will be used to identify an individual over time. For example, company name.\\
 \hline
-values & The column name that contains the numeric values to be visualized.\\
+values & The column name in the data that will be used for the y-axis (must be numerical).\\
 \hline
-time & The column name represents the time variable.\\
+time & The column name in the data represents the time variable (x-axis).\\
+\hline
+group & The column name in the data for distinguishes between the values group (for example, country). In the visualization, this will be used as a color argument.\\
+\hline
+ncat & The number of categories to create for scaling values. The default for this function is 5 categories.\\
+\hline
+breaks & A vector of breaks for creating bins. If this is not provided, the bins will have equal size.\\
+\hline
+label & A vector of labels to be used for the y-axis in the visualization. If this is not provided, the labels will be the position on the y-axis.\\
+\hline
+group\_scaling & The column name in the data that will be used for grouping. Allow the function to isolate the calculation between the groups.\\
+\hline
+scaling & The scaling method to be used; "rank" or "absolute". The default scaling is "rank".\\
 \hline
@@
 
-\caption{\label{tab:tbl-animprep}The argument in the anim\_prep for customized the data scaling.}
+\caption{\label{tab:tbl-cat-la}The argumenst for the anim\_prep\_cat function.}
 \centering
-\begin{tabular}[t]{l|l}
+\begin{tabular}[t]{l|>{\raggedright\arraybackslash}p{30em}}
 \hline
@@
 \hline
-ncat & The number of groups or categories to create for scaling values.\\
+data & The numerical data to be prepared for visualization.\\
 \hline
-breaks & A vector of breaks for creating bins.\\
+id & The column name in the data that will be used to identify an individual over time. For example, company name.\\
 \hline
-group\_scaling & The column name that represents the grouping variable.\\
+values & The column name in the data that will be used for the y-axis (must be numerical).\\
 \hline
-scaling & The scaling method to be used; "rank" or "absolute."\\
+time & The column name in the data represents the time variable (x-axis).\\
+\hline
+group & The column name in the data for distinguishes between the values group (for example, country). In the visualization, this will be used as a color argument.\\
+\hline
+ncat & The number of categories to create for scaling values. The default for this function is 5 categories.\\
+\hline
+breaks & A vector of breaks for creating bins. If this is not provided, the bins will have equal size.\\
+\hline
+label & A vector of labels to be used for the y-axis in the visualization. If this is not provided, the labels will be the position on the y-axis.\\
+\hline
+group\_scaling & The column name in the data that will be used for grouping. Allow the function to isolate the calculation between the groups.\\
+\hline
+scaling & The scaling method to be used; "rank" or "absolute". The default scaling is "rank".\\
 \hline
@@
 
-\begin{table}
+The argument for the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} function are listed in the Table \ref{tab:tbl-num-la} and \ref{tab:tbl-cat-la} respectively.
+The \texttt{data}, \texttt{id}, \texttt{values}, and \texttt{time} arguments are required for both functions.
 
-\caption{\label{tab:tbl-animprepcat}The argument in the anim\_prep\_cat for customized the order of the category.}
-\centering
-\begin{tabular}[t]{l|l}
-\hline
-Argument & Description\\
-\hline
-order & A vector of order for sorting the category values.\\
-\hline
-\end{tabular}
-\end{table}
+The \texttt{ncat}, \texttt{breaks}, \texttt{group\_scaling}, and \texttt{scaling} arguments are for the user to customize the data scaling calculation in the \texttt{anim\_prep()} function.
+In the \texttt{anim\_prep\_cat} function, the users can customize the order of the category to be shown on the y-axis using the \texttt{order} argument.
 
-\begin{table}
-
-\caption{\label{tab:tbl-visual}The additional argument for customizing the aesthetics of the visualization.}
-\centering
-\begin{tabular}[t]{l|l}
-\hline
-Argument & Description\\
-\hline
-group & The column name that distinguishes between the values group.\\
-\hline
-label & A vector of labels to be used for the y-axis in the visualization.\\
-\hline
-time\_dependent & Logical. Should the visualization be time-dependent? Default is TRUE.\\
-\hline
-\end{tabular}
-\end{table}
-
-In the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()}, there are required arguments that need to be specified. The lists are in the Table \ref{tab:tbl-required}.
-
-As shown previously, there are a total of four different scaling for the \texttt{anim\_prep()} function.
-Both the use can customization of these scaling can be set using the following arguments in Table \ref{tab:tbl-animprep}.
-
-For the \texttt{anim\_prep\_cat()} function, the arguments that allowed the user to order the category are by using this argument in Table \ref{tab:tbl-animprepcat}.
-
-Then, for further customization regarding how the final visualization looks. The following arguments in Table \ref{tab:tbl-visual} can be adjusted.
+Then, for further customization regarding how the final visualization looks. The \texttt{group}, \texttt{label}, and \texttt{time\_dependent} arguments can be adjusted.
 
@@
 \hline
-rendering & The choice of method used to create and display the plot, either gganimate or plotly.\\
+rendering & The choice of method used to create and display the plot, either gganimate or plotly. Default is gganimate.\\
 \hline
-subset & A character string specifying the variable used for subsetting the data. The "top" and "bottom" strings can also be used in this argument.\\
+subset & A character string specifying the variable used for subsetting the data. The "top" and "bottom" strings can also be used in this argument. Default is "top".\\
 \hline
-relation & The choice of relationship for the values to display on the plot, either "one\_many." or "many\_one."\\
+relation & The choice of relationship for the values to display on the plot, either "one\_many." or "many\_one". Default is "one\_many".\\
 \hline
@@
 \hline
-height & The proportion of the area occupied by the observations in the shaded areas.\\
+height & The proportion of the area occupied by the observations in the shaded areas. Default is 0.6.\\
 \hline
-width & The distance between the first and last observation in the animation.\\
+width & The distance between the first and last observation in the animation. Default is 50.\\
 \hline
-size & The point size.\\
+size & The point size. Default is 2.\\
 \hline
-alpha & The opacity of the proportional shaded areas.\\
+alpha & The opacity of the proportional shaded areas. Default is 0.1.\\
 \hline
@@
 
-The accounting Osiris data that will be used in this section was collected from Bureau van Dijk ({``Osiris''} (2023)).
-This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide.
-The variables of interest from this data set are ID, year, country, and sales.
-A subset of companies from this data set is used recorded from 2006 to 2018.
-This sample is included in the package.
+The data included in the package contained a record of 790 companies from 2006 to 2018.
+The variables in this data are year, ID, country, sales, and japan.
+It is a subset of the 2021 sample data collected from the Bureau van Dijk ({``Osiris''} (2023)).
+The original data comprises 1000 companies from 1991 to 2020.
+It has 94 variables of information on listed and major unlisted/delisted companies worldwide.
 
-An OECD report (McGowan, Andrews, and Millot (2017)) claims that the United States has a faster metabolic rate relative to Japanese companies.
-We use the wallaby plot and kangaroo plot animation to explore this.
-The steps are:
+An OECD report (McGowan, Andrews, and Millot (2017)) claims that the United States has a faster metabolic rate relative to Japanese companies, indicating that more US companies are listed and exited.
+The wallaby plot allows for the observation of the entry and exit behavior.
+It provides an insight into the number of companies involved in these actions.
+Additionally, the kangaroo plot animation displays a full view of the movement of the companies over time, helping to explain any behavior not depicted in the wallaby plot.
+It particularly looks at the movement between the beginning and end of the observation period.
 
-\begin{itemize}
-\tightlist
-\item
-  Filter the countries to include only the United States and Japan.
-\item
-  Prepare the data using the \texttt{anim\_prep} function with the first scaling, which is a ranking method.
-\item
-  Use the \texttt{wallaby\_plot} and \texttt{kangaroo\_plot} functions to create \texttt{ggplot} objects and add default settings for \texttt{gganimate} rendering.
-\end{itemize}
+The steps needed to create a visualization:
+1. Filter the countries to include only the United States and Japan.
+2. Prepare the data using the \texttt{anim\_prep} function with the first scaling, which is a ranking method.
+3. Use the \texttt{wallaby\_plot} and \texttt{kangaroo\_plot} functions to create \texttt{ggplot} objects and add default settings for \texttt{gganimate} rendering.
 
@@
 Most of the movement is made by American companies, supporting the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a higher turnover rate compared to Japan.
-To emphasize this point, the wallaby plot can be utilized (Figure \ref{fig:osiris-figure}).
-There are clearly more American companies de-listed compared to Japanese companies, and we can see that there are no Japanese companies in the Top 25\% in 2006 that were de-listed.
+
+Using the wallaby plot (Figure \ref{fig:osiris-figure}), it emphasize the high turnover rate from the kangaroo plot.
+There are clearly more American companies de-listed compared to Japanese companies, and it can be seen that there are no Japanese companies in the Top 25\% in 2006 that were de-listed.
 
@@
 
-The Australian Election Study data was collected from ADA Dataverse (McAllister et al.
+The election survey dataset included in the \pkg{animbook} package focuses on the voter behavior of the 734 individuals who participated in the 2019 survey.
+The variables in this data are id, year, party, and gender.
+The ID variable has been de-identified to ensure the privacy of the responders, preventing the identification of the survey participants.
+The year column is derived from the two different questions in the survey, which answered how the top party performs in keeping the old voters of different genders relative to the 2016 Australian election results.
+This dataset was collected from ADA Dataverse (McAllister et al.
 (2023)).
-The dataset included in the \pkg{animbook} package contains 1,468 rows and 4 variables of information: ID, year, party, and gender.
-This dataset comprises survey responses from the 2019 election.
-The year column was transformed from the two different questions to answer how the top party performs in keeping the old voters for different genders relative to the 2016 Australian election results.
 
@@
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
-Interestingly, individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.}\label{fig:voter-figure}
+Interestingly, an individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.
+However, not many of them are shown in the plot.}\label{fig:voter-figure}
 \end{figure}
@@
 
-Liberal Party analysts may find it worthwhile to delve into this topic further, considering both the benefits and drawbacks.
-If the Liberal Party wishes to retain this demographic of voters, they may need to consider implementing a campaign focused on LGBTIQ+ issues.
-However, this may also lead to a further defection of conservative voters.
+According to the survey ({``LGBTIQ+ Health Australia Party Survey''} (2022)), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities.
+However, the Labor Party only give a broad statement of commitment to a range of LGBTIQ+ and human right issues.
+This includes working with LGBTIQ+ Australians and advocates to ensure equality before the law and full access to Medicare.
 
@@
 Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences.
-In the current version of \pkg{animbook}, the feature to have different speeds for each observation has not yet been implemented.
-This feature will introduce a new dimension that allows the users to explore the data further.
-The plotly rendering is also not yet been optimized for use.
-Additionally, both new animated and static plots could also be added, as seen in the New York Times article (Badger et al.
-(2018)), to compare the demographics at a specific point in time.
-On top of that, the \CRANpkg{cli} package (Csárdi (2023)) could be used for a more aesthetically pleasing command-line interface.
+The paper outlines the anticipated data format for input into the prep function, covering raw, categorized, and animated formats.
+It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualization design choices.
+The software is explained in detail with examples and real-world applications.
+If more time were available, the features allowing a vary in speeds for each observation could enhance the visualization with an additional dimension.
+Additionally, the new animated and static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
 
@@
 This paper is based on the 0.0.0.9 version of the \pkg{animbook} package.
-This version is available on \href{https://github.com/KrisanatA/animbook}{GitHub}.
+This version is available on \url{https://github.com/KrisanatA/animbook}.
 I also acknowledge the use of ChatGPT (\url{https://chat.openai.com/}) to improve the text, grammar, and spelling.
 
-\begin{itemize}
-\tightlist
-\item
-  The presentation for the ETC5543 can be found on \href{https://github.com/KrisanatA/animbook-presentation}{GitHub.}
-\item
-  This paper is contained in the following \href{https://github.com/KrisanatA/animbook-journal}{GitHub repository.}
-\end{itemize}
+I would like to acknowledge Chika Saka for providing the inspiration that led to the development of this R package.
+Additionally, thanks to Masayuki Jimichi for the efforts in collecting the sample Osiris data, which contributed to the practical application of the package.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cli}{}}%
-Csárdi, Gábor. 2023. \emph{Cli: Helpers for Developing Command Line Interfaces}. \url{https://CRAN.R-project.org/package=cli}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-learner-control}{}}%
@@
 Hvitfeldt, Emil. 2018. {``Recreate - Sankey Flow Chart.''} \emph{Recreate - Sankey Flow Chart}. \url{https://emilhvitfeldt.com/post/2018-03-20-recreate-sankey-flow-chart/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lgbtiq}{}}%
+{``LGBTIQ+ Health Australia Party Survey.''} 2022. \emph{LGBTIQ+ Health Australia}. \url{https://www.lgbtiqhealth.org.au/electionsurvey}.
 

### 2023-12-04 animbook-journal.R

@@ -88,48 +88,59 @@ original |>
 
 
 ## -----------------------------------------------------------------------------
-argument <- c("data", "id", "values", "time", "group", "ncat", "breaks", "label",
-              "group_scaling", "scaling", "order", "time_dependent")
+argument_num <- c("data", "id", "values", "time", "group", "ncat", "breaks", "label", 
+              "group_scaling", "scaling")
 
-description <- c("A data frame containing the data to be prepared for visualization.",
-                 "The column name that represents the unique identifier variable.",
-                 "The column name that contains the numeric values to be visualized.",
-                 "The column name represents the time variable.",
-                 "The column name that distinguishes between the values group.",
-                 "The number of groups or categories to create for scaling values.",
-                 "A vector of breaks for creating bins.",
-                 "A vector of labels to be used for the y-axis in the visualization.",
-                 "The column name that represents the grouping variable.",
-                 "The scaling method to be used; \"rank\" or \"absolute.\"",
-                 "A vector of order for sorting the category values.",
-                 "Logical. Should the visualization be time-dependent? Default is TRUE.")
+description_num <- c("The numerical data to be prepared for visualization.",
+                     "The column name in the data that will be used to identify an individual over time. For example, company name.",
+                     "The column name in the data that will be used for the y-axis (must be numerical).",
+                     "The column name in the data represents the time variable (x-axis).",
+                     "The column name in the data for distinguishes between the values group (for example, country). In the visualization, this will be used as a color argument.",
+                     "The number of categories to create for scaling values. The default for this function is 5 categories.",
+                     "A vector of breaks for creating bins. If this is not provided, the bins will have equal size.",
+                     "A vector of labels to be used for the y-axis in the visualization. If this is not provided, the labels will be the position on the y-axis.",
+                     "The column name in the data that will be used for grouping. Allow the function to isolate the calculation between the groups.",
+                     "The scaling method to be used; \"rank\" or \"absolute\". The default scaling is \"rank\".") 
 
-argument_table <- tibble::tibble(Argument = argument,
-                         Description = description)
+argument_num_tab <- tibble::tibble(Argument = argument_num,
+                                   Description = description_num)
 
 
[…]

### 2024-01-03 animbook-journal.Rmd
02/01/2024 to do list

@@
 
-The development version of \pkg{animbook} can be installed from [https://github.com/KrisanatA/animbook](https://github.com/KrisanatA/animbook) with:
+\pkg{animbook} is available through CRAN. The development version of this package can be found in the Github repositories.
 
 ``` r
-# install.packages("devtools")
+# CRAN
+install.packages("animbook")
+
+# Development version
 devtools::install_github("KrisanatA/animbook")
@@
 
-# Application
+# Applications
+
+Two examples of usage are provided.
+The osiris example studies company movement between quantiles of sales performance over a 12-year period.
+The voting example studies party preference changes between 2016 and 2019 elections.
 
@@
 
-The data included in the package contained a record of 790 companies from 2006 to 2018.
-The variables in this data are year, ID, country, sales, and japan.
-It is a subset of the 2021 sample data collected from the Bureau van Dijk (@bvd).
-The original data comprises 1000 companies from 1991 to 2020.
-It has 94 variables of information on listed and major unlisted/delisted companies worldwide.
+The Osiris data presented in this section was acquired from Bureau van Dijk (@bvd), compiling information on a total of 122,318 companies.
+It was subsequently a subset for the 2021 report, consisting of 1000 companies with 94 variables.
+The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018.
+The variables in this dataset include year, ID, country, sales, and japan.
 
-  An OECD report (@oecd_report) claims that the United States has a faster metabolic rate relative to Japanese companies, indicating that more US companies are listed and exited.
-The wallaby plot allows for the observation of the entry and exit behavior.
-It provides an insight into the number of companies involved in these actions.
-Additionally, the kangaroo plot animation displays a full view of the movement of the companies over time, helping to explain any behavior not depicted in the wallaby plot.
-It particularly looks at the movement between the beginning and end of the observation period.
+  @oecd_report reported that companies in the United States have a faster metabolic rate relative to Japanese companies.
+This means that US companies tends to move up and down performance metrics more frequently than Japanese companies.
+This can be examine using the wallaby and kangaroo plots.
+The wallaby plot allows the study of entry and exit behavior.
+The kangaroo plot allows studying the full movement of companies over time.
 
-  The steps needed to create a visualization:
+  The steps needed to create both plots are:
+
 1. Filter the countries to include only the United States and Japan. 
-2. Prepare the data using the `anim_prep` function with the first scaling, which is a ranking method. 
-3. Use the `wallaby_plot` and `kangaroo_plot` functions to create `ggplot` objects and add default settings for `gganimate` rendering.
+2.
+Prepare the data using the `anim_prep` function with the first scaling, which is a ranking method.
+The variable `sales` is used as the performance metric.
+Four quantiles are used as specified by the `ncat` option, and NAs formed a fifth category labeled as "Not listed".
+3.
+Use the `wallaby_plot` and `kangaroo_plot` functions to create `ggplot` objects and add default settings for `gganimate` rendering.
+In the wallaby plot, the `subset` and `relation` options are set to "bottom" and "many_one", respectively, to focus on exiting behavior.
 
@@
 p <- wallaby_plot(accounting,
-                  group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-                  shade_palette = c("#737373", "#969696", "#BDBDBD",
-                                    "#D9D9D9","#D9D9D9","#D9D9D9"),
                   subset = "bottom",
@@
 
+From the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`) it can be seen that most companies stay in the same quantile group over the time period.
+There are several companies that move up and down, and most of these are US companies.
+This support the @oecd_report claim that US companies have a higher turnover rate compared to Japanese companies.
+
+Perceiving the differences between the movement pattern of groups can be difficult, especially when the groups have different sizes as the case here.
+There are more US companies than Japanese companies and particularly there are more US companies in the top 25 percent quantile.
+Thus there will be more blue points (US) moving than red points (JP) purely for this reason.
+Interpreting differences requires the reader to mentally calculated the **relative proportion** between the blue and red points, which is hard.
+
 ```{r osiris-figure, fig.cap = "The wallaby plot visualization shows the companies that exited the market.
@@
 
-  From the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`), most companies are staying in the same quantile group, with only a small number moving upward or downward.
-Most of the movement is made by American companies, supporting the OECD report (@oecd_report) that the United States has a higher turnover rate compared to Japan.
+  From Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`, there are clearly more US companies de-listed compared to Japanese companies, and it can be seen that there are no Japanese companies in the Top 25% in 2006 that were de-listed.
 
-  Using the wallaby plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`), it emphasize the high turnover rate from the kangaroo plot.
-There are clearly more American companies de-listed compared to Japanese companies, and it can be seen that there are no Japanese companies in the Top 25% in 2006 that were de-listed.
+  Using the wallaby plot, it can be employed to emphasized the high turnvoer rate observed in the kangaroo plot, as it specifically focuses on a subset, allowing the users to better perceive the **relative proportion**.
+However, it is important to note that this plot is confined to only two-time points (start and end), which may not provide a comprehensive view of the entire story.
 

### 2024-01-03 animbook-journal.tex
02/01/2024 to do list

@@
 
-The development version of \pkg{animbook} can be installed from \url{https://github.com/KrisanatA/animbook} with:
+\pkg{animbook} is available through CRAN. The development version of this package can be found in the Github repositories.
 
 \begin{verbatim}
-# install.packages("devtools")
+# CRAN
+install.packages("animbook")
+
+# Development version
 devtools::install_github("KrisanatA/animbook")
@@
 
-\hypertarget{application}{%
-\section{Application}\label{application}}
+\hypertarget{applications}{%
+\section{Applications}\label{applications}}
+
+Two examples of usage are provided.
+The osiris example studies company movement between quantiles of sales performance over a 12-year period.
+The voting example studies party preference changes between 2016 and 2019 elections.
 
@@
 
-The data included in the package contained a record of 790 companies from 2006 to 2018.
-The variables in this data are year, ID, country, sales, and japan.
-It is a subset of the 2021 sample data collected from the Bureau van Dijk ({``Osiris''} (2023)).
-The original data comprises 1000 companies from 1991 to 2020.
-It has 94 variables of information on listed and major unlisted/delisted companies worldwide.
+The Osiris data presented in this section was acquired from Bureau van Dijk ({``Osiris''} (2023)), compiling information on a total of 122,318 companies.
+It was subsequently a subset for the 2021 report, consisting of 1000 companies with 94 variables.
+The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018.
+The variables in this dataset include year, ID, country, sales, and japan.
 
-An OECD report (McGowan, Andrews, and Millot (2017)) claims that the United States has a faster metabolic rate relative to Japanese companies, indicating that more US companies are listed and exited.
-The wallaby plot allows for the observation of the entry and exit behavior.
-It provides an insight into the number of companies involved in these actions.
-Additionally, the kangaroo plot animation displays a full view of the movement of the companies over time, helping to explain any behavior not depicted in the wallaby plot.
-It particularly looks at the movement between the beginning and end of the observation period.
+McGowan, Andrews, and Millot (2017) reported that companies in the United States have a faster metabolic rate relative to Japanese companies.
+This means that US companies tends to move up and down performance metrics more frequently than Japanese companies.
+This can be examine using the wallaby and kangaroo plots.
+The wallaby plot allows the study of entry and exit behavior.
+The kangaroo plot allows studying the full movement of companies over time.
 
-The steps needed to create a visualization:
-1. Filter the countries to include only the United States and Japan.
-2. Prepare the data using the \texttt{anim\_prep} function with the first scaling, which is a ranking method.
-3. Use the \texttt{wallaby\_plot} and \texttt{kangaroo\_plot} functions to create \texttt{ggplot} objects and add default settings for \texttt{gganimate} rendering.
+The steps needed to create both plots are:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Filter the countries to include only the United States and Japan.
+\item
+  Prepare the data using the \texttt{anim\_prep} function with the first scaling, which is a ranking method.
+The variable \texttt{sales} is used as the performance metric.
+Four quantiles are used as specified by the \texttt{ncat} option, and NAs formed a fifth category labeled as ``Not listed''.
+\item
+  Use the \texttt{wallaby\_plot} and \texttt{kangaroo\_plot} functions to create \texttt{ggplot} objects and add default settings for \texttt{gganimate} rendering.
+In the wallaby plot, the \texttt{subset} and \texttt{relation} options are set to ``bottom'' and ``many\_one'', respectively, to focus on exiting behavior.
+\end{enumerate}
 
@@
 
+From the kangaroo plot (Figure \ref{fig:kan-osiris-figure}) it can be seen that most companies stay in the same quantile group over the time period.
+There are several companies that move up and down, and most of these are US companies.
+This support the McGowan, Andrews, and Millot (2017) claim that US companies have a higher turnover rate compared to Japanese companies.
+
+Perceiving the differences between the movement pattern of groups can be difficult, especially when the groups have different sizes as the case here.
+There are more US companies than Japanese companies and particularly there are more US companies in the top 25 percent quantile.
+Thus there will be more blue points (US) moving than red points (JP) purely for this reason.
+Interpreting differences requires the reader to mentally calculated the \textbf{relative proportion} between the blue and red points, which is hard.
+
 \begin{figure}
@@
 
-From the kangaroo plot (Figure \ref{fig:kan-osiris-figure}), most companies are staying in the same quantile group, with only a small number moving upward or downward.
-Most of the movement is made by American companies, supporting the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a higher turnover rate compared to Japan.
+From Figure \ref{fig:osiris-figure}, there are clearly more US companies de-listed compared to Japanese companies, and it can be seen that there are no Japanese companies in the Top 25\% in 2006 that were de-listed.
 
-Using the wallaby plot (Figure \ref{fig:osiris-figure}), it emphasize the high turnover rate from the kangaroo plot.
-There are clearly more American companies de-listed compared to Japanese companies, and it can be seen that there are no Japanese companies in the Top 25\% in 2006 that were de-listed.
+Using the wallaby plot, it can be employed to emphasized the high turnvoer rate observed in the kangaroo plot, as it specifically focuses on a subset, allowing the users to better perceive the \textbf{relative proportion}.
+However, it is important to note that this plot is confined to only two-time points (start and end), which may not provide a comprehensive view of the entire story.
 

### 2024-01-03 animbook-journal.R

@@ -239,9 +239,6 @@ accounting <- anim_prep(data,
 kan_p <- kangaroo_plot(accounting)
 
 p <- wallaby_plot(accounting,
-                  group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-                  shade_palette = c("#737373", "#969696", "#BDBDBD",
-                                    "#D9D9D9","#D9D9D9","#D9D9D9"),
                   subset = "bottom",
                   relation = "many_one",
                   height = 1,

### 2024-01-03 animbook-journal.Rmd
small adjustment to language

@@
 Two examples of usage are provided.
-The osiris example studies company movement between quantiles of sales performance over a 12-year period.
+The osiris example studies company movement between quartiles of sales performance over a 12-year period.
 The voting example studies party preference changes between 2016 and 2019 elections.
@@
 
-Perceiving the differences between the movement pattern of groups can be difficult, especially when the groups have different sizes as the case here.
+Perceiving the differences between the movement pattern of groups can be difficult, especially when the groups have different sizes, as is the case here.
 There are more US companies than Japanese companies and particularly there are more US companies in the top 25 percent quantile.
-Thus there will be more blue points (US) moving than red points (JP) purely for this reason.
-Interpreting differences requires the reader to mentally calculated the **relative proportion** between the blue and red points, which is hard.
+Thus there will likely be more blue points (US) moving than red points (JP) purely for this reason.
+The difference that is of interest is **relative proportion**, that one country has a higher fraction of companies moving between quartiles than the other.
+This animated sankey plot requires the reader to mentally calculate the fraction of points that are moving, separately for the blue and red points, to answer the question whether one group has a higher movement rate.
+The task is easier if the two groups have a similar number of points.
 
@@
 It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualization design choices.
-The software is explained in detail with examples and real-world applications.
+The software usage is illustrated with two applications.
 If more time were available, the features allowing a vary in speeds for each observation could enhance the visualization with an additional dimension.
 Additionally, the new animated and static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
+
+- positives and negatives about the method
+- extensions that would be desirable for the software
 

### 2024-01-08 animbook-journal.Rmd
04/01/2023 to do list - data section and example

@@
 Between elections, voters often switch party preferences, which produces categorical values over time.
-Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," we provide new visualization functions to generate animations that display this type of data in an R package called \pkg{animbook}.
+Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," we provide new visualization functions to generate animations that display this type of data in an R package called \CRANpkg{animbook}.
 Functions to pre-process the data and prepare it for the animation are provided.
@@
 On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins.
-For the animation in this paper, the programming language that will be used for recreating and revising the visualization done by The New York Times articles is R (@r).
+
+  There was an implementation of the New York Times animation in R (@r) by @Hvitfeldt_2018.
+This article demonstrates the path generation for each point and how to map them to the animation.
+Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization by incorporating additional elements, particularly the proportional shaded area, and introduces new visualizations inspired by the New York Times animation.
+
+  As mentioned about the proportional shaded area, a similar static visualization of the animation is known as the Sankey plot.
+Sankey plots are flow diagrams that show the movement/change from one state to another, with the width of each arrow representing the proportional changes between states.
+R packages capable of generating a Sankey plot type include  \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}, both are extensions from the \CRANpkg{ggplot2} {@ggplot2}.
+The main difference between the Sankey plot visualization and the animation featured in the New York Times lies in their methods of representing the proportion of changes between states.
+Sankey plots utilize the width of connecting lines, while the New York Times animation employs the density and color of points accompanied by counters.
+Combining the differences between these two features will be shown in the Visualization design section.
 
@@
 
-  The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (@ggplot2) to include the description of an animation.
+  The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package to include the description of an animation.
 It added new grammar classes to the plot object, allowing it to understand how the plot should change over time.
@@
 
-  In the animation, the proportional shaded area has been incorporated to facilitate a quick grasp of the proportion information.
-It displays the proportion of observation within each group.
-The design also needs to account for situations where the visualization lacks an adequate number of data points.
-In such cases, it can be challenging to visually discern the movement pattern of the subgroup, requiring the implementation of observation interpolation.
+  In the animation, the use of proportional shaded areas serves to enhances the quick comprehension of proportion information, effectively displaying the distribution within each group.
+This method replaces the coutners seen in the New York Times animation, alleviating information overload for users and reducing the computation required.
+To represents sub-groups, the plot utilizes color to distinguish differences among observation.
+
+  However, discerning the movement pattern or proportion of sub-groups can be challenging when the visualization lacks a sufficient number of data points.
+Addressing this, observation interpolation is employed by calculating the sub-group proportion and multiplying it by the desired number of generated points.
+This approach ensures a more detailed representation of movement patterns, particularly in scenarios where a limited number of data points may impede visual clarity.
+
+  The issue with this type of animation in the New York Times lies in point clustering, particularly when all points start simultaneously.
+This clustering poses a challenge in distinguishing and tracking individual observations.
+In the context of time series data (e.g., year), the observations in the animation enter the visualization at different times.
+It is important to note that this does not necessarily reflect the real-time occurrence of observations.
+The neglect of the time-dependent nature of observations is a deliberate choice made for visualization purposes, aiming enhance the clarity of the presented information.
 
@@
 
-\pkg{animbook} is available through CRAN. The development version of this package can be found in the Github repositories.
+\CRANpkg{animbook} is available through CRAN. The development version of this package can be found in the Github repositories.
 
@@
 
-In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation.
+In designing the \CRANpkg{animbook} package, a three-step structured approach was developed to create an animation.
 The initial step is to reformat the data into a categorized data structure, as seen in Figure \@ref(fig:data-diagram).
@@
 
+  The names of these plots draws inspiration from a native Australian animals.
+The comprehensive plot is named Kangaroo, while its subset is referred to as Wallaby, representing a smaller version of the Kangaroo.
+The final plot is names after Funnel Web Spider, drawing parallels between the plot's features and the distinctive legs of the spider.
+
   The main focus of this paper will be on the `wallaby_plot()`, which draws inspiration from the New York Times animation and combines the knowledge gained from the previous sections in creating the visualization.
@@
 ```{r}
-argument2 <- c("data", "group_palette", "shade_palette", "rendering",
+argument2 <- c("data", "group_palette", "shade_palette", "rendering", "time_dependent",
                "subset", "relation", "total_point", "height", "width", "size",
@@
                   "The choice of method used to create and display the plot, either gganimate or plotly. Default is gganimate.",
+                  "Should the observations entered the visualization at the same time. Default is FALSE",
                   "A character string specifying the variable used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument. Default is \"top\".",
@@
 The variable `sales` is used as the performance metric.
-Four quantiles are used as specified by the `ncat` option, and NAs formed a fifth category labeled as "Not listed".
+Four quantiles (quartiles) are used as specified by `ncat = 4`, and NAs are converted into a fifth category labeled as "Not listed".
 3.
@@
 
-From the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`) it can be seen that most companies stay in the same quantile group over the time period.
+In the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`) the five grey bars indicate the five categories (Top 25%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018.
+Points represent individual companies with color indicating country of registration.
+Points that stay within the bar indicate companies that remain in the same quartile over the entire time period.
+If a company drop in performance or improve performance to the extent of switching quartile, the corresponding point will jump up or down in this plot.
+Note that all the companies in the "Not listed" category were listed at some point during this time period.
+It can be seen that most companies stay in the same quantile group over the time period.
 There are several companies that move up and down, and most of these are US companies.
@@
 The difference that is of interest is **relative proportion**, that one country has a higher fraction of companies moving between quartiles than the other.
-This animated sankey plot requires the reader to mentally calculate the fraction of points that are moving, separately for the blue and red points, to answer the question whether one group has a higher movement rate.
+This animated Sankey plot requires the reader to mentally calculate the fraction of points that are moving, separately for the blue and red points, to answer the question whether one group has a higher movement rate.
 The task is easier if the two groups have a similar number of points.
@@
 
-  From Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`, there are clearly more US companies de-listed compared to Japanese companies, and it can be seen that there are no Japanese companies in the Top 25% in 2006 that were de-listed.
+  In Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006.
+The grey regions show the proportion of companies in each of the categories in 2006 on the left that were exited the market by 2018.
+(explain the different in proportion and not listed companies).
+In 2006, the companies represented by points, colored by country are in one of the quartiles or "Not listed" category.
+All the companies in the Top 25% were US companies.
+Any Japanese companies in the Top 25% in 2006 did not exited the market (Not listed).
+But actually, there were non Japanese companies in the Top 25% in 2006.
+It is also interesting that the larger proportion of the companies in the Top 25% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.
 
@@
 
-The election survey dataset included in the \pkg{animbook} package focuses on the voter behavior of the 734 individuals who participated in the 2019 survey.
+The election survey dataset included in the \CRANpkg{animbook} package focuses on the voter behavior of the 734 individuals who participated in the 2019 survey.
 The variables in this data are id, year, party, and gender.
@@
 
-Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences.
-The paper outlines the anticipated data format for input into the prep function, covering raw, categorized, and animated formats.
-It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualization design choices.
-The software usage is illustrated with two applications.
-If more time were available, the features allowing a vary in speeds for each observation could enhance the visualization with an additional dimension.
-Additionally, the new animated and static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
+Beginning with inspiration drawn from the New York Times article, this packages provides tools to facilitate the communication of complex data to broader audiences.
+The paper outlies the anticipated data format for input into the prep function, covering raw, categorized, and animated formats.
+It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualizatoin design choices.
+
+The paper further proviedes illustrative examples of software usage through two application to the real world data.
+Given more time, introducing geatures that allow variation in speeds for each observation could enhance the visualization by introducing an additional dimension.
+The new animated adn static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
+Additionally, the potential re-parameterization of the x-axis from years to ages (e.g., company) could add different details to the visualization.
 
@@
 This paper is created using the \CRANpkg{rjtools} packages (@rjtools) and utilized the \CRANpkg{dplyr}, \CRANpkg{knitr}, \CRANpkg{gganimate}, and \CRANpkg{kableExtra} for creating the visual included in this paper.
-This paper is based on the 0.0.0.9 version of the \pkg{animbook} package.
+This paper is based on the 0.0.0.9 version of the \CRANpkg{animbook} package.
 This version is available on [https://github.com/KrisanatA/animbook](https://github.com/KrisanatA/animbook).

### 2024-01-08 animbook-journal.tex
04/01/2023 to do list - data section and example

@@
 Between elections, voters often switch party preferences, which produces categorical values over time.
-Inspired by the animation in the New York Times article ``Extensive data show punishing reach of racism for black boys,'' we provide new visualization functions to generate animations that display this type of data in an R package called \pkg{animbook}.
+Inspired by the animation in the New York Times article ``Extensive data show punishing reach of racism for black boys,'' we provide new visualization functions to generate animations that display this type of data in an R package called \CRANpkg{animbook}.
 Functions to pre-process the data and prepare it for the animation are provided.
@@
 On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins.
-For the animation in this paper, the programming language that will be used for recreating and revising the visualization done by The New York Times articles is R (R Core Team (2021)).
+
+There was an implementation of the New York Times animation in R (R Core Team (2021)) by Hvitfeldt (2018).
+This article demonstrates the path generation for each point and how to map them to the animation.
+Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization by incorporating additional elements, particularly the proportional shaded area, and introduces new visualizations inspired by the New York Times animation.
+
+As mentioned about the proportional shaded area, a similar static visualization of the animation is known as the Sankey plot.
+Sankey plots are flow diagrams that show the movement/change from one state to another, with the width of each arrow representing the proportional changes between states.
+R packages capable of generating a Sankey plot type include \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}, both are extensions from the \CRANpkg{ggplot2} \{Wickham (2016)\}.
+The main difference between the Sankey plot visualization and the animation featured in the New York Times lies in their methods of representing the proportion of changes between states.
+Sankey plots utilize the width of connecting lines, while the New York Times animation employs the density and color of points accompanied by counters.
+Combining the differences between these two features will be shown in the Visualization design section.
 
@@
 
-The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (Wickham (2016)) to include the description of an animation.
+The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package to include the description of an animation.
 It added new grammar classes to the plot object, allowing it to understand how the plot should change over time.
@@
 
-In the animation, the proportional shaded area has been incorporated to facilitate a quick grasp of the proportion information.
-It displays the proportion of observation within each group.
-The design also needs to account for situations where the visualization lacks an adequate number of data points.
-In such cases, it can be challenging to visually discern the movement pattern of the subgroup, requiring the implementation of observation interpolation.
+In the animation, the use of proportional shaded areas serves to enhances the quick comprehension of proportion information, effectively displaying the distribution within each group.
+This method replaces the coutners seen in the New York Times animation, alleviating information overload for users and reducing the computation required.
+To represents sub-groups, the plot utilizes color to distinguish differences among observation.
+
+However, discerning the movement pattern or proportion of sub-groups can be challenging when the visualization lacks a sufficient number of data points.
+Addressing this, observation interpolation is employed by calculating the sub-group proportion and multiplying it by the desired number of generated points.
+This approach ensures a more detailed representation of movement patterns, particularly in scenarios where a limited number of data points may impede visual clarity.
+
+The issue with this type of animation in the New York Times lies in point clustering, particularly when all points start simultaneously.
+This clustering poses a challenge in distinguishing and tracking individual observations.
+In the context of time series data (e.g., year), the observations in the animation enter the visualization at different times.
+It is important to note that this does not necessarily reflect the real-time occurrence of observations.
+The neglect of the time-dependent nature of observations is a deliberate choice made for visualization purposes, aiming enhance the clarity of the presented information.
 
@@
 
-In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation.
+In designing the \CRANpkg{animbook} package, a three-step structured approach was developed to create an animation.
 The initial step is to reformat the data into a categorized data structure, as seen in Figure \ref{fig:data-diagram}.
@@
 
+The names of these plots draws inspiration from a native Australian animals.
+The comprehensive plot is named Kangaroo, while its subset is referred to as Wallaby, representing a smaller version of the Kangaroo.
+The final plot is names after Funnel Web Spider, drawing parallels between the plot's features and the distinctive legs of the spider.
+
 The main focus of this paper will be on the \texttt{wallaby\_plot()}, which draws inspiration from the New York Times animation and combines the knowledge gained from the previous sections in creating the visualization.
@@
 rendering & The choice of method used to create and display the plot, either gganimate or plotly. Default is gganimate.\\
+\hline
+time\_dependent & Should the observations entered the visualization at the same time. Default is FALSE\\
 \hline
@@
 The variable \texttt{sales} is used as the performance metric.
-Four quantiles are used as specified by the \texttt{ncat} option, and NAs formed a fifth category labeled as ``Not listed''.
+Four quantiles (quartiles) are used as specified by \texttt{ncat\ =\ 4}, and NAs are converted into a fifth category labeled as ``Not listed''.
 \item
@@
 
-From the kangaroo plot (Figure \ref{fig:kan-osiris-figure}) it can be seen that most companies stay in the same quantile group over the time period.
+In the kangaroo plot (Figure \ref{fig:kan-osiris-figure}) the five grey bars indicate the five categories (Top 25\%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018.
+Points represent individual companies with color indicating country of registration.
+Points that stay within the bar indicate companies that remain in the same quartile over the entire time period.
+If a company drop in performance or improve performance to the extent of switching quartile, the corresponding point will jump up or down in this plot.
+Note that all the companies in the ``Not listed'' category were listed at some point during this time period.
+It can be seen that most companies stay in the same quantile group over the time period.
 There are several companies that move up and down, and most of these are US companies.
@@
 
-Perceiving the differences between the movement pattern of groups can be difficult, especially when the groups have different sizes as the case here.
+Perceiving the differences between the movement pattern of groups can be difficult, especially when the groups have different sizes, as is the case here.
 There are more US companies than Japanese companies and particularly there are more US companies in the top 25 percent quantile.
-Thus there will be more blue points (US) moving than red points (JP) purely for this reason.
-Interpreting differences requires the reader to mentally calculated the \textbf{relative proportion} between the blue and red points, which is hard.
+Thus there will likely be more blue points (US) moving than red points (JP) purely for this reason.
+The difference that is of interest is \textbf{relative proportion}, that one country has a higher fraction of companies moving between quartiles than the other.
+This animated Sankey plot requires the reader to mentally calculate the fraction of points that are moving, separately for the blue and red points, to answer the question whether one group has a higher movement rate.
+The task is easier if the two groups have a similar number of points.
 
@@
 
-From Figure \ref{fig:osiris-figure}, there are clearly more US companies de-listed compared to Japanese companies, and it can be seen that there are no Japanese companies in the Top 25\% in 2006 that were de-listed.
+In Figure \ref{fig:osiris-figure}, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006.
+The grey regions show the proportion of companies in each of the categories in 2006 on the left that were exited the market by 2018.
+(explain the different in proportion and not listed companies).
+In 2006, the companies represented by points, colored by country are in one of the quartiles or ``Not listed'' category.
+All the companies in the Top 25\% were US companies.
+Any Japanese companies in the Top 25\% in 2006 did not exited the market (Not listed).
+But actually, there were non Japanese companies in the Top 25\% in 2006.
+It is also interesting that the larger proportion of the companies in the Top 25\% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.
 
@@
 
-Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences.
-The paper outlines the anticipated data format for input into the prep function, covering raw, categorized, and animated formats.
-It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualization design choices.
-The software is explained in detail with examples and real-world applications.
-If more time were available, the features allowing a vary in speeds for each observation could enhance the visualization with an additional dimension.
-Additionally, the new animated and static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
+Beginning with inspiration drawn from the New York Times article, this packages provides tools to facilitate the communication of complex data to broader audiences.
+The paper outlies the anticipated data format for input into the prep function, covering raw, categorized, and animated formats.
+It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualizatoin design choices.
+
+The paper further proviedes illustrative examples of software usage through two application to the real world data.
+Given more time, introducing geatures that allow variation in speeds for each observation could enhance the visualization by introducing an additional dimension.
+The new animated adn static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
+Additionally, the potential re-parameterization of the x-axis from years to ages (e.g., company) could add different details to the visualization.
+
+\begin{itemize}
+\tightlist
+\item
+  positives and negatives about the method
+\item
+  extensions that would be desirable for the software
+\end{itemize}
 
@@
 (2023)) and utilized the \CRANpkg{dplyr}, \CRANpkg{knitr}, \CRANpkg{gganimate}, and \CRANpkg{kableExtra} for creating the visual included in this paper.
-This paper is based on the 0.0.0.9 version of the \pkg{animbook} package.
+This paper is based on the 0.0.0.9 version of the \CRANpkg{animbook} package.
 This version is available on \url{https://github.com/KrisanatA/animbook}.

### 2024-01-08 animbook-journal.R

@@ -149,7 +149,7 @@ knitr::include_graphics("figures/sankey-shade-2.png")
 
 
 ## -----------------------------------------------------------------------------
-argument2 <- c("data", "group_palette", "shade_palette", "rendering",
+argument2 <- c("data", "group_palette", "shade_palette", "rendering", "time_dependent",
                "subset", "relation", "total_point", "height", "width", "size",
                "alpha")
 
@@ -157,6 +157,7 @@ description2 <- c("The categorized data returned from the prep function.",
                   "The vector of the palette used by the function to supply the color to each group.",
                   "The vector of the palette used by the function to supply the color to the shaded area.",
                   "The choice of method used to create and display the plot, either gganimate or plotly. Default is gganimate.",
+                  "Should the observations entered the visualization at the same time. Default is FALSE",
                   "A character string specifying the variable used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument. Default is \"top\".",
                   "The choice of relationship for the values to display on the plot, either \"one_many.\" or \"many_one\". Default is \"one_many\".",
                   "The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.",

### 2024-01-11 animbook-journal.Rmd
09/01/2024 To do list with NAs handling

@@
 
-  There was an implementation of the New York Times animation in R (@r) by @Hvitfeldt_2018.
-This article demonstrates the path generation for each point and how to map them to the animation.
-Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization by incorporating additional elements, particularly the proportional shaded area, and introduces new visualizations inspired by the New York Times animation.
+  @Hvitfeldt_2018 provides R (@r) code to generate an animation similar to that of the New York Times.
+Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be use for a variety of similar animations for studying flow and temporal change data.
 
-  As mentioned about the proportional shaded area, a similar static visualization of the animation is known as the Sankey plot.
-Sankey plots are flow diagrams that show the movement/change from one state to another, with the width of each arrow representing the proportional changes between states.
-R packages capable of generating a Sankey plot type include  \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}, both are extensions from the \CRANpkg{ggplot2} {@ggplot2}.
-The main difference between the Sankey plot visualization and the animation featured in the New York Times lies in their methods of representing the proportion of changes between states.
-Sankey plots utilize the width of connecting lines, while the New York Times animation employs the density and color of points accompanied by counters.
-Combining the differences between these two features will be shown in the Visualization design section.
+  The New York Times visualization is also similar to what is called a Sankey plot.
+Sankey plots are flow diagrams that show the movement/change from one category levels to another, with the width of each arrow representing the proportional changes between levels.
+There are several R packages available to generate version of Sankey plots including \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}.
+The main difference between the Sankey plot visualization and the animation featured in the New York Times lies in their methods of representing the proportion of changes.
+Sankey plots utilize the width of connecting lines, while the New York Times animation employs the density and color of points.
 
@@
 The last form is animated data, where the frame is assigned to each unique ID.
+
+  One of the frequently encountered values in the dataset is NA, commonly known as missing values.
+In the context of accounting data, NA might signify that a company is either not yet listed or has been de-listed.
+In scenarios like voter data, NA may indicate that individuals did not provide the necessary information.
+Disregarding NA values could result in the loss of valuable information.
+Therefore, instead of completely removing NA entries, this information is categorized into its quantiles, ensuring that the missing data are factored into the visualization.
 
@@
 
-  In the animation, the use of proportional shaded areas serves to enhances the quick comprehension of proportion information, effectively displaying the distribution within each group.
-This method replaces the coutners seen in the New York Times animation, alleviating information overload for users and reducing the computation required.
-To represents sub-groups, the plot utilizes color to distinguish differences among observation.
+  In the animation, the use of proportional shaded areas serves to enhances the comprehension of proportion information, effectively displaying the distribution within each group.
+To represent sub-groups, points are colored to focus attention on differences between groups of observation.
 
-  However, discerning the movement pattern or proportion of sub-groups can be challenging when the visualization lacks a sufficient number of data points.
-Addressing this, observation interpolation is employed by calculating the sub-group proportion and multiplying it by the desired number of generated points.
-This approach ensures a more detailed representation of movement patterns, particularly in scenarios where a limited number of data points may impede visual clarity.
+  Discerning the movement pattern or proportion of sub-groups can be challenging when there is only a small number of points.
+To address this, sample size are inflated by calculating the sub-group proportion and multiplying it by the desired total number of points.
+This approach ensures a richer representation of movement patterns.
 
-  The issue with this type of animation in the New York Times lies in point clustering, particularly when all points start simultaneously.
-This clustering poses a challenge in distinguishing and tracking individual observations.
-In the context of time series data (e.g., year), the observations in the animation enter the visualization at different times.
+ Another issue is that all observations have a common starting time.
+This would mean all points start the animation simultaneously and move as a block through time.
+This poses a challenge in distinguishing and tracking individual observations and their change patterns.
+To alleviate this, the animation randomly starts observations at different times so a continuous flow of points is shown.
 It is important to note that this does not necessarily reflect the real-time occurrence of observations.
-The neglect of the time-dependent nature of observations is a deliberate choice made for visualization purposes, aiming enhance the clarity of the presented information.
 
-  The paths of observations need to be interpolated to create small changes in the position of points to produce the appearance of motion, as mentioned in the Animation tools section.
-These interpolate functions in \CRANpkg{gganimate} and \CRANpkg{plotly} only generate a linear path between points.
-However, linear paths are visually less appealing than non-linear paths.
+  The paths of observations are also interpolated to create small changes in the position of points to produce the appearance of motion.
+The interpolation functions in \CRANpkg{gganimate} and \CRANpkg{plotly} are inadequate because they only generate a linear path.
+Our animation needs non-linear path to show the flow.
 Sigmoid curves are commonly used in Sankey diagrams (@Hvitfeldt_2018).
 However, @Shaffer_2019 argues that a sine curve more accurately represents proportion throughout the path.
-This is illustrated in Figure \@ref(fig:proportional-shade).
+As illustrated in Figure \@ref(fig:proportional-shade).
 The sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.
+New interpolation functions are needed to compute both the sigmoid and sine path.
 
@@
 
-# Summary
+# Discussion
 
 Beginning with inspiration drawn from the New York Times article, this packages provides tools to facilitate the communication of complex data to broader audiences.
-The paper outlies the anticipated data format for input into the prep function, covering raw, categorized, and animated formats.
-It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualizatoin design choices.
+The paper outlines the anticipated data format for input into the prep function, covering raw, categorized, and animated data formats.
+It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualization design choices.
 
-The paper further proviedes illustrative examples of software usage through two application to the real world data.
-Given more time, introducing geatures that allow variation in speeds for each observation could enhance the visualization by introducing an additional dimension.
-The new animated adn static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
-Additionally, the potential re-parameterization of the x-axis from years to ages (e.g., company) could add different details to the visualization.
+  The \CRANpkg{animbook} package comes with certain drawbacks.
+Firstly, it leans more towards being a communication tool rather than an exploratory one, as the information it presents can often be obtained from a summary table.
+Secondly, it may struggle to handle datasets with numerous categories (quantiles), limiting its applicability in such scenarios.
+Furthermore, perceiving patterns from the animation might be challenging for users when there are differences in sample sizes across groups.
+Lastly, the animation requires the reader to mentally calculate the fraction of points that are in motion.
+However, the package provides tools that provides a simple solution for creating meaningful animations through a simple step process.
 
-- positives and negatives about the method
-- extensions that would be desirable for the software
+  Introducing features that allow variation in speeds for each observation could enhance the visualization by introducing an additonal dimension.
+The new animated and static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
+Additionally, the potential re-parameterization of the x-axis from years to ages (e.g., company ages) could add different ways of viewing the visualization.
+
+- the first paragraph is to summarize the achievement of this
+- the second paragraph is about the pro and con, what works, what doesn't works.
+- the third paragraph, if you have another 6 months, what would you implemented.
 

### 2024-01-11 animbook-journal.tex
09/01/2024 To do list with NAs handling

@@
 
-There was an implementation of the New York Times animation in R (R Core Team (2021)) by Hvitfeldt (2018).
-This article demonstrates the path generation for each point and how to map them to the animation.
-Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization by incorporating additional elements, particularly the proportional shaded area, and introduces new visualizations inspired by the New York Times animation.
+Hvitfeldt (2018) provides R (R Core Team (2021)) code to generate an animation similar to that of the New York Times.
+Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be use for a variety of similar animations for studying flow and temporal change data.
 
-As mentioned about the proportional shaded area, a similar static visualization of the animation is known as the Sankey plot.
-Sankey plots are flow diagrams that show the movement/change from one state to another, with the width of each arrow representing the proportional changes between states.
-R packages capable of generating a Sankey plot type include \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}, both are extensions from the \CRANpkg{ggplot2} \{Wickham (2016)\}.
-The main difference between the Sankey plot visualization and the animation featured in the New York Times lies in their methods of representing the proportion of changes between states.
-Sankey plots utilize the width of connecting lines, while the New York Times animation employs the density and color of points accompanied by counters.
-Combining the differences between these two features will be shown in the Visualization design section.
+The New York Times visualization is also similar to what is called a Sankey plot.
+Sankey plots are flow diagrams that show the movement/change from one category levels to another, with the width of each arrow representing the proportional changes between levels.
+There are several R packages available to generate version of Sankey plots including \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}.
+The main difference between the Sankey plot visualization and the animation featured in the New York Times lies in their methods of representing the proportion of changes.
+Sankey plots utilize the width of connecting lines, while the New York Times animation employs the density and color of points.
 
@@
 The last form is animated data, where the frame is assigned to each unique ID.
+
+One of the frequently encountered values in the dataset is NA, commonly known as missing values.
+In the context of accounting data, NA might signify that a company is either not yet listed or has been de-listed.
+In scenarios like voter data, NA may indicate that individuals did not provide the necessary information.
+Disregarding NA values could result in the loss of valuable information.
+Therefore, instead of completely removing NA entries, this information is categorized into its quantiles, ensuring that the missing data are factored into the visualization.
 
@@
 
-In the animation, the use of proportional shaded areas serves to enhances the quick comprehension of proportion information, effectively displaying the distribution within each group.
-This method replaces the coutners seen in the New York Times animation, alleviating information overload for users and reducing the computation required.
-To represents sub-groups, the plot utilizes color to distinguish differences among observation.
+In the animation, the use of proportional shaded areas serves to enhances the comprehension of proportion information, effectively displaying the distribution within each group.
+To represent sub-groups, points are colored to focus attention on differences between groups of observation.
 
-However, discerning the movement pattern or proportion of sub-groups can be challenging when the visualization lacks a sufficient number of data points.
-Addressing this, observation interpolation is employed by calculating the sub-group proportion and multiplying it by the desired number of generated points.
-This approach ensures a more detailed representation of movement patterns, particularly in scenarios where a limited number of data points may impede visual clarity.
+Discerning the movement pattern or proportion of sub-groups can be challenging when there is only a small number of points.
+To address this, sample size are inflated by calculating the sub-group proportion and multiplying it by the desired total number of points.
+This approach ensures a richer representation of movement patterns.
 
-The issue with this type of animation in the New York Times lies in point clustering, particularly when all points start simultaneously.
-This clustering poses a challenge in distinguishing and tracking individual observations.
-In the context of time series data (e.g., year), the observations in the animation enter the visualization at different times.
+Another issue is that all observations have a common starting time.
+This would mean all points start the animation simultaneously and move as a block through time.
+This poses a challenge in distinguishing and tracking individual observations and their change patterns.
+To alleviate this, the animation randomly starts observations at different times so a continuous flow of points is shown.
 It is important to note that this does not necessarily reflect the real-time occurrence of observations.
-The neglect of the time-dependent nature of observations is a deliberate choice made for visualization purposes, aiming enhance the clarity of the presented information.
 
-The paths of observations need to be interpolated to create small changes in the position of points to produce the appearance of motion, as mentioned in the Animation tools section.
-These interpolate functions in \CRANpkg{gganimate} and \CRANpkg{plotly} only generate a linear path between points.
-However, linear paths are visually less appealing than non-linear paths.
+The paths of observations are also interpolated to create small changes in the position of points to produce the appearance of motion.
+The interpolation functions in \CRANpkg{gganimate} and \CRANpkg{plotly} are inadequate because they only generate a linear path.
+Our animation needs non-linear path to show the flow.
 Sigmoid curves are commonly used in Sankey diagrams (Hvitfeldt (2018)).
 However, Shaffer (2019) argues that a sine curve more accurately represents proportion throughout the path.
-This is illustrated in Figure \ref{fig:proportional-shade}.
+As illustrated in Figure \ref{fig:proportional-shade}.
 The sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.
+New interpolation functions are needed to compute both the sigmoid and sine path.
 
@@
 
-\hypertarget{summary}{%
-\section{Summary}\label{summary}}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
 Beginning with inspiration drawn from the New York Times article, this packages provides tools to facilitate the communication of complex data to broader audiences.
-The paper outlies the anticipated data format for input into the prep function, covering raw, categorized, and animated formats.
-It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualizatoin design choices.
+The paper outlines the anticipated data format for input into the prep function, covering raw, categorized, and animated data formats.
+It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualization design choices.
 
-The paper further proviedes illustrative examples of software usage through two application to the real world data.
-Given more time, introducing geatures that allow variation in speeds for each observation could enhance the visualization by introducing an additional dimension.
-The new animated adn static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
-Additionally, the potential re-parameterization of the x-axis from years to ages (e.g., company) could add different details to the visualization.
+The \CRANpkg{animbook} package comes with certain drawbacks.
+Firstly, it leans more towards being a communication tool rather than an exploratory one, as the information it presents can often be obtained from a summary table.
+Secondly, it may struggle to handle datasets with numerous categories (quantiles), limiting its applicability in such scenarios.
+Furthermore, perceiving patterns from the animation might be challenging for users when there are differences in sample sizes across groups.
+Lastly, the animation requires the reader to mentally calculate the fraction of points that are in motion.
+However, the package provides tools that provides a simple solution for creating meaningful animations through a simple step process.
+
+Introducing features that allow variation in speeds for each observation could enhance the visualization by introducing an additonal dimension.
+The new animated and static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
+Additionally, the potential re-parameterization of the x-axis from years to ages (e.g., company ages) could add different ways of viewing the visualization.
 
@@
 \item
-  positives and negatives about the method
+  the first paragraph is to summarize the achievement of this
 \item
-  extensions that would be desirable for the software
+  the second paragraph is about the pro and con, what works, what doesn't works.
+\item
+  the third paragraph, if you have another 6 months, what would you implemented.
 \end{itemize}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
----------. 2016. \emph{Ggplot2: Elegant Graphics for Data Analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-dplyr}{}}%

### 2024-01-12 animbook-journal.Rmd
more examples

@@
              group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-             shade_palette = c("#737373", "#969696", "#BDBDBD",
-                               "#D9D9D9","#D9D9D9","#D9D9D9"),
              rendering = "gganimate",
@@
 p
+```
+
+  Additionally, users have the flexibility to explore various options, such as subset or relation, allowing them to customize how the plot will appear.
+
+```{r}
+p_2 <- wallaby_plot(data = animbook,
+                   rendering = "gganimate",
+                   subset = "top",
+                   relation = "many_one",
+                   total_point = NULL)
+
+p_2
+
+p_3 <- wallaby_plot(data = animbook,
+                    rendering = "gganimate",
+                    subset = "B",
+                    relation = "many_one",
+                    total_point = NULL)
+
+p_3
 ```

### 2024-01-12 animbook-journal.tex
more examples

@@
 \begin{center}\includegraphics[width=1\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-10-1} \end{center}
+
+Additionally, users have the flexibility to explore various options, such as subset or relation, allowing them to customize how the plot will appear.
+
+\includegraphics{animbook-journal_files/figure-latex/unnamed-chunk-11-1.pdf} \includegraphics{animbook-journal_files/figure-latex/unnamed-chunk-11-2.pdf}
 

### 2024-01-12 animbook-journal.R

@@ -195,14 +195,31 @@ str(animbook)
 ## ----echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
 p <- wallaby_plot(data = animbook,
              group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-             shade_palette = c("#737373", "#969696", "#BDBDBD",
-                               "#D9D9D9","#D9D9D9","#D9D9D9"),
              rendering = "gganimate",
              subset = "top",
              relation = "one_many",
              total_point = NULL)
 
 p
+
+
+## -----------------------------------------------------------------------------
+p_2 <- wallaby_plot(data = animbook,
+                   rendering = "gganimate",
+                   subset = "top",
+                   relation = "many_one",
+                   total_point = NULL)
+
+p_2
+
+
+p_3 <- wallaby_plot(data = animbook,
+                    rendering = "gganimate",
+                    subset = "B",
+                    relation = "many_one",
+                    total_point = NULL)
+
+p_3
 
 
 ## ----eval=FALSE---------------------------------------------------------------

### 2024-01-18 animbook-journal.Rmd
polishing conclusions and usage example

--- 2024-01-11 animbook-journal.Rmd
@@
 
-In this section, the package usage will be demonstrated using the `cat_change` dataset included in this package.
-This dataset is simulated data that has changed from category A to E between two time points.
-Since this data is already in the categorized data structure, the `anim_prep_cat()` function is utilized.
-The output produced from this package is referred to as the `categorized` data.
+The `cat_change` data in the package is used to illustrate how to use this package.
+It has five categories, A to E, over two time points.
+Since the data is already in the categorized data structure, the `anim_prep_cat()` function is used.
+The output from this function is a class called `categorized`.
 
 ```{r, echo=TRUE}
-animbook <- anim_prep_cat(cat_change, 
+a <- anim_prep_cat(cat_change, 
                           id = id, 
@@
                           group = gp)
-
-head(animbook, 10)
-str(animbook)
+class(a)
+glimpse(a)
 ```
 
-  To obtain a `ggplot` object for the animation function, the `wallaby_plot` is used.
-For further customization, the `shade_palette`, `subset`, and `relation` arguments are applied to define the final appearance of the animation.
+  To obtain an object for the animation function, the `wallaby_plot` is used.
+The `shade_palette`, `subset`, and `relation` arguments are applied to refine the final appearance of the animation.
+REFER TO FIGURE
 
-```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
-p <- wallaby_plot(data = animbook,
+```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="FIXME"}
+p <- wallaby_plot(data = a,
              group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-             shade_palette = c("#737373", "#969696", "#BDBDBD",
-                               "#D9D9D9","#D9D9D9","#D9D9D9"),
              rendering = "gganimate",
@@
 
-  Once the `ggplot` object is obtained, the `anim_animate()` function can be used to transform it into a `gganimate` object.
-This then can be passed onto the `animate()` function from the \CRANpkg{gganimate} for rendering.
+  Users have the flexibility to use various options, such as `subset` or `relation`, to customize the plot appearance.
+Here "top" is used to to specify category A for the final time point, and "many_one" is used to specify that all categories flowing into A at time point 2 are shown.
+REFER TO FIGURE
+
+```{r fig.cap="FIXME"}
+p_2 <- wallaby_plot(data = a,
+                   rendering = "gganimate",
+                   subset = "top",
+                   relation = "many_one",
+                   total_point = NULL)
+
+p_2
+```
+
+Using `subset = "B"` will only show the point for a single category. REFER TO FIGURE
+
+```{r fig.cap="FIXME"}
+p_3 <- wallaby_plot(data = a,
+                    rendering = "gganimate",
+                    subset = "B",
+                    relation = "many_one",
+                    total_point = NULL)
+
+p_3
+```
+
+  This plot object is passed to the `anim_animate()` function to transform it into a `gganimate` object, which appears as an animation when the `animate()` function from \CRANpkg{gganimate} is used for rendering.
+REFER TO PLOT
 
@@
 ```
-
-  This is an example of how the users can apply the three-step process in creating an animation plot using the `animbook` package.
 
@@
 
-Beginning with inspiration drawn from the New York Times article, this packages provides tools to facilitate the communication of complex data to broader audiences.
-The paper outlines the anticipated data format for input into the prep function, covering raw, categorized, and animated data formats.
-It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualization design choices.
+Beginning with inspiration drawn from the New York Times article, this package provides tools to generate animations for temporal flow data to study changes in groups over time.
+The paper describes how to pre-process the data into a format for making several types of plots and animation.
+It also explains what needs to be considered when making an animation such as persistence of objects, how to achieve this using interpolation, and the visualization design choices automated and those available to users.
 
-  The \CRANpkg{animbook} package comes with certain drawbacks.
-Firstly, it leans more towards being a communication tool rather than an exploratory one, as the information it presents can often be obtained from a summary table.
-Secondly, it may struggle to handle datasets with numerous categories (quantiles), limiting its applicability in such scenarios.
-Furthermore, perceiving patterns from the animation might be challenging for users when there are differences in sample sizes across groups.
-Lastly, the animation requires the reader to mentally calculate the fraction of points that are in motion.
-However, the package provides tools that provides a simple solution for creating meaningful animations through a simple step process.
+  The package provides the tools to create animations for simple temporal patterns, with a few steps, but these visualization methods have some limitations.
+It is primarily for communication rather than exploration because one typically knows what the main patterns are.
+If there are many categories (quantiles) the display will be too crowded.
+Because the animation involves perceiving patterns in groups of moving points it can be challenging with unbalanced sample sizes.
+This requires the reader to mentally calculate the fraction of points that are in motion.
 
-  Introducing features that allow variation in speeds for each observation could enhance the visualization by introducing an additonal dimension.
-The new animated and static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
-Additionally, the potential re-parameterization of the x-axis from years to ages (e.g., company ages) could add different ways of viewing the visualization.
-
-- the first paragraph is to summarize the achievement of this
-- the second paragraph is about the pro and con, what works, what doesn't works.
-- the third paragraph, if you have another 6 months, what would you implemented.
+  There are some potential new directions to develop this work.
+Some applications might benefit by re-parameterization of the x-axis from years to ages (e.g.
+company ages, time since the company was founded).
+One could also re-arrange the mapping of variables to the plot and animations.
+For example, the New York Times article, mentioned that to better compare distributions in time, one could plot the quantiles, which would form something like an S-curve, and animate over time, to observe how the distributions are changing.
 

### 2024-01-22 animbook-journal.Rmd
fix example usage section

@@
 
-### Data preprocessing
+### Data pre-processing
 
@@
 To obtain an object for the animation function, the `wallaby_plot` is used.
-The `shade_palette`, `subset`, and `relation` arguments are applied to refine the final appearance of the animation.
-REFER TO FIGURE
+The `subset` and `relation` arguments are applied to refine the final appearance of the animation, Figure \@ref(fig:top-one).
 
-```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="FIXME"}
+```{r top-one, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points transferred from the left category A to the right category A and E before being animated."}
 p <- wallaby_plot(data = a,
@@
 
-  Users have the flexibility to use various options, such as `subset` or `relation`, to customize the plot appearance.
-Here "top" is used to to specify category A for the final time point, and "many_one" is used to specify that all categories flowing into A at time point 2 are shown.
-REFER TO FIGURE
+Figure \@ref(fig:top-many), show the flexibility to use various options, such as `subset` or `relation`, to customize the plot appearance.
+Here `subset = "top"` is used to specify category A for the final time point, and `relation = "many_one"` is used to specify that all categories flowing into A at time point 2 are shown.
 
-```{r fig.cap="FIXME"}
+```{r top-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points transferred from the right category A and E to the left category A before being animated.
+This is called a many-to-one relationship."}
 p_2 <- wallaby_plot(data = a,
@@
 
-Using `subset = "B"` will only show the point for a single category. REFER TO FIGURE
+Using `subset = "B"` will only show the point for a single category as shown in the Figure \@ref(fig:b-many).
 
-```{r fig.cap="FIXME"}
+```{r b-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points that got transferred to category B on the right are only from category B.
+The plot shown is the plot before it is being animated."}
 p_3 <- wallaby_plot(data = a,
@@
 This plot object is passed to the `anim_animate()` function to transform it into a `gganimate` object, which appears as an animation when the `animate()` function from \CRANpkg{gganimate} is used for rendering.
-REFER TO PLOT
+This can be seen in Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:catchange-figure}','\\@ref(fig:catchange-gif)'))`
 

### 2024-01-22 animbook-journal.tex
fix example usage section

--- 2024-01-11 animbook-journal.tex
@@
 
-\hypertarget{data-preprocessing}{%
-\subsubsection{Data preprocessing}\label{data-preprocessing}}
+\hypertarget{data-pre-processing}{%
+\subsubsection{Data pre-processing}\label{data-pre-processing}}
 
@@
 
-In this section, the package usage will be demonstrated using the \texttt{cat\_change} dataset included in this package.
-This dataset is simulated data that has changed from category A to E between two time points.
-Since this data is already in the categorized data structure, the \texttt{anim\_prep\_cat()} function is utilized.
-The output produced from this package is referred to as the \texttt{categorized} data.
+The \texttt{cat\_change} data in the package is used to illustrate how to use this package.
+It has five categories, A to E, over two time points.
+Since the data is already in the categorized data structure, the \texttt{anim\_prep\_cat()} function is used.
+The output from this function is a class called \texttt{categorized}.
 
 \begin{verbatim}
-animbook <- anim_prep_cat(cat_change, 
+a <- anim_prep_cat(cat_change, 
                    id = id, 
@@
                    group = gp)
-
-head(animbook, 10)
+class(a)
 \end{verbatim}
@@
 \begin{verbatim}
-#> # A tibble: 10 x 5
-#>    id     time qtile label group
-#>    <fct> <int> <dbl> <chr> <fct>
-#>  1 1      2020     5 A     X    
-#>  2 2      2020     5 A     X    
-#>  3 3      2020     5 A     X    
-#>  4 4      2020     5 A     X    
-#>  5 5      2020     5 A     X    
-#>  6 6      2020     5 A     X    
-#>  7 7      2020     5 A     X    
-#>  8 8      2020     5 A     X    
-#>  9 9      2020     5 A     X    
-#> 10 10     2020     5 A     X
+#> [1] "tbl_df"      "tbl"         "data.frame"  "categorized"
 \end{verbatim}
@@
 \begin{verbatim}
-str(animbook)
+glimpse(a)
 \end{verbatim}
@@
 \begin{verbatim}
-#> tibble[,5] (S3: tbl_df/tbl/data.frame/categorized)
-#>  $ id   : Factor w/ 200 levels "1","2","3","4",..: 1 2 3 4 5 6 7 8 9 10 ...
-#>  $ time : int [1:400] 2020 2020 2020 2020 2020 2020 2020 2020 2020 2020 ...
-#>  $ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
-#>  $ label: chr [1:400] "A" "A" "A" "A" ...
-#>  $ group: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
+#> Rows: 400
+#> Columns: 5
+#> $ id    <fct> 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 1~
+#> $ time  <int> 2020, 2020, 2020, 2020, 2020, 2020, 2020, 2020, 2020, 2020, 2020~
+#> $ qtile <dbl> 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5~
+#> $ label <chr> "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",~
+#> $ group <fct> X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, Y, Y~
 \end{verbatim}
 
-To obtain a \texttt{ggplot} object for the animation function, the \texttt{wallaby\_plot} is used.
-For further customization, the \texttt{shade\_palette}, \texttt{subset}, and \texttt{relation} arguments are applied to define the final appearance of the animation.
+To obtain an object for the animation function, the \texttt{wallaby\_plot} is used.
+The \texttt{subset} and \texttt{relation} arguments are applied to refine the final appearance of the animation, Figure \ref{fig:top-one}.
 
 \begin{verbatim}
-p <- wallaby_plot(data = animbook,
+p <- wallaby_plot(data = a,
                   group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-             shade_palette = c("#737373", "#969696", "#BDBDBD",
-                               "#D9D9D9","#D9D9D9","#D9D9D9"),
                   rendering = "gganimate",
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{animbook-journal_files/figure-latex/unnamed-chunk-10-1} \end{center}
+\begin{figure}
 
-Once the \texttt{ggplot} object is obtained, the \texttt{anim\_animate()} function can be used to transform it into a \texttt{gganimate} object.
-This then can be passed onto the \texttt{animate()} function from the \CRANpkg{gganimate} for rendering.
+{\centering \includegraphics[width=1\linewidth]{animbook-journal_files/figure-latex/top-one-1}
+
+}
+
+\caption{The static plot shows the points transferred from the left category A to the right category A and E before being animated.}\label{fig:top-one}
+\end{figure}
+
+Figure \ref{fig:top-many}, show the flexibility to use various options, such as \texttt{subset} or \texttt{relation}, to customize the plot appearance.
+Here \texttt{subset\ =\ "top"} is used to specify category A for the final time point, and \texttt{relation\ =\ "many\_one"} is used to specify that all categories flowing into A at time point 2 are shown.
+
+\begin{verbatim}
+p_2 <- wallaby_plot(data = a,
+                    rendering = "gganimate",
+                    subset = "top",
+                    relation = "many_one",
+                    total_point = NULL)
+
+p_2
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{animbook-journal_files/figure-latex/top-many-1}
+
+}
+
+\caption{The static plot shows the points transferred from the right category A and E to the left category A before being animated. This is called a many-to-one relationship.}\label{fig:top-many}
+\end{figure}
+
+Using \texttt{subset\ =\ "B"} will only show the point for a single category as shown in the Figure \ref{fig:b-many}.
+
+\begin{verbatim}
+p_3 <- wallaby_plot(data = a,
+                    rendering = "gganimate",
+                    subset = "B",
+                    relation = "many_one",
+                    total_point = NULL)
+
+p_3
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{animbook-journal_files/figure-latex/b-many-1}
+
+}
+
+\caption{The static plot shows the points that got transferred to category B on the right are only from category B. The plot shown is the plot before it is being animated.}\label{fig:b-many}
+\end{figure}
+
+This plot object is passed to the \texttt{anim\_animate()} function to transform it into a \texttt{gganimate} object, which appears as an animation when the \texttt{animate()} function from \CRANpkg{gganimate} is used for rendering.
+This can be seen in Figure \ref{fig:catchange-figure}
 
@@
 \end{figure}
-
-This is an example of how the users can apply the three-step process in creating an animation plot using the \texttt{animbook} package.
 
@@
 
-Beginning with inspiration drawn from the New York Times article, this packages provides tools to facilitate the communication of complex data to broader audiences.
-The paper outlines the anticipated data format for input into the prep function, covering raw, categorized, and animated data formats.
-It delves into the animation concept, persistence of vision, achieved through point interpolation, and the visualization design choices.
+Beginning with inspiration drawn from the New York Times article, this package provides tools to generate animations for temporal flow data to study changes in groups over time.
+The paper describes how to pre-process the data into a format for making several types of plots and animation.
+It also explains what needs to be considered when making an animation such as persistence of objects, how to achieve this using interpolation, and the visualization design choices automated and those available to users.
 
-The \CRANpkg{animbook} package comes with certain drawbacks.
-Firstly, it leans more towards being a communication tool rather than an exploratory one, as the information it presents can often be obtained from a summary table.
-Secondly, it may struggle to handle datasets with numerous categories (quantiles), limiting its applicability in such scenarios.
-Furthermore, perceiving patterns from the animation might be challenging for users when there are differences in sample sizes across groups.
-Lastly, the animation requires the reader to mentally calculate the fraction of points that are in motion.
-However, the package provides tools that provides a simple solution for creating meaningful animations through a simple step process.
+The package provides the tools to create animations for simple temporal patterns, with a few steps, but these visualization methods have some limitations.
+It is primarily for communication rather than exploration because one typically knows what the main patterns are.
+If there are many categories (quantiles) the display will be too crowded.
+Because the animation involves perceiving patterns in groups of moving points it can be challenging with unbalanced sample sizes.
+This requires the reader to mentally calculate the fraction of points that are in motion.
 
-Introducing features that allow variation in speeds for each observation could enhance the visualization by introducing an additonal dimension.
-The new animated and static plots, as demonstrated in the New York Times article, would enable comparisons of demographics at specific points in time.
-Additionally, the potential re-parameterization of the x-axis from years to ages (e.g., company ages) could add different ways of viewing the visualization.
-
-\begin{itemize}
-\tightlist
-\item
-  the first paragraph is to summarize the achievement of this
-\item
-  the second paragraph is about the pro and con, what works, what doesn't works.
-\item
-  the third paragraph, if you have another 6 months, what would you implemented.
-\end{itemize}
+There are some potential new directions to develop this work.
+Some applications might benefit by re-parameterization of the x-axis from years to ages (e.g.~company ages, time since the company was founded).
+One could also re-arrange the mapping of variables to the plot and animations.
+For example, the New York Times article, mentioned that to better compare distributions in time, one could plot the quantiles, which would form something like an S-curve, and animate over time, to observe how the distributions are changing.
 

### 2024-01-22 animbook-journal.R

@@ -182,38 +182,38 @@ argument_table2 |>
 
 
 ## ----echo=TRUE----------------------------------------------------------------
-animbook <- anim_prep_cat(cat_change, 
-                          id = id, 
-                          values = qnt, 
-                          time = time, 
-                          group = gp)
+a <- anim_prep_cat(cat_change, 
+                   id = id, 
+                   values = qnt, 
+                   time = time, 
+                   group = gp)
+class(a)
+glimpse(a)
 
-head(animbook, 10)
-str(animbook)
 
-
-## ----echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
-p <- wallaby_plot(data = animbook,
-             group_palette = RColorBrewer::brewer.pal(9, "Set1"),
-             rendering = "gganimate",
-             subset = "top",
-             relation = "one_many",
-             total_point = NULL)
+## ----top-one, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points transferred from the left category A to the right category A and E before being animated."----
+p <- wallaby_plot(data = a,
+                  group_palette = RColorBrewer::brewer.pal(9, "Set1"),
+                  rendering = "gganimate",
+                  subset = "top",
+                  relation = "one_many",
+                  total_point = NULL)
 
 p
 
 
-## -----------------------------------------------------------------------------
-p_2 <- wallaby_plot(data = animbook,
-                   rendering = "gganimate",
-                   subset = "top",
-                   relation = "many_one",
-                   total_point = NULL)
+## ----top-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points transferred from the right category A and E to the left category A before being animated. This is called a many-to-one relationship."----
+p_2 <- wallaby_plot(data = a,
+                    rendering = "gganimate",
+                    subset = "top",
+                    relation = "many_one",
+                    total_point = NULL)
 
 p_2
 
 
-p_3 <- wallaby_plot(data = animbook,
+## ----b-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points that got transferred to category B on the right are only from category B. The plot shown is the plot before it is being animated."----
+p_3 <- wallaby_plot(data = a,
                     rendering = "gganimate",
                     subset = "B",
                     relation = "many_one",

### 2024-01-29 animbook-journal.Rmd
figure caption

@@
 
+  The `time_dependent` argument provides the user flexibility to choose whether points will start simultaneously (`time_dependent = TRUE`) or randomly (`time_dependent = FALSE`).
+The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points.
+Allowing for the random starting time makes the point tracking simpler.
+The starting times for the points are generated using the `runif()` function, where the `max` argument can be adjusted using the `width` parameter in the plotting function.
+
 ### Plotting function
@@
 
-```{r top-one, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points transferred from the left category A to the right category A and E before being animated."}
+```{r top-one, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the transition of points from the left category A to the right categories A and E.
+This is also referred to as a one-to-many relationship plot.
+The points shown in this plot only originated in category A.
+It emphasizes that these points only stay within the same category A or change to category E."}
 p <- wallaby_plot(data = a,
@@
 
-```{r top-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points transferred from the right category A and E to the left category A before being animated.
-This is called a many-to-one relationship."}
+```{r top-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the movement of points from categories A and E on the right to category A on the left, representing a many-to-one relationship.
+This specifically highlights the points that have moved to category A, which are the points that originate from categories A and E."}
 p_2 <- wallaby_plot(data = a,
@@
 
-```{r b-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points that got transferred to category B on the right are only from category B.
-The plot shown is the plot before it is being animated."}
+```{r b-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the transfer of points from the right category B to the left category B.
+It underscores that the points ultimately landing in category B originate specifically from category B itself."}
 p_3 <- wallaby_plot(data = a,

### 2024-01-29 animbook-journal.tex
figure caption

@@
 
+The \texttt{time\_dependent} argument provides the user flexibility to choose whether points will start simultaneously (\texttt{time\_dependent\ =\ TRUE}) or randomly (\texttt{time\_dependent\ =\ FALSE}).
+The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points.
+Allowing for the random starting time makes the point tracking simpler.
+The starting times for the points are generated using the \texttt{runif()} function, where the \texttt{max} argument can be adjusted using the \texttt{width} parameter in the plotting function.
+
 \hypertarget{plotting-function}{%
@@
 
-\caption{The static plot shows the points transferred from the left category A to the right category A and E before being animated.}\label{fig:top-one}
+\caption{The static plot shows the transition of points from the left category A to the right categories A and E.
+This is also referred to as a one-to-many relationship plot.
+The points shown in this plot only originated in category A.
+It emphasizes that these points only stay within the same category A or change to category E.}\label{fig:top-one}
 \end{figure}
@@
 
-\caption{The static plot shows the points transferred from the right category A and E to the left category A before being animated. This is called a many-to-one relationship.}\label{fig:top-many}
+\caption{The static plot shows the movement of points from categories A and E on the right to category A on the left, representing a many-to-one relationship.
+This specifically highlights the points that have moved to category A, which are the points that originate from categories A and E.}\label{fig:top-many}
 \end{figure}
@@
 
-\caption{The static plot shows the points that got transferred to category B on the right are only from category B. The plot shown is the plot before it is being animated.}\label{fig:b-many}
+\caption{The static plot shows the transfer of points from the right category B to the left category B.
+It underscores that the points ultimately landing in category B originate specifically from category B itself.}\label{fig:b-many}
 \end{figure}

### 2024-01-29 animbook-journal.R

@@ -191,7 +191,7 @@ class(a)
 glimpse(a)
 
 
-## ----top-one, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points transferred from the left category A to the right category A and E before being animated."----
+## ----top-one, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the transition of points from the left category A to the right categories A and E. This is also referred to as a one-to-many relationship plot. The points shown in this plot only originated in category A. It emphasizes that these points only stay within the same category A or change to category E."----
 p <- wallaby_plot(data = a,
                   group_palette = RColorBrewer::brewer.pal(9, "Set1"),
                   rendering = "gganimate",
@@ -202,7 +202,7 @@ p <- wallaby_plot(data = a,
 p
 
 
-## ----top-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points transferred from the right category A and E to the left category A before being animated. This is called a many-to-one relationship."----
+## ----top-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the movement of points from categories A and E on the right to category A on the left, representing a many-to-one relationship. This specifically highlights the points that have moved to category A, which are the points that originate from categories A and E."----
 p_2 <- wallaby_plot(data = a,
                     rendering = "gganimate",
                     subset = "top",
@@ -212,7 +212,7 @@ p_2 <- wallaby_plot(data = a,
 p_2
 
 
-## ----b-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the points that got transferred to category B on the right are only from category B. The plot shown is the plot before it is being animated."----
+## ----b-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the transfer of points from the right category B to the left category B. It underscores that the points ultimately landing in category B originate specifically from category B itself."----
 p_3 <- wallaby_plot(data = a,
                     rendering = "gganimate",
                     subset = "B",

### 2024-02-08 animbook-journal.Rmd
discussion

@@
 company ages, time since the company was founded).
-One could also re-arrange the mapping of variables to the plot and animations.
-For example, the New York Times article, mentioned that to better compare distributions in time, one could plot the quantiles, which would form something like an S-curve, and animate over time, to observe how the distributions are changing.
+This can be done by pre-processing before passing to animbook, but it would be more convenient to automate for the user.
+One could also imagine re-arranging the mapping of variables to the plot and animations, particularly, split on time, and animate on the quantiles to focus on movement through the ranks.
+The New York Times article had examples of this idea.
+The static funnel web plot is a good place to experiment with this, and to further enhance visually.
 

### 2024-02-08 animbook-journal.Rmd
figure captions

@@
 The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
-The next section describes the expected data format.
-Following this is an explanation of available animation tools and how they are employed for this problem.
-A section on the functions of the package and how the visualization is designed demonstrates how the data is mapped to the animation.
-The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.
+It is followed by sections that describe the data format needed, considerations about making animations, and visual design.
+The software and its functions and usage are detailed in the next section.
+The next section illustrates the usage of the software to examine company performance, particularly zombie patterns, and changing political allegiance of voters in Australia.
+The discussion section summarises, outlines some limitations and suggests some future directions.
 
@@
 
-```{r animation-diagram, fig.cap="The diagram shows how the animation is done using the successive pictures.
-When small changes are seen in quick succession, it will appear as if the objects are in motion.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
+```{r animation-diagram, fig.cap="An animation requires small changes shown in quick succession to make it appear as if the objects are in motion.
+The three plots above show a single point changing position by a small amount, which when shown quickly will look like that point has moved up and to the right.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/animation-diagram.png")
@@
 
-```{r animated-diagram, fig.cap="The diagram shows how the frames were used in the animated plot.
-Frame one is depicted in blue, and frame two is represented in red.
-Each blue component is mapped exclusively to the Frame 1 plot, while all the second-frame elements are excluded, and vice versa.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
+```{r animated-diagram, fig.cap="Frames 1 and 2 show the year 1 and year 2 positions of points, from the data in the table at top.
+The id is necessary to enable interpolation to make the small changes to generate a perception of motion from frame 1 position to frame 2 position.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/animated-diagram.png")
@@
 
-```{r proportional-shade, fig.show="hold", out.width="50%", fig.cap="The plot shows the difference between the sigmoid (shown in the left figure) and the sine curve (shown in the right figure).
-In the sigmoid, as the curve progresses, it becomes narrower, resulting in a less accurate representation of proportions compared to the sine curve."}
+```{r proportional-shade, fig.show="hold", out.width="50%", fig.cap="The plot shows the difference between the sigmoid (left) and the sine curve (right).
+In the sigmoid, as the curve progresses it appears to become narrower, possibly resulting in more misperception of relative proportions compared to the sine curve."}
 knitr::include_graphics("figures/sigmoid-shade.png")
@@
 
-```{r top-one, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the transition of points from the left category A to the right categories A and E.
+```{r top-one, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="This illustrates the transition of points from the left category A to the right categories A and E.
 This is also referred to as a one-to-many relationship plot.
@@
 
-```{r top-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the movement of points from categories A and E on the right to category A on the left, representing a many-to-one relationship.
+```{r top-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The plot shows the movement of points from categories A and E on the right to category A on the left, representing a many-to-one relationship.
 This specifically highlights the points that have moved to category A, which are the points that originate from categories A and E."}
@@
 
-```{r b-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The static plot shows the transfer of points from the right category B to the left category B.
+```{r b-many, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body", fig.cap="The plot shows the transfer of points from the right category B to the left category B.
 It underscores that the points ultimately landing in category B originate specifically from category B itself."}
@@
 
-```{r catchange-figure, fig.cap = "Animate visualization using example data.
+```{r catchange-figure, fig.cap = "Four single frames from the animated visualization using example data.
 All of the X observations stay within the same group, while Y observations change from group A to group E.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
@@
 
-```{r catchange-gif, out.extra="class = 'gif'", fig.cap = "Animate visualization using example data.
+```{r catchange-gif, out.extra="class = 'gif'", fig.cap = "Animated visualization using example data.
 All of the X observations stay within the same group, while some of the Y observations change from group A to group E.", eval=knitr::is_html_output()}
@@
 
-```{r kan-osiris-figure, fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database.
+```{r kan-osiris-figure, fig.cap = "Four frames from the kangaroo plot visualization showing the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database.
 The 'not listed' category indicates companies not yet listed or removed from the listing.
 Most companies stay in the same quantile group, with a small number moving up and down.
-Most of the movement is made by American companies, which supports the OECD report.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+Most of the movement is made by American companies, which supports the OECD report that US companies have higher turnover rate relative to Japanese companies.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
 knitr::include_graphics("figures/osiris.png")
@@
 Most companies stay in the same quantile group, with a small number moving up and down.
-Most of the movement is made by American companies, which supports the OECD report.", eval=knitr::is_html_output()}
+Most of the movement is made by American companies, which supports the OECD report that US companies have higher turnover rate relative to Japanese companies.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/kan-osiris.gif")
@@
 
-```{r voter-figure, fig.cap = "The wallaby plot visualization shows how the top party performs in keeping the old voters of different genders.
+```{r voter-figure, fig.cap = "Four frames from a wallaby plot visualization shows how the top party performs in keeping the old voters of different genders.
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
-Interestingly, an individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.
-However, not many of them are shown in the plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+Interestingly, the few individuals who identified as neither male or female overwhelmingly shifted their party affiliations to the Greens.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
 knitr::include_graphics("figures/animation-voter.png")
@@
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
-Interestingly, an individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.
-However, not many of them are shown in the plot.", eval=knitr::is_html_output()}
+Interestingly, the few individuals who identified as neither male or female overwhelmingly shifted their party affiliations to the Greens.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/voter.gif")

### 2024-02-14 animbook-journal.Rmd
08/02/2024 to do list

@@
 The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
-It is followed by sections that describe the data format needed, considerations about making animations, and visual design.
+It is followed by sections describing the data format needed, considerations about making animations, and visual design.
 The software and its functions and usage are detailed in the next section.
-The next section illustrates the usage of the software to examine company performance, particularly zombie patterns, and changing political allegiance of voters in Australia.
-The discussion section summarises, outlines some limitations and suggests some future directions.
+The next section illustrates the usage of the software to examine company performance, particularly zombie patterns, and the changing political allegiance of voters in Australia.
+The discussion section summarizes, outlines some limitations, and suggests some future directions.
 
@@
 
-```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
+```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package.
+The animation illustrates the disparity between white men and black men.
+It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/NYT.png")
@@
   The New York Times visualization is also similar to what is called a Sankey plot.
-Sankey plots are flow diagrams that show the movement/change from one category levels to another, with the width of each arrow representing the proportional changes between levels.
-There are several R packages available to generate version of Sankey plots including \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}.
+Sankey plots are flow diagrams that show the movement/change from one category level to another, with the width of each arrow representing the proportional changes between levels.
+There are several R packages available to generate versions of Sankey plots, including \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}.
 The main difference between the Sankey plot visualization and the animation featured in the New York Times lies in their methods of representing the proportion of changes.
@@
 ```{r animation-diagram, fig.cap="An animation requires small changes shown in quick succession to make it appear as if the objects are in motion.
-The three plots above show a single point changing position by a small amount, which when shown quickly will look like that point has moved up and to the right.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
+The three plots above show a single point changing position by a small amount, which when shown quickly, will look like that point has moved up and to the right.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/animation-diagram.png")
@@
 
-```{r animated-diagram, fig.cap="Frames 1 and 2 show the year 1 and year 2 positions of points, from the data in the table at top.
+```{r animated-diagram, fig.cap="Frames 1 and 2 show the year 1 and year 2 positions of points from the data in the table at the top.
 The id is necessary to enable interpolation to make the small changes to generate a perception of motion from frame 1 position to frame 2 position.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
@@
 ```{r proportional-shade, fig.show="hold", out.width="50%", fig.cap="The plot shows the difference between the sigmoid (left) and the sine curve (right).
-In the sigmoid, as the curve progresses it appears to become narrower, possibly resulting in more misperception of relative proportions compared to the sine curve."}
+In the sigmoid, as the curve progresses, it appears to become narrower, possibly resulting in more misperception of relative proportions compared to the sine curve."}
 knitr::include_graphics("figures/sigmoid-shade.png")
@@
 
-  In the animation, the use of proportional shaded areas serves to enhances the comprehension of proportion information, effectively displaying the distribution within each group.
+  In the animation, the use of proportional shaded areas serves to enhance the comprehension of proportion information, effectively displaying the distribution within each group.
 To represent sub-groups, points are colored to focus attention on differences between groups of observation.
 
-  Discerning the movement pattern or proportion of sub-groups can be challenging when there is only a small number of points.
-To address this, sample size are inflated by calculating the sub-group proportion and multiplying it by the desired total number of points.
+  Discerning the movement pattern or proportion of sub-groups can be challenging when there are only a small number of points.
+To address this, the sample size is inflated by calculating the sub-group proportion and multiplying it by the desired total number of points.
 This approach ensures a richer representation of movement patterns.
 
- Another issue is that all observations have a common starting time.
-This would mean all points start the animation simultaneously and move as a block through time.
-This poses a challenge in distinguishing and tracking individual observations and their change patterns.
-To alleviate this, the animation randomly starts observations at different times so a continuous flow of points is shown.
+  Another issue is that all observations would have a common starting time.
+It would mean all points start the animation simultaneously and move as a block through time.
+It poses a challenge in distinguishing and tracking individual observations and their change patterns.
+To alleviate this, the observations in the animation are randomly started at different times so a continuous flow of points can be seen.
 It is important to note that this does not necessarily reflect the real-time occurrence of observations.
@@
 The interpolation functions in \CRANpkg{gganimate} and \CRANpkg{plotly} are inadequate because they only generate a linear path.
-Our animation needs non-linear path to show the flow.
+Our animation needs a non-linear path to show the flow.
 Sigmoid curves are commonly used in Sankey diagrams (@Hvitfeldt_2018).
@@
 The sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.
-New interpolation functions are needed to compute both the sigmoid and sine path.
+New interpolation functions are needed to compute both the sigmoid and sine paths.
 
@@
 The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points.
-Allowing for the random starting time makes the point tracking simpler.
+Allowing for the random starting time makes point tracking simpler.
 The starting times for the points are generated using the `runif()` function, where the `max` argument can be adjusted using the `width` parameter in the plotting function.
@@
 
-  The names of these plots draws inspiration from a native Australian animals.
+  The names of these plots draw inspiration from native Australian animals.
 The comprehensive plot is named Kangaroo, while its subset is referred to as Wallaby, representing a smaller version of the Kangaroo.
-The final plot is names after Funnel Web Spider, drawing parallels between the plot's features and the distinctive legs of the spider.
+The final plot is named after the Funnel Web Spider, drawing parallels between the plot's features and the distinctive legs of the spider.
 
@@
 
-```{r shade-algorithm, fig.show="hold", out.width="50%", fig.cap="The plot shows how the algorithm for the proportional\\_shade() function works.
-The left figure represents the initial step of the algorithm, which calculates all the corner points.
-The right figure demonstrates the subsequent step, where points in-between the left and right are interpolated using the sine() function."}
-knitr::include_graphics("figures/sankey-shade-1.png")
-knitr::include_graphics("figures/sankey-shade-2.png")
-```
-
-  The algorithm behind the `proportional_shade()` function for generating the proportional shaded data is illustrated in Figure \@ref(fig:shade-algorithm).
-It started by calculating the corner points for all of the shaded areas.
-Then, use the `sine()` function to interpolate the point between the left and right.
+  The `proportional_shade()` function's algorithm begins by calculating the corner points for each shaded area.
+Subsequently, the algorithm utilizes the `sine()` function to interpolate points between the left and right boundaries.
+Once this interpolation is completed, all the generated points are interconnected to form the shaded regions.
 
@@
 The `cat_change` data in the package is used to illustrate how to use this package.
-It has five categories, A to E, over two time points.
+It has five categories, A to E, over two-time points.
 Since the data is already in the categorized data structure, the `anim_prep_cat()` function is used.
@@
 
-Figure \@ref(fig:top-many), show the flexibility to use various options, such as `subset` or `relation`, to customize the plot appearance.
+Figure \@ref(fig:top-many), shows the flexibility to use various options, such as `subset` or `relation`, to customize the plot appearance.
 Here `subset = "top"` is used to specify category A for the final time point, and `relation = "many_one"` is used to specify that all categories flowing into A at time point 2 are shown.
@@
 
-Using `subset = "B"` will only show the point for a single category as shown in the Figure \@ref(fig:b-many).
+Using `subset = "B"` will only show the point for a single category as shown in Figure \@ref(fig:b-many).
 
@@
   @oecd_report reported that companies in the United States have a faster metabolic rate relative to Japanese companies.
-This means that US companies tends to move up and down performance metrics more frequently than Japanese companies.
-This can be examine using the wallaby and kangaroo plots.
+This means that US companies tend to move up and down performance metrics more frequently than Japanese companies.
+This can be examined using the wallaby and kangaroo plots.
 The wallaby plot allows the study of entry and exit behavior.
-The kangaroo plot allows studying the full movement of companies over time.
+The kangaroo plot allows for studying the full movement of companies over time.
 
@@
 Most companies stay in the same quantile group, with a small number moving up and down.
-Most of the movement is made by American companies, which supports the OECD report that US companies have higher turnover rate relative to Japanese companies.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+Most of the movement is made by American companies, which supports the OECD report that US companies have a higher turnover rate relative to Japanese companies.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
 knitr::include_graphics("figures/osiris.png")
@@
 Most companies stay in the same quantile group, with a small number moving up and down.
-Most of the movement is made by American companies, which supports the OECD report that US companies have higher turnover rate relative to Japanese companies.", eval=knitr::is_html_output()}
+Most of the movement is made by American companies, which supports the OECD report that US companies have a higher turnover rate relative to Japanese companies.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/kan-osiris.gif")
@@
 In the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`) the five grey bars indicate the five categories (Top 25%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018.
-Points represent individual companies with color indicating country of registration.
+Points represent individual companies with color indicating the country of registration.
 Points that stay within the bar indicate companies that remain in the same quartile over the entire time period.
-If a company drop in performance or improve performance to the extent of switching quartile, the corresponding point will jump up or down in this plot.
+If a company drops in performance or improves performance to the extent of switching quartile, the corresponding point will jump up or down in this plot.
 Note that all the companies in the "Not listed" category were listed at some point during this time period.
@@
 There are several companies that move up and down, and most of these are US companies.
-This support the @oecd_report claim that US companies have a higher turnover rate compared to Japanese companies.
+This supports the @oecd_report claim that US companies have a higher turnover rate compared to Japanese companies.
 
-Perceiving the differences between the movement pattern of groups can be difficult, especially when the groups have different sizes, as is the case here.
-There are more US companies than Japanese companies and particularly there are more US companies in the top 25 percent quantile.
-Thus there will likely be more blue points (US) moving than red points (JP) purely for this reason.
+Perceiving the differences between the movement patterns of groups can be difficult, especially when the groups have different sizes, as is the case here.
+There are more US companies than Japanese companies, and particularly, there are more US companies in the top 25 percent quantile.
+Thus, there will likely be more blue points (US) moving than red points (JP) purely for this reason.
 The difference that is of interest is **relative proportion**, that one country has a higher fraction of companies moving between quartiles than the other.
-This animated Sankey plot requires the reader to mentally calculate the fraction of points that are moving, separately for the blue and red points, to answer the question whether one group has a higher movement rate.
+This animated Sankey plot requires the reader to mentally calculate the fraction of points that are moving, separately for the blue and red points, to answer the question of whether one group has a higher movement rate.
 The task is easier if the two groups have a similar number of points.
@@
   In Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006.
-The grey regions show the proportion of companies in each of the categories in 2006 on the left that were exited the market by 2018.
-(explain the different in proportion and not listed companies).
-In 2006, the companies represented by points, colored by country are in one of the quartiles or "Not listed" category.
+The grey regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018.
+(explain the difference in proportion and not listed companies).
+In 2006, the companies represented by points, colored by country, were in one of the quartiles or "Not listed" category.
 All the companies in the Top 25% were US companies.
-Any Japanese companies in the Top 25% in 2006 did not exited the market (Not listed).
-But actually, there were non Japanese companies in the Top 25% in 2006.
+Any Japanese companies in the Top 25% in 2006 did not exit the market (Not listed).
+But actually, there were non-Japanese companies in the Top 25% in 2006.
 It is also interesting that the larger proportion of the companies in the Top 25% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.
 
-  Using the wallaby plot, it can be employed to emphasized the high turnvoer rate observed in the kangaroo plot, as it specifically focuses on a subset, allowing the users to better perceive the **relative proportion**.
-However, it is important to note that this plot is confined to only two-time points (start and end), which may not provide a comprehensive view of the entire story.
+  The wallaby plot can be employed to emphasize the high turnover rate observed in the kangaroo plot, as it specifically focuses on a subset, allowing the users to better perceive the **relative proportion**.
+However, it is also important to note that this plot is confined to only two-time points (start and end), which may not provide a comprehensive view of the entire story.
 
@@
 This dataset was collected from ADA Dataverse (@aeles).
+
+```{r}
+aeles <- aeles |> 
+  filter(party != "other")
+```
 
@@
 
-```{r voter-figure, fig.cap = "Four frames from a wallaby plot visualization shows how the top party performs in keeping the old voters of different genders.
+```{r voter-figure, fig.cap = "Four frames from a wallaby plot visualization show how the top party performs in keeping the old voters of different genders.
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
-Interestingly, the few individuals who identified as neither male or female overwhelmingly shifted their party affiliations to the Greens.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
+Interestingly, the few individuals who identified as neither male nor female overwhelmingly shifted their party affiliations to the Greens.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
 knitr::include_graphics("figures/animation-voter.png")
@@
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
-Interestingly, the few individuals who identified as neither male or female overwhelmingly shifted their party affiliations to the Greens.", eval=knitr::is_html_output()}
+Interestingly, the few individuals who identified as neither male nor female overwhelmingly shifted their party affiliations to the Greens.", eval=knitr::is_html_output()}
 knitr::include_graphics("figures/voter.gif")
@@
   According to the survey (@lgbtiq), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities.
-However, the Labor Party only give a broad statement of commitment to a range of LGBTIQ+ and human right issues.
+However, the Labor Party only gives a broad statement of commitment to a range of LGBTIQ+ and human rights issues.
 This includes working with LGBTIQ+ Australians and advocates to ensure equality before the law and full access to Medicare.
@@
 The paper describes how to pre-process the data into a format for making several types of plots and animation.
-It also explains what needs to be considered when making an animation such as persistence of objects, how to achieve this using interpolation, and the visualization design choices automated and those available to users.
+It also explains what needs to be considered when making an animation, such as the persistence of objects, how to achieve this using interpolation, and the visualization design choices automated and those available to users.
 
-  The package provides the tools to create animations for simple temporal patterns, with a few steps, but these visualization methods have some limitations.
+  The package provides the tools to create animations for simple temporal patterns with a few steps, but these visualization methods have some limitations.
 It is primarily for communication rather than exploration because one typically knows what the main patterns are.
-If there are many categories (quantiles) the display will be too crowded.
-Because the animation involves perceiving patterns in groups of moving points it can be challenging with unbalanced sample sizes.
+If there are many categories (quantiles), the display will be too crowded.
+Because the animation involves perceiving patterns in groups of moving points, it can be challenging with unbalanced sample sizes.
 This requires the reader to mentally calculate the fraction of points that are in motion.
@@
 This can be done by pre-processing before passing to animbook, but it would be more convenient to automate for the user.
-One could also imagine re-arranging the mapping of variables to the plot and animations, particularly, split on time, and animate on the quantiles to focus on movement through the ranks.
+One could also imagine re-arranging the mapping of variables to the plot and animations, particularly, split on time and animate on the quantiles to focus on movement through the ranks.
 The New York Times article had examples of this idea.
-The static funnel web plot is a good place to experiment with this, and to further enhance visually.
+The static funnel web plot is a good place to experiment with this and to further enhance it visually.
 

### 2024-02-14 animbook-journal.tex
08/02/2024 to do list

@@
 The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
-The next section describes the expected data format.
-Following this is an explanation of available animation tools and how they are employed for this problem.
-A section on the functions of the package and how the visualization is designed demonstrates how the data is mapped to the animation.
-The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.
+It is followed by sections describing the data format needed, considerations about making animations, and visual design.
+The software and its functions and usage are detailed in the next section.
+The next section illustrates the usage of the software to examine company performance, particularly zombie patterns, and the changing political allegiance of voters in Australia.
+The discussion section summarizes, outlines some limitations, and suggests some future directions.
 
@@
 
-\caption{Screenshot of the New York Times animation, which is the motivation for this visualization package.}\label{fig:nyt}
+\caption{Screenshot of the New York Times animation, which is the motivation for this visualization package.
+The animation illustrates the disparity between white men and black men.
+It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.}\label{fig:nyt}
 \end{figure}
@@
 The New York Times visualization is also similar to what is called a Sankey plot.
-Sankey plots are flow diagrams that show the movement/change from one category levels to another, with the width of each arrow representing the proportional changes between levels.
-There are several R packages available to generate version of Sankey plots including \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}.
+Sankey plots are flow diagrams that show the movement/change from one category level to another, with the width of each arrow representing the proportional changes between levels.
+There are several R packages available to generate versions of Sankey plots, including \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}.
 The main difference between the Sankey plot visualization and the animation featured in the New York Times lies in their methods of representing the proportion of changes.
@@
 
-\caption{The diagram shows how the animation is done using the successive pictures.
-When small changes are seen in quick succession, it will appear as if the objects are in motion.}\label{fig:animation-diagram}
+\caption{An animation requires small changes shown in quick succession to make it appear as if the objects are in motion.
+The three plots above show a single point changing position by a small amount, which when shown quickly, will look like that point has moved up and to the right.}\label{fig:animation-diagram}
 \end{figure}
@@
 
-\caption{The diagram shows how the frames were used in the animated plot.
-Frame one is depicted in blue, and frame two is represented in red.
-Each blue component is mapped exclusively to the Frame 1 plot, while all the second-frame elements are excluded, and vice versa.}\label{fig:animated-diagram}
+\caption{Frames 1 and 2 show the year 1 and year 2 positions of points from the data in the table at the top.
+The id is necessary to enable interpolation to make the small changes to generate a perception of motion from frame 1 position to frame 2 position.}\label{fig:animated-diagram}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=0.5\linewidth]{figures/sigmoid-shade} \includegraphics[width=0.5\linewidth]{figures/sine-shade} \caption{The plot shows the difference between the sigmoid (shown in the left figure) and the sine curve (shown in the right figure).
-In the sigmoid, as the curve progresses, it becomes narrower, resulting in a less accurate representation of proportions compared to the sine curve.}\label{fig:proportional-shade}
+\includegraphics[width=0.5\linewidth]{figures/sigmoid-shade} \includegraphics[width=0.5\linewidth]{figures/sine-shade} \caption{The plot shows the difference between the sigmoid (left) and the sine curve (right).
+In the sigmoid, as the curve progresses, it appears to become narrower, possibly resulting in more misperception of relative proportions compared to the sine curve.}\label{fig:proportional-shade}
 \end{figure}
 
-In the animation, the use of proportional shaded areas serves to enhances the comprehension of proportion information, effectively displaying the distribution within each group.
+In the animation, the use of proportional shaded areas serves to enhance the comprehension of proportion information, effectively displaying the distribution within each group.
 To represent sub-groups, points are colored to focus attention on differences between groups of observation.
 
-Discerning the movement pattern or proportion of sub-groups can be challenging when there is only a small number of points.
-To address this, sample size are inflated by calculating the sub-group proportion and multiplying it by the desired total number of points.
+Discerning the movement pattern or proportion of sub-groups can be challenging when there are only a small number of points.
+To address this, the sample size is inflated by calculating the sub-group proportion and multiplying it by the desired total number of points.
 This approach ensures a richer representation of movement patterns.
 
-Another issue is that all observations have a common starting time.
-This would mean all points start the animation simultaneously and move as a block through time.
-This poses a challenge in distinguishing and tracking individual observations and their change patterns.
-To alleviate this, the animation randomly starts observations at different times so a continuous flow of points is shown.
+Another issue is that all observations would have a common starting time.
+It would mean all points start the animation simultaneously and move as a block through time.
+It poses a challenge in distinguishing and tracking individual observations and their change patterns.
+To alleviate this, the observations in the animation are randomly started at different times so a continuous flow of points can be seen.
 It is important to note that this does not necessarily reflect the real-time occurrence of observations.
@@
 The interpolation functions in \CRANpkg{gganimate} and \CRANpkg{plotly} are inadequate because they only generate a linear path.
-Our animation needs non-linear path to show the flow.
+Our animation needs a non-linear path to show the flow.
 Sigmoid curves are commonly used in Sankey diagrams (Hvitfeldt (2018)).
@@
 The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points.
-Allowing for the random starting time makes the point tracking simpler.
+Allowing for the random starting time makes point tracking simpler.
 The starting times for the points are generated using the \texttt{runif()} function, where the \texttt{max} argument can be adjusted using the \texttt{width} parameter in the plotting function.
@@
 
-The names of these plots draws inspiration from a native Australian animals.
+The names of these plots draw inspiration from native Australian animals.
 The comprehensive plot is named Kangaroo, while its subset is referred to as Wallaby, representing a smaller version of the Kangaroo.
-The final plot is names after Funnel Web Spider, drawing parallels between the plot's features and the distinctive legs of the spider.
+The final plot is named after the Funnel Web Spider, drawing parallels between the plot's features and the distinctive legs of the spider.
 
@@
 
-\begin{figure}
-\includegraphics[width=0.5\linewidth]{figures/sankey-shade-1} \includegraphics[width=0.5\linewidth]{figures/sankey-shade-2} \caption{The plot shows how the algorithm for the proportional\_shade() function works.
-The left figure represents the initial step of the algorithm, which calculates all the corner points.
-The right figure demonstrates the subsequent step, where points in-between the left and right are interpolated using the sine() function.}\label{fig:shade-algorithm}
-\end{figure}
-
-The algorithm behind the \texttt{proportional\_shade()} function for generating the proportional shaded data is illustrated in Figure \ref{fig:shade-algorithm}.
-It started by calculating the corner points for all of the shaded areas.
-Then, use the \texttt{sine()} function to interpolate the point between the left and right.
+The \texttt{proportional\_shade()} function's algorithm begins by calculating the corner points for each shaded area.
+Subsequently, the algorithm utilizes the \texttt{sine()} function to interpolate points between the left and right boundaries.
+Once this interpolation is completed, all the generated points are interconnected to form the shaded regions.
 
@@
 The \texttt{cat\_change} data in the package is used to illustrate how to use this package.
-It has five categories, A to E, over two time points.
+It has five categories, A to E, over two-time points.
 Since the data is already in the categorized data structure, the \texttt{anim\_prep\_cat()} function is used.
@@
 
-\caption{The static plot shows the transition of points from the left category A to the right categories A and E.
+\caption{This illustrates the transition of points from the left category A to the right categories A and E.
 This is also referred to as a one-to-many relationship plot.
@@
 
-Figure \ref{fig:top-many}, show the flexibility to use various options, such as \texttt{subset} or \texttt{relation}, to customize the plot appearance.
+Figure \ref{fig:top-many}, shows the flexibility to use various options, such as \texttt{subset} or \texttt{relation}, to customize the plot appearance.
 Here \texttt{subset\ =\ "top"} is used to specify category A for the final time point, and \texttt{relation\ =\ "many\_one"} is used to specify that all categories flowing into A at time point 2 are shown.
@@
 
-\caption{The static plot shows the movement of points from categories A and E on the right to category A on the left, representing a many-to-one relationship.
+\caption{The plot shows the movement of points from categories A and E on the right to category A on the left, representing a many-to-one relationship.
 This specifically highlights the points that have moved to category A, which are the points that originate from categories A and E.}\label{fig:top-many}
@@
 
-Using \texttt{subset\ =\ "B"} will only show the point for a single category as shown in the Figure \ref{fig:b-many}.
+Using \texttt{subset\ =\ "B"} will only show the point for a single category as shown in Figure \ref{fig:b-many}.
 
@@
 
-\caption{The static plot shows the transfer of points from the right category B to the left category B.
+\caption{The plot shows the transfer of points from the right category B to the left category B.
 It underscores that the points ultimately landing in category B originate specifically from category B itself.}\label{fig:b-many}
@@
 
-\caption{Animate visualization using example data. All of the X observations stay within the same group, while Y observations change from group A to group E.}\label{fig:catchange-figure}
+\caption{Four single frames from the animated visualization using example data.
+All of the X observations stay within the same group, while Y observations change from group A to group E.}\label{fig:catchange-figure}
 \end{figure}
@@
 McGowan, Andrews, and Millot (2017) reported that companies in the United States have a faster metabolic rate relative to Japanese companies.
-This means that US companies tends to move up and down performance metrics more frequently than Japanese companies.
-This can be examine using the wallaby and kangaroo plots.
+This means that US companies tend to move up and down performance metrics more frequently than Japanese companies.
+This can be examined using the wallaby and kangaroo plots.
 The wallaby plot allows the study of entry and exit behavior.
-The kangaroo plot allows studying the full movement of companies over time.
+The kangaroo plot allows for studying the full movement of companies over time.
 
@@
 
-\caption{The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database.
+\caption{Four frames from the kangaroo plot visualization showing the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database.
 The 'not listed' category indicates companies not yet listed or removed from the listing.
 Most companies stay in the same quantile group, with a small number moving up and down.
-Most of the movement is made by American companies, which supports the OECD report.}\label{fig:kan-osiris-figure}
+Most of the movement is made by American companies, which supports the OECD report that US companies have a higher turnover rate relative to Japanese companies.}\label{fig:kan-osiris-figure}
 \end{figure}
@@
 In the kangaroo plot (Figure \ref{fig:kan-osiris-figure}) the five grey bars indicate the five categories (Top 25\%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018.
-Points represent individual companies with color indicating country of registration.
+Points represent individual companies with color indicating the country of registration.
 Points that stay within the bar indicate companies that remain in the same quartile over the entire time period.
-If a company drop in performance or improve performance to the extent of switching quartile, the corresponding point will jump up or down in this plot.
+If a company drops in performance or improves performance to the extent of switching quartile, the corresponding point will jump up or down in this plot.
 Note that all the companies in the ``Not listed'' category were listed at some point during this time period.
@@
 There are several companies that move up and down, and most of these are US companies.
-This support the McGowan, Andrews, and Millot (2017) claim that US companies have a higher turnover rate compared to Japanese companies.
+This supports the McGowan, Andrews, and Millot (2017) claim that US companies have a higher turnover rate compared to Japanese companies.
 
-Perceiving the differences between the movement pattern of groups can be difficult, especially when the groups have different sizes, as is the case here.
-There are more US companies than Japanese companies and particularly there are more US companies in the top 25 percent quantile.
-Thus there will likely be more blue points (US) moving than red points (JP) purely for this reason.
+Perceiving the differences between the movement patterns of groups can be difficult, especially when the groups have different sizes, as is the case here.
+There are more US companies than Japanese companies, and particularly, there are more US companies in the top 25 percent quantile.
+Thus, there will likely be more blue points (US) moving than red points (JP) purely for this reason.
 The difference that is of interest is \textbf{relative proportion}, that one country has a higher fraction of companies moving between quartiles than the other.
-This animated Sankey plot requires the reader to mentally calculate the fraction of points that are moving, separately for the blue and red points, to answer the question whether one group has a higher movement rate.
+This animated Sankey plot requires the reader to mentally calculate the fraction of points that are moving, separately for the blue and red points, to answer the question of whether one group has a higher movement rate.
 The task is easier if the two groups have a similar number of points.
@@
 In Figure \ref{fig:osiris-figure}, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006.
-The grey regions show the proportion of companies in each of the categories in 2006 on the left that were exited the market by 2018.
-(explain the different in proportion and not listed companies).
-In 2006, the companies represented by points, colored by country are in one of the quartiles or ``Not listed'' category.
+The grey regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018.
+(explain the difference in proportion and not listed companies).
+In 2006, the companies represented by points, colored by country, were in one of the quartiles or ``Not listed'' category.
 All the companies in the Top 25\% were US companies.
-Any Japanese companies in the Top 25\% in 2006 did not exited the market (Not listed).
-But actually, there were non Japanese companies in the Top 25\% in 2006.
+Any Japanese companies in the Top 25\% in 2006 did not exit the market (Not listed).
+But actually, there were non-Japanese companies in the Top 25\% in 2006.
 It is also interesting that the larger proportion of the companies in the Top 25\% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.
 
-Using the wallaby plot, it can be employed to emphasized the high turnvoer rate observed in the kangaroo plot, as it specifically focuses on a subset, allowing the users to better perceive the \textbf{relative proportion}.
-However, it is important to note that this plot is confined to only two-time points (start and end), which may not provide a comprehensive view of the entire story.
+The wallaby plot can be employed to emphasize the high turnover rate observed in the kangaroo plot, as it specifically focuses on a subset, allowing the users to better perceive the \textbf{relative proportion}.
+However, it is also important to note that this plot is confined to only two-time points (start and end), which may not provide a comprehensive view of the entire story.
 
@@
 
-\caption{The wallaby plot visualization shows how the top party performs in keeping the old voters of different genders.
+\caption{Four frames from a wallaby plot visualization show how the top party performs in keeping the old voters of different genders.
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
-Interestingly, an individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.
-However, not many of them are shown in the plot.}\label{fig:voter-figure}
+Interestingly, the few individuals who identified as neither male nor female overwhelmingly shifted their party affiliations to the Greens.}\label{fig:voter-figure}
 \end{figure}
@@
 
-According to the survey ({``LGBTIQ+ Health Australia Party Survey''} (2022)), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities.
-However, the Labor Party only give a broad statement of commitment to a range of LGBTIQ+ and human right issues.
+According to the survey ({``{LGBTIQ+ Health Australia Party survey}''} (2022)), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities.
+However, the Labor Party only gives a broad statement of commitment to a range of LGBTIQ+ and human rights issues.
 This includes working with LGBTIQ+ Australians and advocates to ensure equality before the law and full access to Medicare.
@@
 The paper describes how to pre-process the data into a format for making several types of plots and animation.
-It also explains what needs to be considered when making an animation such as persistence of objects, how to achieve this using interpolation, and the visualization design choices automated and those available to users.
+It also explains what needs to be considered when making an animation, such as the persistence of objects, how to achieve this using interpolation, and the visualization design choices automated and those available to users.
 
-The package provides the tools to create animations for simple temporal patterns, with a few steps, but these visualization methods have some limitations.
+The package provides the tools to create animations for simple temporal patterns with a few steps, but these visualization methods have some limitations.
 It is primarily for communication rather than exploration because one typically knows what the main patterns are.
-If there are many categories (quantiles) the display will be too crowded.
-Because the animation involves perceiving patterns in groups of moving points it can be challenging with unbalanced sample sizes.
+If there are many categories (quantiles), the display will be too crowded.
+Because the animation involves perceiving patterns in groups of moving points, it can be challenging with unbalanced sample sizes.
 This requires the reader to mentally calculate the fraction of points that are in motion.
@@
 Some applications might benefit by re-parameterization of the x-axis from years to ages (e.g.~company ages, time since the company was founded).
-One could also re-arrange the mapping of variables to the plot and animations.
-For example, the New York Times article, mentioned that to better compare distributions in time, one could plot the quantiles, which would form something like an S-curve, and animate over time, to observe how the distributions are changing.
+This can be done by pre-processing before passing to animbook, but it would be more convenient to automate for the user.
+One could also imagine re-arranging the mapping of variables to the plot and animations, particularly, split on time and animate on the quantiles to focus on movement through the ranks.
+The New York Times article had examples of this idea.
+The static funnel web plot is a good place to experiment with this and to further enhance it visually.
 
@@
 2018.
-{``Extensive Data Shows Punishing Reach of Racism for Black Boys.''} \emph{The New York Times}.
+{``{Extensive data shows punishing reach of racism for black boys}.''} \emph{The New York Times}.
 The New York Times.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-d3js}{}}%
-Bostock, Mike. 2012. {``D3.js - Data-Driven Documents.''} 2012. \url{http://d3js.org/}.
+Bostock, Mike. 2012. {``{D3.js - Data-Driven Documents}.''} 2012. \url{http://d3js.org/}.
 
@@
 2008.
-{``Zombie Lending and Depressed Restructuring in {J}apan.''} \emph{The American Economic Review} 98 (5): 1943--77.
+{``{Zombie Lending and Depressed Restructuring in Japan}.''} \emph{The American Economic Review} 98 (5): 1943--77.
 \url{http://www.jstor.org/stable/29730158}.
@@
 2020.
-{``Race and Economic Opportunity in the United States: An Intergenerational Perspective*.''} \emph{The Quarterly Journal of Economics} 135 (May): 711--83.
+{``{Race and Economic Opportunity in the United States: an Intergenerational Perspective}.''} \emph{The Quarterly Journal of Economics} 135 (May): 711--83.
 \url{https://doi.org/10.1093/qje/qjz042}.
@@
 2007.
-{``Learner Control, Cognitive Load and Instructional Animation.
-Applied Cognitive Psychology, 21, 713-729.''} \emph{Applied Cognitive Psychology} 21 (September): 713--29.
+{``{Learner control, cognitive load and instructional animation.
+Applied Cognitive Psychology, 21, 713-729}.''} \emph{Applied Cognitive Psychology} 21 (September): 713--29.
 \url{https://doi.org/10.1002/acp.1345}.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Hvitfeldt_2018}{}}%
-Hvitfeldt, Emil. 2018. {``Recreate - Sankey Flow Chart.''} \emph{Recreate - Sankey Flow Chart}. \url{https://emilhvitfeldt.com/post/2018-03-20-recreate-sankey-flow-chart/}.
+Hvitfeldt, Emil. 2018. {``{Recreate - Sankey flow chart}.''} \emph{Recreate - Sankey Flow Chart}. \url{https://emilhvitfeldt.com/post/2018-03-20-recreate-sankey-flow-chart/}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-lgbtiq}{}}%
-{``LGBTIQ+ Health Australia Party Survey.''} 2022. \emph{LGBTIQ+ Health Australia}. \url{https://www.lgbtiqhealth.org.au/electionsurvey}.
+{``{LGBTIQ+ Health Australia Party survey}.''} 2022. \emph{LGBTIQ+ Health Australia}. \url{https://www.lgbtiqhealth.org.au/electionsurvey}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-mayer-2010}{}}%
-Mayer, Richard. 2010. {``Applying the Science of Learning to Medical Education.''} \emph{Medical Education} 44 (June): 543--49. \url{https://doi.org/10.1111/j.1365-2923.2010.03624.x}.
+Mayer, Richard. 2010. {``{Applying the science of learning to medical education}.''} \emph{Medical Education} 44 (June): 543--49. \url{https://doi.org/10.1111/j.1365-2923.2010.03624.x}.
 
@@
 2005.
-{``Cognitive Theory of Multimedia Learning.''} In \emph{The Cambridge Handbook of Multimedia Learning}, edited by RichardEditor Mayer, 31--48.
+{``{Cognitive Theory of Multimedia Learning}.''} In \emph{The Cambridge Handbook of Multimedia Learning}, edited by RichardEditor Mayer, 31--48.
 Cambridge Handbooks in Psychology.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-aeles}{}}%
-McAllister, Ian, Jill Sheppard, Sarah Cameron, and Jackman Simon. 2023. {``Australian Election Study, 2022.''} ADA Dataverse. \url{https://doi.org/10.26193/W3U2S3}.
+McAllister, Ian, Jill Sheppard, Sarah Cameron, and Jackman Simon. 2023. {``{Australian Election Study, 2022}.''} ADA Dataverse. \url{https://doi.org/10.26193/W3U2S3}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-oecd_report}{}}%
-McGowan, Müge Adalet, Dan Andrews, and Valentine Millot. 2017. {``The Walking Dead?''} no. 1372. https://doi.org/\url{https://doi.org/https://doi.org/10.1787/180d80ad-en}.
+McGowan, Müge Adalet, Dan Andrews, and Valentine Millot. 2017. {``{The Walking Dead?}''} no. 1372. https://doi.org/\url{https://doi.org/https://doi.org/10.1787/180d80ad-en}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-webgl}{}}%
-Mozilla Foundation. 2011. {``WebGL.''} Khronos WebGL Working Group. \href{https://www.khronos.org/webgl/}{www.khronos.org/webgl/}.
+Mozilla Foundation. 2011. {``{WebGL}.''} Khronos WebGL Working Group. \href{https://www.khronos.org/webgl/}{www.khronos.org/webgl/}.
 
@@
 2023.
-\emph{Rjtools: Preparing, Checking, and Submitting Articles to the 'r Journal'}.
+\emph{{rjtools: Preparing, Checking, and Submitting Articles to the 'R Journal'}}.
 \url{https://CRAN.R-project.org/package=rjtools}.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-av}{}}%
-Ooms, Jeroen. 2023a. \emph{Av: Working with Audio and Video in r}. \url{https://CRAN.R-project.org/package=av}.
+Ooms, Jeroen. 2023a. \emph{{av: Working with Audio and Video in R}}. \url{https://CRAN.R-project.org/package=av}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-gifski}{}}%
----------. 2023b. \emph{Gifski: Highest Quality GIF Encoder}. \url{https://CRAN.R-project.org/package=gifski}.
+---------. 2023b. \emph{{gifski: Highest Quality GIF Encoder}}. \url{https://CRAN.R-project.org/package=gifski}.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tweenr}{}}%
-Pedersen, Thomas Lin. 2022. \emph{Tweenr: Interpolate Data for Smooth Animations}. \url{https://CRAN.R-project.org/package=tweenr}.
+Pedersen, Thomas Lin. 2022. \emph{{tweenr: Interpolate Data for Smooth Animations}}. \url{https://CRAN.R-project.org/package=tweenr}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-gganimate}{}}%
-Pedersen, Thomas Lin, and David Robinson. 2020. {``Gganimate: A Grammar of Animated Graphics.''} \emph{R Package Version} 1 (7): 403--8.
+Pedersen, Thomas Lin, and David Robinson. 2020. {``{Gganimate: A grammar of animated graphics}.''} \emph{R Package Version} 1 (7): 403--8.
 
 \leavevmode\vadjust pre{\hypertarget{ref-r}{}}%
-R Core Team. 2021. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
+R Core Team. 2021. \emph{{R: A Language and Environment for Statistical Computing}}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
 
@@
 2008.
-{``Effectiveness of Animation in Trend Visualization.''} \emph{IEEE Transactions on Visualization and Computer Graphics} 14 (6): 1325--32.
+{``{Effectiveness of Animation in Trend Visualization}.''} \emph{IEEE Transactions on Visualization and Computer Graphics} 14 (6): 1325--32.
 \url{https://doi.org/10.1109/TVCG.2008.125}.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Shaffer_2019}{}}%
-Shaffer, Jeffrey. 2019. {``Sankey Diagrams: Why i Used the Sigmoid Function and Why You Probably Shouldn't.''} \emph{Data + Science}. \url{https://www.dataplusscience.com/Sigmoid.html}.
+Shaffer, Jeffrey. 2019. {``{Sankey Diagrams: Why I Used the Sigmoid Function and Why You Probably Shouldn't}.''} \emph{Data + Science}. \url{https://www.dataplusscience.com/Sigmoid.html}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-plotly}{}}%
-Sievert, Carson. 2020. {``Interactive {Web-Based} Data Visualization with r, Plotly, and Shiny.''} Chapman; Hall/CRC. \url{https://plotly-r.com}.
+Sievert, Carson. 2020. {``{Interactive {Web-Based} Data Visualization with R, plotly, and shiny}.''} Chapman; Hall/CRC. \url{https://plotly-r.com}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-animation-mechanic}{}}%
-Webster, Chris. 2005. \emph{Animation : The Mechanics of Motion}. Focal Press Visual Effects and Animation Series. Oxford ; Burlington, MA: Elsevier Focal Press.
+Webster, Chris. 2005. \emph{{Animation : the mechanics of motion}}. Focal Press Visual Effects and Animation Series. Oxford ; Burlington, MA: Elsevier Focal Press.
 
 \leavevmode\vadjust pre{\hypertarget{ref-tidy-data}{}}%
-Wickham, Hadley. 2014. {``Tidy Data.''} \emph{Journal of Statistical Software} 59 (10): 1--23. \url{https://doi.org/10.18637/jss.v059.i10}.
+Wickham, Hadley. 2014. {``{Tidy Data}.''} \emph{Journal of Statistical Software} 59 (10): 1--23. \url{https://doi.org/10.18637/jss.v059.i10}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-dplyr}{}}%
-Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis Vaughan. 2023. \emph{Dplyr: A Grammar of Data Manipulation}.
+Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis Vaughan. 2023. \emph{{dplyr: A Grammar of Data Manipulation}}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-purrr}{}}%
-Wickham, Hadley, and Lionel Henry. 2023. \emph{Purrr: Functional Programming Tools}. \url{https://CRAN.R-project.org/package=purrr}.
+Wickham, Hadley, and Lionel Henry. 2023. \emph{{purrr: Functional Programming Tools}}. \url{https://CRAN.R-project.org/package=purrr}.
 

### 2024-02-14 animbook-journal.R

@@ -10,7 +10,7 @@ library(animbook)
 library(tidyverse)
 
 
-## ----nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+## ----nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package. The animation illustrates the disparity between white men and black men. It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
 knitr::include_graphics("figures/NYT.png")
 
 
@@ -18,15 +18,15 @@ knitr::include_graphics("figures/NYT.png")
 knitr::include_graphics("figures/data-diagram.png")
 
 
-## ----animation-diagram, fig.cap="The diagram shows how the animation is done using the successive pictures. When small changes are seen in quick succession, it will appear as if the objects are in motion.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+## ----animation-diagram, fig.cap="An animation requires small changes shown in quick succession to make it appear as if the objects are in motion. The three plots above show a single point changing position by a small amount, which when shown quickly, will look like that point has moved up and to the right.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
 knitr::include_graphics("figures/animation-diagram.png")
 
 
-## ----animated-diagram, fig.cap="The diagram shows how the frames were used in the animated plot. Frame one is depicted in blue, and frame two is represented in red. Each blue component is mapped exclusively to the Frame 1 plot, while all the second-frame elements are excluded, and vice versa.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+## ----animated-diagram, fig.cap="Frames 1 and 2 show the year 1 and year 2 positions of points from the data in the table at the top. The id is necessary to enable interpolation to make the small changes to generate a perception of motion from frame 1 position to frame 2 position.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
 knitr::include_graphics("figures/animated-diagram.png")
 
 
[…]

### 2024-02-19 animbook-journal.Rmd
19/02/2024 check on the paper

@@
 
-  The challenge in producing an animation like that in the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated.
+  The challenge in producing an animation similar to the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated.
 The complexities include allowing the user to choose the number of categories, standardizing distributions, and allowing the user to input pre-computed categorical data.
@@
   The structure of this paper is as follows.
-The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
-It is followed by sections describing the data format needed, considerations about making animations, and visual design.
-The software and its functions and usage are detailed in the next section.
-The next section illustrates the usage of the software to examine company performance, particularly zombie patterns, and the changing political allegiance of voters in Australia.
-The discussion section summarizes, outlines some limitations, and suggests some future directions.
+The subsequent section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
+It is then followed by sections describing the data format needed, considerations about making animations, and visual design.
+The functions and usage of the software are detailed in the next section.
+Just prior to the final section, the paper illustrates the usage of the software to examine company performance, particularly zombie patterns, and the changing political allegiance of voters in Australia.
+The concluding discussion section summarizes, outlines some limitations, and suggests future directions for the software.
 
@@
   In the visualization, each observation is initially classified into one group at the start and potentially transitions into either the same group or a different group.
-This dynamics visualization constructs questions on the broader use of this visualization to other types of data.
+This dynamic visualization constructs questions on the broader use of this visualization to other types of data.
 The potential use of this visualization on accounting data is to convey a message, as reported by the @oecd_report, that the concept of zombie companies is not unique to Japan alone.
-It is also present in the United States, which has a faster metabolize rate (more new listings and exits) relative to Japan.
+It is also present in the United States, which has a faster metabolization rate (more new listings and exits) relative to Japan.
 
   The political data that exhibits the movement of voters switching party affiliations between elections can be a valuable insight into the behavior of the voters.
-This data could be extended to incorporate demographic information about the voters, providing analysts with a significant insight into voter behavior.
-This allows them to consolidate effective campaigns for their political party.
-This also applies to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.
+This data could be extended to incorporate demographic information about the voters, providing analysts with significant insight into voter behavior and allowing them to consolidate effective campaigns for their political party.
+It can also be applied to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.
 
@@
   @Hvitfeldt_2018 provides R (@r) code to generate an animation similar to that of the New York Times.
-Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be use for a variety of similar animations for studying flow and temporal change data.
+Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be used for a variety of similar animations for studying flow and temporal change data.
 
-  The New York Times visualization is also similar to what is called a Sankey plot.
+  The New York Times visualization is similar to a Sankey plot.
 Sankey plots are flow diagrams that show the movement/change from one category level to another, with the width of each arrow representing the proportional changes between levels.
@@
 
-  One of the frequently encountered values in the dataset is NA, commonly known as missing values.
+  One of the frequently encountered values in the dataset is NA, commonly known as a missing value.
 In the context of accounting data, NA might signify that a company is either not yet listed or has been de-listed.
@@
 The use of `transition_*()` functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time.
-This includes `gifski_renderer()` from the \CRANpkg{gifski} package (@gifski) to save animation in GIF format or `av_renderer()` from the \CRANpkg{av} package (@av) to save it into a video file format.
+The \CRANpkg{gganimate} includes `gifski_renderer()` from the \CRANpkg{gifski} package (@gifski) to save animation in GIF format or `av_renderer()` from the \CRANpkg{av} package (@av) to save it into a video file format.
 
@@
 
-  In the animation, the use of proportional shaded areas serves to enhance the comprehension of proportion information, effectively displaying the distribution within each group.
+  The incorporation of proportional shaded areas in this animation package serves to enhance the comprehension of proportion information, effectively displaying the distribution within each group.
 To represent sub-groups, points are colored to focus attention on differences between groups of observation.
@@
 In some cases, this may not be the best option.
-When the observation is moved up by quantile, one is bound to move down.
+When the observation is moved up by quantile, one is bound to move down, making the amount of observation in the quantile remain the same.
 This issue can be resolved by using an alternative method, which is grouping values based on their absolute values.
@@
 This generalization leads to four different scaling methods for the numerical data.
+
+  1. Ranking by year. (rank)
+  2. Ranking by year within a group. (rank_group)
+  3. Fix bins relative to absolute values by year. (absolute)
+  4. Fix bins relative to absolute values by year within a group. (absolute_group)
 
@@
 
-  1. Ranking by year. (rank)
-  2. Ranking by year within a group. (rank_group)
-  3. Fix bins relative to absolute values by year. (absolute)
-  4. Fix bins relative to absolute values by year within a group. (absolute_group)
-
   For the first and second scaling methods, it is necessary to rank the values based on time, and in cases where a group is provided, they are ranked based on both time and groups.
@@
 Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animated data structure.
-It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values.
+It is carried out by assigning a frame to each individual observation, ensuring that each ID does not contain repeated frame values.
 It lets the \CRANpkg{gganimate} or \CRANpkg{plotly} perceive where the observation would be on the plot at a given frame, as seen in Figure \@ref(fig:animated-diagram).
@@
 Two of the plots could be used for the animation, and another plot is used as a static visualization.
-All of the plots have an internal function that converts the categorized data format into the animated structure for each plotting function.
+All of each plot has an associated internal function that converts the categorized data format into the animated structure.
 
@@
 It includes creating additional data components for labeling and shading.
-This function also responds by interpolating the non-linear path.
+This function is also responsible for interpolating the non-linear path.
 It performs this task by mapping the `sine()` function provided in this package to each observation using the `map()` function from the \CRANpkg{purrr} package (@purrr).
@@
 
-It is necessary to save the plot as a `ggplot` object before passing it to the final function, `anim_animate()`, to animate.
+It is necessary to store the plot as a `ggplot` object before passing it to the final function, `anim_animate()`, to animate.
 This function will automatically detect which rendering method was specified in the previous steps and add the minimum requirement functions accordingly.
@@
 The `cat_change` data in the package is used to illustrate how to use this package.
-It has five categories, A to E, over two-time points.
+It has five categories, A to E, over two time points.
 Since the data is already in the categorized data structure, the `anim_prep_cat()` function is used.
@@
 
-To obtain an object for the animation function, the `wallaby_plot` is used.
+To obtain an object for the animation function, the `wallaby_plot` function is used.
 The `subset` and `relation` arguments are applied to refine the final appearance of the animation, Figure \@ref(fig:top-one).
@@
 
-Two examples of usage are provided.
+Two real-world examples of usage are provided.
 The osiris example studies company movement between quartiles of sales performance over a 12-year period.
-The voting example studies party preference changes between 2016 and 2019 elections.
+The voting example studies party preference changes between the 2016 and 2019 elections.
 
@@
 The Osiris data presented in this section was acquired from Bureau van Dijk (@bvd), compiling information on a total of 122,318 companies.
-It was subsequently a subset for the 2021 report, consisting of 1000 companies with 94 variables.
+It was subsequently subsetted for the 2021 report, consisting of 1000 companies with 94 variables.
 The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018.
@@
   @oecd_report reported that companies in the United States have a faster metabolic rate relative to Japanese companies.
-This means that US companies tend to move up and down performance metrics more frequently than Japanese companies.
+This means that US companies tend to move up and down in the performance metrics more frequently than Japanese companies.
 This can be examined using the wallaby and kangaroo plots.
@@
 Any Japanese companies in the Top 25% in 2006 did not exit the market (Not listed).
-But actually, there were non-Japanese companies in the Top 25% in 2006.
+It is worth noting that there are actually none of the Japanese companies in the Top 25% in 2006.
 It is also interesting that the larger proportion of the companies in the Top 25% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.
@@
   The package provides the tools to create animations for simple temporal patterns with a few steps, but these visualization methods have some limitations.
-It is primarily for communication rather than exploration because one typically knows what the main patterns are.
+This package is to be used primarily for communication rather than exploration because the end-user typically knows what the main patterns are.
 If there are many categories (quantiles), the display will be too crowded.

### 2024-02-23 animbook-journal.Rmd
spell checked

@@
 ---
-title: "animbook: Visualizing changes in performance measures and demographic affiliations using animation"
+title: "animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation"
 abstract: >
@@
 Between elections, voters often switch party preferences, which produces categorical values over time.
-Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," we provide new visualization functions to generate animations that display this type of data in an R package called \CRANpkg{animbook}.
+Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," we provide new visualization functions to generate animations that display this type of data in an R package called animbook.
 Functions to pre-process the data and prepare it for the animation are provided.
@@
 
-The interactive chart featured in the New York Times article (Figure \@ref(fig:nyt)) unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the @race.
+The interactive chart featured in the New York Times article (Figure \@ref(fig:nyt)) unveils the issue of income disparities between black and white children who were raised in families with comparable income according to @race.
 This visualization reveals that, compared to white children, black children are more likely to drop down to the lower-income group, given that they both grew up in wealthy families.
@@
 This dynamic visualization constructs questions on the broader use of this visualization to other types of data.
-The potential use of this visualization on accounting data is to convey a message, as reported by the @oecd_report, that the concept of zombie companies is not unique to Japan alone.
+The potential use of this visualization on accounting data is to convey a message, as reported by @oecd_report, that the concept of zombie companies is not unique to Japan alone.
 It is also present in the United States, which has a faster metabolization rate (more new listings and exits) relative to Japan.
@@
 
-  This animation was developed using the software based on JavaScript, D3.js (@d3js), and WebGL (@webgl).
+  This animation was developed using software based on JavaScript, D3.js (@d3js), and WebGL (@webgl).
 The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization.
@@
 In the data structure, there are requirements that must be followed for reproducing the animation.
-First, the data set needs to be in the `tidy data` format (@tidy-data).
+First, the data set needs to be in a `tidy data` format (@tidy-data).
 The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well.
@@
 
-  The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package to include the description of an animation.
+  The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (@ggplot2) to include the description of an animation.
 It added new grammar classes to the plot object, allowing it to understand how the plot should change over time.
@@
 As for adjusting the length and speed of the animation, the `nframes` and `fps` arguments can be utilized.
-The `nframes` dictates the number of frames to be rendered, while `fps` controls how many frames are displayed in one second.
+The `nframes` dictate the number of frames to be rendered, while `fps` controls how many frames are displayed in one second.
 Using these two parameters, the duration of the animation in seconds can be calculated as follows: length = nframes/fps.
@@
 
-  The argument for the `anim_prep()` and `anim_prep_cat()` function are listed in the Table `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-num-la}','\\@ref(tab:tbl-num)'))` and `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-cat-la}','\\@ref(tab:tbl-cat)'))` respectively.
+  The arguments for the `anim_prep()` and `anim_prep_cat()` functions are listed in Tables `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-num-la}','\\@ref(tab:tbl-num)'))` and `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-cat-la}','\\@ref(tab:tbl-cat)'))` respectively.
 The `data`, `id`, `values`, and `time` arguments are required for both functions.
@@
 The comprehensive plot is named Kangaroo, while its subset is referred to as Wallaby, representing a smaller version of the Kangaroo.
-The final plot is named after the Funnel Web Spider, drawing parallels between the plot's features and the distinctive legs of the spider.
+The final plot is named after the Funnel Web Spider, drawing inspiration from the plot's features and the distinctive legs of the spider.
 
@@
 
-In the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`) the five grey bars indicate the five categories (Top 25%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018.
+In the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`) the five gray bars indicate the five categories (Top 25%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018.
 Points represent individual companies with color indicating the country of registration.
@@
   In Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006.
-The grey regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018.
+The gray regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018.
 (explain the difference in proportion and not listed companies).

### 2024-02-23 animbook-journal.Rmd
remove log files

@@
 The methods will be suitable generally for data where categorical variables are measured over time, and provide a way to engagingly view changes.
-draft: true
 author:  
@@
 
-rank <- anim_prep(dbl_change, id, values, time, group = gp)
+rank <- anim_prep(dbl_change, id, values, time, 
+                  group = gp)
 
@@
 
-absolute <- anim_prep(dbl_change, id, values, time, group = gp, scaling = "absolute")
+absolute <- anim_prep(dbl_change, id, values, time, 
+                      group = gp, 
+                      scaling = "absolute")
 
@@
 
-rank_group <- anim_prep(dbl_change, id, values, time, group = gp, group_scaling = gp)
+rank_group <- anim_prep(dbl_change, id, values, time, 
+                        group = gp, 
+                        group_scaling = gp)
 
@@
 
-absolute_group <- anim_prep(dbl_change, id, values, time, group = gp, group_scaling = gp, scaling = "absolute")
+absolute_group <- anim_prep(dbl_change, id, values, time, 
+                            group = gp, 
+                            group_scaling = gp, 
+                            scaling = "absolute")
 

### 2024-02-23 submission/animbook-journal.tex
submission folder

--- 2024-02-14 animbook-journal.tex
@@
 
-The challenge in producing an animation like that in the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated.
+The challenge in producing an animation similar to the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated.
 The complexities include allowing the user to choose the number of categories, standardizing distributions, and allowing the user to input pre-computed categorical data.
@@
 The structure of this paper is as follows.
-The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
-It is followed by sections describing the data format needed, considerations about making animations, and visual design.
-The software and its functions and usage are detailed in the next section.
-The next section illustrates the usage of the software to examine company performance, particularly zombie patterns, and the changing political allegiance of voters in Australia.
-The discussion section summarizes, outlines some limitations, and suggests some future directions.
+The subsequent section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
+It is then followed by sections describing the data format needed, considerations about making animations, and visual design.
+The functions and usage of the software are detailed in the next section.
+Just prior to the final section, the paper illustrates the usage of the software to examine company performance, particularly zombie patterns, and the changing political allegiance of voters in Australia.
+The concluding discussion section summarizes, outlines some limitations, and suggests future directions for the software.
 
@@
 In the visualization, each observation is initially classified into one group at the start and potentially transitions into either the same group or a different group.
-This dynamics visualization constructs questions on the broader use of this visualization to other types of data.
+This dynamic visualization constructs questions on the broader use of this visualization to other types of data.
 The potential use of this visualization on accounting data is to convey a message, as reported by the McGowan, Andrews, and Millot (2017), that the concept of zombie companies is not unique to Japan alone.
-It is also present in the United States, which has a faster metabolize rate (more new listings and exits) relative to Japan.
+It is also present in the United States, which has a faster metabolization rate (more new listings and exits) relative to Japan.
 
 The political data that exhibits the movement of voters switching party affiliations between elections can be a valuable insight into the behavior of the voters.
-This data could be extended to incorporate demographic information about the voters, providing analysts with a significant insight into voter behavior.
-This allows them to consolidate effective campaigns for their political party.
-This also applies to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.
+This data could be extended to incorporate demographic information about the voters, providing analysts with significant insight into voter behavior and allowing them to consolidate effective campaigns for their political party.
+It can also be applied to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.
 
@@
 Hvitfeldt (2018) provides R (R Core Team (2021)) code to generate an animation similar to that of the New York Times.
-Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be use for a variety of similar animations for studying flow and temporal change data.
+Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be used for a variety of similar animations for studying flow and temporal change data.
 
-The New York Times visualization is also similar to what is called a Sankey plot.
+The New York Times visualization is similar to a Sankey plot.
 Sankey plots are flow diagrams that show the movement/change from one category level to another, with the width of each arrow representing the proportional changes between levels.
@@
 
-One of the frequently encountered values in the dataset is NA, commonly known as missing values.
+One of the frequently encountered values in the dataset is NA, commonly known as a missing value.
 In the context of accounting data, NA might signify that a company is either not yet listed or has been de-listed.
@@
 The use of \texttt{transition\_*()} functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time.
-This includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package (Ooms (2023b)) to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package (Ooms (2023a)) to save it into a video file format.
+The \CRANpkg{gganimate} includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package (Ooms (2023b)) to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package (Ooms (2023a)) to save it into a video file format.
 
@@
 
-In the animation, the use of proportional shaded areas serves to enhance the comprehension of proportion information, effectively displaying the distribution within each group.
+The incorporation of proportional shaded areas in this animation package serves to enhance the comprehension of proportion information, effectively displaying the distribution within each group.
 To represent sub-groups, points are colored to focus attention on differences between groups of observation.
@@
 This generalization leads to four different scaling methods for the numerical data.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Ranking by year. (rank)
+\item
+  Ranking by year within a group. (rank\_group)
+\item
+  Fix bins relative to absolute values by year. (absolute)
+\item
+  Fix bins relative to absolute values by year within a group. (absolute\_group)
+\end{enumerate}
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Ranking by year. (rank)
-\item
-  Ranking by year within a group. (rank\_group)
-\item
-  Fix bins relative to absolute values by year. (absolute)
-\item
-  Fix bins relative to absolute values by year within a group. (absolute\_group)
-\end{enumerate}
-
 For the first and second scaling methods, it is necessary to rank the values based on time, and in cases where a group is provided, they are ranked based on both time and groups.
@@
 Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animated data structure.
-It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values.
+It is carried out by assigning a frame to each individual observation, ensuring that each ID does not contain repeated frame values.
 It lets the \CRANpkg{gganimate} or \CRANpkg{plotly} perceive where the observation would be on the plot at a given frame, as seen in Figure \ref{fig:animated-diagram}.
@@
 It includes creating additional data components for labeling and shading.
-This function also responds by interpolating the non-linear path.
+This function is also responsible for interpolating the non-linear path.
 It performs this task by mapping the \texttt{sine()} function provided in this package to each observation using the \texttt{map()} function from the \CRANpkg{purrr} package (Wickham and Henry (2023)).
@@
 
-It is necessary to save the plot as a \texttt{ggplot} object before passing it to the final function, \texttt{anim\_animate()}, to animate.
+It is necessary to store the plot as a \texttt{ggplot} object before passing it to the final function, \texttt{anim\_animate()}, to animate.
 This function will automatically detect which rendering method was specified in the previous steps and add the minimum requirement functions accordingly.
@@
 The \texttt{cat\_change} data in the package is used to illustrate how to use this package.
-It has five categories, A to E, over two-time points.
+It has five categories, A to E, over two time points.
 Since the data is already in the categorized data structure, the \texttt{anim\_prep\_cat()} function is used.
@@
 
-To obtain an object for the animation function, the \texttt{wallaby\_plot} is used.
+To obtain an object for the animation function, the \texttt{wallaby\_plot} function is used.
 The \texttt{subset} and \texttt{relation} arguments are applied to refine the final appearance of the animation, Figure \ref{fig:top-one}.
@@
 The Osiris data presented in this section was acquired from Bureau van Dijk ({``Osiris''} (2023)), compiling information on a total of 122,318 companies.
-It was subsequently a subset for the 2021 report, consisting of 1000 companies with 94 variables.
+It was subsequently subsetted for the 2021 report, consisting of 1000 companies with 94 variables.
 The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018.
@@
 McGowan, Andrews, and Millot (2017) reported that companies in the United States have a faster metabolic rate relative to Japanese companies.
-This means that US companies tend to move up and down performance metrics more frequently than Japanese companies.
+This means that US companies tend to move up and down in the performance metrics more frequently than Japanese companies.
 This can be examined using the wallaby and kangaroo plots.
@@
 Any Japanese companies in the Top 25\% in 2006 did not exit the market (Not listed).
-But actually, there were non-Japanese companies in the Top 25\% in 2006.
+It is worth noting that there are actually none of the Japanese companies in the Top 25\% in 2006.
 It is also interesting that the larger proportion of the companies in the Top 25\% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.
@@
 The package provides the tools to create animations for simple temporal patterns with a few steps, but these visualization methods have some limitations.
-It is primarily for communication rather than exploration because one typically knows what the main patterns are.
+This package is to be used primarily for communication rather than exploration because the end-user typically knows what the main patterns are.
 If there are many categories (quantiles), the display will be too crowded.

### 2024-02-23 submission/animbook-journal.R

@@ -1,0 +1,330 @@
+# Generated by `rjournal_pdf_article()` using `knitr::purl()`: do not edit by hand
+# Please edit animbook-journal.Rmd to modify this file
+
+## ----setup, include=FALSE-----------------------------------------------------
+knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
+
+
+## -----------------------------------------------------------------------------
+library(animbook)
+library(tidyverse)
+
+
+## ----nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package. The animation illustrates the disparity between white men and black men. It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+knitr::include_graphics("figures/NYT.png")
+
+
+## ----data-diagram, fig.cap="The animation expects data with an ID and a time variable, along with a numerical variable (raw form), which is possibly converted to categorical (categorized). The data can be provided in the raw or categorized form and will be processed into the format needed for the animation, where the categorical variable is treated as a quantile and an animation frame variable is created.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+knitr::include_graphics("figures/data-diagram.png")
+
+
+## ----animation-diagram, fig.cap="An animation requires small changes shown in quick succession to make it appear as if the objects are in motion. The three plots above show a single point changing position by a small amount, which when shown quickly, will look like that point has moved up and to the right.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+knitr::include_graphics("figures/animation-diagram.png")
+
+
+## ----animated-diagram, fig.cap="Frames 1 and 2 show the year 1 and year 2 positions of points from the data in the table at the top. The id is necessary to enable interpolation to make the small changes to generate a perception of motion from frame 1 position to frame 2 position.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+knitr::include_graphics("figures/animated-diagram.png")
+
+
+## ----proportional-shade, fig.show="hold", out.width="50%", fig.cap="The plot shows the difference between the sigmoid (left) and the sine curve (right). In the sigmoid, as the curve progresses, it appears to become narrower, possibly resulting in more misperception of relative proportions compared to the sine curve."----
[…]

### 2024-03-14 submission/animbook-journal.Rmd
modified the submission folder

--- 2024-02-23 animbook-journal.Rmd
@@
 
-```{r catchange-gif, out.extra="class = 'gif'", fig.cap = "Animated visualization using example data.
+```{r catchange-gif, fig.cap = "Animated visualization using example data.
 All of the X observations stay within the same group, while some of the Y observations change from group A to group E.", eval=knitr::is_html_output()}
-knitr::include_graphics("figures/catchange.gif")
+knitr::include_url("https://www.youtube.com/embed/j-azl7vKjwo")
 ```
@@
 
-```{r kan-osiris-gif, out.extra="class = 'gif'", fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database.
+```{r kan-osiris-gif, fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database.
 The 'not listed' category indicates companies not yet listed or removed from the listing.
@@
 Most of the movement is made by American companies, which supports the OECD report that US companies have a higher turnover rate relative to Japanese companies.", eval=knitr::is_html_output()}
-knitr::include_graphics("figures/kan-osiris.gif")
+knitr::include_url("https://www.youtube.com/embed/xB9DK5efEL8")
 ```
@@
 
-```{r osiris-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows the companies that exited the market.
+```{r osiris-gif, fig.cap = "The wallaby plot visualization shows the companies that exited the market.
 There are more United States companies that fall down into a not listed group (got de-listed) compared to Japanese companies.", eval=knitr::is_html_output()}
-knitr::include_graphics("figures/exit.gif")
+knitr::include_url("https://www.youtube.com/embed/TIWtFf6KaCI")
 ```
@@
 
-```{r voter-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows how the top party performs in keeping the old voters of different genders.
+```{r voter-gif, fig.cap = "The wallaby plot visualization shows how the top party performs in keeping the old voters of different genders.
 Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.
 Interestingly, the few individuals who identified as neither male nor female overwhelmingly shifted their party affiliations to the Greens.", eval=knitr::is_html_output()}
-knitr::include_graphics("figures/voter.gif")
+knitr::include_url("https://www.youtube.com/embed/6afmJ0sxvtc")
 ```

### 2025-03-20 response_to_review.qmd
start of changes in response to review

---
title: "Response to Review"
subtitle: "animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation"
author: "Krisanat Anukarnsakulchularp, Dianne Cook"
format: pdf
---

We thank the editor and reviewers for reading and offering improvements for our article. These are the changes we have made in response. *The reviewer comment is in italics*, and our response is regular text.

## Reviewer 2

### *General*

*The article explores the use of animated ggplot2 plots with the animbook package. This package was inspired by an animated graphic from the New York Times and has the benefit of helping to visualize trends over time. The package takes a three stage approach, using a data cleaning step, then graphing step, and finally an animation step. The end result is an animated graphic that shows the relationship of categorical data over time.*

Response:

### *Detailed comments*

*Overall, the authors did a good job at guiding the narrative in a logical fashion. One major recurring theme that I noticed was that paragraphs tended to be short and had uneven transitions. My comments are below and follow the progression of the paper.*

- *Page 1, second paragraph: this paragraph is really short and would benefit by describing the animation in detail.*

Response:

- *Page 2, paragraph starting with Hvitfeldt: it might be helpful to include parts of the example from Hvitfeldt, or at least describe what parts of the example inspired animbook*

Response:

- *Page 2, paragraph starting with "In the data structure": I suggest a little more pretext for the example of company name and where the company is registered. Or state the purpose of ID and grouping before giving a cohesive example.*

Response:

- *Page 3, paragraph starting with "One of the frequently": I was initially confused about how NA were handled, but it was clearer later in the paper that NA became its own category.*

Response:

- *Page 3, paragraph starting with "A principle important": switch to "An important principle"*

Response:

- *Page 3, paragraph starting with "There are multiple": avoid single sentence paragraphs. This could be included at the end of the previous paragraph to make a cleaner transition.*

Response:

- *Page 4, paragraphs 2 and 3: these paragraphs could be combined*

Response:

- *Page 5, paragraph 2: I don't think that redundancy needs to be capitalized here*

Response:

- *Page 5, last paragraph of section 5: "As illustrated in Figure 5." is left as its own sentence, but should be included with the surrounding sentence.*

Response:

- *Page 5, last sentence: change "Github" to "GitHub". Also, it would be helpful to include the GitHub link here as well.*

Response:

- *Page 6, Data pre-processing section: "ranking the sales" should be replaced with "ranking the observations".*

Response:

- *Page 6: the sentence with "When the observation", can be improved for clarity ("When an observation is moved up by a quantile, another one is bound to ...")*

Response:

- *Page 6: Place tibble into table with a caption*

Response:

- *Page 7, first paragraph: replace "from the raw into" to "from the raw format into"*

Response:

- *Page 7, 3rd paragraph: include this information in another paragraph to help transitions.*

Response:

- *Page 7, 3rd and 4th paragraphs: the time_dependent argument only appears in the _plot() functions, so it should be mentioned in the later section.*

Response:

- *Page 8, table 2: "argumenst" should be "arguments"*

Response:

- *Page 8, paragraph 2/3: the proportional_shade() function can be discussed solely in one paragraph for better transition.*

Response:

- *Page 8, paragraph 4: should "wallaby's plot" be "wallaby plot"?*

Response:

- *Page 8, last paragraph: state that the data is included in the animbook package.*

Response:

- *Page 9: remove comma after "Figure 7"*

Response:

- *Page 10, applications: include sources at the first mention of each example.*

Response:

- *Page 13: use consistent naming for the plot objects (kan_p vs. p)*

Response:

- *Page 15, paragraph starting with "In Figure 11": There is a sentence prompt that should be filled in "(explain the difference in proportion ...)"*

Response:

- *Page 16, the two paragraphs before discussion: the second paragraph leads to explanation from the previous paragraph, so these ideas should stay together in one paragraph.*

Response:

- *Page 18: There is a reference starting with "---------" that should be filled in.*

Response:

- *An example with the funnel_web_plot() would be a nice addition in the applications section.*

Response:

## Code

*Usability:*

- *Page 6: it states that users can specify breaks on a 0 to 1 scale. Is there a reason why users can't provide breaks on the raw data scale and have the function transforms the values to fit the 0 and 1 scale?*

Response:

- *Page 8: could the last_plot() function be used by default so that users don't have to save the plot into a ggplot2 object?*

Response:

- *In the wallaby plot, the applicable points move from all categories to a single category (or vice versa). Is there a way to choose which single category gets used?*

*Code:*

- *When using custom breaks, the error displays "The breaks vector must have the same number of groups as ncat argument", but it is stated in the article that the length of breaks need to equal the number of categories plus 1.*

Response:

- *When running the code on an M1 MacBook Pro, some of the shaded sections tear apart and look like white circles. This happens particularly with the wallaby plots.*

Response:

### *Other comments:*

- *Are there plans to include additional visuals to help keep track of the points as they disappear? In the NYT article, the points are summed and proportions are calculated as the points reach the right side of the plot and I think this would be a nice addition in the future.*

Response:

- *When there are many data points, it becomes difficult track the general movement of observations. Would there be any options to trace the paths to show where the points have moved (like a line with low alpha)?*

Response:

- *Overall, I really like this package!*

Response: Thank you!

## Reviewer 3

### *General*

*The paper presents a graphical tool for visualizing changes in some measurements over time. It also allows for multiple groups to appear in the Figure. At first glance, this sounds like a useful tool. Me personally, I was not amazed by this tool simply because of the lack of simplicity and straightforward interpretation. On the positive side, the paper is very professionally written, but it is not that easy to follow.*

Response:

### Detailed comments

*1. Figure 1 for instance. What is the interpretation of this figure? I struggled to understand and did not manage to do so.*

Response:

*2. Figures 2 and 4. Since the data entered in R are numerical or categorical values, what is the use of these figures? Why should the reader be informed of the raw, handwritten data?*

Response:

*3. I have spotted a few grammatical errors:*

*a) First paragraph after Figure 1. “This data…” > “These data…”. The word data is plural, the singular form is datum.*

Response:

*b) Beginning of Section 5. Please delete the letters “R. E.” from the reference of Mayer and Moreno (2002).*

Response:

*c) Page 13. First paragraph, 3rd and 4rth lines probably have a typo (“…and japan”).*

Response:

*4. The description you give for Figure 10 helps the reader understand the meaning of this plot. But, in the example in the R package with the aeles dataset, things are not so obvious. There are many observations that mask the visibility of the points.Also, what do the X and Y mean?*

Response:

*5. Why do the authors write “I acknowledge…” and not “We…” in the acknowledgements?*

Response:

### *Code*

*I did not find the commands in the package very user-friendly. For instance, to produce a plot I must go through many functions, prior to typing the plot to appear. The example in the aeles dataset is such a case. I need to type 4 commands in order to see a plot, which I repeat, cannot understand, nor interpret easily. I would prefer a function that does all this preprocessing and plots the data. Legends are missing, and in my opinion, the help files are not very helpful for someone who wants to use this package easily, to visualize their data.*

Response:

### 2025-04-29 response_to_review.qmd
Reviwer 2 page 13

@@
 ---
+
+Put in alt-text
+
+Write short response
 
@@
 
-Response:
+Response: Nothing to change.
 
@@
 
-Response:
+Response: We have added a short description of the New York Times animation.
 
@@
 
-Response:
+Response: We have emphasized that his example code that reproduces the New York Times visualization inspires this package.
 
@@
 
-Response:
+Response: ??? I have added US and Japan as an example, not sure what else can be added.
 
@@
 
-Response:
+Response: We have make it more clear in this paragraph.
 
@@
 
-Response:
+Response: Fixed
 
@@
 
-Response:
+Response: Fixed and switching the order.
 
@@
 
-Response:
+Response: ???
 
@@
 
-Response:
+Response: ??? I feel like the function should be mentioned first in the second paragraph. The third paragraph is mainly about the function algorithm.
 
@@
 
-Response:
+Response: Be more clear (you should be able to)
 
@@
 - *In the wallaby plot, the applicable points move from all categories to a single category (or vice versa). Is there a way to choose which single category gets used?*
+
+Response: Be more clear
 
@@
 
-Response:
+Response: Make it clear.
 
@@
 
-Response:
+Response: Describe what do we learn.
 
@@
 
-Response:
+Response: Not change, this image is important base on discussion with user. (see how other use the package). (be more forceful)
 
@@
 
-Response:
+Response: Just change.
 
@@
 
-Response:
+Response: All referencing are automated and the style is consistent with the R journal style so we have no control over this.
 
@@
 
-Response:
+Response: Just change
 
@@
 
-Response:
+Response: Add detail for X and Y.
 
@@
 
-Response:
+Response: Fix helpfile.

### 2025-04-29 animbook-journal.Rmd
Reviwer 2 page 13

@@
 output: 
+  rjtools::rjournal_pdf_article:
+    toc: no
   rjtools::rjournal_web_article:
@@
 
-  The New York Times provided a possible solution in the article titled "Extensive data show punishing reach of racism for black boys" (@the_new_york_time) to tell the story of how racism appears to inhibit socioeconomic change.
+  The New York Times provided a possible solution in the article titled "Extensive data show punishing reach of racism for black boys" (@the_new_york_time) to tell the story of how racism appears to inhibit socioeconomic change represent using the animation showing an individual transition from one category to another.
 This animation is the motivation for the new visualization presented here to be applied generally.
@@
 
-  @Hvitfeldt_2018 provides R (@r) code to generate an animation similar to that of the New York Times.
-Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be used for a variety of similar animations for studying flow and temporal change data.
+  @Hvitfeldt_2018 provides R (@r) code to reproduce an animation similar to that of the New York Times.
+Taking inspiration from this coding example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be used for a variety of similar animations for studying flow and temporal change data.
 
@@
 In the data structure, there are requirements that must be followed for reproducing the animation.
-First, the data set needs to be in a `tidy data` format (@tidy-data).
+First, the dataset needs to be in a `tidy data` format (@tidy-data).
 The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well.
 The ID variable indicates the individual, which is followed over time, such as the company name.
-There may also be a grouping variable, such as the country where the company is registered.
+There may also be a grouping variable, such as the country where the company is registered (United States and Japan).
 
@@
 Disregarding NA values could result in the loss of valuable information.
-Therefore, instead of completely removing NA entries, this information is categorized into its quantiles, ensuring that the missing data are factored into the visualization.
+Therefore, instead of completely removing NA entries, it will get converted into its own quantiles, ensuring that the missing data are factored into the visualization.
 
@@
 
-A principle important for designing a useful animation is called persistence of vision (@animation-mechanic).
+An principle important for designing a useful animation is called persistence of vision (@animation-mechanic).
 When an image disappears, the brain will retain the previous images for a brief period of time.
@@
 This is illustrated in Figure \@ref(fig:animation-diagram).
-
 There are multiple ways to create an animation in the R environment (@r), including the packages \CRANpkg{gganimate} (@gganimate) and \CRANpkg{plotly} (@plotly).
@@
 
-  In the context of data, as shown in Figure \@ref(fig:animated-diagram), observations are positioned at specific points in time.
+  Figure \@ref(fig:animated-diagram) demonstrates how the frame variables are applied in an animated plot.
+The frame variable within the animated data structure allows the animation function to determine the position of observations on the plot at any given frame.
+These observations are positioned at specific points in time.
 The further the distance between these points, the less smooth the animation becomes.
@@
 In the \CRANpkg{gganimate} package, the interpolation is achieved using the \CRANpkg{tweenr} package (@tweenr), while in \CRANpkg{plotly}, it utilizes d3.interpolate (@d3js).
-
-  Figure \@ref(fig:animated-diagram) demonstrates how the frame variables are applied in an animated plot.
-The frame variable within the animated data structure allows the animation function to determine the position of observations on the plot at any given frame.
 
@@
 However, @Shaffer_2019 argues that a sine curve more accurately represents proportion throughout the path.
-As illustrated in Figure \@ref(fig:proportional-shade).
-The sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.
+As illustrated in Figure \@ref(fig:proportional-shade), the sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.
 New interpolation functions are needed to compute both the sigmoid and sine paths.
@@
 
-\CRANpkg{animbook} is available through CRAN. The development version of this package can be found in the Github repositories.
+\CRANpkg{animbook} is available through CRAN.
+The development version of this package can be found in the GitHub repositories at [https://github.com/KrisanatA/animbook](https://github.com/KrisanatA/animbook).
 
@@
 From Figure \@ref(fig:data-diagram), there is a need to map numerical value to a category.
-One way to handle this is by ranking the sales and grouping the rankings into quantiles.
-In some cases, this may not be the best option.
-When the observation is moved up by quantile, one is bound to move down, making the amount of observation in the quantile remain the same.
+One way to handle this is by ranking the observation and grouping the rankings into quantiles.
+In some cases, this may not be the best option because when an observation is moved up by a quantile, another one is bound to move down, making the amount of observation in the quantile remain the same.
 This issue can be resolved by using an alternative method, which is grouping values based on their absolute values.
@@
 ```{r}
-original |> 
+scaling_table <- original |> 
   left_join(rank_data, by = c("id", "time", "gp")) |> 
@@
   reframe(id, time, gp, values, rank, rank_group, absolute, absolute_group)
+```
+
+```{r tbl-scaling, eval=knitr::is_html_output()}
+scaling_table |> 
+  knitr::kable(caption = "A summary of different scaling methods applied to the dataset.")
+```
+
+```{r tbl-scaling-la, eval=knitr::is_latex_output()}
+scaling_table |> 
+  knitr::kable(caption = "A summary of different scaling methods applied to the dataset.") |> 
+  kableExtra::column_spec(8, width = "30em")
 ```
@@
   These are only the initial steps in formatting the data into a category.
-Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animated data structure.
+Now that there is a method to transform the data from the raw format into a categorized format, the next step is to modify it into an animated data structure.
 It is carried out by assigning a frame to each individual observation, ensuring that each ID does not contain repeated frame values.
@@
 argument_num_tab |> 
-  kableExtra::kable(caption = "The argumenst for the anim\\_prep\\_cat function.", format = "latex") |> 
+  kableExtra::kable(caption = "The arguments for the anim\\_prep\\_cat function.", format = "latex") |> 
   kableExtra::column_spec(2, width = "30em")
@@
 The `data`, `id`, `values`, and `time` arguments are required for both functions.
-
 The `ncat`, `breaks`, `group_scaling`, and `scaling` arguments are for the user to customize the data scaling calculation in the `anim_prep()` function.
 In the `anim_prep_cat` function, the users can customize the order of the category to be shown on the y-axis using the `order` argument.
-
-  Then, for further customization regarding how the final visualization looks. The `group`, `label`, and `time_dependent` arguments can be adjusted.
+Then, for further customization regarding how the final visualization looks.
+The `group`, `label`, and `time_dependent` arguments can be adjusted.
 
@@
 
-The `cat_change` data in the package is used to illustrate how to use this package.
+The `cat_change` data in the \CRANpkg{animbook} package is used to illustrate how to use this package.
 It has five categories, A to E, over two time points.
@@
 
-Figure \@ref(fig:top-many), shows the flexibility to use various options, such as `subset` or `relation`, to customize the plot appearance.
+Figure \@ref(fig:top-many) shows the flexibility to use various options, such as `subset` or `relation`, to customize the plot appearance.
 Here `subset = "top"` is used to specify category A for the final time point, and `relation = "many_one"` is used to specify that all categories flowing into A at time point 2 are shown.

### 2025-04-29 animbook-journal.tex
Reviwer 2 page 13

@@
 % !TeX root = RJwrapper.tex
-\title{animbook: Visualizing changes in performance measures and demographic affiliations using animation}
+\title{animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation}
+
 \author{by Krisanat Anukarnsakulchularp and Dianne Cook}
@@
 Between elections, voters often switch party preferences, which produces categorical values over time.
-Inspired by the animation in the New York Times article ``Extensive data show punishing reach of racism for black boys,'' we provide new visualization functions to generate animations that display this type of data in an R package called \CRANpkg{animbook}.
+Inspired by the animation in the New York Times article ``Extensive data show punishing reach of racism for black boys,'' we provide new visualization functions to generate animations that display this type of data in an R package called animbook.
 Functions to pre-process the data and prepare it for the animation are provided.
@@
 
-\hypertarget{intro}{%
-\section{Introduction}\label{intro}}
+\section{Introduction}\label{intro}
 
-The concept of ``zombie companies'' began to attract attention when Caballero, Hoshi, and Kashyap (2008) reported on their proliferation in Japan.
+The concept of ``zombie companies'' began to attract attention when \citet{zombie_companies_2008} reported on their proliferation in Japan.
 Zombie companies are those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy.
@@
 
-The New York Times provided a possible solution in the article titled ``Extensive data show punishing reach of racism for black boys'' (Badger et al.
-(2018)) to tell the story of how racism appears to inhibit socioeconomic change.
+The New York Times provided a possible solution in the article titled ``Extensive data show punishing reach of racism for black boys'' (\citet{the_new_york_time}) to tell the story of how racism appears to inhibit socioeconomic change represent using the animation showing an individual transition from one category to another.
 This animation is the motivation for the new visualization presented here to be applied generally.
 
-The challenge in producing an animation like that in the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated.
+The challenge in producing an animation similar to the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated.
 The complexities include allowing the user to choose the number of categories, standardizing distributions, and allowing the user to input pre-computed categorical data.
@@
 The structure of this paper is as follows.
-The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
-It is followed by sections describing the data format needed, considerations about making animations, and visual design.
-The software and its functions and usage are detailed in the next section.
-The next section illustrates the usage of the software to examine company performance, particularly zombie patterns, and the changing political allegiance of voters in Australia.
-The discussion section summarizes, outlines some limitations, and suggests some future directions.
+The subsequent section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies.
+It is then followed by sections describing the data format needed, considerations about making animations, and visual design.
+The functions and usage of the software are detailed in the next section.
+Just prior to the final section, the paper illustrates the usage of the software to examine company performance, particularly zombie patterns, and the changing political allegiance of voters in Australia.
+The concluding discussion section summarizes, outlines some limitations, and suggests future directions for the software.
 
-\hypertarget{NYTvis}{%
-\section{Explanation of the New York Times visualization}\label{NYTvis}}
+\section{Explanation of the New York Times visualization}\label{NYTvis}
 
@@
 
-The interactive chart featured in the New York Times article (Figure \ref{fig:nyt}) unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the Chetty et al.
-(2020).
+The interactive chart featured in the New York Times article (Figure \ref{fig:nyt}) unveils the issue of income disparities between black and white children who were raised in families with comparable income according to \citet{race}.
 This visualization reveals that, compared to white children, black children are more likely to drop down to the lower-income group, given that they both grew up in wealthy families.
@@
 In the visualization, each observation is initially classified into one group at the start and potentially transitions into either the same group or a different group.
-This dynamics visualization constructs questions on the broader use of this visualization to other types of data.
-The potential use of this visualization on accounting data is to convey a message, as reported by the McGowan, Andrews, and Millot (2017), that the concept of zombie companies is not unique to Japan alone.
-It is also present in the United States, which has a faster metabolize rate (more new listings and exits) relative to Japan.
+This dynamic visualization constructs questions on the broader use of this visualization to other types of data.
+The potential use of this visualization on accounting data is to convey a message, as reported by \citet{oecd_report}, that the concept of zombie companies is not unique to Japan alone.
+It is also present in the United States, which has a faster metabolization rate (more new listings and exits) relative to Japan.
 
 The political data that exhibits the movement of voters switching party affiliations between elections can be a valuable insight into the behavior of the voters.
-This data could be extended to incorporate demographic information about the voters, providing analysts with a significant insight into voter behavior.
-This allows them to consolidate effective campaigns for their political party.
-This also applies to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.
+This data could be extended to incorporate demographic information about the voters, providing analysts with significant insight into voter behavior and allowing them to consolidate effective campaigns for their political party.
+It can also be applied to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.
 
-This animation was developed using the software based on JavaScript, D3.js (Bostock (2012)), and WebGL (Mozilla Foundation (2011)).
+This animation was developed using software based on JavaScript, D3.js (\citet{d3js}), and WebGL (\citet{webgl}).
 The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization.
@@
 
-Hvitfeldt (2018) provides R (R Core Team (2021)) code to generate an animation similar to that of the New York Times.
-Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be use for a variety of similar animations for studying flow and temporal change data.
+\citet{Hvitfeldt_2018} provides R (\citet{r}) code to reproduce an animation similar to that of the New York Times.
+Taking inspiration from this coding example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be used for a variety of similar animations for studying flow and temporal change data.
 
-The New York Times visualization is also similar to what is called a Sankey plot.
+The New York Times visualization is similar to a Sankey plot.
 Sankey plots are flow diagrams that show the movement/change from one category level to another, with the width of each arrow representing the proportional changes between levels.
@@
 
-\hypertarget{data}{%
-\section{Data}\label{data}}
+\section{Data}\label{data}
 
@@
 In the data structure, there are requirements that must be followed for reproducing the animation.
-First, the data set needs to be in the \texttt{tidy\ data} format (Wickham (2014)).
+First, the dataset needs to be in a \texttt{tidy\ data} format (\citet{tidy-data}).
 The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well.
 The ID variable indicates the individual, which is followed over time, such as the company name.
-There may also be a grouping variable, such as the country where the company is registered.
+There may also be a grouping variable, such as the country where the company is registered (United States and Japan).
 
@@
 Disregarding NA values could result in the loss of valuable information.
-Therefore, instead of completely removing NA entries, this information is categorized into its quantiles, ensuring that the missing data are factored into the visualization.
+Therefore, instead of completely removing NA entries, it will get converted into its own quantiles, ensuring that the missing data are factored into the visualization.
 
-\hypertarget{animation}{%
-\section{Animation tools}\label{animation}}
+\section{Animation tools}\label{animation}
 
@@
 
-A principle important for designing a useful animation is called persistence of vision (Webster (2005)).
+An principle important for designing a useful animation is called persistence of vision (\citet{animation-mechanic}).
 When an image disappears, the brain will retain the previous images for a brief period of time.
@@
 This is illustrated in Figure \ref{fig:animation-diagram}.
+There are multiple ways to create an animation in the R environment (\citet{r}), including the packages \CRANpkg{gganimate} (\citet{gganimate}) and \CRANpkg{plotly} (\citet{plotly}).
 
-There are multiple ways to create an animation in the R environment (R Core Team (2021)), including the packages \CRANpkg{gganimate} (Pedersen and Robinson (2020)) and \CRANpkg{plotly} (Sievert (2020)).
-
-The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package to include the description of an animation.
+The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (\citet{ggplot2}) to include the description of an animation.
 It added new grammar classes to the plot object, allowing it to understand how the plot should change over time.
 The use of \texttt{transition\_*()} functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time.
-This includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package (Ooms (2023b)) to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package (Ooms (2023a)) to save it into a video file format.
+The \CRANpkg{gganimate} includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package (\citet{gifski}) to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package (\citet{av}) to save it into a video file format.
 
@@
 
-In the context of data, as shown in Figure \ref{fig:animated-diagram}, observations are positioned at specific points in time.
+Figure \ref{fig:animated-diagram} demonstrates how the frame variables are applied in an animated plot.
+The frame variable within the animated data structure allows the animation function to determine the position of observations on the plot at any given frame.
+These observations are positioned at specific points in time.
 The further the distance between these points, the less smooth the animation becomes.
 This issue can be eliminated by interpolating additional points in between the observations.
-In the \CRANpkg{gganimate} package, the interpolation is achieved using the \CRANpkg{tweenr} package (Pedersen (2022)), while in \CRANpkg{plotly}, it utilizes d3.interpolate (Bostock (2012)).
+In the \CRANpkg{gganimate} package, the interpolation is achieved using the \CRANpkg{tweenr} package (\citet{tweenr}), while in \CRANpkg{plotly}, it utilizes d3.interpolate (\citet{d3js}).
 
-Figure \ref{fig:animated-diagram} demonstrates how the frame variables are applied in an animated plot.
-The frame variable within the animated data structure allows the animation function to determine the position of observations on the plot at any given frame.
-
-From Hasler, Kersten, and Sweller (2007), it suggests that having control options for the animation can improve the efficiency of the learning process.
+From \citet{learner-control}, it suggests that having control options for the animation can improve the efficiency of the learning process.
 Additionally, the length and speed of the animation should also be taken into consideration.
-According to R.
-Mayer (2010), the working memory, responsible for selecting and processing information from sensory memory, only holds a processed version of what was presented for generally less than thirty seconds.
+According to \citet{mayer-2010}, the working memory, responsible for selecting and processing information from sensory memory, only holds a processed version of what was presented for generally less than thirty seconds.
 
@@
 As for adjusting the length and speed of the animation, the \texttt{nframes} and \texttt{fps} arguments can be utilized.
-The \texttt{nframes} dictates the number of frames to be rendered, while \texttt{fps} controls how many frames are displayed in one second.
+The \texttt{nframes} dictate the number of frames to be rendered, while \texttt{fps} controls how many frames are displayed in one second.
 Using these two parameters, the duration of the animation in seconds can be calculated as follows: length = nframes/fps.
@@
 
-\hypertarget{design}{%
-\section{Visualization design}\label{design}}
+\section{Visualization design}\label{design}
 
-The animated visualization can be an effective communication tool (R.
-E.
-Mayer and Moreno (2002); Robertson et al.
-(2008)).
+The animated visualization can be an effective communication tool (\citet{Mayer_Moreno_2002}; \citet{effective-trend}).
 It helps with communicating changing data values, enhancing the narrative, and keeping it engaging for the audience.
-According to R.
-E.
-Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.
+According to \citet{Mayer_Moreno_2002}, animation can improve learning, especially when the goal is to promote deep understanding.
 
-R.
-E.
-Mayer (2005) states that designing multimedia requires the designer to understand how people learn.
-One of the principles in R.
-E.
-Mayer (2005), Redundancy, suggests that a piece of excess information could overload the learners.
+\citet{mayer_2005} states that designing multimedia requires the designer to understand how people learn.
+One of the principles in \citet{mayer_2005}, Redundancy, suggests that a piece of excess information could overload the learners.
 By this principle, the animation must be carefully designed to avoid this pitfall.
@@
 Our animation needs a non-linear path to show the flow.
-Sigmoid curves are commonly used in Sankey diagrams (Hvitfeldt (2018)).
-However, Shaffer (2019) argues that a sine curve more accurately represents proportion throughout the path.
-As illustrated in Figure \ref{fig:proportional-shade}.
-The sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.
+Sigmoid curves are commonly used in Sankey diagrams (\citet{Hvitfeldt_2018}).
+However, \citet{Shaffer_2019} argues that a sine curve more accurately represents proportion throughout the path.
+As illustrated in Figure \ref{fig:proportional-shade}, the sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.
 New interpolation functions are needed to compute both the sigmoid and sine paths.
 
-\hypertarget{software}{%
-\section{Software}\label{software}}
+\section{Software}\label{software}
 
-\hypertarget{installation}{%
-\subsection{Installation}\label{installation}}
+\subsection{Installation}\label{installation}
 
-\CRANpkg{animbook} is available through CRAN. The development version of this package can be found in the Github repositories.
+\CRANpkg{animbook} is available through CRAN. The development version of this package can be found in the GitHub repositories at \url{https://github.com/KrisanatA/animbook}.
 
@@
 
-\hypertarget{overview-of-functions}{%
-\subsection{Overview of functions}\label{overview-of-functions}}
+\subsection{Overview of functions}\label{overview-of-functions}
 
@@
 
-\hypertarget{data-pre-processing}{%
-\subsubsection{Data pre-processing}\label{data-pre-processing}}
+\subsubsection{Data pre-processing}\label{data-pre-processing}
 
 From Figure \ref{fig:data-diagram}, there is a need to map numerical value to a category.
-One way to handle this is by ranking the sales and grouping the rankings into quantiles.
-In some cases, this may not be the best option.
-When the observation is moved up by quantile, one is bound to move down.
+One way to handle this is by ranking the observation and grouping the rankings into quantiles.
+In some cases, this may not be the best option because when an observation is moved up by a quantile, another one is bound to move down, making the amount of observation in the quantile remain the same.
 This issue can be resolved by using an alternative method, which is grouping values based on their absolute values.
@@
 This generalization leads to four different scaling methods for the numerical data.
-
-\begin{verbatim}
-#> # A tibble: 12 x 8
-#>    id     time gp    values  rank rank_group absolute absolute_group
-#>    <fct> <int> <fct>  <dbl> <int>      <int>    <int>          <int>
-#>  1 1      2020 X      4255.     3          3        3              3
-#>  2 1      2023 X      3357.     2          2        4              4
-#>  3 14     2020 X      6763.     2          2        2              2
-#>  4 14     2023 X      1197.     4          5        5              5
-#>  5 100    2020 X      6864.     2          2        2              2
-#>  6 100    2023 X      2321.     3          3        4              4
-#>  7 21     2020 Y       698.     5          5        5              5
-#>  8 21     2023 Y      3970.     2          2        4              3
-#>  9 106    2020 Y      4110.     3          3        3              3
-#> 10 106    2023 Y      2866.     3          3        4              4
-#> 11 148    2020 Y      7174.     2          2        2              2
-#> 12 148    2023 Y      4217.     1          1        3              3
-\end{verbatim}
 
@@
 
+\begin{table}
+
+\caption{\label{tab:tbl-scaling-la}A summary of different scaling methods applied to the dataset.}
+\centering
+\begin{tabular}[t]{l|>{\raggedleft\arraybackslash}p{30em}|l|r|r|r|r|r}
+\hline
+id & time & gp & values & rank & rank\_group & absolute & absolute\_group\\
+\hline
+1 & 2020 & X & 4254.6677 & 3 & 3 & 3 & 3\\
+\hline
+1 & 2023 & X & 3357.0312 & 2 & 2 & 4 & 4\\
+\hline
+14 & 2020 & X & 6763.4772 & 2 & 2 & 2 & 2\\
+\hline
+14 & 2023 & X & 1197.4183 & 4 & 5 & 5 & 5\\
+\hline
+100 & 2020 & X & 6864.4950 & 2 & 2 & 2 & 2\\
+\hline
+100 & 2023 & X & 2321.3183 & 3 & 3 & 4 & 4\\
+\hline
+21 & 2020 & Y & 698.2479 & 5 & 5 & 5 & 5\\
+\hline
+21 & 2023 & Y & 3970.0503 & 2 & 2 & 4 & 3\\
+\hline
+106 & 2020 & Y & 4109.6530 & 3 & 3 & 3 & 3\\
+\hline
+106 & 2023 & Y & 2865.6471 & 3 & 3 & 4 & 4\\
+\hline
+148 & 2020 & Y & 7173.7712 & 2 & 2 & 2 & 2\\
+\hline
+148 & 2023 & Y & 4217.4130 & 1 & 1 & 3 & 3\\
+\hline
+\end{tabular}
+\end{table}
+
 For the first and second scaling methods, it is necessary to rank the values based on time, and in cases where a group is provided, they are ranked based on both time and groups.
@@
 
-All of these scaling methods utilized the \texttt{cut()} function from the base R package (R Core Team (2021)) to split the values into quantiles.
+All of these scaling methods utilized the \texttt{cut()} function from the base R package (\citet{r}) to split the values into quantiles.
 The \texttt{cut()} function requires the specification of the \texttt{breaks} argument.
@@
 The frame variable is assigned by sorting the data based on the ID and time using the \texttt{arrange()} function, followed by applying the \texttt{group\_by()} function on the ID, allowing the \texttt{row\_number()} function to be performed within each group.
-The functions mentioned in this paragraph are from the \CRANpkg{dplyr} package (Wickham et al.
-(2023)).
+The functions mentioned in this paragraph are from the \CRANpkg{dplyr} package (\citet{dplyr}).
 These are done by the internal function for each of the plots provided in the packages.
@@
 
-The argument for the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} function are listed in the Table \ref{tab:tbl-num-la} and \ref{tab:tbl-cat-la} respectively.
+The arguments for the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} functions are listed in Tables \ref{tab:tbl-num-la} and \ref{tab:tbl-cat-la} respectively.
 The \texttt{data}, \texttt{id}, \texttt{values}, and \texttt{time} arguments are required for both functions.
@@
 
-\hypertarget{plotting-function}{%
-\subsubsection{Plotting function}\label{plotting-function}}
+\subsubsection{Plotting function}\label{plotting-function}
 
@@
 It includes creating additional data components for labeling and shading.
-This function also responds by interpolating the non-linear path.
-It performs this task by mapping the \texttt{sine()} function provided in this package to each observation using the \texttt{map()} function from the \CRANpkg{purrr} package (Wickham and Henry (2023)).
+This function is also responsible for interpolating the non-linear path.
+It performs this task by mapping the \texttt{sine()} function provided in this package to each observation using the \texttt{map()} function from the \CRANpkg{purrr} package (\citet{purrr}).
 The frame is recalculated using the same method mentioned in the data preprocessing section.
@@
 
-\hypertarget{animating-function}{%
-\subsubsection{Animating function}\label{animating-function}}
+\subsubsection{Animating function}\label{animating-function}
 
-It is necessary to save the plot as a \texttt{ggplot} object before passing it to the final function, \texttt{anim\_animate()}, to animate.
+It is necessary to store the plot as a \texttt{ggplot} object before passing it to the final function, \texttt{anim\_animate()}, to animate.
 This function will automatically detect which rendering method was specified in the previous steps and add the minimum requirement functions accordingly.
@@
 
-\hypertarget{example-usage}{%
-\subsection{Example usage}\label{example-usage}}
+\subsection{Example usage}\label{example-usage}
 
 The \texttt{cat\_change} data in the package is used to illustrate how to use this package.
-It has five categories, A to E, over two-time points.
+It has five categories, A to E, over two time points.
 Since the data is already in the categorized data structure, the \texttt{anim\_prep\_cat()} function is used.
@@
 
-\hypertarget{applications}{%
-\section{Applications}\label{applications}}
+\section{Applications}\label{applications}
 
-Two examples of usage are provided.
+Two real-world examples of usage are provided.
 The osiris example studies company movement between quartiles of sales performance over a 12-year period.
-The voting example studies party preference changes between 2016 and 2019 elections.
+The voting example studies party preference changes between the 2016 and 2019 elections.
 
-\hypertarget{accounting-database-osiris}{%
-\subsection{Accounting database: osiris}\label{accounting-database-osiris}}
+\subsection{Accounting database: osiris}\label{accounting-database-osiris}
 
-The Osiris data presented in this section was acquired from Bureau van Dijk ({``Osiris''} (2023)), compiling information on a total of 122,318 companies.
-It was subsequently a subset for the 2021 report, consisting of 1000 companies with 94 variables.
+The Osiris data presented in this section was acquired from Bureau van Dijk (\citet{bvd}), compiling information on a total of 122,318 companies.
+It was subsequently subsetted for the 2021 report, consisting of 1000 companies with 94 variables.
 The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018.
@@
 
-McGowan, Andrews, and Millot (2017) reported that companies in the United States have a faster metabolic rate relative to Japanese companies.
-This means that US companies tend to move up and down performance metrics more frequently than Japanese companies.
+\citet{oecd_report} reported that companies in the United States have a faster metabolic rate relative to Japanese companies.
+This means that US companies tend to move up and down in the performance metrics more frequently than Japanese companies.
 This can be examined using the wallaby and kangaroo plots.
@@
 
-In the kangaroo plot (Figure \ref{fig:kan-osiris-figure}) the five grey bars indicate the five categories (Top 25\%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018.
+In the kangaroo plot (Figure \ref{fig:kan-osiris-figure}) the five gray bars indicate the five categories (Top 25\%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018.
 Points represent individual companies with color indicating the country of registration.
@@
 There are several companies that move up and down, and most of these are US companies.
-This supports the McGowan, Andrews, and Millot (2017) claim that US companies have a higher turnover rate compared to Japanese companies.
+This supports the \citet{oecd_report} claim that US companies have a higher turnover rate compared to Japanese companies.
 
@@
 In Figure \ref{fig:osiris-figure}, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006.
-The grey regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018.
+The gray regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018.
 (explain the difference in proportion and not listed companies).
@@
 
-\hypertarget{voter-behavior}{%
-\subsection{Voter behavior}\label{voter-behavior}}
+\subsection{Voter behavior}\label{voter-behavior}
 
@@
 The year column is derived from the two different questions in the survey, which answered how the top party performs in keeping the old voters of different genders relative to the 2016 Australian election results.
-This dataset was collected from ADA Dataverse (McAllister et al.
-(2023)).
+This dataset was collected from ADA Dataverse (\citet{aeles}).
 
@@
 
-According to the survey ({``{LGBTIQ+ Health Australia Party survey}''} (2022)), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities.
+According to the survey (\citet{lgbtiq}), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities.
 However, the Labor Party only gives a broad statement of commitment to a range of LGBTIQ+ and human rights issues.
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Discussion}\label{discussion}
 
@@
 
-\hypertarget{acknowledgements}{%
-\section*{Acknowledgements}\label{acknowledgements}}
+\section*{Acknowledgements}\label{acknowledgements}
 \addcontentsline{toc}{section}{Acknowledgements}
 
-This paper is created using the \CRANpkg{rjtools} packages (O'Hara-Wild et al.
-(2023)) and utilized the \CRANpkg{dplyr}, \CRANpkg{knitr}, \CRANpkg{gganimate}, and \CRANpkg{kableExtra} for creating the visual included in this paper.
+This paper is created using the \CRANpkg{rjtools} packages (\citet{rjtools}) and utilized the \CRANpkg{dplyr}, \CRANpkg{knitr}, \CRANpkg{gganimate}, and \CRANpkg{kableExtra} for creating the visual included in this paper.
 This paper is based on the 0.0.0.9 version of the \CRANpkg{animbook} package.
@@
 Additionally, thanks to Masayuki Jimichi for the efforts in collecting the sample Osiris data, which contributed to the practical application of the package.
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-the_new_york_time}{}}%
-Badger, Emily, Claire Cain Miller, Adam Pearce, and Kevin Quealy.
-2018.
-{``{Extensive data shows punishing reach of racism for black boys}.''} \emph{The New York Times}.
-The New York Times.
-\url{https://www.nytimes.com/interactive/2018/03/19/upshot/race-class-white-and-black-men.html}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-d3js}{}}%
-Bostock, Mike. 2012. {``{D3.js - Data-Driven Documents}.''} 2012. \url{http://d3js.org/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-zombie_companies_2008}{}}%
-Caballero, Ricardo J., Takeo Hoshi, and Anil K.
-Kashyap.
-2008.
-{``{Zombie Lending and Depressed Restructuring in Japan}.''} \emph{The American Economic Review} 98 (5): 1943--77.
-\url{http://www.jstor.org/stable/29730158}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-race}{}}%
-Chetty, Raj, Nathaniel Hendren, Maggie Jones, and Sonya Porter.
-2020.
-{``{Race and Economic Opportunity in the United States: an Intergenerational Perspective}.''} \emph{The Quarterly Journal of Economics} 135 (May): 711--83.
-\url{https://doi.org/10.1093/qje/qjz042}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-learner-control}{}}%
-Hasler, Béatrice, Bernd Kersten, and John Sweller.
-2007.
-{``{Learner control, cognitive load and instructional animation.
-Applied Cognitive Psychology, 21, 713-729}.''} \emph{Applied Cognitive Psychology} 21 (September): 713--29.
-\url{https://doi.org/10.1002/acp.1345}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hvitfeldt_2018}{}}%
-Hvitfeldt, Emil. 2018. {``{Recreate - Sankey flow chart}.''} \emph{Recreate - Sankey Flow Chart}. \url{https://emilhvitfeldt.com/post/2018-03-20-recreate-sankey-flow-chart/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lgbtiq}{}}%
-{``{LGBTIQ+ Health Australia Party survey}.''} 2022. \emph{LGBTIQ+ Health Australia}. \url{https://www.lgbtiqhealth.org.au/electionsurvey}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mayer-2010}{}}%
-Mayer, Richard. 2010. {``{Applying the science of learning to medical education}.''} \emph{Medical Education} 44 (June): 543--49. \url{https://doi.org/10.1111/j.1365-2923.2010.03624.x}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mayer_2005}{}}%
-Mayer, Richard E.
-2005.
-{``{Cognitive Theory of Multimedia Learning}.''} In \emph{The Cambridge Handbook of Multimedia Learning}, edited by RichardEditor Mayer, 31--48.
-Cambridge Handbooks in Psychology.
-Cambridge University Press.
-\url{https://doi.org/10.1017/CBO9780511816819.004}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mayer_Moreno_2002}{}}%
-Mayer, Richard E., and Roxana Moreno. 2002. \emph{Educational Psychology Review} 14 (1): 87--99. \url{https://doi.org/10.1023/a:1013184611077}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-aeles}{}}%
-McAllister, Ian, Jill Sheppard, Sarah Cameron, and Jackman Simon. 2023. {``{Australian Election Study, 2022}.''} ADA Dataverse. \url{https://doi.org/10.26193/W3U2S3}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-oecd_report}{}}%
-McGowan, Müge Adalet, Dan Andrews, and Valentine Millot. 2017. {``{The Walking Dead?}''} no. 1372. https://doi.org/\url{https://doi.org/https://doi.org/10.1787/180d80ad-en}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-webgl}{}}%
-Mozilla Foundation. 2011. {``{WebGL}.''} Khronos WebGL Working Group. \href{https://www.khronos.org/webgl/}{www.khronos.org/webgl/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rjtools}{}}%
-O'Hara-Wild, Mitchell, Stephanie Kobakian, H.
-Sherry Zhang, Di Cook, Simon Urbanek, and Christophe Dervieux.
-2023.
-\emph{{rjtools: Preparing, Checking, and Submitting Articles to the 'R Journal'}}.
-\url{https://CRAN.R-project.org/package=rjtools}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-av}{}}%
-Ooms, Jeroen. 2023a. \emph{{av: Working with Audio and Video in R}}. \url{https://CRAN.R-project.org/package=av}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gifski}{}}%
----------. 2023b. \emph{{gifski: Highest Quality GIF Encoder}}. \url{https://CRAN.R-project.org/package=gifski}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bvd}{}}%
-{``Osiris.''} 2023. \emph{Bvd}. Bureau van Dijk. \url{https://www.bvdinfo.com/en-gb/our-products/data/international/osiris}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tweenr}{}}%
-Pedersen, Thomas Lin. 2022. \emph{{tweenr: Interpolate Data for Smooth Animations}}. \url{https://CRAN.R-project.org/package=tweenr}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gganimate}{}}%
-Pedersen, Thomas Lin, and David Robinson. 2020. {``{Gganimate: A grammar of animated graphics}.''} \emph{R Package Version} 1 (7): 403--8.
-
-\leavevmode\vadjust pre{\hypertarget{ref-r}{}}%
-R Core Team. 2021. \emph{{R: A Language and Environment for Statistical Computing}}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-effective-trend}{}}%
-Robertson, George, Roland Fernandez, Danyel Fisher, Bongshin Lee, and John Stasko.
-2008.
-{``{Effectiveness of Animation in Trend Visualization}.''} \emph{IEEE Transactions on Visualization and Computer Graphics} 14 (6): 1325--32.
-\url{https://doi.org/10.1109/TVCG.2008.125}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Shaffer_2019}{}}%
-Shaffer, Jeffrey. 2019. {``{Sankey Diagrams: Why I Used the Sigmoid Function and Why You Probably Shouldn't}.''} \emph{Data + Science}. \url{https://www.dataplusscience.com/Sigmoid.html}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-plotly}{}}%
-Sievert, Carson. 2020. {``{Interactive {Web-Based} Data Visualization with R, plotly, and shiny}.''} Chapman; Hall/CRC. \url{https://plotly-r.com}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-animation-mechanic}{}}%
-Webster, Chris. 2005. \emph{{Animation : the mechanics of motion}}. Focal Press Visual Effects and Animation Series. Oxford ; Burlington, MA: Elsevier Focal Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tidy-data}{}}%
-Wickham, Hadley. 2014. {``{Tidy Data}.''} \emph{Journal of Statistical Software} 59 (10): 1--23. \url{https://doi.org/10.18637/jss.v059.i10}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dplyr}{}}%
-Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis Vaughan. 2023. \emph{{dplyr: A Grammar of Data Manipulation}}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-purrr}{}}%
-Wickham, Hadley, and Lionel Henry. 2023. \emph{{purrr: Functional Programming Tools}}. \url{https://CRAN.R-project.org/package=purrr}.
-
-\end{CSLReferences}
 

### 2025-04-29 animbook-journal.R

@@ -37,7 +37,8 @@ original <- dbl_change |>
   reframe(id, time, values, gp) |> 
   arrange(gp, id)
 
-rank <- anim_prep(dbl_change, id, values, time, group = gp) 
+rank <- anim_prep(dbl_change, id, values, time, 
+                  group = gp) 
 
 class(rank) <- c("tbl_df", "tbl", "data.frame")
 
@@ -47,7 +48,9 @@ rank_data <- rank |>
          rank = qtile) |>  
   arrange(gp, id)
 
-absolute <- anim_prep(dbl_change, id, values, time, group = gp, scaling = "absolute") 
+absolute <- anim_prep(dbl_change, id, values, time, 
+                      group = gp, 
+                      scaling = "absolute") 
 
 class(absolute) <- c("tbl_df", "tbl", "data.frame")
 
@@ -57,7 +60,9 @@ absolute_data <- absolute |>
          absolute = qtile) |> 
   arrange(gp, id)
 
-rank_group <- anim_prep(dbl_change, id, values, time, group = gp, group_scaling = gp) 
+rank_group <- anim_prep(dbl_change, id, values, time, 
+                        group = gp, 
+                        group_scaling = gp) 
 
 class(rank_group) <- c("tbl_df", "tbl", "data.frame")
 
@@ -67,7 +72,10 @@ rank_group_data <- rank_group |>
          rank_group = qtile) |> 
   arrange(gp, id)
 
-absolute_group <- anim_prep(dbl_change, id, values, time, group = gp, group_scaling = gp, scaling = "absolute") 
+absolute_group <- anim_prep(dbl_change, id, values, time, 
+                            group = gp, 
+                            group_scaling = gp, 
+                            scaling = "absolute") 
 
 class(absolute_group) <- c("tbl_df", "tbl", "data.frame")
 
@@ -79,12 +87,23 @@ absolute_group_data <- absolute_group |>
 
 
 ## -----------------------------------------------------------------------------
-original |> 
+scaling_table <- original |> 
   left_join(rank_data, by = c("id", "time", "gp")) |> 
   left_join(rank_group_data, by = c("id", "time", "gp")) |> 
   left_join(absolute_data, by = c("id", "time", "gp")) |> 
   left_join(absolute_group_data, by = c("id", "time", "gp")) |> 
   reframe(id, time, gp, values, rank, rank_group, absolute, absolute_group)
+
+
[…]

### 2025-04-30 animbook-journal.Rmd
cleaning and glimpse function give latex error

@@
 
-```{r tbl-scaling, eval=knitr::is_html_output()}
+```{r tbl-scaling}
 scaling_table |> 
   knitr::kable(caption = "A summary of different scaling methods applied to the dataset.")
-```
-
-```{r tbl-scaling-la, eval=knitr::is_latex_output()}
-scaling_table |> 
-  knitr::kable(caption = "A summary of different scaling methods applied to the dataset.") |> 
-  kableExtra::column_spec(8, width = "30em")
 ```
@@
                    group = gp)
-class(a)
-glimpse(a)
+# class(a)
+# glimpse(a)
 ```
@@
 
-p <- wallaby_plot(accounting,
+wal_p <- wallaby_plot(accounting,
                   subset = "bottom",
@@
 
-p2 <- anim_animate(p)
+wal_p2 <- anim_animate(wal_p)
 ```
@@
 ```{r, eval=FALSE}
-gganimate::anim_save("figures/exit.gif", p2, height = 8, fps = 30,
+gganimate::anim_save("figures/exit.gif", wal_p2, height = 8, fps = 30,
                      nframes = 400, width = 9, units = "in", res = 150)
@@
 
-gganimate::animate(p2)
+gganimate::animate(wal_p2)
 ```

### 2025-04-30 animbook-journal.tex
cleaning and glimpse function give latex error

@@
 
-\section{Introduction}\label{intro}
+\hypertarget{intro}{%
+\section{Introduction}\label{intro}}
 
@@
 
-\section{Explanation of the New York Times visualization}\label{NYTvis}
+\hypertarget{NYTvis}{%
+\section{Explanation of the New York Times visualization}\label{NYTvis}}
 
@@
 
-\section{Data}\label{data}
+\hypertarget{data}{%
+\section{Data}\label{data}}
 
@@
 
-\section{Animation tools}\label{animation}
+\hypertarget{animation}{%
+\section{Animation tools}\label{animation}}
 
@@
 
-\section{Visualization design}\label{design}
+\hypertarget{design}{%
+\section{Visualization design}\label{design}}
 
@@
 
-\section{Software}\label{software}
+\hypertarget{software}{%
+\section{Software}\label{software}}
 
-\subsection{Installation}\label{installation}
+\hypertarget{installation}{%
+\subsection{Installation}\label{installation}}
 
@@
 
-\subsection{Overview of functions}\label{overview-of-functions}
+\hypertarget{overview-of-functions}{%
+\subsection{Overview of functions}\label{overview-of-functions}}
 
@@
 
-\subsubsection{Data pre-processing}\label{data-pre-processing}
+\hypertarget{data-pre-processing}{%
+\subsubsection{Data pre-processing}\label{data-pre-processing}}
 
@@
 
-\caption{\label{tab:tbl-scaling-la}A summary of different scaling methods applied to the dataset.}
+\caption{\label{tab:tbl-scaling}A summary of different scaling methods applied to the dataset.}
 \centering
-\begin{tabular}[t]{l|>{\raggedleft\arraybackslash}p{30em}|l|r|r|r|r|r}
+\begin{tabular}[t]{l|r|l|r|r|r|r|r}
 \hline
@@
 These are only the initial steps in formatting the data into a category.
-Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animated data structure.
+Now that there is a method to transform the data from the raw format into a categorized format, the next step is to modify it into an animated data structure.
 It is carried out by assigning a frame to each individual observation, ensuring that each ID does not contain repeated frame values.
@@
 
-\caption{\label{tab:tbl-cat-la}The argumenst for the anim\_prep\_cat function.}
+\caption{\label{tab:tbl-cat-la}The arguments for the anim\_prep\_cat function.}
 \centering
@@
 The \texttt{data}, \texttt{id}, \texttt{values}, and \texttt{time} arguments are required for both functions.
-
 The \texttt{ncat}, \texttt{breaks}, \texttt{group\_scaling}, and \texttt{scaling} arguments are for the user to customize the data scaling calculation in the \texttt{anim\_prep()} function.
 In the \texttt{anim\_prep\_cat} function, the users can customize the order of the category to be shown on the y-axis using the \texttt{order} argument.
-
-Then, for further customization regarding how the final visualization looks. The \texttt{group}, \texttt{label}, and \texttt{time\_dependent} arguments can be adjusted.
+Then, for further customization regarding how the final visualization looks.
+The \texttt{group}, \texttt{label}, and \texttt{time\_dependent} arguments can be adjusted.
 
@@
 
-\subsubsection{Plotting function}\label{plotting-function}
+\hypertarget{plotting-function}{%
+\subsubsection{Plotting function}\label{plotting-function}}
 
@@
 
-\caption{\label{tab:unnamed-chunk-8}The arguments for the wallaby\_plot function.}
+\caption{\label{tab:unnamed-chunk-9}The arguments for the wallaby\_plot function.}
 \centering
@@
 
-\subsubsection{Animating function}\label{animating-function}
+\hypertarget{animating-function}{%
+\subsubsection{Animating function}\label{animating-function}}
 
@@
 
-\subsection{Example usage}\label{example-usage}
+\hypertarget{example-usage}{%
+\subsection{Example usage}\label{example-usage}}
 
-The \texttt{cat\_change} data in the package is used to illustrate how to use this package.
+The \texttt{cat\_change} data in the \CRANpkg{animbook} package is used to illustrate how to use this package.
 It has five categories, A to E, over two time points.
@@
                    group = gp)
-class(a)
-\end{verbatim}
-
-\begin{verbatim}
-#> [1] "tbl_df"      "tbl"         "data.frame"  "categorized"
-\end{verbatim}
-
-\begin{verbatim}
-glimpse(a)
-\end{verbatim}
-
-\begin{verbatim}
-#> Rows: 400
-#> Columns: 5
-#> $ id    <fct> 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 1~
-#> $ time  <int> 2020, 2020, 2020, 2020, 2020, 2020, 2020, 2020, 2020, 2020, 2020~
-#> $ qtile <dbl> 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5~
-#> $ label <chr> "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",~
-#> $ group <fct> X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, X, Y, Y~
+# class(a)
+# glimpse(a)
 \end{verbatim}
@@
 
-Figure \ref{fig:top-many}, shows the flexibility to use various options, such as \texttt{subset} or \texttt{relation}, to customize the plot appearance.
+Figure \ref{fig:top-many} shows the flexibility to use various options, such as \texttt{subset} or \texttt{relation}, to customize the plot appearance.
 Here \texttt{subset\ =\ "top"} is used to specify category A for the final time point, and \texttt{relation\ =\ "many\_one"} is used to specify that all categories flowing into A at time point 2 are shown.
@@
 
-\section{Applications}\label{applications}
+\hypertarget{applications}{%
+\section{Applications}\label{applications}}
 
@@
 
-\subsection{Accounting database: osiris}\label{accounting-database-osiris}
+\hypertarget{accounting-database-osiris}{%
+\subsection{Accounting database: osiris}\label{accounting-database-osiris}}
 
@@
 
-p2 <- anim_animate(p)
+wal_p2 <- anim_animate(wal_p)
 \end{verbatim}
@@
 
-gganimate::animate(p2)
+gganimate::animate(wal_p2)
 \end{verbatim}
@@
 
-\subsection{Voter behavior}\label{voter-behavior}
+\hypertarget{voter-behavior}{%
+\subsection{Voter behavior}\label{voter-behavior}}
 
@@
 
-\section{Discussion}\label{discussion}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 
-\section*{Acknowledgements}\label{acknowledgements}
+\hypertarget{acknowledgements}{%
+\section*{Acknowledgements}\label{acknowledgements}}
 \addcontentsline{toc}{section}{Acknowledgements}

### 2025-04-30 animbook-journal.R

@@ -1,11 +1,11 @@
 # Generated by `rjournal_pdf_article()` using `knitr::purl()`: do not edit by hand
 # Please edit animbook-journal.Rmd to modify this file
 
-## ----setup, include=FALSE-----------------------------------------------------
+## ----setup, include=FALSE----------------------------------------------------------------------------------------------------------
 knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
 
 
-## -----------------------------------------------------------------------------
+## ----------------------------------------------------------------------------------------------------------------------------------
 library(animbook)
 library(tidyverse)
 
@@ -31,7 +31,7 @@ knitr::include_graphics("figures/sigmoid-shade.png")
 knitr::include_graphics("figures/sine-shade.png")
 
 
-## -----------------------------------------------------------------------------
+## ----------------------------------------------------------------------------------------------------------------------------------
 original <- dbl_change |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
   reframe(id, time, values, gp) |> 
@@ -86,7 +86,7 @@ absolute_group_data <- absolute_group |>
   arrange(gp, id)
 
 
-## -----------------------------------------------------------------------------
+## ----------------------------------------------------------------------------------------------------------------------------------
 scaling_table <- original |> 
   left_join(rank_data, by = c("id", "time", "gp")) |> 
   left_join(rank_group_data, by = c("id", "time", "gp")) |> 
@@ -95,18 +95,12 @@ scaling_table <- original |>
   reframe(id, time, gp, values, rank, rank_group, absolute, absolute_group)
 
 
-## ----tbl-scaling, eval=knitr::is_html_output()--------------------------------
-# scaling_table |>
-#   knitr::kable(caption = "A summary of different scaling methods applied to the dataset.")
-
-
-## ----tbl-scaling-la, eval=knitr::is_latex_output()----------------------------
+## ----tbl-scaling-------------------------------------------------------------------------------------------------------------------
 scaling_table |> 
-  knitr::kable(caption = "A summary of different scaling methods applied to the dataset.") |> 
-  kableExtra::column_spec(2, width = "30em")
+  knitr::kable(caption = "A summary of different scaling methods applied to the dataset.")
 
 
-## -----------------------------------------------------------------------------
+## ----------------------------------------------------------------------------------------------------------------------------------
[…]

### 2025-07-08 response_to_review.qmd
reviewer 2 other comments section

@@
 
-Response:
+Response: We forgot to remove that.
 
@@
 
-Response:
+Response: ??? I think this is more like an experimental visualization.
 
@@
 
-Response: Be more clear (you should be able to)
+Response: In the function, before separating the observation into groups, it will go through normalization (the data scale will be between 0 and 1).
+If we implement the raw data scale, it would require redesigning the function, as it would have to be able to distinguish between normalization and raw data scale.
+???
+is this too long?
 
@@
 
-Response:
+Response: It should work by default.
 
@@
 
-Response: Be more clear
+Response: Yes, we have made it clearer in the arguments description and on page 10.
 
@@
 
-Response:
+Response: The code has been fixed.
 

### 2025-07-08 animbook-journal.Rmd
reviewer 2 other comments section

@@
 The `group`, `label`, and `time_dependent` arguments can be adjusted.
-
-  The `time_dependent` argument provides the user flexibility to choose whether points will start simultaneously (`time_dependent = TRUE`) or randomly (`time_dependent = FALSE`).
-The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points.
-Allowing for the random starting time makes point tracking simpler.
-The starting times for the points are generated using the `runif()` function, where the `max` argument can be adjusted using the `width` parameter in the plotting function.
+The `time_dependent` argument will be further discussed in the next section.
 
@@
 
+  The user can further use the `time_dependent` argument to choose whether points will start simultaneously (`time_dependent = TRUE`) or randomly (`time_dependent = FALSE`).
+The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points.
+Allowing for the random starting time makes point tracking simpler.
+The starting times for the points are generated using the `runif()` function, where the `max` argument can be adjusted using the `width` parameter in the plotting function.
+
   Now that the data are in the right format for the wallaby's plot, the `geom_point()` function is used for plotting the observations, `geom_polygon()` is used for creating the proportional shaded areas, and `geom_text()` is used for creating labels.
@@
                   "Should the observations entered the visualization at the same time. Default is FALSE",
-                  "A character string specifying the variable used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument. Default is \"top\".",
+                  "A character string specifying the label used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument. Default is \"top\".",
                   "The choice of relationship for the values to display on the plot, either \"one_many.\" or \"many_one\". Default is \"one_many\".",
@@
 Here `subset = "top"` is used to specify category A for the final time point, and `relation = "many_one"` is used to specify that all categories flowing into A at time point 2 are shown.
+However, if category B is the focusing point, setting `subset = "B"` will also allow for a choice of category to be shown as in Figure \@ref(fig:b-many).
 
@@
 ```
-
-Using `subset = "B"` will only show the point for a single category as shown in Figure \@ref(fig:b-many).
 
@@
 The gray regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018.
-(explain the difference in proportion and not listed companies).
 In 2006, the companies represented by points, colored by country, were in one of the quartiles or "Not listed" category.
@@
 This change in behavior could be linked to the Green Party's "A FAIRER, MORE EQUAL COMMUNITY" campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.
-
 According to the survey (@lgbtiq), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities.

### 2025-07-08 animbook-journal.tex
reviewer 2 other comments section

@@
 
-\hypertarget{intro}{%
-\section{Introduction}\label{intro}}
+\section{Introduction}\label{intro}
 
@@
 
-\hypertarget{NYTvis}{%
-\section{Explanation of the New York Times visualization}\label{NYTvis}}
+\section{Explanation of the New York Times visualization}\label{NYTvis}
 
@@
 
-\hypertarget{animation}{%
-\section{Animation tools}\label{animation}}
+\section{Animation tools}\label{animation}
 
@@
 
-\hypertarget{design}{%
-\section{Visualization design}\label{design}}
+\section{Visualization design}\label{design}
 
@@
 
-\hypertarget{software}{%
-\section{Software}\label{software}}
+\section{Software}\label{software}
 
-\hypertarget{installation}{%
-\subsection{Installation}\label{installation}}
+\subsection{Installation}\label{installation}
 
@@
 
-\hypertarget{data-pre-processing}{%
-\subsubsection{Data pre-processing}\label{data-pre-processing}}
+\subsubsection{Data pre-processing}\label{data-pre-processing}
 
@@
 The \texttt{group}, \texttt{label}, and \texttt{time\_dependent} arguments can be adjusted.
+The \texttt{time\_dependent} argument will be further discussed in the next section.
 
-The \texttt{time\_dependent} argument provides the user flexibility to choose whether points will start simultaneously (\texttt{time\_dependent\ =\ TRUE}) or randomly (\texttt{time\_dependent\ =\ FALSE}).
-The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points.
-Allowing for the random starting time makes point tracking simpler.
-The starting times for the points are generated using the \texttt{runif()} function, where the \texttt{max} argument can be adjusted using the \texttt{width} parameter in the plotting function.
-
-\hypertarget{plotting-function}{%
-\subsubsection{Plotting function}\label{plotting-function}}
+\subsubsection{Plotting function}\label{plotting-function}
 
@@
 
+The user can further use the \texttt{time\_dependent} argument to choose whether points will start simultaneously (\texttt{time\_dependent\ =\ TRUE}) or randomly (\texttt{time\_dependent\ =\ FALSE}).
+The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points.
+Allowing for the random starting time makes point tracking simpler.
+The starting times for the points are generated using the \texttt{runif()} function, where the \texttt{max} argument can be adjusted using the \texttt{width} parameter in the plotting function.
+
 Now that the data are in the right format for the wallaby's plot, the \texttt{geom\_point()} function is used for plotting the observations, \texttt{geom\_polygon()} is used for creating the proportional shaded areas, and \texttt{geom\_text()} is used for creating labels.
@@
 
-\caption{\label{tab:unnamed-chunk-9}The arguments for the wallaby\_plot function.}
+\caption{\label{tab:unnamed-chunk-8}The arguments for the wallaby\_plot function.}
 \centering
@@
 \hline
-subset & A character string specifying the variable used for subsetting the data. The "top" and "bottom" strings can also be used in this argument. Default is "top".\\
+subset & A character string specifying the label used for subsetting the data. The "top" and "bottom" strings can also be used in this argument. Default is "top".\\
 \hline
@@
 
-\hypertarget{animating-function}{%
-\subsubsection{Animating function}\label{animating-function}}
+\subsubsection{Animating function}\label{animating-function}
 
@@
 
-\hypertarget{example-usage}{%
-\subsection{Example usage}\label{example-usage}}
+\subsection{Example usage}\label{example-usage}
 
@@
 Here \texttt{subset\ =\ "top"} is used to specify category A for the final time point, and \texttt{relation\ =\ "many\_one"} is used to specify that all categories flowing into A at time point 2 are shown.
+However, if category B is the focusing point, setting \texttt{subset\ =\ "B"} will also allow for a choice of category to be shown as in Figure \ref{fig:b-many}.
 
@@
 \end{figure}
-
-Using \texttt{subset\ =\ "B"} will only show the point for a single category as shown in Figure \ref{fig:b-many}.
 
@@
 
-\hypertarget{applications}{%
-\section{Applications}\label{applications}}
+\section{Applications}\label{applications}
 
@@
 
-\hypertarget{accounting-database-osiris}{%
-\subsection{Accounting database: osiris}\label{accounting-database-osiris}}
+\subsection{Accounting database: osiris}\label{accounting-database-osiris}
 
@@
 The gray regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018.
-(explain the difference in proportion and not listed companies).
 In 2006, the companies represented by points, colored by country, were in one of the quartiles or ``Not listed'' category.
@@
 This change in behavior could be linked to the Green Party's ``A FAIRER, MORE EQUAL COMMUNITY'' campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.
-
 According to the survey (\citet{lgbtiq}), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities.
@@
 
-\hypertarget{acknowledgements}{%
-\section*{Acknowledgements}\label{acknowledgements}}
+\section*{Acknowledgements}\label{acknowledgements}
 \addcontentsline{toc}{section}{Acknowledgements}

### 2025-07-08 animbook-journal.R

@@ -1,11 +1,11 @@
 # Generated by `rjournal_pdf_article()` using `knitr::purl()`: do not edit by hand
 # Please edit animbook-journal.Rmd to modify this file
 
-## ----setup, include=FALSE----------------------------------------------------------------------------------------------------------
+## ----setup, include=FALSE-----------------------------------------------------
 knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
 
 
-## ----------------------------------------------------------------------------------------------------------------------------------
+## -----------------------------------------------------------------------------
 library(animbook)
 library(tidyverse)
 
@@ -31,7 +31,7 @@ knitr::include_graphics("figures/sigmoid-shade.png")
 knitr::include_graphics("figures/sine-shade.png")
 
 
-## ----------------------------------------------------------------------------------------------------------------------------------
+## -----------------------------------------------------------------------------
 original <- dbl_change |> 
   filter(id %in% c(1, 14, 21, 100, 106, 148)) |> 
   reframe(id, time, values, gp) |> 
@@ -86,7 +86,7 @@ absolute_group_data <- absolute_group |>
   arrange(gp, id)
 
 
-## ----------------------------------------------------------------------------------------------------------------------------------
+## -----------------------------------------------------------------------------
 scaling_table <- original |> 
   left_join(rank_data, by = c("id", "time", "gp")) |> 
   left_join(rank_group_data, by = c("id", "time", "gp")) |> 
@@ -95,12 +95,12 @@ scaling_table <- original |>
   reframe(id, time, gp, values, rank, rank_group, absolute, absolute_group)
 
 
-## ----tbl-scaling-------------------------------------------------------------------------------------------------------------------
+## ----tbl-scaling--------------------------------------------------------------
 scaling_table |> 
   knitr::kable(caption = "A summary of different scaling methods applied to the dataset.")
 
 
-## ----------------------------------------------------------------------------------------------------------------------------------
+## -----------------------------------------------------------------------------
 argument_num <- c("data", "id", "values", "time", "group", "ncat", "breaks", "label", 
               "group_scaling", "scaling")
 
@@ -119,7 +119,7 @@ argument_num_tab <- tibble::tibble(Argument = argument_num,
                                    Description = description_num)
 
 
-## ----------------------------------------------------------------------------------------------------------------------------------
+## -----------------------------------------------------------------------------
[…]

### 2025-07-08 response_to_review.qmd
first review draft

@@
 
-Response:
+Response: ??? It might be related to the default colour for shaded sections. Will need examples to replicate.
 
@@
 
-Response:
+Response: ??? Not at the moment since it can lead to a visual overload.
 
@@
 
-Response: Make it clear.
+Response: The gganimate elements (e.g., shadow trail) work normally with this package. We have added an explanation on page 8.
 
@@
 
-Response: Describe what do we learn.
+Response: ??? Already in the caption.
 
@@
 
-Response: Just change.
+Response: Fixed
 
@@
 
-Response: Just change
+Response: ???
 
@@
 
-Response: Add detail for X and Y.
+Response: ??? Not sure what the reviewer means.
 
@@
 
-Response: Just change
+Response: Fixed
 
@@
 
-Response: Fix helpfile.
+Response: ???
+It was a design choice to allow for flexibility.
+For example, to add ggplot or gganimate elements, it needs to be done between the processes.
+There is also a page for getting started, which discusses it in more detail.
+(https://krisanata.github.io/animbook/articles/animbook.html)[https://krisanata.github.io/animbook/articles/animbook.html]

### 2025-07-08 animbook-journal.Rmd
first review draft

@@
 output: 
-  rjtools::rjournal_pdf_article:
-    toc: no
   rjtools::rjournal_web_article:
     self_contained: yes
+    toc: no
+  rjtools::rjournal_pdf_article:
     toc: no
@@
   The political data that exhibits the movement of voters switching party affiliations between elections can be a valuable insight into the behavior of the voters.
-This data could be extended to incorporate demographic information about the voters, providing analysts with significant insight into voter behavior and allowing them to consolidate effective campaigns for their political party.
+These data could be extended to incorporate demographic information about the voters, providing analysts with significant insight into voter behavior and allowing them to consolidate effective campaigns for their political party.
 It can also be applied to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.
@@
 By default, if the user specifies the rendering as `gganimate`, then it will add the `transition_time()` function from the \CRANpkg{gganimate} package.
+It also means that the functionality from the \CRANpkg{gganimate} package (e.g., `shadow_trail()` function) will work by default.
 Otherwise, the `animation_opts()` function will be added from the \CRANpkg{plotly} package.
@@
 
-I would like to acknowledge Chika Saka for providing the inspiration that led to the development of this R package.
+We would like to acknowledge Chika Saka for providing the inspiration that led to the development of this R package.
 Additionally, thanks to Masayuki Jimichi for the efforts in collecting the sample Osiris data, which contributed to the practical application of the package.

### 2025-07-08 animbook-journal.tex
first review draft

@@
 The political data that exhibits the movement of voters switching party affiliations between elections can be a valuable insight into the behavior of the voters.
-This data could be extended to incorporate demographic information about the voters, providing analysts with significant insight into voter behavior and allowing them to consolidate effective campaigns for their political party.
+These data could be extended to incorporate demographic information about the voters, providing analysts with significant insight into voter behavior and allowing them to consolidate effective campaigns for their political party.
 It can also be applied to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.
@@
 By default, if the user specifies the rendering as \texttt{gganimate}, then it will add the \texttt{transition\_time()} function from the \CRANpkg{gganimate} package.
+It also means that the functionality from the \CRANpkg{gganimate} package (e.g., \texttt{shadow\_trail()} function) will work by default.
 Otherwise, the \texttt{animation\_opts()} function will be added from the \CRANpkg{plotly} package.

### 2025-07-11 response_to_review.qmd
and japan comment
comment about the aeles example
four steps comment

@@
 
-Response: ???
+Response: "japan" is one of the variables in the osiris data. We have changed the text so that this is clearer.
 
@@
 
-Response: ??? Not sure what the reviewer means.
+Response: XXX We have fixed the example on the package website and provide more documentation about the animation.
 
@@
 
-Response: ???
-It was a design choice to allow for flexibility.
-For example, to add ggplot or gganimate elements, it needs to be done between the processes.
-There is also a page for getting started, which discusses it in more detail.
-(https://krisanata.github.io/animbook/articles/animbook.html)[https://krisanata.github.io/animbook/articles/animbook.html]
+Response: This was a design choice for transparency so the user can see the steps. We have updated the web page to make the steps clearer, and also added a single function that does all the steps. XXX

### 2025-07-11 animbook-journal.Rmd
and japan comment
ID and grouping comment finished

@@
 The ID variable indicates the individual, which is followed over time, such as the company name.
-There may also be a grouping variable, such as the country where the company is registered (United States and Japan).
+There may also be a grouping variable, such as the country where the company is registered (United States and Japan), which would be used to color points for group comparison.
 
@@
 The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018.
-The variables in this dataset include year, ID, country, sales, and japan.
+The variables in this dataset include year, ID, country, sales, and the binary variable called japan.
 

### 2025-07-11 animbook-journal.Rmd
fixed redundancy comment
proportional shade comment
wallaby plot not wallabys plot

@@
   @mayer_2005 states that designing multimedia requires the designer to understand how people learn.
-One of the principles in @mayer_2005, Redundancy, suggests that a piece of excess information could overload the learners.
+One of the principles in @mayer_2005,  redundancy, suggests that a piece of excess information could overload the learners.
 By this principle, the animation must be carefully designed to avoid this pitfall.
@@
 The frame is recalculated using the same method mentioned in the data preprocessing section.
+
   The `proportional_shade()` function is called to generate the proportional shaded data.
-
 The `proportional_shade()` function's algorithm begins by calculating the corner points for each shaded area.
@@
 
-  Now that the data are in the right format for the wallaby's plot, the `geom_point()` function is used for plotting the observations, `geom_polygon()` is used for creating the proportional shaded areas, and `geom_text()` is used for creating labels.
+  Now that the data are in the right format for the wallaby plot, the `geom_point()` function is used for plotting the observations, `geom_polygon()` is used for creating the proportional shaded areas, and `geom_text()` is used for creating labels.
 These three functions are from the \CRANpkg{ggplot2} package.

### 2025-07-11 response_to_review.qmd
ID and grouping comment finished
fixed redundancy comment
proportional shade comment
wallaby plot not wallabys plot
macbook issue response

@@
 
-Response: ??? I have added US and Japan as an example, not sure what else can be added.
+Response: Text has been modified to include an example using the US and Japan osiris data.
 
@@
 
-Response: ???
+Response: Fixed
 
@@
 
-Response: ??? I feel like the function should be mentioned first in the second paragraph. The third paragraph is mainly about the function algorithm.
+Response: Fixed.
 
@@
 
-Response: ???
+Response: Fixed.
 
@@
 
-Response: ??? I think this is more like an experimental visualization.
+Response: We would rather not because it is experimental and retained in the package in case it is useful at some point.
 
@@
 If we implement the raw data scale, it would require redesigning the function, as it would have to be able to distinguish between normalization and raw data scale.
-???
-is this too long?
 
@@
 
-Response: ??? It might be related to the default colour for shaded sections. Will need examples to replicate.
+Response: We are not sure what is happening here.
+We have tested on an M1 MacBook Pro and don't see the problem.
+Ideally this sort of problem is reported as an issue on the package website with a small code example.
 

### 2025-07-11 animbook-journal.Rmd
macbook issue response

@@
 Two real-world examples of usage are provided.
-The osiris example studies company movement between quartiles of sales performance over a 12-year period.
+The Osiris [@bvd] example studies company movement between quartiles of sales performance over a 12-year period.
 The voting example studies party preference changes between the 2016 and 2019 elections.
@@
 
-The Osiris data presented in this section was acquired from Bureau van Dijk (@bvd), compiling information on a total of 122,318 companies.
-It was subsequently subsetted for the 2021 report, consisting of 1000 companies with 94 variables.
+The full Osiris provides information on a total of 122,318 companies.
 The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018.

### 2025-07-11 animbook-journal.Rmd
address the NY Times figure comment

@@
 ```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package.
-The animation illustrates the disparity between white men and black men.
-It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
+The animation illustrates the disparity between white men (yellow) and black men (blue).
+It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.This is observed by more yellow points apparently falling from the top bar to lower bars in the animated plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
 knitr::include_graphics("figures/NYT.png")

### 2025-07-11 animbook-journal.Rmd
fixed render arguments in yaml

@@
 output: 
-  rjtools::rjournal_web_article:
+  rjtools::rjournal_article:
     self_contained: yes
-    toc: no
-  rjtools::rjournal_pdf_article:
     toc: no
@@
 Two real-world examples of usage are provided.
-The Osiris [@bvd] example studies company movement between quartiles of sales performance over a 12-year period.
+The Osiris data [@bvd] example studies company movement between quartiles of sales performance over a 12-year period.
 The voting example studies party preference changes between the 2016 and 2019 elections.

### 2025-07-11 animbook-journal.tex
fixed render arguments in yaml

@@
 \caption{Screenshot of the New York Times animation, which is the motivation for this visualization package.
-The animation illustrates the disparity between white men and black men.
-It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.}\label{fig:nyt}
+The animation illustrates the disparity between white men (yellow) and black men (blue).
+It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.This is observed by more yellow points apparently falling from the top bar to lower bars in the animated plot.}\label{fig:nyt}
 \end{figure}
@@
 \citet{mayer_2005} states that designing multimedia requires the designer to understand how people learn.
-One of the principles in \citet{mayer_2005}, Redundancy, suggests that a piece of excess information could overload the learners.
+One of the principles in \citet{mayer_2005}, redundancy, suggests that a piece of excess information could overload the learners.
 By this principle, the animation must be carefully designed to avoid this pitfall.
@@
 The frame is recalculated using the same method mentioned in the data preprocessing section.
+
 The \texttt{proportional\_shade()} function is called to generate the proportional shaded data.
-
 The \texttt{proportional\_shade()} function's algorithm begins by calculating the corner points for each shaded area.
@@
 
-Now that the data are in the right format for the wallaby's plot, the \texttt{geom\_point()} function is used for plotting the observations, \texttt{geom\_polygon()} is used for creating the proportional shaded areas, and \texttt{geom\_text()} is used for creating labels.
+Now that the data are in the right format for the wallaby plot, the \texttt{geom\_point()} function is used for plotting the observations, \texttt{geom\_polygon()} is used for creating the proportional shaded areas, and \texttt{geom\_text()} is used for creating labels.
 These three functions are from the \CRANpkg{ggplot2} package.
@@
 Two real-world examples of usage are provided.
-The osiris example studies company movement between quartiles of sales performance over a 12-year period.
+The Osiris data \citep{bvd} example studies company movement between quartiles of sales performance over a 12-year period.
 The voting example studies party preference changes between the 2016 and 2019 elections.
@@
 
-The Osiris data presented in this section was acquired from Bureau van Dijk (\citet{bvd}), compiling information on a total of 122,318 companies.
-It was subsequently subsetted for the 2021 report, consisting of 1000 companies with 94 variables.
+The full Osiris provides information on a total of 122,318 companies.
 The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018.
-The variables in this dataset include year, ID, country, sales, and japan.
+The variables in this dataset include year, ID, country, sales, and the binary variable called japan.
 

### 2025-07-11 animbook-journal.R

@@ -10,7 +10,7 @@ library(animbook)
 library(tidyverse)
 
 
-## ----nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package. The animation illustrates the disparity between white men and black men. It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+## ----nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package. The animation illustrates the disparity between white men (yellow) and black men (blue). It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.This is observed by more yellow points apparently falling from the top bar to lower bars in the animated plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
 knitr::include_graphics("figures/NYT.png")
 
 

### 2025-09-28 second-submission/animbook-journal.R
resubmission

@@ -1,0 +1,343 @@
+# Generated by `rjournal_pdf_article()` using `knitr::purl()`: do not edit by hand
+# Please edit animbook-journal.Rmd to modify this file
+
+## ----setup, include=FALSE-----------------------------------------------------
+knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
+
+
+## -----------------------------------------------------------------------------
+library(animbook)
+library(tidyverse)
+
+
+## ----nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package. The animation illustrates the disparity between white men (yellow) and black men (blue). It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.This is observed by more yellow points apparently falling from the top bar to lower bars in the animated plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+knitr::include_graphics("figures/NYT.png")
+
+
+## ----data-diagram, fig.cap="The animation expects data with an ID and a time variable, along with a numerical variable (raw form), which is possibly converted to categorical (categorized). The data can be provided in the raw or categorized form and will be processed into the format needed for the animation, where the categorical variable is treated as a quantile and an animation frame variable is created.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+knitr::include_graphics("figures/data-diagram.png")
+
+
+## ----animation-diagram, fig.cap="An animation requires small changes shown in quick succession to make it appear as if the objects are in motion. The three plots above show a single point changing position by a small amount, which when shown quickly, will look like that point has moved up and to the right.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+knitr::include_graphics("figures/animation-diagram.png")
+
+
+## ----animated-diagram, fig.cap="Frames 1 and 2 show the year 1 and year 2 positions of points from the data in the table at the top. The id is necessary to enable interpolation to make the small changes to generate a perception of motion from frame 1 position to frame 2 position.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"----
+knitr::include_graphics("figures/animated-diagram.png")
+
+
[…]
